### 2015-04-04 paper.tex
Migrating project to git

\documentclass[envcountsame]{cls/cccg15}
\usepackage{graphicx}

\usepackage{amssymb,amsmath}
\usepackage[mathscr]{euscript}

\usepackage{graphicx}
\usepackage{caption,subcaption}

\usepackage[noend]{algpseudocode}

%----------------------- Environments --------------------------
\newtheorem{corollary}{Corollary} 
\newtheorem{problem}{Problem}
\newtheorem{algorithm}{Algorithm}
\newtheorem{definition}{Definition}

%------------------------ Paper Notations -----------------------------
\DeclareMathOperator*{\argmin}{arg\,min}

%-------------------------- Notations ------------------------------------
\newcommand{\cO}{\ensuremath{{\rm O}}}
\newcommand{\st}{\textsuperscript{\textit{st}} }
\newcommand{\nd}{\textsuperscript{\textit{nd}} }
\newcommand{\nth}{\textsuperscript{\textit{th}} }

\newcommand{\IN}{\ensuremath{\mathbb{N}}} 
\newcommand{\IZ}{\ensuremath{\mathbb{Z}}} 
\newcommand{\IQ}{\ensuremath{\mathbb{Q}}} 
\newcommand{\IR}{\ensuremath{\mathbb{R}}} 
\newcommand{\IC}{\ensuremath{\mathbb{C}}}

\newcommand{\set}[1]{\left\{ #1 \right\}}
\newcommand{\seq}[1]{\left< #1 \right>}
\newcommand{\ceil}[1]{\left\lceil{#1}\right\rceil}
\newcommand{\floor}[1]{\left\lfloor{#1}\right\rfloor}
\newcommand{\card}[1]{\left|{#1}\right|}
\newcommand{\setcomp}[1]{\overline{#1}}
\newcommand{\provided}{\,:\,}

\newcommand{\poly}{\mathop{\mathrm{poly}}}
\newcommand{\polylog}{\mathop{\mathrm{\scriptsize polylog}}}
\newcommand{\lcm}{\mathop{\mathrm{lcm}}}

\newcommand{\lee}{\leqslant}
\newcommand{\gee}{\geqslant}
\renewcommand{\leq}{\lee}
\renewcommand{\le}{\lee}
\renewcommand{\geq}{\gee}
\renewcommand{\ge}{\gee}
\newcommand{\lei}{\prec}

\newcommand{\OPT}{\ensuremath{\mathop{\mathrm{OPT}}}}
\newcommand{\APX}{\ensuremath{\text{\sc APX}}}
\newcommand{\opt}{\ensuremath{\mbox{\tt opt}}}
\newcommand{\apx}{\ensuremath{\mbox{\tt apx}}}

\newcommand{\eps}{\varepsilon}
\newcommand{\bslash}{\!\setminus\!}
\newcommand{\bigOmega}{{\rm\Omega}}
\newcommand{\etal}{{\em et~al.\/}}
\newcommand{\REM}[1]{}
\newcommand{\qed}{}
\newcommand {\backspace}{\vspace{-3em}\\}

\newcommand{\linprog}[6]{
  \begin{alignat}{2}
    \text{#1}  \quad & #2\\
    \text{s.t.}  \quad & #3 & \qquad #4 \notag\\
                     & #5 & \qquad #6 \notag
  \end{alignat}}

\newcommand*\samethanks[1][\value{footnote}]{\footnotemark[#1]}

%----------------------- Title -----------------------------------------
\title{Streaming $2$-Center with Outliers in High Dimension}
\author{Hamid~Zarrabi-Zadeh\thanks{Department of Computer Engineering, 
	Sharif University of Technology. 
	{\tt zarrabi@sharif.edu}}
	\and 
}

%------------------------------ Text -------------------------------------
\begin{document}

\maketitle
\pagestyle{plain}

% ---------------------- Abstract --------------------------------------

\begin{abstract}

\end{abstract}

% ---------------------- Introduction ---------------------------------

\section{Introduction}

% ---------------------------- Preliminaries -------------------------------

\section{Preliminaries}
\label{sec:pre}
Let $B(c,r)$ denote a ball with center $c$ and radius $r$. We denote by $pq$ the straight line segment between these two points and by $\card{pq}$ the length of this segment. 
%kiana: tarife delta ro chanja didam nagofte budan! benazaram ma ham mitunim nagim, baz age fek mikonin lazeme tarif konam:
% Define $\delta$ of two balls B(c,r) and B'(c',r'), the minimum distance between $B$ and $B'$ which is equal to $\card{cc'}-r-r'$.

Let $B_1^*(c_{2,1}^*, r_2^*)$ and $B_2^*(c_{2,2}^*, r_2^*)$ denote the optimal solution to $2$-center problem with $z$ outliers. By $\delta^*$ we denote the distance between $B_1^*$ and $B_2^*$, that is, $\delta^* = \max (0, \card{c_1^*c_2^*} − 2r^*)$.

Two congruent balls $B_1$ and $B_2$ with radius $r$ are said to be \emph{$C$-separated}, whenever the distance $\delta$ of two balls is at least $Cr$.

%Let $\mathcal{P}$ be a configuration of $n$ point in $d$-dimensional Euclidean space. A point $c_p$, not necessarily in $\mathcal{P}$, is a \emph{centerpoint} of $\mathcal{P}$, if no open half-space that omits $c_p$ contains more than $\frac{dn}{d+1}$ points of $\mathcal{P}$.

% kiana: man be nazaram in tarif painie vase center point behtare

Given an $n$-point set $\mathcal{P}$ in $d$ dimensions, a point $c \in R^d$ is called a \emph{centerpoint} of $\mathcal{P}$ if any halfspace containing $c$ contains at least $\ceil{\frac{n}{(d + 1}}e$ points of $\mathcal{P}$. In other words, any halfspace (or convex set) that avoids a centerpoint can contain at most $\floor{\frac{dn}{d + 1}}$ points of $\mathcal{P}$.

%-------------------------- 1-center ---------------------------------

\section{A Simple $2$-Approximation Algorithm for $1$-Center with Outliers}

\begin{algorithm}
\label{alg:1center}
\leavevmode
\begin{algorithmic}
\Function{$1$-centerWithOutliers}{$\mathcal{P}, z$}
	\State Let $p_i$ denote the elements of $\mathcal{P}$, for $i \in \set{1, \dots, n}$.
	\ForAll{$i \gets 1, \dots, z+1$}
		\State Assume $p_i$ is a non-outlier point in optimal solution.
		\State $B(c_i, r_i) \gets$ \Call{KnownPoint}{$\mathcal{P}, z, p_i$}
	\EndFor
	\State $i^* \gets \argmin_{i=1}^{z+1} r_i$
	\State \Return $B(c_{i^*}, r_{i^*})$
\EndFunction
\Statex
\Function{KnownPoint}{$\mathcal{P}, z, p$}
	\State $B \gets B(p, 0)$
	\State $Q \gets \emptyset$
	\For{$p'$ in $\mathcal{P}$}
		\If{$p' \notin B$}
			\State Insert $p'$ into $Q$
			\If{$\card{Q} = z + 1$}
				\State Remove from $Q$ a point $q$ which is closest to $p$.
				\State $B \gets B(p, \card{pq})$
			\EndIf
		\EndIf
	\EndFor
	\State \Return{B}
\EndFunction
\end{algorithmic}
\end{algorithm}
Function \textproc{KnownPoint} in Algorithm~\ref{alg:1center}, takes a point $p$ as an argument which is guaranteed to be a non-outlier point in the optimal solution. To overcome the lack of knowledge such a point, function \textproc{$1$-centerWithOutliers} tries each of the first $z+1$ points of the stream as a candidate for a non-outlier point and generates a ball for each, using function \textproc{KnownPoint}. It returns the ball with the minimum radius. Note that, due to space limitations inherent to streaming data model, the body of for-all loop in function \textproc{$1$-centerWithOutliers} is run in parallel.

\begin{theorem}
Algorithm~\ref{alg:1center} is a $2$-approximation algorithm for $1$-center problem with $z$ outliers, in any dimension.
\end{theorem}

\begin{proof}
Let $B^*(c^*, r^*)$ be the optimal solution. Clearly, there exists a point $p$ among the first $z+1$ points of $\mathcal{P}$, which is not an outlier in the optimal solution. Since $p \in B^*$, then $\card{pp'} \le 2r^*$ for any point $p'\in B^*$. There is at least one point $q'$ among the $(z+1)$-furthest points from $p$ that is not an outlier in the optimal solution. Thus $\card{pq} \le \card{pq'} \le 2r^*$ and Algorithm~\ref{alg:1center} returns a valid solution of radius at most $2r^*$. So the proof is complete.
\end{proof}

\begin{figure}[h]
	\centering
	\includegraphics[width=17em]{figs/one-center}
	\caption{Output of Algorithm~\ref{alg:1center}}
	\label{fig:1center}
\end{figure}

The space complexity of Algorithm~\ref{alg:1center} is $\cO(z^2 + zd)$, the update time is $\cO (z \log z + zd)$ and the query time is $\cO (z)$.
If a non-outlier point $p$ is known then the space, update time and query time complexity of algorithm can be reduced by a factor of $z$.

%-------------------------- 2-center ---------------------------------

\section{The $2$-Center Problem with $z$ Outliers}

\begin{theorem}
For any fixed $d > 1$, our single-pass data stream algorithm whose working space and update time are polynomial in $d$ and sub-linear in $n$ and returns two centers that guarantees a $(1.8 + \eps)$-approximation for the Euclidean $2$-center problem with outliers.
\end{theorem}

%--- from kim and ahn

In all the algorithms given this section it is assumed that $p_1$ is a non-outlier point. It is not hard to see that, this limitation can be remedied by considering $\cO(z)$ parallel instances of the algorithm, similar to Algorithm~\ref{alg:1center}.

In Section \ref{subsec:smaller}, we give a description of our algorithm for a given $r' > 0$ for the case where $\delta^* < C r^*$ and $1.2r^* \le r' < (1.2 + 2\eps/3)r^*$, our algorithm returns a $(1.8 + \eps)$-approximate solution. We explain how to find such an $r'$ and present a full description of our algorithm for the case where $\delta^* < C r^*$ in Subsection~\ref{subsec:findr}. Then we inspect the case where $\delta^* \ge C r^*$ in Subsection~\ref{subsec:bigger}.

\subsection{The Case $\delta^* < C r*$}
\label{subsec:smaller}
Our idea in this section is derived from \cite[Sec.~3.1]{kim}. To avoid duplication, we just outline the important parts of their algorithm and our modifications to it. Kim's algorithm has $10$ different states. In each step one or many of the states can be valid and their algorithm considers all of them in parallel. In each state, we have two balls. A transition between the states occurs whenever a point not covered by any of the two balls has arrived in the stream. This transition graph starts with a blank node (with no balls) and has depth four (without considering the end nodes). It is straightforward to see that this transition graph is a DAG.
Our modification is on the transition part. 
%For computing outliers, we just need to consider the points that may cause a transition so instead of exiting a node we ignore this point as an outlier. % Sahand: Chi shode? Kiana: benazaram in jomle bayad pak beshe chon ham vazeh ni ham tu badesh tozih dade mishe ghashang
In each state the number of points that should be considered as outlier is unknown. So all the possible choices should be considered. It is sufficient to have four integers, $n_1,\dots, n_4$ representing the number of outliers in depth $1$ to $4$, such that $\sum_{i=1}^{4} n_i=z$. To sum up, the modified algorithm is defined as follows:
\begin{algorithm}
\label{alg:smallc}
\leavevmode
\begin{algorithmic}
% Kiana: man be nazaram in if p_{o_i} arrives ha ro bardarim! niazi nis beheshun
%kiana: ba in definition avalie movafeghin aya? "(Denote that $p_{o_1}=p_1$ and $p_{o_i, S'}$ is the $(n_{i-1}+1)^{st}$ point that arrives after $p_{o_{i-1},S}$ and does not lie in the candidate solution S)" fek konam algorithm khana beshe
\Function{Known$r'$}{$\mathcal{P}, z, r'$}
	\For{$(n_1, \dots, n_4) \gets \set{(n_1, \dots, n_4) \provided \sum n_i=z}$}
		\State $CS \gets B(p_1,r')$.
		\State $p_{o_2} \gets $ $(n_1+1)$\st point of $\mathcal{P}$ that arrives after $p_1$ and does not lie in the corresponding candidate solution.
		\If{$p_{o_2}$ arrives}
			\State $CS\gets$ the case of $p_{o_2} \in B_1^*$ $\cup$ the case of $p_{o_2} \in B_2^*$.
			\For{each case $S$}
				\State $p_{o_3} \gets$ $(n_2+1)$\st point of $\mathcal{P}$ that arrives after $p_{o_2}$ and does not lie in the corresponding candidate solution.

				\If{$p_{o_3}$ arrives} 
					\State $CS\gets CS\setminus S$ $\cup$ the sub-case of $p_{o_3} \in B_1^*$ $\cup$ the sub-case of $p_{o_3} \in B_2^*$.
					\For {each sub-case $S'$} 
						\State $p_{o_4} \gets$ $(n_3+1)$\st point of $\mathcal{P}$ that arrives after $p_{o_3}$ and does not lie in the corresponding candidate solution.

						\If {$p_{o_4}$ arrives} 
							\State Replace $S'$ with a new candidate solution.
							\If{more than $n_4$ points arrive after $p_{o_4}$ that lie outside of the corresponding candidate solutions}
								\State Abandon the solution
							\EndIf
						\EndIf

					\EndFor
				\EndIf
			\EndFor

		\EndIf

		\State $\mathop{Sol}_{n_1,n_2,n_3,n_4} \gets$ the solution with the smallest larger radius, among all the sub-cases.
	\EndFor
	\State \Return the solution $\mathop{Sol}_{n_1,n_2,n_3,n_4}$ with the smallest radius, for all valid values of $(n_1,n_2,n_3,n_4)$.
\EndFunction
\end{algorithmic}
\end{algorithm}
\begin{theorem}
Given $\delta^* < C r*$ and $1.2r^* \le r' < (1.2 + 2\eps/3)r^*$, Algorithm~\ref{alg:smallc} uses $\cO (dz^3)$ space and returns a $(1.8+\eps)$-approximate solution. Algorithm~\ref{alg:smallc} spends $\cO (dz^3)$ update time for each point in $\mathcal{P}$ and answers a query in $\cO (dz^3)$.
\end{theorem}

\begin{proof}
Since our algorithm considers all possible input cases of streaming points, there is at least one feasible solution. Since every feasible solution has its larger radius at most $3r'/2$, the final solution has larger radius at most $3r'/2 \le (1.8 + \eps)r^*$.
For space complexity, our algorithm maintains at most two balls in each case, and therefore it uses $\cO(dz^3)$ space. Whenever the next point is inserted, the algorithm updates the solution for each sub-case in $\cO (d)$ time. Therefore, the algorithm spends $\cO (dz^3)$ update time for each point of $\mathcal{P}$. Answering a query consists of choosing the minimum radius among all the candidate solutions, which amounts to $\cO (dz^3)$ time.
\end{proof}

\subsubsection{Finding $r'$}
\label{subsec:findr}

\begin{lemma}
\label{lem:1lt2}
A $1$-center optimal solution with $z$ outliers for a streaming set of points is also an upper bound for the $2$-center optimal solution with $z$ outliers.
\end{lemma}
\begin{proof}
Let $B_1^*(c^*, r_1^*)$ be the optimal solution for the $1$-center problem. Let $B_2$ be a ball with radius $r_1^*$ and center at $\infty$. Clearly, $(B_1^*, B_2)$ is a solution for $2$-center problem. Thus, the proof is complete.
\end{proof}

\begin{lemma}
\label{lem:2lt1}
Let $r_1^*, r_2^*$ be the radius of $1$-center and $2$-center optimal solutions with $z$ outliers, respectively. Then $r_1^* \le \left(\frac{C}{2} + 2\right) r_2^*$.
\end{lemma}
\begin{proof}
Suppose that $(B_1^*(c_1^*, r_2^*), B_2^*(c_2^*, r_2^*))$ is an optimal solution for $2$-center problem. Consider $m$ as the midpoint of segment 
%$c_1c_2$. Kiana: verify this
$c_1^*c_2^*$.
Clearly, $B\left(m, \frac{\delta}{2} + 2r_2^*\right)$ covers both $B_1^*$ and $B_2^*$. So it is a solution for $1$-center problem and the proof is complete.
\end{proof}

\begin{figure}[h]
	\centering
	\includegraphics[width=19em]{figs/2lt1}
	\caption{Proof of Lemma~\ref{lem:2lt1}}
	\label{fig:2lt1}
\end{figure}

Algorithm~\ref{alg:1center} finds a $2$-approximation for $r_1^*$. By Lemma \ref{lem:1lt2} and \ref{lem:2lt1}, it gives a $2\left(\frac{C}{2} + 2\right)$-approximation for $r_2^*$.

\begin{obs}
\label{obs:2apr}
Let $r_1$ and $k_0$ be two positive real numbers. Define $k=k_0 2^i$ to be the smallest real number satisfying the inequality $k \ge r_1$, where $i$ is a non-negative integer. Clearly, $k$ is a $2$-approximation for $r_1$.
\end{obs}

%In this section, we explain how we get r' such that 1.2r^*  r' < (1.2 + 2\eps/3)r^*. The basic procedure works as follows:

%Our algorithm maintains $m=\ceil{(3C+12)\eps}$ candidate lengths.	Sahand: Verify my modification.
Our algorithm maintains $m=\ceil{\frac{1.2(3C+12)}{\eps}}$ candidate lengths.
For each candidate length $t$, we assume that $r' = t$ and use it to run Algorithm~\ref{alg:smallc}. We use Algorithm~\ref{alg:1center} to estimate $r'$. Let $k_i$ be the $i$\nth non-zero radius calculated by the algorithm. Obviously, the sequence of answers given by the algorithm is increasing.

Let $l_1=k_1$ and $l_i=2^j l_1$, where $l_i$ is the smallest number satisfying $l_i \ge k_i$. By Observation~\ref{obs:2apr}, $l_i$ is a $(2C + 8)$-approximation for $r_2^*$. So the following inequalities hold:
\[
\frac{2\eps}{3}\frac{1.2l_i}{2C+8}	% Sahand: in nabarabari be che dardi khord?
\le \frac{1.2l_i}{2C+8}\le 1.2 r_2^* \le 1.2 l_i 
\]
Define $t_i = \frac{1.2 l_i}{m}$. If we divide the
%interval $(0, l_i]$
 interval $(0, 1.2 l_i]$	%Sahand: Verify this
into $m$ equal segments, then length of each segment is at most $2/3 \eps r_2^*$ and the endpoints as candidates are $\mathcal{L}_i = \set{j \times t_i \provided j = 1, \dots, m}$.
The inequality $1.2 r_2^* \le j \times l_i \le (1.2 + \frac{2\eps}{3})r_2^*$ holds for at least one of these candidates.

\begin{figure}[h]
	\centering
	\includegraphics[width=21em]{figs/findr}
	\caption{Subdivision of $(0, 1.2 l_i]$ interval}
	\label{fig:findr}
\end{figure}

%kiana: bacheha in paragraph paini kheili bad bud benazaram. man ye talashai rush kardam vali hanuzam benazaram jaye kar dare

When the first non-zero radius is observed, $l_1$ is set. Algorithm~\ref{alg:smallc} should be executed for each candidate in $\mathcal{L}_1$ for all the previous points, which have been stored in a buffer. It is not hard to see that the space complexity for storing these points is $\cO(z)$. For each new point, if $l_i=l_{i-1}$ then $\mathcal{L}_i = \mathcal{L}_{i-1}$ and it suffices to add the new point to all parallel instances corresponding to candidates in $\mathcal{L}_i$. Otherwise, Algorithm~\ref{alg:smallc} should be executed for all of the candidates in $\mathcal{L}_i$, with all the points. But this is not achievable due to space limitations. To remedy
%remedy?? really??
this problem, note that if the candidate $x_j=j \times t_i \in \mathcal{L}_i$ is also in $\mathcal{L}_{i-1}$, there is no need to start Algorithm~\ref{alg:smallc} over and the current execution will be continued. If $x_j \notin \mathcal{L}_{i-1}$, then it is certain that $x_j \ge l_{i - 1}$ (Observe that $l_i=ul_{i-1}$, for some $u\in \mathbb{N}$). Since the ball $B_1(p_1, l_{i-1})$, obtained from Algorithm~\ref{alg:1center}, has at most $z$ outliers, all the non-outlier points lie in the candidate balls in Algorithm~\ref{alg:smallc}.
%kiana: in jomle balai oke be nazaretun? 
These outliers have been stored in a buffer, so for the new candidate length, it suffices to execute Algorithm~\ref{alg:smallc} with only the outlier points of $B_1$.

\begin{theorem}
\label{thm:1st-cmplx}
Algorithm~\ref{alg:smallc} uses $\cO(\frac{dz^3}{\eps})$ space, and takes $\cO(\frac{dz^4}{\eps})$ and $\cO(\frac{dz^3}{\eps})$ time for update and query, respectively.
\end{theorem}

\subsection{The Case $\delta^* \ge C r^*$}
\label{subsec:bigger}

\begin{obs}
\label{obs:c+4}
Let $d$ be the distance between any pair of points from two $C$-separated balls. Then $1 \le \frac{d}{\delta} \le \frac{C+4}{C}$.
\end{obs}

\begin{figure}[h]
	\centering
	\includegraphics[width=21em]{figs/c_plus_4}
	\caption{Depiction of two extreme case of Observation~\ref{obs:c+4}}
	\label{fig:c+4}
\end{figure}

\begin{obs}
\label{obs:intersection}
Let $B_1$ and $B_2$ be two disjoint balls with distance $\delta$ and $B$ be an arbitrary ball of radius at most $\frac{\delta}{2}$. Then $B$ can intersect at most one of $B_1$ and $B_2$.
\end{obs}

\begin{lemma}
\label{lem:c-sep}
Let $\mathcal{P}$ be a set of points and assume that $B_{2,1}^*$ and $B_{2,2}^*$ are $C$-separated ($C \ge 4$) and let $p_1$ be an arbitrary point in $B_{2,1}^*$. Define $S$ as the $z+1$ furthest points of $\mathcal{P}$ from $p_1$. Then $S \cap B_{2,2}^*$ is nonempty.
\end{lemma}
\begin{proof}
By contradiction, assume that $S \cap B_{2,2}^*$ is empty. It is clear that $S$ contains at least one non-outlier point. Let $q$ be the furthest point of $S \cap B_{2,1}^*$ from $p_1$. Consider $B(p_1, \card{p_1q})$. It is clear that $B$ covers $\mathcal{P} \setminus S$. Since $p_1, q \in B_{2,1}^*$, then $\card{p_1q}$ is at most $2r_2^*$. Thus by Observation~\ref{obs:intersection}, $B_{2,2}^* \cap B = \emptyset$. Therefore $B_{2,2}^* \cap \mathcal{P} = \emptyset$ and hence $B_{2,2}^*$ is empty, which contradicts the optimality of this solution.
\end{proof}

Let $B_1, B_2$ and $B_u$, be instances of a data structure that supports adding 
% Kiana: and removing
a point and gives a $\beta$-approximation for $1$-center problem with $k$ outliers, for $k=0,\dots,z$ (This data structure, does not need to maintain all the points. Suppose that it has a buffer with length $(d+1)(z+1)$ that maintains the most recently added points). Algorithm~\ref{alg:case2} assumes point $p_1$ to be in $B_{2,1}^*$. This assumption can be omitted by executing a parallel instances of the algorithm for each of the first $z+1$ points in the stream, similar to the approach in Algorithm~\ref{alg:smallc}. This algorithm maintains $c_1$ as an arbitrary point in $B_{2,1}^*$ and $c_2$ as a candidate that may be in $B_{2,2}^*$. It tries to divide points into three subdivisions:
\begin{itemize}
\item $B_1$, a subset of $\mathcal{P}$ where $B_1 \cap B_{2,2}^* = \emptyset$, that is a set of points that provably lie outside $B_{2, 2}^*$.
\item $B_2$, a subset of $\mathcal{P}$ along with a \emph{secondary point}, such that if $B_{2, 2}^*$ covered the secondary point, then $B_2 \cap B_{2, 1}^* = \emptyset$.
\item Buffer, with size at most $z$ that if $c_2 \in B_{2, 2}^*$ then all of them are outliers.
\end{itemize}
Algorithm~\ref{alg:case2} also maintains $B_u$ as union of $B_1$ and $B_2$.

%\begin{algorithmic}
%\Procedure{add to furthest buffer(z+1)}{p}
%	\State add p to buffer
%	\If{size of buffer $> z+1$}
%		\State remove nearest point from $p_1$
%	\EndIf
%\EndProcedure
%\end{algorithmic}

\begin{lemma}
\label{lem:(z+1)-furthest}
Let $\mathcal{P}$ be a set of points and $B_1$ and $B_2$ be two $C$-separated balls covering all but at most $z$ of the points in $\mathcal{P}$. Furthermore, let $p_1$ be arbitrary points in $B_1$ and $q$ be the $(z+1)$\st furthest point from $p_1$. Then $\frac{C}{C+4}\card{qp_1}$ is a lower bound for the distance between $B_1$ and $B_2$.
\end{lemma}
\begin{proof}
Due to Lemma~\ref{lem:c-sep}, there exists $p_2 \in B_{2,2}^*$ such that $\card{p_1p_2} \ge \card{qp_1}$. Thus, by Observation~\ref{obs:c+4}, $\frac{C}{C+4} \card{p_1p_2} \le \delta$. The claim follows immediately.
\end{proof}

Function \textproc{AddTo$B_1$} is used to add a point $p$ to $B_1$. The point will be added only if the point is within $\delta$-radius of the center $c_1$, where $\delta$, calculated by Algorithm~\ref{alg:case2}, is $\frac{C}{C+4}\card{qc_1}$ and $q$ is the $(z+1)$\nth furthest point from $c_1$. By Lemma~\ref{lem:(z+1)-furthest}, $\delta$ is a lower bound for $\delta^*$. So any point within $\delta$-radius of $c_1$ is guaranteed to lie outside $B_{2,2}^*$. Thus Function \textsc{AddTo$B_1$} does not violate the property $B_1 \cap B_{2,2}^* = \emptyset$.
\begin{algorithmic}
\Function{AddTo$B_1$}{$p$}
	\If{$p \in B(p_1, \delta)$}
		\State $B_1 = B_1 \cup \set{p}, B_u = B_u \cup \set{p}$
		\State \Return{true}
	\Else
		\State \Return{false}
	\EndIf
\EndFunction
\end{algorithmic}

Function \textproc{AddTo$B_2$} is used to add a point $p$ to $B_2$. Initially, $B_2$ is empty and $c_2$ and $r_c$ are not initialized. When an appropriate candidate is found, Algorithm~\ref{alg:case2} sets $c_2$ to that candidate and $r_c$ to $\frac{2\card{c_1c_2}}{C}$ and thereafter
%kiana: bacheha kudumetun in kalame ro gozashtin? azash motmaeni? man hichja nadide budamesh
points are added to $B_2$ only if they lie within $r_c$-radius of $c_2$. At this point $c_2$ is considered as the secondary point for $B_2$. Clearly the subdivision property for $B_2$ holds initially when $B_2$ consists of the single point $c_2$. All the subsequent points added to $B_2$ are within $r_c$-radius of $c_2$ and given $C\ge 7$, by Observation~\ref{obs:intersection} subdivision property is invariant under this operation.

When $\card{B_2}$ reaches $(d+1)(z+1)$, $r_c$ is increased by a factor of $(2 + \frac{2}{C})$. It is easy to see that $(2 + \frac{2}{C})r_c < \frac{\delta}{2}$ provided $C \ge 14$ and thus by Observation~\ref{obs:intersection} the property is not violated.

\begin{algorithmic}
\Function{AddTo$B_2$}{p}
	\If{$c_2$ is set and $p \in B(c_2, r_c)$}
		\State $B_2 \gets B_2 \cup \set{p}, B_u \gets B_u \cup \set{p}$
		\If{$\card{B_2} = (d+1)(z+1)$}
			\State $r_c \gets  (2 + \frac{2}{C}) \times r_c$
			\For{$p$ in Buffer}
				\If{$p$ in $B(c_2, r_c)$}
					\State $B_2 \gets B_2 \cup \set{p}, B_u \gets B_u \cup \set{p}$
				\EndIf
			\EndFor
		\EndIf
		\State \Return{true}
	\Else
		\State \Return{false}
	\EndIf
\EndFunction
\end{algorithmic}

\begin{prop}
Any set $\mathcal{P}$ of points in $d$-dimensional Euclidean space has a centerpoint.\cite{edelsbrunner}
\end{prop}

\begin{cor}
\label{cor:omitting-centerpoint}
Given a set $\mathcal{P}$ of $k(d+1)$ points in $d$-dimensional Euclidean space, there is a point $c_p$, not necessarily in $\mathcal{P}$, that any convex object that does not cover $c_p$, leaves at least $k$ point of $\mathcal{P}$ uncovered.
\end{cor}

Let $c_p$ be a centerpoint of points in $B_2$, when $(z+1)(d+1)$ points have been added to $B_2$. We claim that with $B_2 = B(c_2, (2 + \frac{2}{C})r_c)$, $c_p$ can be chosen as the secondary point for $B_2(c_2, (2 + \frac{2}{C})r_c)$.
%As it was mentioned earlier, if $c_p \in B_{2,2}^*$ then $r^* \le \frac{2\card{c_1c_p}}{C}$. Thus $B_{2,2}^* \subseteq B(c_2, \frac{2\card{c_1c_p}}{C})$.	% Sahand: Verify my modification:
If $c_p \in B_{2,2}^*$ then by Observation~\ref{obs:c+4}, $r^* \le \frac{\card{c_1c_p}}{C}$. Thus $B_{2,2}^* \subseteq B(c_p, \frac{2\card{c_1c_p}}{C})$.
Since:
\[
\frac{2\card{c_1c_p}}{C} \leq \frac{2}{C}(\card{c_1c_2} + r_c) \leq (1 + \frac{2}{C})r_c
\]
%then $B_{2,2}^* \subseteq B(c_2, (1 + \frac{2}{C})r_c)$.	%Sahand: Verify my modification:
 then $B_{2,2}^* \subseteq B(c_p, (1 + \frac{2}{C})r_c) \subseteq B(c_2, (2 + \frac{2}{C})r_c)$.
So $B_2(c_2, (2 + \frac{2}{C})r_c) \cap B_{2,2}^* \neq \emptyset$. Thus supposing $C \ge 14$ and by Observation~\ref{obs:intersection}, $B_2 \cap B_{2,1}^* = \emptyset$. Thus the claim follows.

At some point during the execution of Algorithm \ref{alg:case2}, the assumption about $c_2$ lying in $B_{2,2}^*$ might be contradicted when the buffer overflows. We can then conclude that $c_2 \notin B_{2,2}^*$.
At this point, behavior of Algorithm~\ref{alg:case2} depends on size of $B_2$ relative to $(d+1)(z+1)$:
\begin{itemize}
\item If $\card{B_2} < (d+1)(z+1)$ then $c_2$ can be added to $B_1$, by definition of $B_1$.
The algorithm then tries all points in $B_2 \cup \mbox{Buffer} \setminus \set{c_2}$, until it finds a suitable candidate point for $c_2$ that does not leave too many points uncovered. Note that at most $(z+1)(d+1) + z$ points have to be tried.
\item If $\card{B_2} \ge (d+1)(z+1)$, let $q$ be the $(z+1)$\st furthest point from $p_1$ and $p'$ be the nearest point of ball $B_2(c_2, r_c)$ to $p_1$. Then $\card{qp_1} > \card{p'p_1}$, since $B_2$ contains more than $z+1$ points. So by Lemma~\ref{lem:(z+1)-furthest}:
\[
\delta \ge \frac{C \card{qp_1}}{C+4} \ge \frac{C}{C+4} (\card{c_1c_2} - r_c) = \frac{C^2 - 2C}{2C + 8} r_c
\]
As a result, if $C \geq 14$ then $(2 + \frac{2}{C}) r_c < \frac{\delta}{2}$. As shown in Observation~\ref{obs:intersection}, the ball $B_2(c_2, (2 + \frac{2}{C}) r_c)$ has nonempty intersection with exactly one of $B_{2, 1}^*$ and $B_{2, 2}^*$ (not all of its points can be outliers). Since the buffer overflowed, the assumption about the secondary point, $c_p$, being in $B_{2,2}^*$ must have been invalid. By Corollary~\ref{cor:omitting-centerpoint} if $c_p$ is not covered, then circle $B_{2,1}^*$ leaves at least $z+1$ points of $B_2$ uncovered, and there will be more than $z$ outliers. Thus, $c_p$ has to be covered. As a result, $c_p \in B_{2, 1}^*$ and all the points of $B_2$ can be added to $B_1$. This is done by replacing $B_1$ with $B_u$ and initializing $B_2$ over again.
\end{itemize}

\begin{algorithm}
\label{alg:case2}
\leavevmode
\begin{algorithmic}
\State $\delta \gets 0, r_c \gets 0$
\State $c_1 \gets p_1$
\For{$p \in P$}
	\If{at least $z+1$ points have been processed}
		\State $q \gets$  $(z+1)$-furthest point from $c_1$
	\Else
		\State $q \gets c_1$
	\EndIf
	\State $\delta \gets \frac{C}{C+4} \card{c_1q}$
	\If{!\Call{AddTo$B_1$}{$p$} and !\Call{AddTo$B_2$}{$p$}}
		\State add $p$ to Buffer
		\While{$\card{\mbox{Buffer}} > z$}
			\If{$\card{B_2} \ge (d+1)(z+1)$}
				\State $B_1 \gets B_u$, $B_2 \gets \emptyset$
			\ElsIf{$c_2$ is set}
				\State $B_1 \gets B_1 \cup \set{c_2}$
				\State remove $c_2$ from $B_2$	%Sahand: Is it clear that removing does not mean that B_2 is a dynamic data structure? Kiana: benazare man dynamic mishe! un bala ham ke goftam bayad begin and removing ro! vali gand nemikhore be 1-center?
			\EndIf
			\State $T \gets \mbox{Buffer} \cup B_2$
			\State $\mbox{Buffer} \gets \emptyset, B_2 \gets \emptyset$
			\If{first iteration of while}
				\For{$p \in T$}
					\If{\Call{AddTo$B_1$}{$p$}}
						\State remove $p$ from $T$
					\EndIf
				\EndFor
			\EndIf
			\State $c_2 \gets$ arbitrary point in $T$
			\State $r_c \gets \frac{2}{C}\card{c_1 c_2}$
			\For{$p \in T$}
				\State \Call{AddTo$B_2$}{$p$}
			\EndFor				
			\State $\mbox{Buffer} \gets T \setminus B_2$
		\EndWhile
	\EndIf
\EndFor
\end{algorithmic}
\end{algorithm}

Let $B_1'$, $B_2'$ and $B_u'$ be the $1$-centers obtained from $B_1$, $B_2$ and $B_u$ by the $\beta$-approximation algorithm, respectively. To answer a query, we use these balls. By the initial assumption about $p_1$, $B_1$ contains $B_{2,1}^*$ and $B_1'$ is a $\beta$-approximation for $B_{2,1}^*$. But for $B_2$ it may be the case that our assumption about the secondary point was incorrect or non-optimal, so $B_2'$ is not a good approximation for $B_{2,2}^*$. There are two cases for $\card{B_2}$ to be considered. If $\card{B_2} < (z+1)(d+1)$, then we can try each point in $B_2 \cup \mbox{Buffer}$ as a candidate for the secondary point. If $\card{B_2} \ge (d+1)(z+1)$, then there is no need for points in $B_2$ to be considered, since for those points as secondary point, $B_1$ would be replaced by $B_u$ and $B_2$ would be empty. Thus it suffices to consider points of Buffer as candidates and compare them to the solution $(B_u, \emptyset)$.

\begin{algorithm}
\label{alg:query}
\leavevmode
\begin{algorithmic}
\Function{Query}{}
	\State solutions = [query $B_1$ $B_2$ Buffer]

	\If {$\card{B_2} \geq (d+1)(z+1)$}
		\State candidates $\gets$ Buffer
	\Else
		\State candidates $\gets$ Buffer $\cup B_2 - \set{c_2}$
	\EndIf

	\For{$c_2 \in$ candidates}
		\State $r_c \gets \frac{2}{C} \card{c_1 c_2}$
		\State $B_2 \gets \emptyset$, Buffer $\gets \emptyset$ 
		\For{$p \in$ candidates}
			\If{not \Call{AddTo$B_2$}{$p$}}
				\State add $p$ to Buffer
			\EndIf
		\EndFor
		\State add \Call{QuerySubdivision}{$B_1$, $B_2$, Buffer} to solutions
	\EndFor
	\State \Return \Call{$\min$}{solutions}
\EndFunction
\Statex
\Function{QuerySubdivision}{$B_1$, $B_2$, Buffer}
	\State solutions $\gets$ empty list
	\For{$k \gets 0, \dots,(z - \card{\mbox{Buffer}})$}
		\State $r \gets \max(1-\mbox{center}(B_1, k), 1-\mbox{center}(B_2, z - \card{\mbox{Buffer}} - k))$
		\State add $r$ to solutions
	\EndFor
	\State \Return \Call{$\min$}{solutions}
\EndFunction
\end{algorithmic}
\end{algorithm}

Suppose that our data structure for maintaining $B_1$, $B_2$ and $B_u$ uses $S(n,z,d)$ space, $T(n,z,d)$ update and $Q(n,z,d)$ query time. Note that by $Q_{o}(zd,z,d)$ we mean the query time for the offline $1$-center problem with $z$ outlier in $d$ dimensions. The best known algorithm for $1$-center without outliers is $1.22$-approximation by \cite{chan}. The buffering framework introduced in \cite{zarrabi} can use this algorithm to achieve a $(1.22\sqrt{2})$-approximation ($1.22\sqrt{2} < 1.8$) for $1$-center problem with outliers.

\begin{theorem}
\label{thm:2nd-cmplx}
Space complexity of Algorithm~\ref{alg:case2} is $\cO(dz+S(n,z,d))$. It takes $\cO^*(dzT(n,z,d))$ time for update. Query time in Algorithm~\ref{alg:query} is $\cO(zQ(n,z,d) + dz(dz+zQ_o(zd,z,d)))$ and it returns two centers that guarantee a $(1.8 + \eps)$-approximation for $2$-center problem with outliers.
\end{theorem}

\begin{proof}
The space complexity for this algorithm is derived from the space used by $B_1$, $B_2$, $B_u$ and the Buffer which is obviously $\cO(dz+S(n,z,d))$. The while loop runs at most once for each point, so amortized time is $\cO(zdT(n,z,d))$. The candidates in the Algorithm \ref{alg:query} are at most $zd$ points  so the query time will easily follows.
\end{proof}

\begin{theorem}
Our algorithm uses $\cO(zS(n, z, d) + \frac{dz^4}{\eps})$ space and has time complexity $\cO^*(dz^2T(n,z,d) + \frac{dz^5}{\eps})$ and $\cO(z^2Q(n,z,d) + dz^2(dz+zQ_o(zd,z,d)) + \frac{dz^4}{\eps})$ for update and query operations, respectively. It returns a $(1.8 + \eps)$-approximate solution for $2$-center problem with outliers in any dimension.
\end{theorem}
\begin{proof}
Result follows immediately from Theorems~\ref{thm:1st-cmplx} and \ref{thm:2nd-cmplx} and the fact that $p_1$ was assumed to be a non-outlier.
\end{proof}

%--------------- BIBS --------------------

\small
\baselineskip=.85\baselineskip
\bibliographystyle{abbrv}
\bibliography{bibs/abbrv,bibs/ref}

\end{document}

### 2015-04-05 paper.tex
Revision 1

@@
 Let $B(c,r)$ denote a ball with center $c$ and radius $r$. We denote by $pq$ the straight line segment between these two points and by $\card{pq}$ the length of this segment. 
-%kiana: tarife delta ro chanja didam nagofte budan! benazaram ma ham mitunim nagim, baz age fek mikonin lazeme tarif konam:
-% Define $\delta$ of two balls B(c,r) and B'(c',r'), the minimum distance between $B$ and $B'$ which is equal to $\card{cc'}-r-r'$.
+%kiana: tarife delta ro chanja didam nagofte budan! benazaram ma ham mitunim nagim, baz age fek mikonin lazeme tarif konam
+%Behnam: be nazaram alan bashe behtare, age doctor khast hazf mikone
+Define $\delta$ of two balls $B(c,r)$ and $B'(c',r')$, the minimum distance between $B$ and $B'$ which is equal to $\card{cc'}-r-r'$.
 
-Let $B_1^*(c_{2,1}^*, r_2^*)$ and $B_2^*(c_{2,2}^*, r_2^*)$ denote the optimal solution to $2$-center problem with $z$ outliers.
-By $\delta^*$ we denote the distance between $B_1^*$ and $B_2^*$, that is, $\delta^* = \max (0, \card{c_1^*c_2^*} − 2r^*)$.
+Let $B_{2,1}^*(c_{2,1}^*, r_2^*)$ and $B_{2,2}^*(c_{2,2}^*, r_2^*)$ denote the optimal solution to $2$-center problem with $z$ outliers.
+By $\delta^*$ we denote the distance between $B_{2,1}^*$ and $B_{2,2}^*$, that is, $\delta^* = \max (0, \card{c_1^*c_2^*} - 2r^*)$.
 
@@
 % kiana: man be nazaram in tarif painie vase center point behtare
+% Behnam: bahat moafegham
 
-Given an $n$-point set $\mathcal{P}$ in $d$ dimensions, a point $c \in R^d$ is called a \emph{centerpoint} of $\mathcal{P}$ if any halfspace containing $c$ contains at least $\ceil{\frac{n}{(d + 1}}e$ points of $\mathcal{P}$.
+Given an $n$-point set $\mathcal{P}$ in $d$ dimensions, a point $c \in R^d$ is called a \emph{centerpoint} of $\mathcal{P}$ if any halfspace containing $c$ contains at least $\ceil{\frac{n}{d + 1}}$ points of $\mathcal{P}$.
 In other words, any halfspace (or convex set) that avoids a centerpoint can contain at most $\floor{\frac{dn}{d + 1}}$ points of $\mathcal{P}$.
@@
 Function \textproc{KnownPoint} in Algorithm~\ref{alg:1center}, takes a point $p$ as an argument which is guaranteed to be a non-outlier point in the optimal solution.
-To overcome the lack of knowledge such a point, function \textproc{$1$-centerWithOutliers} tries each of the first $z+1$ points of the stream as a candidate for a non-outlier point and generates a ball for each, using function \textproc{KnownPoint}.
+To overcome the lack of knowledge about such a point, function \textproc{$1$-centerWithOutliers} tries each of the first $z+1$ points of the stream as a candidate for a non-outlier point and generates a ball for each, using function \textproc{KnownPoint}.
 It returns the ball with the minimum radius.
@@
 
+% Behnam: Aks be nazaram gooya nist ziad. va inke jaii behesh refrence dade nashode!
+
 The space complexity of Algorithm~\ref{alg:1center} is $\cO(z^2 + zd)$, the update time is $\cO (z \log z + zd)$ and the query time is $\cO (z)$.
@@
 
-In all the algorithms given this section it is assumed that $p_1$ is a non-outlier point.
+In all the algorithms given in this section it is assumed that $p_1$ is a non-outlier point.
 It is not hard to see that, this limitation can be remedied by considering $\cO(z)$ parallel instances of the algorithm, similar to Algorithm~\ref{alg:1center}.
+% Behnam: Move this to upper section, this assumption can be used for previous algorithm
 
@@
 Our modification is on the transition part. 
-%For computing outliers, we just need to consider the points that may cause a transition so instead of exiting a node we ignore this point as an outlier.
-% Sahand: Chi shode?
-Kiana: benazaram in jomle bayad pak beshe chon ham vazeh ni ham tu badesh tozih dade mishe ghashang
+%For determining outliers, we just need to consider the points that may cause a transition so instead of exiting a node we ignore this point as an outlier. % Sahand: Chi shode? 
+%Kiana: benazaram in jomle bayad pak beshe chon ham vazeh ni ham tu badesh tozih dade mishe ghashang 
+%Behnam: be nazare man baiad bashe, chon baiad begim bara outlier ha faghat hamin noghteha moheman, in nokte mohemie!
 In each state the number of points that should be considered as outlier is unknown.
@@
 "(Denote that $p_{o_1}=p_1$ and $p_{o_i, S'}$ is the $(n_{i-1}+1)^{st}$ point that arrives after $p_{o_{i-1},S}$ and does not lie in the candidate solution S)" fek konam algorithm khana beshe
+% man ba tarife kiana kheili moafegham
 \Function{Known$r'$}{$\mathcal{P}, z, r'$}
@@
 		\If{$p_{o_2}$ arrives}
-			\State $CS\gets$ the case of $p_{o_2} \in B_1^*$ $\cup$ the case of $p_{o_2} \in B_2^*$.
+			\State $CS\gets$ the case of $p_{o_2} \in B_{2, 1}^*$ $\cup$ the case of $p_{o_2} \in B_{2,2}^*$.
 			\For{each case $S$}
@@
 				\If{$p_{o_3}$ arrives} 
-					\State $CS\gets CS\setminus S$ $\cup$ the sub-case of $p_{o_3} \in B_1^*$ $\cup$ the sub-case of $p_{o_3} \in B_2^*$.
+					\State $CS\gets CS\setminus S$ $\cup$ the sub-case of $p_{o_3} \in B_{2, 1}^*$ $\cup$ the sub-case of $p_{o_3} \in B_{2,2}^*$.
 					\For {each sub-case $S'$} 
@@
 \begin{proof}
-Let $B_1^*(c^*, r_1^*)$ be the optimal solution for the $1$-center problem.
-Let $B_2$ be a ball with radius $r_1^*$ and center at $\infty$.
-Clearly, $(B_1^*, B_2)$ is a solution for $2$-center problem.
+Let $B^*(c^*, r_1^*)$ be the optimal solution for the $1$-center problem.
+Let $B'$ be a ball with radius $r_1^*$ and center at $\infty$.
+Clearly, $(B^*, B')$ is a solution for $2$-center problem.
 Thus, the proof is complete.
@@
 \label{lem:2lt1}
-Let $r_1^*, r_2^*$ be the radius of $1$-center and $2$-center optimal solutions with $z$ outliers, respectively. Then $r_1^* \le \left(\frac{C}{2} + 2\right) r_2^*$.
+Let $r_1^*, r_2^*$ be the radius of $1$-center and $2$-center optimal solutions with $z$ outliers, respectively. Then $r_1^* < \left(\frac{C}{2} + 2\right) r_2^*$.
 \end{lemma}
 \begin{proof}
-Suppose that $(B_1^*(c_1^*, r_2^*), B_2^*(c_2^*, r_2^*))$ is an optimal solution for $2$-center problem. Consider $m$ as the midpoint of segment 
-%$c_1c_2$. Kiana: verify this
+Suppose that $(B_{2, 1}^*(c_1^*, r_2^*), B_{2,2}^*(c_2^*, r_2^*))$ is an optimal solution for $2$-center problem. Consider $m$ as the midpoint of segment 
 $c_1^*c_2^*$.
-Clearly, $B\left(m, \frac{\delta}{2} + 2r_2^*\right)$ covers both $B_1^*$ and $B_2^*$. So it is a solution for $1$-center problem and the proof is complete.
+Clearly, $B\left(m, \frac{\delta}{2} + 2r_2^*\right)$ covers both $B_{2, 1}^*$ and $B_{2,2}^*$. So it is a solution for $1$-center problem and the proof is complete.
 \end{proof}
@@
 \end{figure}
+%Behnam: tooie aks namosavit eshtebas baiad be delta/d koochiktar az C/2r* tabdil beshe
 
@@
 
-%Our algorithm maintains $m=\ceil{(3C+12)\eps}$ candidate lengths.	Sahand: Verify my modification.
 Our algorithm maintains $m=\ceil{\frac{1.2(3C+12)}{\eps}}$ candidate lengths.
@@
 By Observation~\ref{obs:2apr}, $l_i$ is a $(2C + 8)$-approximation for $r_2^*$.
-So the following inequalities hold:
-\[
-\frac{2\eps}{3}\frac{1.2l_i}{2C+8}	% Sahand: in nabarabari be che dardi khord?
-\le \frac{1.2l_i}{2C+8}\le 1.2 r_2^* \le 1.2 l_i 
-\]
-Define $t_i = \frac{1.2 l_i}{m}$. If we divide the
-%interval $(0, l_i]$
- interval $(0, 1.2 l_i]$	%Sahand: Verify this
-into $m$ equal segments, then length of each segment is at most $2/3 \eps r_2^*$ and the endpoints as candidates are $\mathcal{L}_i = \set{j \times t_i \provided j = 1, \dots, m}$.
+If we divide the interval $(0, 1.2 l_i]$ into $m$ equal segments, then length of each segment is at most $2/3 \eps r_2^*$ and the endpoints as candidates are $\mathcal{L}_i = \set{j \times t_i \provided j = 1, \dots, m}$ where $t_i = \frac{1.2 l_i}{m}$.
 The inequality $1.2 r_2^* \le j \times l_i \le (1.2 + \frac{2\eps}{3})r_2^*$ holds for at least one of these candidates.
@@
 %kiana: bacheha in paragraph paini kheili bad bud benazaram. man ye talashai rush kardam vali hanuzam benazaram jaye kar dare
-
+%Behnam: khoobe
 When the first non-zero radius is observed, $l_1$ is set.
@@
 To remedy
-%remedy?? really??
+%kiana, sahand: remedy?? really??
 this problem, note that if the candidate $x_j=j \times t_i \in \mathcal{L}_i$ is also in $\mathcal{L}_{i-1}$, there is no need to start Algorithm~\ref{alg:smallc} over and the current execution will be continued.
@@
 %kiana: in jomle balai oke be nazaretun? 
+% Behnam: be nazare man gheire vazehe, be nazaram baiad begim hade aksar z ta biroonan, oonam oonaii ke too buffer algorithme 1 an
 These outliers have been stored in a buffer, so for the new candidate length, it suffices to execute Algorithm~\ref{alg:smallc} with only the outlier points of $B_1$.
@@
 \label{obs:c+4}
-Let $d$ be the distance between any pair of points from two $C$-separated balls. Then $1 \le \frac{d}{\delta} \le \frac{C+4}{C}$.
+Let $d$ be the distance between arbitrary pair of points from two $C$-separated balls. Then $1 \le \frac{d}{\delta} \le \frac{C+4}{C}$.
 \end{obs}
@@
 % Kiana: and removing
+% Behnam: we don't need removing a point!
 a point and gives a $\beta$-approximation for $1$-center problem with $k$ outliers, for $k=0,\dots,z$ (This data structure, does not need to maintain all the points.
@@
 Algorithm~\ref{alg:case2} assumes point $p_1$ to be in $B_{2,1}^*$.
-This assumption can be omitted by executing a parallel instances of the algorithm for each of the first $z+1$ points in the stream, similar to the approach in Algorithm~\ref{alg:smallc}.
 This algorithm maintains $c_1$ as an arbitrary point in $B_{2,1}^*$ and $c_2$ as a candidate that may be in $B_{2,2}^*$.
@@
 \item $B_1$, a subset of $\mathcal{P}$ where $B_1 \cap B_{2,2}^* = \emptyset$, that is a set of points that provably lie outside $B_{2, 2}^*$.
-\item $B_2$, a subset of $\mathcal{P}$ along with a \emph{secondary point}, such that if $B_{2, 2}^*$ covered the secondary point, then $B_2 \cap B_{2, 1}^* = \emptyset$.
-\item Buffer, with size at most $z$ that if $c_2 \in B_{2, 2}^*$ then all of them are outliers.
+\item $B_2$, a subset of $\mathcal{P}$ along with a \emph{candidate point} $c_p$, such that if $B_{2, 2}^*$ covered the candidate point, then $B_2 \cap B_{2, 1}^* = \emptyset$.
+\item Buffer, with size at most $z$ that if $c_p \in B_{2, 2}^*$ then all of them are outliers.
 \end{itemize}
@@
 \label{lem:(z+1)-furthest}
-Let $\mathcal{P}$ be a set of points and $B_1$ and $B_2$ be two $C$-separated balls covering all but at most $z$ of the points in $\mathcal{P}$.
-Furthermore, let $p_1$ be arbitrary points in $B_1$ and $q$ be the $(z+1)$\st furthest point from $p_1$.
-Then $\frac{C}{C+4}\card{qp_1}$ is a lower bound for the distance between $B_1$ and $B_2$.
+Let $p_1$ be an arbitrary points in $B_{2,1}^{*}$ and $q$ be the $(z+1)$\st furthest point from $p_1$. Then $\frac{C}{C+4}\card{qp_1}$ is a lower bound for $\delta^*$.
 \end{lemma}
@@
 Due to Lemma~\ref{lem:c-sep}, there exists $p_2 \in B_{2,2}^*$ such that $\card{p_1p_2} \ge \card{qp_1}$.
-Thus, by Observation~\ref{obs:c+4}, $\frac{C}{C+4} \card{p_1p_2} \le \delta$.
+Thus, by Observation~\ref{obs:c+4}, $\frac{C}{C+4} \card{p_1p_2} \le \delta^*$.
 The claim follows immediately.
@@
 points are added to $B_2$ only if they lie within $r_c$-radius of $c_2$.
-At this point $c_2$ is considered as the secondary point for $B_2$.
+At this point $c_2$ is considered as the \emph{candidate point} $c_p$.
 Clearly the subdivision property for $B_2$ holds initially when $B_2$ consists of the single point $c_2$.
@@
 
-When $\card{B_2}$ reaches $(d+1)(z+1)$, $r_c$ is increased by a factor of $(2 + \frac{2}{C})$.
+When $\card{B_2}$ reaches $(d+1)(z+1)$, we move \emph{candidate point} to center point of $B_2$ and $r_c$ is increased by a factor of $(2 + \frac{2}{C})$ to completly cover the new \emph{candidate point} and it's surronding ball.
 It is easy to see that $(2 + \frac{2}{C})r_c < \frac{\delta}{2}$ provided $C \ge 14$ and thus by Observation~\ref{obs:intersection} the property is not violated.
@@
 
-Let $c_p$ be a centerpoint of points in $B_2$, when $(z+1)(d+1)$ points have been added to $B_2$.
-We claim that with $B_2 = B(c_2, (2 + \frac{2}{C})r_c)$, $c_p$ can be chosen as the secondary point for $B_2(c_2, (2 + \frac{2}{C})r_c)$.
-%As it was mentioned earlier, if $c_p \in B_{2,2}^*$ then $r^* \le \frac{2\card{c_1c_p}}{C}$. Thus $B_{2,2}^* \subseteq B(c_2, \frac{2\card{c_1c_p}}{C})$.	% Sahand: Verify my modification:
+Let new \emph{candidate point} be $c_p$, centerpoint of points in $B_2$, when $(z+1)(d+1)$ points have been added to $B_2$.
+We claim that with $B_2 = B(c_2, (2 + \frac{2}{C})r_c)$, ball $B(c_p, \frac{2\card{c_1c_p}}{C})$ completly covered.
 If $c_p \in B_{2,2}^*$ then by Observation~\ref{obs:c+4}, $r^* \le \frac{\card{c_1c_p}}{C}$. Thus $B_{2,2}^* \subseteq B(c_p, \frac{2\card{c_1c_p}}{C})$.
@@
 \]
-%then $B_{2,2}^* \subseteq B(c_2, (1 + \frac{2}{C})r_c)$.	%Sahand: Verify my modification:
  then $B_{2,2}^* \subseteq B(c_p, (1 + \frac{2}{C})r_c) \subseteq B(c_2, (2 + \frac{2}{C})r_c)$.
-So $B_2(c_2, (2 + \frac{2}{C})r_c) \cap B_{2,2}^* \neq \emptyset$. Thus supposing $C \ge 14$ and by Observation~\ref{obs:intersection}, $B_2 \cap B_{2,1}^* = \emptyset$. Thus the claim follows.
+Thus supposing $C \ge 14$ and by Observation~\ref{obs:intersection}, $B_2 \cap B_{2,1}^* = \emptyset$.
+Thus the claim follows.
 
-At some point during the execution of Algorithm \ref{alg:case2}, the assumption about $c_2$ lying in $B_{2,2}^*$ might be contradicted when the buffer overflows.
+At some point during the execution of Algorithm \ref{alg:case2}, the assumption about $c_p \in B_{2,2}^*$ might be contradicted when the buffer overflows.
 We can then conclude that $c_2 \notin B_{2,2}^*$.
@@
 As shown in Observation~\ref{obs:intersection}, the ball $B_2(c_2, (2 + \frac{2}{C}) r_c)$ has nonempty intersection with exactly one of $B_{2, 1}^*$ and $B_{2, 2}^*$ (not all of its points can be outliers).
-Since the buffer overflowed, the assumption about the secondary point, $c_p$, being in $B_{2,2}^*$ must have been invalid.
+Since the buffer overflowed, the assumption about the candidate point, $c_p$, being in $B_{2,2}^*$ must have been invalid.
 By Corollary~\ref{cor:omitting-centerpoint} if $c_p$ is not covered, then circle $B_{2,1}^*$ leaves at least $z+1$ points of $B_2$ uncovered, and there will be more than $z$ outliers.
@@
 				\State $B_1 \gets B_1 \cup \set{c_2}$
-				\State remove $c_2$ from $B_2$	%Sahand: Is it clear that removing does not mean that B_2 is a dynamic data structure?
-Kiana: benazare man dynamic mishe!
-un bala ham ke goftam bayad begin and removing ro!
-vali gand nemikhore be 1-center?
 			\EndIf
-			\State $T \gets \mbox{Buffer} \cup B_2$
+			\State $T \gets \mbox{Buffer} \cup B_2 - {c_2}$
 			\State $\mbox{Buffer} \gets \emptyset, B_2 \gets \emptyset$
@@
 By the initial assumption about $p_1$, $B_1$ contains $B_{2,1}^*$ and $B_1'$ is a $\beta$-approximation for $B_{2,1}^*$.
-But for $B_2$ it may be the case that our assumption about the secondary point was incorrect or non-optimal, so $B_2'$ is not a good approximation for $B_{2,2}^*$.
+But for $B_2$ it may be the case that our assumption about the \emph{candidate point} was incorrect or non-optimal, so $B_2'$ is not a good approximation for $B_{2,2}^*$.
 There are two cases for $\card{B_2}$ to be considered.
-If $\card{B_2} < (z+1)(d+1)$, then we can try each point in $B_2 \cup \mbox{Buffer}$ as a candidate for the secondary point.
-If $\card{B_2} \ge (d+1)(z+1)$, then there is no need for points in $B_2$ to be considered, since for those points as secondary point, $B_1$ would be replaced by $B_u$ and $B_2$ would be empty.
+If $\card{B_2} < (z+1)(d+1)$, then we can try each point in $B_2 \cup \mbox{Buffer}$ as a candidate for the \emph{candidate point}.
+If $\card{B_2} \ge (d+1)(z+1)$, then there is no need for points in $B_2$ to be considered, since for those points as \emph{candidate point}, $B_1$ would be replaced by $B_u$ and $B_2$ would be empty.
 Thus it suffices to consider points of Buffer as candidates and compare them to the solution $(B_u, \emptyset)$.
@@
 \Function{Query}{}
-	\State solutions = [query $B_1$ $B_2$ Buffer]
+	\State solutions = [\Call{QuerySubdivision}{$B_1$ $B_2$ Buffer}]
 

### 2015-04-07 paper.tex
Using set definition
Removed redundant $p_{o_i}$ definitions from function "Known$r'$"; Fixed figure 2lt1 (\ge -> \le)

@@
 Our modification is on the transition part. 
-%For determining outliers, we just need to consider the points that may cause a transition so instead of exiting a node we ignore this point as an outlier. % Sahand: Chi shode? 
+%For determining outliers, we just need to consider the points that may cause a transition so instead of exiting a node we ignore this point as an outlier.
+% Sahand: Chi shode?
 %Kiana: benazaram in jomle bayad pak beshe chon ham vazeh ni ham tu badesh tozih dade mishe ghashang 
 %Behnam: be nazare man baiad bashe, chon baiad begim bara outlier ha faghat hamin noghteha moheman, in nokte mohemie!
+%Sahand: In chetore masalan?:
+Points that are covered by current solution can safely be ignored, as they do not cause any transitions in the state, and only those points that lie outside the solution are candidates for being an outlier.
 In each state the number of points that should be considered as outlier is unknown.
@@
 % Kiana: man be nazaram in if p_{o_i} arrives ha ro bardarim! niazi nis beheshun
-%kiana: ba in definition avalie movafeghin aya?
-"(Denote that $p_{o_1}=p_1$ and $p_{o_i, S'}$ is the $(n_{i-1}+1)^{st}$ point that arrives after $p_{o_{i-1},S}$ and does not lie in the candidate solution S)" fek konam algorithm khana beshe
-% man ba tarife kiana kheili moafegham
+% kiana: ba in definition avalie movafeghin aya? "
+% behnam: man ba tarife kiana kheili moafegham
+% sahand: done
 \Function{Known$r'$}{$\mathcal{P}, z, r'$}
@@
 		\State $CS \gets B(p_1,r')$.
-		\State $p_{o_2} \gets $ $(n_1+1)$\st point of $\mathcal{P}$ that arrives after $p_1$ and does not lie in the corresponding candidate solution.
+		\State $p_{o_2} \gets $ \Call{NthOutlier}{$n_1 + 1$}
 		\If{$p_{o_2}$ arrives}
-			\State $CS\gets$ the case of $p_{o_2} \in B_{2, 1}^*$ $\cup$ the case of $p_{o_2} \in B_{2,2}^*$.
+			\State $CS\gets$ the sub-case of $p_{o_2} \in B_{2, 1}^*$ $\cup$ the sub-case of $p_{o_2} \in B_{2,2}^*$.
 			\For{each case $S$}
-				\State $p_{o_3} \gets$ $(n_2+1)$\st point of $\mathcal{P}$ that arrives after $p_{o_2}$ and does not lie in the corresponding candidate solution.
-
+				\State $p_{o_3} \gets$ \Call{NthOutlier}{$n_2 + 1$}
 				\If{$p_{o_3}$ arrives} 
@@
 					\For {each sub-case $S'$} 
-						\State $p_{o_4} \gets$ $(n_3+1)$\st point of $\mathcal{P}$ that arrives after $p_{o_3}$ and does not lie in the corresponding candidate solution.
-
+						\State $p_{o_4} \gets$ \Call{NthOutlier}{$n_3 + 1$}
 						\If {$p_{o_4}$ arrives} 
 							\State Replace $S'$ with a new candidate solution.
-							\If{more than $n_4$ points arrive after $p_{o_4}$ that lie outside of the corresponding candidate solutions}
-								\State Abandon the solution
+							\State $p_{o_5} \gets$ \Call{NthOutlier}{$n_4 + 1$}
+							\If{$p_{o_5}$ arrives}
+								\State Abandon the solution.
 							\EndIf
 						\EndIf
-
 					\EndFor
@@
 		\EndIf
-
 		\State $\mathop{Sol}_{n_1,n_2,n_3,n_4} \gets$ the solution with the smallest larger radius, among all the sub-cases.
@@
 \end{algorithm}
+Here, \textproc{NthOutlier}$(n)$ returns the $n$\nth next point in $\mathcal{P}$ that does not lie in current candidate solution.
+
 \begin{theorem}
@@
 \label{cor:omitting-centerpoint}
-Given a set $\mathcal{P}$ of $k(d+1)$ points in $d$-dimensional Euclidean space, there is a point $c_p$, not necessarily in $\mathcal{P}$, that any convex object that does not cover $c_p$, leaves at least $k$ point of $\mathcal{P}$ uncovered.
+Given a set $\mathcal{P}$ of $k(d+1)$ points in $d$-dimensional Euclidean space, there is a point $c_p$, not necessarily in $\mathcal{P}$, that any convex object that does not cover $c_p$, leaves at least $k$ points of $\mathcal{P}$ uncovered.
 \end{cor}
@@
 			\ElsIf{$c_2$ is set}
-				\State $B_1 \gets B_1 \cup \set{c_2}$
+				\State $B_1 \gets B_1 \cup \set{c_2}$, $B_u \gets B_u \cup \set{c_2}$
 			\EndIf
-			\State $T \gets \mbox{Buffer} \cup B_2 - {c_2}$
+			\State $T \gets \mbox{Buffer} \cup B_2 - \set{c_2}$
 			\State $\mbox{Buffer} \gets \emptyset, B_2 \gets \emptyset$

### 2015-04-07 paper.tex
Adding refrence and some comment clean up

@@
 \label{subsec:smaller}
-Our idea in this section is derived from \cite[Sec.~3.1]{kim}.
+Our idea in this section is derived from \cite[Sec.~3.1]{ahn2014computing, kim2014improved}.
 To avoid duplication, we just outline the important parts of their algorithm and our modifications to it.
@@
 Our modification is on the transition part.
-%For determining outliers, we just need to consider the points that may cause a transition so instead of exiting a node we ignore this point as an outlier.
-% Sahand: Chi shode?
-%Kiana: benazaram in jomle bayad pak beshe chon ham vazeh ni ham tu badesh tozih dade mishe ghashang 
-%Behnam: be nazare man baiad bashe, chon baiad begim bara outlier ha faghat hamin noghteha moheman, in nokte mohemie!
-%Sahand: In chetore masalan?:
 Points that are covered by current solution can safely be ignored, as they do not cause any transitions in the state, and only those points that lie outside the solution are candidates for being an outlier.
@@
 \begin{algorithmic}
-% Kiana: man be nazaram in if p_{o_i} arrives ha ro bardarim! niazi nis beheshun
-% kiana: ba in definition avalie movafeghin aya? "
-% behnam: man ba tarife kiana kheili moafegham
-% sahand: done
 \Function{Known$r'$}{$\mathcal{P}, z, r'$}
@@
 \end{figure}
-%Behnam: tooie aks namosavit eshtebas baiad be delta/d koochiktar az C/2r* tabdil beshe
 
@@
 
-Let $B_1, B_2$ and $B_u$, be instances of a data structure that supports adding 
-% Kiana: and removing
-% Behnam: we don't need removing a point!
-a point and gives a $\beta$-approximation for $1$-center problem with $k$ outliers, for $k=0,\dots,z$ (This data structure, does not need to maintain all the points.
+Let $B_1, B_2$ and $B_u$, be instances of a data structure that supports adding a point and gives a $\beta$-approximation for $1$-center problem with $k$ outliers, for $k=0,\dots,z$ (This data structure, does not need to maintain all the points.
 Suppose that it has a buffer with length $(d+1)(z+1)$ that maintains the most recently added points).
@@
 Note that by $Q_{o}(zd,z,d)$ we mean the query time for the offline $1$-center problem with $z$ outlier in $d$ dimensions.
-The best known algorithm for $1$-center without outliers is $1.22$-approximation by \cite{chan}.
-The buffering framework introduced in \cite{zarrabi} can use this algorithm to achieve a $(1.22\sqrt{2})$-approximation ($1.22\sqrt{2} < 1.8$) for $1$-center problem with outliers.
+The best known algorithm for $1$-center without outliers is $1.22$-approximation by \cite{chan2014streaming, agarwal2010streaming}.
+The buffering framework introduced in \cite{zarrabi2009streaming} can use this algorithm to achieve a $(1.22\sqrt{2})$-approximation ($1.22\sqrt{2} < 1.8$) for $1$-center problem with outliers.
 

### 2015-04-10 paper.tex
added reference for centerpoint existance thm
Add one aditional refrence, correcting definition of \delta, replacing r* with r^* and some minor corrections

@@
 %Behnam: be nazaram alan bashe behtare, age doctor khast hazf mikone
-Define $\delta$ of two balls $B(c,r)$ and $B'(c',r')$, the minimum distance between $B$ and $B'$ which is equal to $\card{cc'}-r-r'$.
+Define $\delta$ of two balls $B(c,r)$ and $B'(c',r')$, the minimum distance between $B$ and $B'$ which is equal to $\max (0, \card{cc'}-r-r')$.
 
@@
 It returns the ball with the minimum radius.
-Note that, due to space limitations inherent to streaming data model, the body of for-all loop in function \textproc{$1$-centerWithOutliers} is run in parallel.
+Note that, due to space limitations inherent to streaming data model, the body of for-all loop in function \textproc{$1$-centerWithOutliers} run in parallel.
 
@@
 \begin{theorem}
-Given $\delta^* < C r*$ and $1.2r^* \le r' < (1.2 + 2\eps/3)r^*$, Algorithm~\ref{alg:smallc} uses $\cO (dz^3)$ space and returns a $(1.8+\eps)$-approximate solution.
+Given $\delta^* < C r^*$ and $1.2r^* \le r' < (1.2 + 2\eps/3)r^*$, Algorithm~\ref{alg:smallc} uses $\cO (dz^3)$ space and returns a $(1.8+\eps)$-approximate solution.
 Algorithm~\ref{alg:smallc} spends $\cO (dz^3)$ update time for each point in $\mathcal{P}$ and answers a query in $\cO (dz^3)$.
@@
 If $x_j \notin \mathcal{L}_{i-1}$, then it is certain that $x_j \ge l_{i - 1}$ (Observe that $l_i=ul_{i-1}$, for some $u\in \mathbb{N}$).
-Since the ball $B_1(p_1, l_{i-1})$, obtained from Algorithm~\ref{alg:1center}, has at most $z$ outliers, all the non-outlier points lie in the candidate balls in Algorithm~\ref{alg:smallc}.
+Since the ball $B_1(p_1, l_{i-1})$, obtained from Algorithm~\ref{alg:1center}, has at most $z$ outliers, all the non-outlier points of Algorithm~\ref{alg:1center}  lie in the candidate balls in Algorithm~\ref{alg:smallc}.
 %kiana: in jomle balai oke be nazaretun? 
@@
 \begin{prop}
-Any set $\mathcal{P}$ of points in $d$-dimensional Euclidean space has a centerpoint.\cite{edelsbrunner}
+Every finite set of points in $d$-dimensional Euclidean space admits a centerpoint.\cite{edelsbrunner1987algorithms}
 \end{prop}

### 2015-04-10 paper.tex
kiana_edition1

@@
 Let $B(c,r)$ denote a ball with center $c$ and radius $r$. We denote by $pq$ the straight line segment between these two points and by $\card{pq}$ the length of this segment. 
-%kiana: tarife delta ro chanja didam nagofte budan! benazaram ma ham mitunim nagim, baz age fek mikonin lazeme tarif konam
-%Behnam: be nazaram alan bashe behtare, age doctor khast hazf mikone
 Define $\delta$ of two balls $B(c,r)$ and $B'(c',r')$, the minimum distance between $B$ and $B'$ which is equal to $\max (0, \card{cc'}-r-r')$.
@@
 A point $c_p$, not necessarily in $\mathcal{P}$, is a \emph{centerpoint} of $\mathcal{P}$, if no open half-space that omits $c_p$ contains more than $\frac{dn}{d+1}$ points of $\mathcal{P}$.
-
-% kiana: man be nazaram in tarif painie vase center point behtare
-% Behnam: bahat moafegham
 
@@
 			\If{$\card{Q} = z + 1$}
-				\State Remove from $Q$ a point $q$ which is closest to $p$.
+				\State $q$ $\gets$ closest point to $p$ in $Q$
+				\State Remove $q$ from $Q$.
 				\State $B \gets B(p, \card{pq})$
@@
 It returns the ball with the minimum radius.
-Note that, due to space limitations inherent to streaming data model, the body of for-all loop in function \textproc{$1$-centerWithOutliers} run in parallel.
+Note that, due to space limitations inherent to streaming data model, the body of for-all loop in function \textproc{$1$-centerWithOutliers} runs in parallel.
 
@@
 Let $B^*(c^*, r^*)$ be the optimal solution.
-Clearly, there exists a point $p$ among the first $z+1$ points of $\mathcal{P}$, which is not an outlier in the optimal solution.
+Clearly, there exists a point $p$ among the first $z+1$ points of $\mathcal{P}$, which is not an outlier in the optimal solution (Figure~\ref{fig:1center}).
 Since $p \in B^*$, then $\card{pp'} \le 2r^*$ for any point $p'\in B^*$.
@@
 % Behnam: Aks be nazaram gooya nist ziad. va inke jaii behesh refrence dade nashode!
+%kiana: hagh ba behname. akse bedune refrence nadarim asan. montaha man benazaram kheili ehtiaji nis behesh asan
 
@@
 \begin{theorem}
-For any fixed $d > 1$, our single-pass data stream algorithm whose working space and update time are polynomial in $d$ and sub-linear in $n$ and returns two centers that guarantees a $(1.8 + \eps)$-approximation for the Euclidean $2$-center problem with outliers.
+For any fixed $d > 1$, our single-pass data stream algorithm whose working space and update time are polynomial in $d$ and sub-linear in $n$, returns two centers that guarantees a $(1.8 + \eps)$-approximation for the Euclidean $2$-center problem with outliers.
 \end{theorem}
@@
 
-In Section \ref{subsec:smaller}, we give a description of our algorithm for a given $r' > 0$ for the case where $\delta^* < C r^*$ and $1.2r^* \le r' < (1.2 + 2\eps/3)r^*$, our algorithm returns a $(1.8 + \eps)$-approximate solution.
+In Section \ref{subsec:smaller}, we give a description of our algorithm for a given $r' > 0$ for the case where $\delta^* < C r^*$ and $1.2r^* \le r' < (1.2 + 2\eps/3)r^*$, which returns a $(1.8 + \eps)$-approximate solution.
 We explain how to find such an $r'$ and present a full description of our algorithm for the case where $\delta^* < C r^*$ in Subsection~\ref{subsec:findr}.
@@
 		\State $CS \gets B(p_1,r')$.
-		\State $p_{o_2} \gets $ \Call{NthOutlier}{$n_1 + 1$}
+		\State $p_{o_2} \gets $ \Call{NthOutlier}{$n_1 + 1$, $p_1$}
 		\If{$p_{o_2}$ arrives}
@@
 			\For{each case $S$}
-				\State $p_{o_3} \gets$ \Call{NthOutlier}{$n_2 + 1$}
+				\State $p_{o_3} \gets$ \Call{NthOutlier}{$n_2 + 1$, $p_{o_2}$}
 				\If{$p_{o_3}$ arrives} 
@@
 					\For {each sub-case $S'$} 
-						\State $p_{o_4} \gets$ \Call{NthOutlier}{$n_3 + 1$}
+						\State $p_{o_4} \gets$ \Call{NthOutlier}{$n_3 + 1$, $p_{o_3}$}
 						\If {$p_{o_4}$ arrives} 
 							\State Replace $S'$ with a new candidate solution.
-							\State $p_{o_5} \gets$ \Call{NthOutlier}{$n_4 + 1$}
+							\State $p_{o_5} \gets$ \Call{NthOutlier}{$n_4 + 1$, $p_{o_4}$}
 							\If{$p_{o_5}$ arrives}
@@
 \end{algorithm}
-Here, \textproc{NthOutlier}$(n)$ returns the $n$\nth next point in $\mathcal{P}$ that does not lie in current candidate solution.
+Here, \textproc{NthOutlier}$(n,)$ returns the $n$\nth next point in $\mathcal{P}$ that does not lie in current candidate solution.
 

### 2015-04-10 paper.tex
last revision on comments

@@
 
+In all the algorithms given in this section it is assumed that $p_1$ is a non-outlier point.
+It is not hard to see that, this limitation can be remedied by considering $\cO(z)$ parallel instances of the algorithm, similar to Algorithm~\ref{alg:1center}.
+% Behnam: Move this to upper section, this assumption can be used for previous algorithm
+%kiana: Here is better. Since we do not have p_1 in section 4.2
+
 \begin{theorem}
@@
 \end{theorem}
-
-%--- from kim and ahn
-
-In all the algorithms given in this section it is assumed that $p_1$ is a non-outlier point.
-It is not hard to see that, this limitation can be remedied by considering $\cO(z)$ parallel instances of the algorithm, similar to Algorithm~\ref{alg:1center}.
-% Behnam: Move this to upper section, this assumption can be used for previous algorithm
 
@@
 To sum up, the modified algorithm is defined as follows:
+{
+\algrenewcommand\algorithmicindent{0.8em}%
 \begin{algorithm}
@@
 \end{algorithm}
-Here, \textproc{NthOutlier}$(n,)$ returns the $n$\nth next point in $\mathcal{P}$ that does not lie in current candidate solution.
+}
+Here, \textproc{NthOutlier}$(n,p)$ returns the $n$\nth point arriving after $p$ in $\mathcal{P}$ that does not lie in current candidate solution.
 
@@
 Suppose that $(B_{2, 1}^*(c_1^*, r_2^*), B_{2,2}^*(c_2^*, r_2^*))$ is an optimal solution for $2$-center problem. Consider $m$ as the midpoint of segment 
-$c_1^*c_2^*$.
+$c_1^*c_2^*$ (Figure~\ref{fig:2lt1}).
 Clearly, $B\left(m, \frac{\delta}{2} + 2r_2^*\right)$ covers both $B_{2, 1}^*$ and $B_{2,2}^*$. So it is a solution for $1$-center problem and the proof is complete.
@@
 
-%In this section, we explain how we get r' such that 1.2r^*  r' < (1.2 + 2\eps/3)r^*. The basic procedure works as follows:
-
 Our algorithm maintains $m=\ceil{\frac{1.2(3C+12)}{\eps}}$ candidate lengths.
@@
 By Observation~\ref{obs:2apr}, $l_i$ is a $(2C + 8)$-approximation for $r_2^*$.
-If we divide the interval $(0, 1.2 l_i]$ into $m$ equal segments, then length of each segment is at most $2/3 \eps r_2^*$ and the endpoints as candidates are $\mathcal{L}_i = \set{j \times t_i \provided j = 1, \dots, m}$ where $t_i = \frac{1.2 l_i}{m}$.
+If we divide the interval $(0, 1.2 l_i]$ into $m$ equal segments (Figure~\ref{fig:findr}), then length of each segment is at most $2/3 \eps r_2^*$ and the endpoints as candidates are $\mathcal{L}_i = \set{j \times t_i \provided j = 1, \dots, m}$ where $t_i = \frac{1.2 l_i}{m}$.
 The inequality $1.2 r_2^* \le j \times l_i \le (1.2 + \frac{2\eps}{3})r_2^*$ holds for at least one of these candidates.
@@
 
-%kiana: bacheha in paragraph paini kheili bad bud benazaram. man ye talashai rush kardam vali hanuzam benazaram jaye kar dare
-%Behnam: khoobe
 When the first non-zero radius is observed, $l_1$ is set.
@@
 But this is not achievable due to space limitations.
-To remedy
-%kiana, sahand: remedy?? really??
-this problem, note that if the candidate $x_j=j \times t_i \in \mathcal{L}_i$ is also in $\mathcal{L}_{i-1}$, there is no need to start Algorithm~\ref{alg:smallc} over and the current execution will be continued.
+To remedy this problem, note that if the candidate $x_j=j \times t_i \in \mathcal{L}_i$ is also in $\mathcal{L}_{i-1}$, there is no need to start Algorithm~\ref{alg:smallc} over and the current execution will be continued.
 If $x_j \notin \mathcal{L}_{i-1}$, then it is certain that $x_j \ge l_{i - 1}$ (Observe that $l_i=ul_{i-1}$, for some $u\in \mathbb{N}$).
-Since the ball $B_1(p_1, l_{i-1})$, obtained from Algorithm~\ref{alg:1center}, has at most $z$ outliers, all the non-outlier points of Algorithm~\ref{alg:1center}  lie in the candidate balls in Algorithm~\ref{alg:smallc}.
-%kiana: in jomle balai oke be nazaretun? 
-% Behnam: be nazare man gheire vazehe, be nazaram baiad begim hade aksar z ta biroonan, oonam oonaii ke too buffer algorithme 1 an
+Since the points that do not lie in the candidate solution are saved in the buffer used in Algorithm~\ref{alg:1center} (which has size at most $z$), all the non-outlier points of this algorithm lie in the candidate balls in Algorithm~\ref{alg:smallc}.
+%kiana: added the above sentece instead of the below
+%Since the ball $B_1(p_1, l_{i-1})$, obtained from Algorithm~\ref{alg:1center}, has at most $z$ outliers, all the non-outlier points of Algorithm~\ref{alg:1center}  lie in the candidate balls in Algorithm~\ref{alg:smallc}.
 These outliers have been stored in a buffer, so for the new candidate length, it suffices to execute Algorithm~\ref{alg:smallc} with only the outlier points of $B_1$.
@@
 
-%\begin{algorithmic}
-%\Procedure{add to furthest buffer(z+1)}{p}
-%	\State add p to buffer
-%	\If{size of buffer $> z+1$}
-%		\State remove nearest point from $p_1$
-%	\EndIf
-%\EndProcedure
-%\end{algorithmic}
-
 \begin{lemma}
@@
 Initially, $B_2$ is empty and $c_2$ and $r_c$ are not initialized.
-When an appropriate candidate is found, Algorithm~\ref{alg:case2} sets $c_2$ to that candidate and $r_c$ to $\frac{2\card{c_1c_2}}{C}$ and thereafter
-%kiana: bacheha kudumetun in kalame ro gozashtin? azash motmaeni? man hichja nadide budamesh
-points are added to $B_2$ only if they lie within $r_c$-radius of $c_2$.
+When an appropriate candidate is found, Algorithm~\ref{alg:case2} sets $c_2$ to that candidate and $r_c$ to $\frac{2\card{c_1c_2}}{C}$ and thereafter points are added to $B_2$ only if they lie within $r_c$-radius of $c_2$.
 At this point $c_2$ is considered as the \emph{candidate point} $c_p$.
@@
 
+{
+\algrenewcommand\algorithmicindent{0.8em}%
 \begin{algorithm}
@@
 \end{algorithm}
+}
 
@@
 Thus it suffices to consider points of Buffer as candidates and compare them to the solution $(B_u, \emptyset)$.
-
+{
+\algrenewcommand\algorithmicindent{0.8em}%
 \begin{algorithm}

### 2015-04-11 paper.tex
Minor modifications

@@
 
-Let $B_{2,1}^*(c_{2,1}^*, r_2^*)$ and $B_{2,2}^*(c_{2,2}^*, r_2^*)$ denote the optimal solution to $2$-center problem with $z$ outliers.
+Let $B_{2,1}^*(c_1^*, r_2^*)$ and $B_{2,2}^*(c_2^*, r_2^*)$ denote the optimal solution to $2$-center problem with $z$ outliers.
 By $\delta^*$ we denote the distance between $B_{2,1}^*$ and $B_{2,2}^*$, that is, $\delta^* = \max (0, \card{c_1^*c_2^*} - 2r^*)$.
@@
 
-Given an $n$-point set $\mathcal{P}$ in $d$ dimensions, a point $c \in R^d$ is called a \emph{centerpoint} of $\mathcal{P}$ if any halfspace containing $c$ contains at least $\ceil{\frac{n}{d + 1}}$ points of $\mathcal{P}$.
+Given an $n$-point set $\mathcal{P}$ in $d$-dimensional Euclidean space, a point $c \in \IR^d$ is called a \emph{centerpoint} of $\mathcal{P}$ if any halfspace containing $c$, contains at least $\ceil{\frac{n}{d + 1}}$ points of $\mathcal{P}$.
 In other words, any halfspace (or convex set) that avoids a centerpoint can contain at most $\floor{\frac{dn}{d + 1}}$ points of $\mathcal{P}$.
@@
 		\If{$p' \notin B$}
-			\State Insert $p'$ into $Q$
+			\State Insert $p'$ into $Q$.
 			\If{$\card{Q} = z + 1$}
@@
 Function \textproc{KnownPoint} in Algorithm~\ref{alg:1center}, takes a point $p$ as an argument which is guaranteed to be a non-outlier point in the optimal solution.
-To overcome the lack of knowledge about such a point, function \textproc{$1$-centerWithOutliers} tries each of the first $z+1$ points of the stream as a candidate for a non-outlier point and generates a ball for each, using function \textproc{KnownPoint}.
+To overcome the lack of knowledge about such a point, function \textproc{$1$\nobreakdash-centerWithOutliers} tries each of the first $z+1$ points of the stream as a candidate for a non-outlier point and generates a ball for each, using function \textproc{KnownPoint}.
 It returns the ball with the minimum radius.
@@
 % Behnam: Aks be nazaram gooya nist ziad. va inke jaii behesh refrence dade nashode!
-%kiana: hagh ba behname. akse bedune refrence nadarim asan. montaha man benazaram kheili ehtiaji nis behesh asan
+% Kiana: hagh ba behname. akse bedune refrence nadarim asan. montaha man benazaram kheili ehtiaji nis behesh asan 
+% Sahand: hazf konim ya pishnehadi baray e behboodesh darid?
 
 The space complexity of Algorithm~\ref{alg:1center} is $\cO(z^2 + zd)$, the update time is $\cO (z \log z + zd)$ and the query time is $\cO (z)$.
-If a non-outlier point $p$ is known then the space, update time and query time complexity of algorithm can be reduced by a factor of $z$.
+If a non-outlier point $p$ is known then the space, update time and query time complexities of Algorithm~\ref{alg:1center} can be reduced by a factor of $z$.
 
@@
 In all the algorithms given in this section it is assumed that $p_1$ is a non-outlier point.
-It is not hard to see that, this limitation can be remedied by considering $\cO(z)$ parallel instances of the algorithm, similar to Algorithm~\ref{alg:1center}.
+It is not hard to see that, this limitation can be overcome by considering $\cO(z)$ parallel instances of the algorithm, similar to Algorithm~\ref{alg:1center}.
 % Behnam: Move this to upper section, this assumption can be used for previous algorithm
@@
 \label{subsec:smaller}
-Our idea in this section is derived from \cite[Sec.~3.1]{ahn2014computing, kim2014improved}.
+Our idea in this section is derived from \cite{ahn2014computing, kim2014improved}.
 To avoid duplication, we just outline the important parts of their algorithm and our modifications to it.
@@
 Points that are covered by current solution can safely be ignored, as they do not cause any transitions in the state, and only those points that lie outside the solution are candidates for being an outlier.
-In each state the number of points that should be considered as outlier is unknown.
+In each state the number of points that should be considered as outliers is unknown.
 So all the possible choices should be considered.
@@
 	\For{$(n_1, \dots, n_4) \gets \set{(n_1, \dots, n_4) \provided \sum n_i=z}$}
-		\State $CS \gets B(p_1,r')$.
+		\State $CS \gets B(p_1,r')$
 		\State $p_{o_2} \gets $ \Call{NthOutlier}{$n_1 + 1$, $p_1$}
 		\If{$p_{o_2}$ arrives}
-			\State $CS\gets$ the sub-case of $p_{o_2} \in B_{2, 1}^*$ $\cup$ the sub-case of $p_{o_2} \in B_{2,2}^*$.
+			\State $CS\gets [ \text{the sub-case of $p_{o_2} \in B_{2, 1}^*$} ] \cup [ \text{the sub-case of $p_{o_2} \in B_{2,2}^*$} ]$
 			\For{each case $S$}
@@
 				\If{$p_{o_3}$ arrives} 
-					\State $CS\gets CS\setminus S$ $\cup$ the sub-case of $p_{o_3} \in B_{2, 1}^*$ $\cup$ the sub-case of $p_{o_3} \in B_{2,2}^*$.
+					\State $CS\gets CS\setminus S \cup [ \text{the sub-case of $p_{o_3} \in B_{2, 1}^*$} ] \cup [ \text{the sub-case of $p_{o_3} \in B_{2,2}^*$}]$
 					\For {each sub-case $S'$} 
@@
 \label{lem:1lt2}
-A $1$-center optimal solution with $z$ outliers for a streaming set of points is also an upper bound for the $2$-center optimal solution with $z$ outliers.
+A $1$-center optimal solution with $z$ outliers for a set of points is also an upper bound for the $2$-center optimal solution with $z$ outliers.
 \end{lemma}
@@
 But this is not achievable due to space limitations.
-To remedy this problem, note that if the candidate $x_j=j \times t_i \in \mathcal{L}_i$ is also in $\mathcal{L}_{i-1}$, there is no need to start Algorithm~\ref{alg:smallc} over and the current execution will be continued.
+To overcome this problem, note that if the candidate $x_j=j \times t_i \in \mathcal{L}_i$ is also in $\mathcal{L}_{i-1}$, there is no need to start Algorithm~\ref{alg:smallc} over and the current execution will be continued.
 If $x_j \notin \mathcal{L}_{i-1}$, then it is certain that $x_j \ge l_{i - 1}$ (Observe that $l_i=ul_{i-1}$, for some $u\in \mathbb{N}$).
 Since the points that do not lie in the candidate solution are saved in the buffer used in Algorithm~\ref{alg:1center} (which has size at most $z$), all the non-outlier points of this algorithm lie in the candidate balls in Algorithm~\ref{alg:smallc}.
-%kiana: added the above sentece instead of the below
-%Since the ball $B_1(p_1, l_{i-1})$, obtained from Algorithm~\ref{alg:1center}, has at most $z$ outliers, all the non-outlier points of Algorithm~\ref{alg:1center}  lie in the candidate balls in Algorithm~\ref{alg:smallc}.
 These outliers have been stored in a buffer, so for the new candidate length, it suffices to execute Algorithm~\ref{alg:smallc} with only the outlier points of $B_1$.
@@
 Function \textproc{AddTo$B_1$} is used to add a point $p$ to $B_1$.
-The point will be added only if the point is within $\delta$-radius of the center $c_1$, where $\delta$, calculated by Algorithm~\ref{alg:case2}, is $\frac{C}{C+4}\card{qc_1}$ and $q$ is the $(z+1)$\nth furthest point from $c_1$.
+The point will be added only if the point is within $\delta$\nobreakdash-radius of the center $c_1$, where $\delta$, calculated by Algorithm~\ref{alg:case2}, is $\frac{C}{C+4}\card{qc_1}$ and $q$ is the $(z+1)$\nth furthest point from $c_1$.
 By Lemma~\ref{lem:(z+1)-furthest}, $\delta$ is a lower bound for $\delta^*$.
@@
 		\State \Return{true}
-	\Else
+	\EndIf
 	\State \Return{false}
-	\EndIf
 \EndFunction
@@
 Initially, $B_2$ is empty and $c_2$ and $r_c$ are not initialized.
-When an appropriate candidate is found, Algorithm~\ref{alg:case2} sets $c_2$ to that candidate and $r_c$ to $\frac{2\card{c_1c_2}}{C}$ and thereafter points are added to $B_2$ only if they lie within $r_c$-radius of $c_2$.
-At this point $c_2$ is considered as the \emph{candidate point} $c_p$.
+When an appropriate candidate is found, Algorithm~\ref{alg:case2} sets $c_2$ to that candidate and $r_c$ to $\frac{2\card{c_1c_2}}{C}$ and after that, points are added to $B_2$ only if they lie within $r_c$-radius of $c_2$.
+At this point $c_2$ is considered as the candidate point $c_p$.
 Clearly the subdivision property for $B_2$ holds initially when $B_2$ consists of the single point $c_2$.
@@
 
-When $\card{B_2}$ reaches $(d+1)(z+1)$, we move \emph{candidate point} to center point of $B_2$ and $r_c$ is increased by a factor of $(2 + \frac{2}{C})$ to completly cover the new \emph{candidate point} and it's surronding ball.
+When $\card{B_2}$ reaches $(d+1)(z+1)$, we move candidate point to center point of $B_2$ and $r_c$ is increased by a factor of $(2 + \frac{2}{C})$ to completly cover the new candidate point and it's surronding ball.
 It is easy to see that $(2 + \frac{2}{C})r_c < \frac{\delta}{2}$ provided $C \ge 14$ and thus by Observation~\ref{obs:intersection} the property is not violated.
@@
 \begin{prop}
-Every finite set of points in $d$-dimensional Euclidean space admits a centerpoint.\cite{edelsbrunner1987algorithms}
+Every finite set of points in $d$\nobreakdash-dimensional Euclidean space admits a centerpoint.\cite{edelsbrunner1987algorithms}
 \end{prop}
@@
 \label{cor:omitting-centerpoint}
-Given a set $\mathcal{P}$ of $k(d+1)$ points in $d$-dimensional Euclidean space, there is a point $c_p$, not necessarily in $\mathcal{P}$, that any convex object that does not cover $c_p$, leaves at least $k$ points of $\mathcal{P}$ uncovered.
+Given a set $\mathcal{P}$ of $k(d+1)$ points in $d$\nobreakdash-dimensional Euclidean space, there is a point $c_p$, not necessarily in $\mathcal{P}$, that any convex object that does not cover $c_p$, leaves at least $k$ points of $\mathcal{P}$ uncovered.
 \end{cor}
 
-Let new \emph{candidate point} be $c_p$, centerpoint of points in $B_2$, when $(z+1)(d+1)$ points have been added to $B_2$.
+Let the new candidate point be the centerpoint of points in $B_2$, when $(z+1)(d+1)$ points have been added to $B_2$.
 We claim that with $B_2 = B(c_2, (2 + \frac{2}{C})r_c)$, ball $B(c_p, \frac{2\card{c_1c_p}}{C})$ completly covered.
@@
 
-At some point during the execution of Algorithm \ref{alg:case2}, the assumption about $c_p \in B_{2,2}^*$ might be contradicted when the buffer overflows.
-We can then conclude that $c_2 \notin B_{2,2}^*$.
+At some point during the execution of Algorithm \ref{alg:case2}, the assumption about $c_p \in B_{2,2}^*$ might be contradicted when the buffer overflows. We can then conclude that
+% Sahand: Verify this:
+%$c_2 \notin B_{2,2}^*$.
+ $c_p \notin B_{2,2}^*$.
 At this point, behavior of Algorithm~\ref{alg:case2} depends on size of $B_2$ relative to $(d+1)(z+1)$:
@@
 	\If{!\Call{AddTo$B_1$}{$p$} and !\Call{AddTo$B_2$}{$p$}}
+% Sahand: is ! a familiar notation for CS people? should we use \neg? or not?
 		\State add $p$ to Buffer
@@
 					\If{\Call{AddTo$B_1$}{$p$}}
-						\State remove $p$ from $T$
+						\State Remove $p$ from $T$.
 					\EndIf
@@
 By the initial assumption about $p_1$, $B_1$ contains $B_{2,1}^*$ and $B_1'$ is a $\beta$-approximation for $B_{2,1}^*$.
-But for $B_2$ it may be the case that our assumption about the \emph{candidate point} was incorrect or non-optimal, so $B_2'$ is not a good approximation for $B_{2,2}^*$.
+But for $B_2$ it may be the case that our assumption about the candidate point was incorrect or non-optimal, so $B_2'$ is not a good approximation for $B_{2,2}^*$.
 There are two cases for $\card{B_2}$ to be considered.
-If $\card{B_2} < (z+1)(d+1)$, then we can try each point in $B_2 \cup \mbox{Buffer}$ as a candidate for the \emph{candidate point}.
-If $\card{B_2} \ge (d+1)(z+1)$, then there is no need for points in $B_2$ to be considered, since for those points as \emph{candidate point}, $B_1$ would be replaced by $B_u$ and $B_2$ would be empty.
+If $\card{B_2} < (z+1)(d+1)$, then we can try each point in $B_2 \cup \mbox{Buffer}$ as a candidate for the candidate point.
+If $\card{B_2} \ge (d+1)(z+1)$, then there is no need for points in $B_2$ to be considered, since for those points as candidate point, $B_1$ would be replaced by $B_u$ and $B_2$ would be empty.
 Thus it suffices to consider points of Buffer as candidates and compare them to the solution $(B_u, \emptyset)$.
@@
 			\If{not \Call{AddTo$B_2$}{$p$}}
-				\State add $p$ to Buffer
+				\State Add $p$ to Buffer.
 			\EndIf
 		\EndFor
-		\State add \Call{QuerySubdivision}{$B_1$, $B_2$, Buffer} to solutions
+		\State Add \Call{QuerySubdivision}{$B_1$, $B_2$, Buffer} to solutions.
 	\EndFor
@@
 		\State $r \gets \max(1-\mbox{center}(B_1, k), 1-\mbox{center}(B_2, z - \card{\mbox{Buffer}} - k))$
-		\State add $r$ to solutions
+		\State Add $r$ to solutions.
 	\EndFor
@@
 Query time in Algorithm~\ref{alg:query} is $\cO(zQ(n,z,d) + dz(dz+zQ_o(zd,z,d)))$ and it returns two centers that guarantee a $(1.8 + \eps)$-approximation for $2$-center problem with outliers.
+% Sahand: Our analysis requires that $\beta \le 1.8+\eps$.
+Should we mention that somewhere?
+Someone might suspect using a worse approximation algorithm for 1-center he can achieve the same result with better time complexity.
 \end{theorem}

### 2015-04-14 paper.tex
began writing introcuction: motivations

@@
 \section{Introduction}
+Metric $k$-center problem -- covering a set of point with $k$ congruent balls of minimum radius -- is a fundamental problem in computer science and has various applications in data mining and image processing.
+One of $k$-center problem variants is $k$-center with $z$-outlier which finds $k$ congruent balls with minimum radius covering all but $z$ points of a point set.
+In real world applications, due to commonness of noisy data, it is important to consider outlier points.
+Because even a small number of outliers ($\cO(k)$) can increase the radius of $k$-center problem unboundedly.
+In this paper we focus on streaming data model.
+In the streaming data model, input arrives as a sequence and there is not enough space to keep the whole data set.
+Algorithms in this model have limitations in space (typically sub-linear in input size) and processing time per item.
+This model is specially suitable for massive data sets, due the its sub-linear space complexity \cite{aggarwal2007data}.
+
+In this paper our concern is about $2$-center problem in high dimensional Euclidean space.
+The formal definition of problem is as follows.
+Given sequence $\mathcal{S}$ of points in $d$ dimensional (for arbitrarily large $d$) Euclidean space, find two congruent balls of minimum radius, covering all but at most $z$ points.
 

### 2015-04-14 paper.tex
introduction

@@
 Given sequence $\mathcal{S}$ of points in $d$ dimensional (for arbitrarily large $d$) Euclidean space, find two congruent balls of minimum radius, covering all but at most $z$ points.
+
+The problem without outliers (i.e., $z=0$) in general (Euclidean) space can not be approximated with a smaller than factor $2$ ($1.822$) unless $\mathbf{P}=\mathbf{NP}$ \cite{kim:6}.
+Gonzalez showed a $2$-approximation algorithm for this problem \cite{kim:17}.
+For small $k$ and $d$, there are more efficient algorithms.
+For Euclidean $1$-center in fixed dimensions, Chazelle \etal{} gave a linear algorithm \cite{kim:12}.
+For $2$-center in the plane the best known algorithm, runs in $\cO(n \log^2 n \log^2 \log n)$ and linear space, given by Chan \cite{kim:8}.
+
+In streaming data model, Guha \cite{kim:18}, in parallel with McCutchen \etal{} \cite{kim:22} gave $(2+\eps)$-approximation for $k$-center without outliers.
+For small $k$, better algorithms are known. For fixed $d$, there exists an $\eps$-coreset for $1$-center with $\cO(1 / \eps^{\frac{d-1}{2}})$ space.
+For higher dimensions, Agarwal gave a $\frac{1+\sqrt{3}}{2}$-approximation for $1$-center problem, and Chan \cite{kim:10} reduced its approximation factor to $1.22$, by an improved analysis.
+For $k=2$, Ahn \etal{} \cite{ahn14} gave a $(2+\eps)$-approximation algorithm using $\cO(\frac{d}{\eps})$ space, which was improved for Euclidean spaces by Kim \etal{} \cite{kim14} to a $(1.8+\eps)$-approximation algorithm, using the same space.
+
+For the problem of $k$-center with outliers, Charikar \etal{} \cite{zarrabi:8} gives the first offline algorithm with approximation factor $3$ ($4$), where the candidate center points of the centers can be enumerated (otherwise).
+For small $k$, there are better results known.
+$1$-center with $z$ outliers can be solved in $\cO(n \log z + z^{3} n^{\eps})$, for any $\eps > 0$, using Matou{\v{s}}ek's framework \cite{on-geometric-optimization-with-few-violated-constraints}.
+Agarwal \cite{an efficient algorithm for 2d euclidean 2-center with outliers} gives an algorithm with running time $\cO(n z^{7} \log^3 z)$ for $2$-center problem in $\IR^2$.
+
+For the problem of $k$-center with $z$ outliers in streaming data model, McCutchen \etal{} \cite{zarrabi:14} (using idea in Charikar \etal{} \cite{zarrabi:8} as subroutine) give a $(3+\eps)$-approximation ($(4+\eps)$-approximation, depending on the used subroutine) algorithm using $\cO(\frac{zk}{\eps})$ space.
+In special case of $k=1$ in fixed dimensions, there exists a streaming algorithm with $\cO(\frac{z}{\eps^{\cO(d)}})$ space \cite{zarrabi:4, zarrabi:15}.
+For Euclidean spaces, Zarrabi-Zadeh gave $(1.22 \sqrt{2})$\nobreakdash-approximation for $1$-center with $z$ outliers running in $\cO(?)$ space.
+
+In this paper we first give a simple $2$-approximation algorithm for $1$-center problem with space complexity $\cO(z^2 + zd)$.
+We then show a $(1.8 + \eps)$-approximation streaming algorithm for $2$-center with $z$ outliers in Euclidean space, with space complexity polynomial in $z$ and $d$ and sub-linear in $n$.
 

### 2015-04-14 paper.tex
Add Conclusion section

--- 2015-04-14 paper.tex
@@
 \title{Streaming $2$-Center with Outliers in High Dimension}
-\author{Hamid~Zarrabi-Zadeh\thanks{Department of Computer Engineering, 
+\author{Hamid~Zarrabi-Zadeh\thanks{De`partment of Computer Engineering, 
 	Sharif University of Technology. 
@@
 Given sequence $\mathcal{S}$ of points in $d$ dimensional (for arbitrarily large $d$) Euclidean space, find two congruent balls of minimum radius, covering all but at most $z$ points.
+
+The problem without outliers (i.e., $z=0$) in general (Euclidean) space can not be approximated with a smaller than factor $2$ ($1.822$) unless $\mathbf{P}=\mathbf{NP}$ \cite{bern1996approximation}.
+Gonzalez showed a $2$-approximation algorithm for this problem \cite{gonzalez1985clustering}.
+For small $k$ and $d$, there are more efficient algorithms.
+For Euclidean $1$-center in fixed dimensions, Chazelle~\etal gave a linear algorithm \cite{chazelle1996linear}.
+For $2$-center in the plane the best known algorithm, runs in $\cO(n \log^2 n \log^2 \log n)$ and linear space, given by Chan \cite{chan1999more}.
+
+In streaming data model, Guha \cite{guha2009tight}, in parallel with McCutchen~\etal \cite{mccutchen2008streaming} gave $(2+\eps)$-approximation for $k$-center without outliers.
+For small $k$, better algorithms are known. For fixed $d$, there exists an $\eps$-coreset for $1$-center with $\cO(1 / \eps^{\frac{d-1}{2}})$ space.
+For higher dimensions, Agarwal gave a $(\frac{1+\sqrt{3}}{2})$-approximation for $1$-center problem, and Chan \cite{chan2004faster} reduced its approximation factor to $1.22$, by an improved analysis.
+For $k=2$, Ahn~\etal ~\cite{ahn2014computing} gave a $(2+\eps)$-approximation algorithm using $\cO(\frac{d}{\eps})$ space, which was improved for Euclidean spaces by Kim ~\etal \cite{kim2014improved} to a $(1.8+\eps)$-approximation algorithm, using the same space.
+
+For the problem of $k$-center with outliers, Charikar ~\etal \cite{charikar2001algorithms} gives the first offline algorithm with approximation factor $3$ ($4$), where the candidate center points of the centers can be enumerated (otherwise).
+For small $k$, there are better results known.
+$1$-center with $z$ outliers can be solved in $\cO(n \log z + z^{3} n^{\eps})$, for any $\eps > 0$, using Matou{\v{s}}ek's framework \cite{matouvsek1995geometric}.
+Agarwal \cite{agarwal2008efficient} gives an algorithm with running time $\cO(n z^{7} \log^3 z)$ for $2$-center problem in $\IR^2$.
+
+For the problem of $k$-center with $z$ outliers in streaming data model, McCutchen ~\etal \cite{mccutchen2008streaming} (using idea in Charikar ~\etal \cite{charikar2001algorithms} as subroutine) give a $(3+\eps)$-approximation ($(4+\eps)$-approximation, depending on the used subroutine) algorithm using $\cO(\frac{zk}{\eps})$ space.
+In special case of $k=1$ in fixed dimensions, there exists a streaming algorithm with $\cO(\frac{z}{\eps^{\cO(d)}})$ space \cite{agarwal2007space, zarrabi2011almost}.
+For Euclidean spaces, Zarrabi-Zadeh \cite{zarrabi2009streaming} gave $(1.22 \sqrt{2})$\nobreakdash-approximation for $1$-center with $z$ outliers running in $\cO(?)$ space.
+
+In this paper we first give a simple $2$-approximation algorithm for $1$-center problem with space complexity $\cO(z^2 + zd)$.
+We then show a $(1.8 + \eps)$-approximation streaming algorithm for $2$-center with $z$ outliers in Euclidean space, with space complexity polynomial in $z$ and $d$ and sub-linear in $n$.
 
@@
 
+%---------------------------- Conclusions ---------------------
+
+\section{Conclusions}
+\label{sec:conc}
+
+In this paper, we presented an $(1.8 + \eps)$-approximation straming algorithm for $2$-center with $z$-outlier in euclidean space, which improves previous $3+\eps$-approximation algorithm by Charikar~\etal ~\cite{mccutchen2008streaming}.
+It remains open whether there can be any improvements in algorithm approximation factor.
+It is intresting problem to find an algorithm with better approximation factor and/or space complexity.
+It is also intresting to see if this algorithm can be generalized to a $k$-center with outliers in streaming data model with the same approximation factor (even for small $k$).
+
 %--------------- BIBS --------------------

### 2015-04-15 paper.tex
revised introduction

--- 2015-04-14 paper.tex
@@
 Metric $k$-center problem -- covering a set of point with $k$ congruent balls of minimum radius -- is a fundamental problem in computer science and has various applications in data mining and image processing.
-One of $k$-center problem variants is $k$-center with $z$-outlier which finds $k$ congruent balls with minimum radius covering all but $z$ points of a point set.
+One of $k$\nobreakdash-center problem variants is $k$-center with $z$-outlier which finds $k$ congruent balls with minimum radius covering all but $z$ points of a point set.
 In real world applications, due to commonness of noisy data, it is important to consider outlier points.
-Because even a small number of outliers ($\cO(k)$) can increase the radius of $k$-center problem unboundedly.
+Because even a small number of outliers ($\cO(k)$) can increase the radius of $k$\nobreakdash-center problem unboundedly.
 In this paper we focus on streaming data model.
@@
 The formal definition of problem is as follows.
-Given sequence $\mathcal{S}$ of points in $d$ dimensional (for arbitrarily large $d$) Euclidean space, find two congruent balls of minimum radius, covering all but at most $z$ points.
+Given sequence $\mathcal{S}$ of points in $d$ dimensional Euclidean space (for arbitrarily large $d$), find two congruent balls of minimum radius, covering all but at most $z$ points.
+
+$k$-center problem without outliers (i.e., $z=0$) in general (Euclidean) space can not be approximated with a smaller factor than $2$ ($1.822$), unless $\mathbf{P}=\mathbf{NP}$ \cite{bern1996approximation}.
+Gonzalez showed a $2$-approximation algorithm for this problem \cite{gonzalez1985clustering}.
+For small $k$ and $d$, there are more efficient algorithms.
+For Euclidean $1$-center in fixed dimensions, Chazelle~\etal{} gave a linear algorithm \cite{chazelle1996linear}.
+For $2$\nobreakdash-center in the plane the best known algorithm, given by Chan \cite{chan1999more}, runs in $\cO(n \log^2 n \log^2 \log n)$ and linear space.
+
+In streaming data model, Guha \cite{guha2009tight}, in parallel with McCutchen~\etal{} \cite{mccutchen2008streaming} gave $(2+\eps)$-approximation for $k$-center without outliers.
+For small $k$, better algorithms are known. For fixed $d$, there exists an $\eps$\nobreakdash-coreset for $1$-center with $\cO(\eps^{-\frac{d-1}{2}})$ space.
+For higher dimensions, Agarwal \cite{agarwal2010streaming} gave a $(\frac{1+\sqrt{3}}{2})$-approximation for $1$\nobreakdash-center problem, and Chan \cite{chan2004faster} reduced its approximation factor to $1.22$, by an improved analysis.
+For $k=2$, Ahn~\etal{}~\cite{ahn2014computing} gave a $(2+\eps)$-approximation algorithm using $\cO(\frac{d}{\eps})$ space, which was improved for Euclidean spaces by Kim~\etal{} \cite{kim2014improved} to a $(1.8+\eps)$-approximation algorithm, using the same space.
+
+For the problem of $k$-center with outliers, Charikar~\etal{} \cite{charikar2001algorithms} gives the first offline algorithm with approximation factor $3$ ($4$), where the candidate center points of the centers can be enumerated (otherwise).
+For small $k$, there are better results known.
+$1$-center with $z$ outliers can be solved in $\cO(n \log n + z^{3} n^{\eps})$, for any $\eps > 0$, using Matou{\v{s}}ek's framework \cite{matouvsek1995geometric}.
+Agarwal \cite{agarwal2008efficient} gives a randomized $\cO(n z^{7} \log^3 z)$-time algorithm for $2$-center problem in $\IR^2$.
+
+For the problem of $k$-center with $z$ outliers in streaming data model, McCutchen~\etal{} \cite{mccutchen2008streaming} (using idea in Charikar~\etal{} \cite{charikar2001algorithms} as subroutine) give a $(3+\eps)$-approximation ($(4+\eps)$-approximation, depending on the used subroutine) algorithm using $\cO(\frac{zk}{\eps})$ space.
+In special case of $k=1$ in fixed dimensions, there is a streaming $\cO(\frac{z}{\eps^{\cO(d)}})$-space algorithm \cite{agarwal2007space, zarrabi2011almost}.
+For Euclidean spaces, Zarrabi-Zadeh \cite{zarrabi2009streaming} gave $(1.22 \sqrt{2})$\nobreakdash-approximation for $1$-center with $z$ outliers running in $\cO(?)$ space.
+
+In this paper we first give a simple $2$-approximation algorithm for $1$-center problem with space complexity $\cO(z^2 + zd)$.
+We then show a $(1.8 + \eps)$-approximation streaming algorithm for $2$-center with $z$ outliers in Euclidean space, with space complexity polynomial in $z$ and $d$ and sub-linear in $n$.
 
@@
 
+%---------------------------- Conclusions ---------------------
+
+\section{Conclusions}
+\label{sec:conc}
+
+In this paper, we presented a $(1.8 + \eps)$-approximation streaming algorithm for $2$-center problem with outliers in Euclidean space, which improves previous $(3+\eps)$-approximation algorithm by Charikar~\etal~\cite{mccutchen2008streaming}.
+It remains open whether there can be any improvements in approximation factor.
+It is an interesting problem to find an algorithm with better approximation factor or space complexity.
+It is also interesting to see if the ideas in this paper can be applied to $k$-center problem with outliers in streaming data model, even for small $k$.
+
 %--------------- BIBS --------------------

### 2015-04-15 paper.tex
Revising orders and refrences, adding exact space complexity of our algorithm

@@
 $k$-center problem without outliers (i.e., $z=0$) in general (Euclidean) space can not be approximated with a smaller factor than $2$ ($1.822$), unless $\mathbf{P}=\mathbf{NP}$ \cite{bern1996approximation}.
-Gonzalez showed a $2$-approximation algorithm for this problem \cite{gonzalez1985clustering}.
+Gonzalez~\cite{gonzalez1985clustering} showed a $2$-approximation algorithm for general case of the problem.
 For small $k$ and $d$, there are more efficient algorithms.
-For Euclidean $1$-center in fixed dimensions, Chazelle~\etal{} gave a linear algorithm \cite{chazelle1996linear}.
+For Euclidean $1$-center in fixed dimensions, Chazelle~\etal~\cite{chazelle1996linear} gave a linear algorithm.
 For $2$\nobreakdash-center in the plane the best known algorithm, given by Chan \cite{chan1999more}, runs in $\cO(n \log^2 n \log^2 \log n)$ and linear space.
 
-In streaming data model, Guha \cite{guha2009tight}, in parallel with McCutchen~\etal{} \cite{mccutchen2008streaming} gave $(2+\eps)$-approximation for $k$-center without outliers.
-For small $k$, better algorithms are known. For fixed $d$, there exists an $\eps$\nobreakdash-coreset for $1$-center with $\cO(\eps^{-\frac{d-1}{2}})$ space.
-For higher dimensions, Agarwal \cite{agarwal2010streaming} gave a $(\frac{1+\sqrt{3}}{2})$-approximation for $1$\nobreakdash-center problem, and Chan \cite{chan2004faster} reduced its approximation factor to $1.22$, by an improved analysis.
-For $k=2$, Ahn~\etal{}~\cite{ahn2014computing} gave a $(2+\eps)$-approximation algorithm using $\cO(\frac{d}{\eps})$ space, which was improved for Euclidean spaces by Kim~\etal{} \cite{kim2014improved} to a $(1.8+\eps)$-approximation algorithm, using the same space.
+In streaming data model, Guha \cite{guha2009tight}, in parallel with McCutchen~\etal~\cite{mccutchen2008streaming} gave $(2+\eps)$-approximation for $k$-center without outliers with $\cO((\frac{dk}{\eps}) \log(\frac{1}{\eps}))$ space.
+For small $k$, better algorithms are known. For fixed $d$, there exists an $\eps$\nobreakdash-coreset for $1$-center with $\cO(\frac{1}{\eps^{\frac{d-1}{2}}})$ space.
+For higher dimensions, Agarwal~\etal~\cite{agarwal2010streaming} gave a $(\frac{1+\sqrt{3}}{2})$-approximation for $1$\nobreakdash-center problem with $\cO((\frac{d}{\eps^3})\log(\frac{1}{\eps}))$ space and and update time, and Chan~\etal~\cite{chan2014streaming} reduced its approximation factor to $1.22$, by an improved analysis.
+For $k=2$, Ahn~\etal~\cite{ahn2014computing} gave a $(2+\eps)$-approximation algorithm using $\cO(\frac{d}{\eps})$ space and update time, which was improved for Euclidean spaces by Kim~\etal~\cite{kim2014improved} to a $(1.8+\eps)$-approximation algorithm, using the same space and update time complexity.
 
-For the problem of $k$-center with outliers, Charikar~\etal{} \cite{charikar2001algorithms} gives the first offline algorithm with approximation factor $3$ ($4$), where the candidate center points of the centers can be enumerated (otherwise).
+For the problem of $k$-center with outliers, Charikar~\etal~\cite{charikar2001algorithms} gives the first offline algorithm with approximation factor $3$ ($4$), where the candidate center points of the centers can be enumerated (otherwise).
 For small $k$, there are better results known.
@@
 
-For the problem of $k$-center with $z$ outliers in streaming data model, McCutchen~\etal{} \cite{mccutchen2008streaming} (using idea in Charikar~\etal{} \cite{charikar2001algorithms} as subroutine) give a $(3+\eps)$-approximation ($(4+\eps)$-approximation, depending on the used subroutine) algorithm using $\cO(\frac{zk}{\eps})$ space.
+For the problem of $k$-center with $z$ outliers in streaming data model, McCutchen~\etal~\cite{mccutchen2008streaming} (using idea in Charikar~\etal \cite{charikar2001algorithms} as subroutine) give a $(3+\eps)$-approximation ($(4+\eps)$-approximation, depending on the used subroutine) algorithm using $\cO(\frac{zk}{\eps})$ space.
 In special case of $k=1$ in fixed dimensions, there is a streaming $\cO(\frac{z}{\eps^{\cO(d)}})$-space algorithm \cite{agarwal2007space, zarrabi2011almost}.
-For Euclidean spaces, Zarrabi-Zadeh \cite{zarrabi2009streaming} gave $(1.22 \sqrt{2})$\nobreakdash-approximation for $1$-center with $z$ outliers running in $\cO(?)$ space.
+For Euclidean spaces, Zarrabi-Zadeh \cite{zarrabi2009streaming} gave $(1.22 \times \sqrt{2})$\nobreakdash-approximation for $1$-center with $z$ outliers running in $\cO(dz^3 + (\frac{d}{\eps^3})\log(\frac{1}{\eps}))$ space and poly$(d)$ update time .
 
@@
 Let $B_{2,1}^*(c_1^*, r_2^*)$ and $B_{2,2}^*(c_2^*, r_2^*)$ denote the optimal solution to $2$-center problem with $z$ outliers.
-By $\delta^*$ we denote the distance between $B_{2,1}^*$ and $B_{2,2}^*$, that is, $\delta^* = \max (0, \card{c_1^*c_2^*} - 2r^*)$.
+By $\delta^*$, denote the distance between $B_{2,1}^*$ and $B_{2,2}^*$, that is, $\delta^* = \max (0, \card{c_1^*c_2^*} - 2r^*)$.
 
@@
 In each step one or many of the states can be valid and their algorithm considers all of them in parallel.
-In each state, we have two balls.
+In each state, there exist at most two balls.
 A transition between the states occurs whenever a point not covered by any of the two balls has arrived in the stream.
@@
 Our algorithm maintains $m=\ceil{\frac{1.2(3C+12)}{\eps}}$ candidate lengths.
-For each candidate length $t$, we assume that $r' = t$ and use it to run Algorithm~\ref{alg:smallc}.
-We use Algorithm~\ref{alg:1center} to estimate $r'$.
+For each candidate length $t$, assume that $r' = t$ and use it to run Algorithm~\ref{alg:smallc}.
+Algorithm~\ref{alg:1center} is used to estimate $r'$.
 Let $k_i$ be the $i$\nth non-zero radius calculated by the algorithm.
@@
 By Observation~\ref{obs:2apr}, $l_i$ is a $(2C + 8)$-approximation for $r_2^*$.
-If we divide the interval $(0, 1.2 l_i]$ into $m$ equal segments (Figure~\ref{fig:findr}), then length of each segment is at most $2/3 \eps r_2^*$ and the endpoints as candidates are $\mathcal{L}_i = \set{j \times t_i \provided j = 1, \dots, m}$ where $t_i = \frac{1.2 l_i}{m}$.
+If the interval $(0, 1.2 l_i]$ divides into $m$ equal segments (Figure~\ref{fig:findr}), then length of each segment is at most $2/3 \eps r_2^*$ and the endpoints as candidates are $\mathcal{L}_i = \set{j \times t_i \provided j = 1, \dots, m}$ where $t_i = \frac{1.2 l_i}{m}$.
 The inequality $1.2 r_2^* \le j \times l_i \le (1.2 + \frac{2\eps}{3})r_2^*$ holds for at least one of these candidates.
@@
 
-When $\card{B_2}$ reaches $(d+1)(z+1)$, we move candidate point to center point of $B_2$ and $r_c$ is increased by a factor of $(2 + \frac{2}{C})$ to completly cover the new candidate point and it's surronding ball.
+When $\card{B_2}$ reaches $(d+1)(z+1)$, the candidate point changes to center point of $B_2$ and $r_c$ is increased by a factor of $(2 + \frac{2}{C})$ to completly cover the new candidate point and it's surronding ball.
 It is easy to see that $(2 + \frac{2}{C})r_c < \frac{\delta}{2}$ provided $C \ge 14$ and thus by Observation~\ref{obs:intersection} the property is not violated.
@@
 The best known algorithm for $1$-center without outliers is $1.22$-approximation by \cite{chan2014streaming, agarwal2010streaming}.
-The buffering framework introduced in \cite{zarrabi2009streaming} can use this algorithm to achieve a $(1.22\sqrt{2})$-approximation ($1.22\sqrt{2} < 1.8$) for $1$-center problem with outliers.
+The buffering framework introduced in \cite{zarrabi2009streaming} with $\cO(dz^3 + (\frac{d}{\eps^3})\log(\frac{1}{\eps}))$ space complexity, can be used with this algorithm as subroutine to achieve a $(1.22\sqrt{2})$-approximation ($1.22\sqrt{2} < 1.8$) for $1$-center problem with outliers.
 
@@
 
+with space complexity of Zarrabi-zadeh \cite{zarrabi2009streaming} algorithm, the space complexity of our algorithm would be $\cO(\frac{dz^4}{\eps} + \frac{dz}{\eps^3})$.
+
 %---------------------------- Conclusions ---------------------

### 2015-04-17 paper.tex
abstract + parallel + revision

@@
 \begin{abstract}
-
+In this paper, we study the $2$-center streaming problem with $z$ outliers in a general space, which means finding two congruent balls covering all the points except $z$ outliers in a streaming work-space.
+Before considering this problem, we provide a  $2$-approximation algorithm for $1$-center with $z$ outliers in a general space.
+Our algorithm for the $2$-center problem uses an update time and working space polynomial in $d$ and sub-linear in $n$ to calculate a $(1.8+\eps)$-approximation solution.
 \end{abstract}
@@
 In this paper we focus on streaming data model.
-In the streaming data model, input arrives as a sequence and there is not enough space to keep the whole data set.
+In the streaming data model, input data arrives as a sequence and there is not enough space to keep the whole data set.
 Algorithms in this model have limitations in space (typically sub-linear in input size) and processing time per item.
-This model is specially suitable for massive data sets, due the its sub-linear space complexity \cite{aggarwal2007data}.
+This model is specially suitable for massive data sets, due to its sub-linear space complexity \cite{aggarwal2007data}.
 
-In this paper our concern is about $2$-center problem in high dimensional Euclidean space.
-The formal definition of problem is as follows.
-Given sequence $\mathcal{S}$ of points in $d$ dimensional Euclidean space (for arbitrarily large $d$), find two congruent balls of minimum radius, covering all but at most $z$ points.
-
-$k$-center problem without outliers (i.e., $z=0$) in general (Euclidean) space can not be approximated with a smaller factor than $2$ ($1.822$), unless $\mathbf{P}=\mathbf{NP}$ \cite{bern1996approximation}.
+The $k$-center problem without outliers (i.e., $z=0$) in general (Euclidean) space can not be approximated with a smaller factor than $2$ ($1.822$), unless $\mathbf{P}=\mathbf{NP}$ \cite{bern1996approximation}.
 Gonzalez~\cite{gonzalez1985clustering} showed a $2$-approximation algorithm for general case of the problem.
@@
 
-For the problem of $k$-center with $z$ outliers in streaming data model, McCutchen~\etal~\cite{mccutchen2008streaming} (using idea in Charikar~\etal \cite{charikar2001algorithms} as subroutine) give a $(3+\eps)$-approximation ($(4+\eps)$-approximation, depending on the used subroutine) algorithm using $\cO(\frac{zk}{\eps})$ space.
+For the problem of $k$-center with $z$ outliers in streaming data model, McCutchen~\etal~\cite{mccutchen2008streaming} (using the idea in Charikar~\etal \cite{charikar2001algorithms} as subroutine) give a $(3+\eps)$-approximation ($(4+\eps)$-approximation, depending on the used subroutine) algorithm using $\cO(\frac{zk}{\eps})$ space.
 In special case of $k=1$ in fixed dimensions, there is a streaming $\cO(\frac{z}{\eps^{\cO(d)}})$-space algorithm \cite{agarwal2007space, zarrabi2011almost}.
@@
 
-In this paper we first give a simple $2$-approximation algorithm for $1$-center problem with space complexity $\cO(z^2 + zd)$.
-We then show a $(1.8 + \eps)$-approximation streaming algorithm for $2$-center with $z$ outliers in Euclidean space, with space complexity polynomial in $z$ and $d$ and sub-linear in $n$.
+In this paper our concern is about $2$-center problem in high dimensional Euclidean space.
+The formal definition of problem is as follows.
+Given sequence $\mathcal{S}$ of points in $d$ dimensional Euclidean space (for arbitrarily large $d$), find two congruent balls of minimum radius, covering all but at most $z$ points.
+In Section~\ref{sec:2apr}, we give a simple $2$-approximation algorithm for $1$-center problem with space complexity $\cO(z^2 + zd)$.
+In the next section, we show a $(1.8 + \eps)$-approximation streaming algorithm for $2$-center with $z$ outliers in Euclidean space, and its space complexity is polynomial in $z$ and $d$ and sub-linear in $n$.
+In Section~\ref{subsec:smaller} we run $z + 1$ parallel instances of the algorithm in order to find the first non-outlier point.
+%Kiana: man ino neveshtam vali manzuretun in bud raje be parallel budan az in bishtar begim yani? yekam ziadi tekrar nemishe?
+
+% Kiana: I think first we should mention what others have done and then start declaring our problem. That's why I changed the location of the previous paragraph.
 
@@
 \section{A Simple $2$-Approximation Algorithm for $1$-Center with Outliers}
+\label{sec:2apr}
 
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=17em]{figs/one-center}
-	\caption{Output of Algorithm~\ref{alg:1center}}
-	\label{fig:1center}
-\end{figure}
+%
+%\begin{figure}[h]
+%	\centering
+%	\includegraphics[width=17em]{figs/one-center}
+%	\caption{Output of Algorithm~\ref{alg:1center}}
+%	\label{fig:1center}
+%\end{figure}
 
@@
 % Sahand: hazf konim ya pishnehadi baray e behboodesh darid?
+% Kiana: Man be nazaram vaghean chon kheili az idehaye basic ham baraye gheire streaming hamine va osulan idash yekam badihitowre hazf beshe.
+felan commentesh kardam age nazaretun chize digei bud avazesh konin.
 
@@
 
-When $\card{B_2}$ reaches $(d+1)(z+1)$, the candidate point changes to center point of $B_2$ and $r_c$ is increased by a factor of $(2 + \frac{2}{C})$ to completly cover the new candidate point and it's surronding ball.
+When $\card{B_2}$ reaches $(d+1)(z+1)$, the candidate point changes to center point of $B_2$ and $r_c$ is increased by a factor of $(2 + \frac{2}{C})$ to completely cover the new candidate point and it's surrounding ball.
 It is easy to see that $(2 + \frac{2}{C})r_c < \frac{\delta}{2}$ provided $C \ge 14$ and thus by Observation~\ref{obs:intersection} the property is not violated.
@@
 Let the new candidate point be the centerpoint of points in $B_2$, when $(z+1)(d+1)$ points have been added to $B_2$.
-We claim that with $B_2 = B(c_2, (2 + \frac{2}{C})r_c)$, ball $B(c_p, \frac{2\card{c_1c_p}}{C})$ completly covered.
+We claim that with $B_2 = B(c_2, (2 + \frac{2}{C})r_c)$, ball $B(c_p, \frac{2\card{c_1c_p}}{C})$ completely covered.
 If $c_p \in B_{2,2}^*$ then by Observation~\ref{obs:c+4}, $r^* \le \frac{\card{c_1c_p}}{C}$. Thus $B_{2,2}^* \subseteq B(c_p, \frac{2\card{c_1c_p}}{C})$.
@@
 {
-\algrenewcommand\algorithmicindent{0.8em}%
+\algrenewcommand\algorithmicindent{0.6em}%
 \begin{algorithm}
@@
 	\State $\delta \gets \frac{C}{C+4} \card{c_1q}$
-	\If{!\Call{AddTo$B_1$}{$p$} and !\Call{AddTo$B_2$}{$p$}}
+	\If{\Call{AddTo$B_1$}{$p$} = False and  \Call{AddTo$B_2$}{$p$} = False}
 % Sahand: is ! a familiar notation for CS people? should we use \neg? or not?
+% Kiana: Agree, What about this one?
 		\State add $p$ to Buffer
@@
 Someone might suspect using a worse approximation algorithm for 1-center he can achieve the same result with better time complexity.
+% Kiana: I don't think so.
 \end{theorem}

### 2015-04-17 paper.tex
Changing general space to euclician space

@@
 \begin{abstract}
-In this paper, we study the $2$-center streaming problem with $z$ outliers in a general space, which means finding two congruent balls covering all the points except $z$ outliers in a streaming work-space.
-Before considering this problem, we provide a  $2$-approximation algorithm for $1$-center with $z$ outliers in a general space.
+In this paper, we study the $2$-center streaming problem with $z$ outliers in a euclidean space, which means finding two congruent balls covering all the points except $z$ outliers in a streaming work-space.
+Before considering this problem, we provide a  $2$-approximation algorithm for $1$-center with $z$ outliers in a euclidean space.
 Our algorithm for the $2$-center problem uses an update time and working space polynomial in $d$ and sub-linear in $n$ to calculate a $(1.8+\eps)$-approximation solution.

### 2015-04-17 paper.tex
changing euclidean to Euclidean

--- 2015-04-17 paper.tex
@@
 \begin{abstract}
-In this paper, we study the $2$-center streaming problem with $z$ outliers in a general space, which means finding two congruent balls covering all the points except $z$ outliers in a streaming work-space.
-Before considering this problem, we provide a  $2$-approximation algorithm for $1$-center with $z$ outliers in a general space.
+In this paper, we study the $2$-center streaming problem with $z$ outliers in a Euclidean space, which means finding two congruent balls covering all the points except $z$ outliers in a streaming work-space.
+Before considering this problem, we provide a  $2$-approximation algorithm for $1$-center with $z$ outliers in a Euclidean space.
 Our algorithm for the $2$-center problem uses an update time and working space polynomial in $d$ and sub-linear in $n$ to calculate a $(1.8+\eps)$-approximation solution.

### 2015-04-26 paper - Copy.tex
paper reorganized
Passed to Behnam for completing the proofs, etc.

--- 2015-04-17 paper.tex
@@
 
-\usepackage{graphicx}
-\usepackage{caption,subcaption}
+\usepackage{caption,subcaption,cleveref}
 
-\usepackage[noend]{algpseudocode}
+\usepackage{algorithm}
+\usepackage[noend]{algorithmic}
 
 %----------------------- Environments --------------------------
+
 \newtheorem{corollary}{Corollary} 
 \newtheorem{problem}{Problem}
-\newtheorem{algorithm}{Algorithm}
+%\newtheorem{algorithm}{Algorithm}
 \newtheorem{definition}{Definition}
 
+%------------------------ Algorithm -----------------------------
+
+\newcommand{\textproc}{\textsc}
+\newcommand{\Call}[2]{\textsc{#1}(#2)}
+\renewcommand{\algorithmicforall}{{\bf for each}}
+
 %------------------------ Paper Notations -----------------------------
+
 \DeclareMathOperator*{\argmin}{arg\,min}
@@
 %-------------------------- Notations ------------------------------------
+
 \newcommand{\cO}{\ensuremath{{\rm O}}}
@@
 \newcommand{\card}[1]{\left|{#1}\right|}
+\newcommand{\len}[1]{\|{#1}\|}
 \newcommand{\setcomp}[1]{\overline{#1}}
@@
 %----------------------- Title -----------------------------------------
-\title{Streaming $2$-Center with Outliers in High Dimension}
-\author{Hamid~Zarrabi-Zadeh\thanks{Department of Computer Engineering, 
+
+\title{A Streaming Algorithm for $2$-Center with Outliers in High Dimensions}
+\author{Behnam~Hatami\thanks{Department of Computer Engineering, 
+	Sharif University of Technology.
+	{\tt hatami@ce.sharif.edu}}
+	\and 
+	Hamid~Zarrabi-Zadeh\thanks{Department of Computer Engineering, 
 	Sharif University of Technology.
 	{\tt zarrabi@sharif.edu}}
-	\and 
 }
@@
 %------------------------------ Text -------------------------------------
+
 \begin{document}
@@
 \begin{abstract}
-In this paper, we study the $2$-center streaming problem with $z$ outliers in a general space, which means finding two congruent balls covering all the points except $z$ outliers in a streaming work-space.
-Before considering this problem, we provide a  $2$-approximation algorithm for $1$-center with $z$ outliers in a general space.
-Our algorithm for the $2$-center problem uses an update time and working space polynomial in $d$ and sub-linear in $n$ to calculate a $(1.8+\eps)$-approximation solution.
+We study the Euclidean $2$-center problem with outliers in the data stream model. 
+Given a stream of points in arbitrary $d$ dimensions, the goal is to find two congruent balls 
+of minimum radius covering all but $z$ points. 
+We provide a $(1.8+\eps)$-approximation streaming algorithm for the problem, %2-center with outliers,
+improving upon the previous $(3 + \eps)$-approximation algorithm available for the problem.
+The space complexity and update time of our algorithm is $\poly(d, z, 1/\eps)$,
+independent of the size of the stream.
 \end{abstract}
@@
 \section{Introduction}
-Metric $k$-center problem -- covering a set of point with $k$ congruent balls of minimum radius -- is a fundamental problem in computer science and has various applications in data mining and image processing.
+The $k$-center problem---covering a set of points 
+using $k$ congruent balls of minimum radius---is a fundamental problem 
+in computer science, having many applications in various areas
+such as data mining, unsupervised learning, statistics, and image processing.
 One of $k$\nobreakdash-center problem variants is $k$-center with $z$-outlier which finds $k$ congruent balls with minimum radius covering all but $z$ points of a point set.
@@
 \label{sec:pre}
-Let $B(c,r)$ denote a ball with center $c$ and radius $r$. We denote by $pq$ the straight line segment between these two points and by $\card{pq}$ the length of this segment. 
-Define $\delta$ of two balls $B(c,r)$ and $B'(c',r')$, the minimum distance between $B$ and $B'$ which is equal to $\max (0, \card{cc'}-r-r')$.
+Let $B(c,r)$ denote a ball of radius $r$ centered at $c$. 
+We denote by $pq$ the straight line segment between $p$ and $q$,
+and denote by $\len{pq}$ the length of this segment. 
+Given two balls $B(c,r)$ and $B'(c',r')$, 
+we define their \emph{distance} to be $\delta = \max \set{0, \len{cc'}-r-r'}$.
 
 Let $B_{2,1}^*(c_1^*, r_2^*)$ and $B_{2,2}^*(c_2^*, r_2^*)$ denote the optimal solution to $2$-center problem with $z$ outliers.
-By $\delta^*$, denote the distance between $B_{2,1}^*$ and $B_{2,2}^*$, that is, $\delta^* = \max (0, \card{c_1^*c_2^*} - 2r^*)$.
+By $\delta^*$, denote the distance between $B_{2,1}^*$ and $B_{2,2}^*$, that is, $\delta^* = \max (0, \len{c_1^*c_2^*} - 2r^*)$.
 
-Two congruent balls $B_1$ and $B_2$ with radius $r$ are said to be \emph{$C$-separated}, whenever the distance $\delta$ of two balls is at least $Cr$.
+Two congruent balls $B_1$ and $B_2$ with radius $r$ are said to be \emph{$\alpha$-separated}, whenever the distance $\delta$ of two balls is at least $Cr$.
 
-%Let $\mathcal{P}$ be a configuration of $n$ point in $d$-dimensional Euclidean space.
-A point $c_p$, not necessarily in $\mathcal{P}$, is a \emph{centerpoint} of $\mathcal{P}$, if no open half-space that omits $c_p$ contains more than $\frac{dn}{d+1}$ points of $\mathcal{P}$.
+%Let $P$ be a configuration of $n$ point in $d$-dimensional Euclidean space.
+A point $c_p$, not necessarily in $P$, is a \emph{centerpoint} of $P$, if no open half-space that omits $c_p$ contains more than $\frac{dn}{d+1}$ points of $P$.
 
-Given an $n$-point set $\mathcal{P}$ in $d$-dimensional Euclidean space, a point $c \in \IR^d$ is called a \emph{centerpoint} of $\mathcal{P}$ if any halfspace containing $c$, contains at least $\ceil{\frac{n}{d + 1}}$ points of $\mathcal{P}$.
-In other words, any halfspace (or convex set) that avoids a centerpoint can contain at most $\floor{\frac{dn}{d + 1}}$ points of $\mathcal{P}$.
+Given an $n$-point set $P$ in $d$-dimensional Euclidean space, a point $c \in \IR^d$ is called a \emph{centerpoint} of $P$ if any halfspace containing $c$, contains at least $\ceil{\frac{n}{d + 1}}$ points of $P$.
+In other words, any halfspace (or convex set) that avoids a centerpoint can contain at most $\floor{\frac{dn}{d + 1}}$ points of $P$.
 
@@
 
-\section{A Simple $2$-Approximation Algorithm for $1$-Center with Outliers}
-\label{sec:2apr}
+\section{A $2$-Approximation for $1$-Center with Outliers}
+\label{sec:1-center}
+
+We warm up by presenting a simple $2$-approximation streaming algorithm
+for the $1$-center problem with outliers.
+The pseudocode is provided in \Cref{alg:1-center}.
+It receives as input a stream of points, $P$,
+and a special point $c \in P$ which is guaranteed to be 
+a non-outlier in the optimal solution.
+The algorithm returns a ball $B$ containing all but $z$ points of $P$.
+%We will show later how to remove this assumption.
+
+%\begin{algorithm}
+%\caption{\sc 1-Center$(P, z)$} 
+%\algsetup{indent=1.5em}
+%\label{alg:1-center}
+%\begin{algorithmic}[1]
+%
+%	%\STATE Let $p_i$ denote the elements of $P$, for $i \in \set{1, \dots, n}$.
+%	\STATE let $p_1, \ldots, p_n$ be the points of $P$
+%	\FOR{$i = 1, \dots, z+1$}
+%		%\STATE move $p_i$ to the front of $P$ %is a non-outlier point in optimal solution.
+%		\STATE $B_i \gets$ \Call{1-Center-Special}{$P, z,p_i$}
+%	\ENDFOR
+%	%\STATE $i^* \gets \argmin_{i=1}^{z+1} r_i$
+%	\RETURN smallest ball among $\set{B_1, \ldots, B_{z+1}}$
+%
+%\end{algorithmic}
+%\end{algorithm}
 
 \begin{algorithm}
-\label{alg:1center}
-\leavevmode
-\begin{algorithmic}
-\Function{$1$-centerWithOutliers}{$\mathcal{P}, z$}
-	\State Let $p_i$ denote the elements of $\mathcal{P}$, for $i \in \set{1, \dots, n}$.
-	\ForAll{$i \gets 1, \dots, z+1$}
-		\State Assume $p_i$ is a non-outlier point in optimal solution.
-		\State $B(c_i, r_i) \gets$ \Call{KnownPoint}{$\mathcal{P}, z, p_i$}
-	\EndFor
-	\State $i^* \gets \argmin_{i=1}^{z+1} r_i$
-	\State \Return $B(c_{i^*}, r_{i^*})$
-\EndFunction
-\Statex
-\Function{KnownPoint}{$\mathcal{P}, z, p$}
-	\State $B \gets B(p, 0)$
-	\State $Q \gets \emptyset$
-	\For{$p'$ in $\mathcal{P}$}
-		\If{$p' \notin B$}
-			\State Insert $p'$ into $Q$.
-			\If{$\card{Q} = z + 1$}
-				\State $q$ $\gets$ closest point to $p$ in $Q$
-				\State Remove $q$ from $Q$.
-				\State $B \gets B(p, \card{pq})$
-			\EndIf
-		\EndIf
-	\EndFor
-	\State \Return{B}
-\EndFunction
+\caption{\sc 1-Center$(P, c, z)$} 
+\algsetup{indent=1.5em}
+\label{alg:1-center}
+\begin{algorithmic}[1]
+	%\STATE {$\triangleright$ $c$ is a non-outlier point in the optimal solution}
+	\STATE $B \gets B(c, 0)$
+	\STATE $Q \gets \emptyset$
+	\FORALL {$p$ in $P$}
+		\IF {$p \notin B$}
+			\STATE insert $p$ into $Q$
+			\IF {$|Q| = z + 1$}
+				\STATE $q$ $\gets$ closest point to $c$ in $Q$
+				\STATE remove $q$ from $Q$
+				\STATE $B \gets B(c, \len{cq})$
+			\ENDIF
+		\ENDIF
+	\ENDFOR
+	\RETURN {B}
 \end{algorithmic}
 \end{algorithm}
-Function \textproc{KnownPoint} in Algorithm~\ref{alg:1center}, takes a point $p$ as an argument which is guaranteed to be a non-outlier point in the optimal solution.
-To overcome the lack of knowledge about such a point, function \textproc{$1$\nobreakdash-centerWithOutliers} tries each of the first $z+1$ points of the stream as a candidate for a non-outlier point and generates a ball for each, using function \textproc{KnownPoint}.
-It returns the ball with the minimum radius.
-Note that, due to space limitations inherent to streaming data model, the body of for-all loop in function \textproc{$1$-centerWithOutliers} runs in parallel.
 
-\begin{theorem}
-Algorithm~\ref{alg:1center} is a $2$-approximation algorithm for $1$-center problem with $z$ outliers, in any dimension.
+%The function \textproc{1-Center-Special} in \Cref{alg:1-center-special}, 
+%takes as input a point $c$ which is guaranteed to be a non-outlier point in the optimal solution. 
+%To overcome the lack of knowledge about such a point, 
+%function \textproc{1-Center} in \Cref{alg:1-center}
+%tries each of the first $z+1$ points of the stream as a candidate for a non-outlier point and 
+%generates a ball for each, using function \textproc{1-Center-Special}. 
+%It returns the ball with the minimum radius. 
+%Note that, in the streaming model, %due to space limitations inherent to streaming data model, 
+%the body of the for loop in function \textproc{1-Center} runs in parallel.
+%To run function \textproc{1-Center} in the data stream model,
+%we run the body of the for loop in $z+1$ parallel streaming instances.
+
+\begin{theorem} \label{thm:1-center-special}
+	Algorithm~\ref{alg:1-center} computes a $2$-approximation to
+	the $1$-center problem with $z$ outliers,
+	provided that a non-outlier point in the optimal solution in given.
 \end{theorem}
@@
 \begin{proof}
-Let $B^*(c^*, r^*)$ be the optimal solution.
-Clearly, there exists a point $p$ among the first $z+1$ points of $\mathcal{P}$, which is not an outlier in the optimal solution (Figure~\ref{fig:1center}).
-Since $p \in B^*$, then $\card{pp'} \le 2r^*$ for any point $p'\in B^*$.
-There is at least one point $q'$ among the $(z+1)$-furthest points from $p$ that is not an outlier in the optimal solution.
-Thus $\card{pq} \le \card{pq'} \le 2r^*$ and Algorithm~\ref{alg:1center} returns a valid solution of radius at most $2r^*$.
-So the proof is complete.
+Let $B^*(c^*, r^*)$ be the optimal solution,
+and $c$ be a non-outlier point in the optimal solution.
+Since $c$ is covered by $B^*$,
+for all points $p \in B^*$, we have
+$\len{cp} \le \len{cc^*} + \len{c^*p} \le 2r^*$.
+Among the $z+1$ points furthest from $c$,
+there is at least one point $q$ which is not outlier in the optimal solution,
+and therefore, is contained in $B^*$
+(see \Cref{fig:1center}). 
+Thus, $\len{cq} \le 2r^*$,
+and therefore, the ball $B(c, \len{cq})$ returned by Algorithm~\ref{alg:1-center} 
+is a 2-approximation. 
 \end{proof}
 
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=12em]{figs/one-center}
+	\caption{Proof of \Cref{thm:1-center-special}}
+	\label{fig:1center}
+\end{figure}
+
+In \Cref{alg:1-center}, 
+we had an assumption that a point $c$ is known in advance
+which is guaranteed to be a non-outlier in the optimal solution. 
+To overcome the lack of knowledge about such a point, 
+we run $z+1$ instances of \Cref{alg:1-center} in parallel,
+each of which is given as $c$ one of the first $z + 1$ points in the stream.
+Clearly, there exists a point among the first $z+1$ points of $P$, 
+which is not an outlier in the optimal solution.
+Therefore, the smallest ball among the $z+1$ balls computed in parallel
+is always within factor 2 of the optimal solution. % by \Cref{thm:1-center-special}.
+Since the space complexity of Algorithm~\ref{alg:1-center} for one instance is $\cO(zd)$, 
+and its update time is $\cO (zd \log z)$, % and the query time is $\cO (z)$.
+we get the following.
+
+\begin{theorem} \label{thm:1-center}
+	Given a stream of points in $d$ dimensions,
+	we can maintain a 2-approximation to the 1-center with $z$ outliers
+	in $\cO(z^2d)$ space and $\cO (z^2d\log z)$ update time.
+\end{theorem}
+
+%function \textproc{1-Center} in \Cref{alg:1-center}
+%tries each of the first $z+1$ points of the stream as a candidate for a non-outlier point and 
+%generates a ball for each, using function \textproc{1-Center-Special}. 
+%It returns the ball with the minimum radius. 
+%Note that, in the streaming model, %due to space limitations inherent to streaming data model, 
+%the body of the for loop in function \textproc{1-Center} runs in parallel.
+%To run function \textproc{1-Center} in the data stream model,
+%we run the body of the for loop in $z+1$ parallel streaming instances.
 %
-%\begin{figure}[h]
-%	\centering
-%	\includegraphics[width=17em]{figs/one-center}
-%	\caption{Output of Algorithm~\ref{alg:1center}}
-%	\label{fig:1center}
-%\end{figure}
-
-% Behnam: Aks be nazaram gooya nist ziad. va inke jaii behesh refrence dade nashode!
-% Kiana: hagh ba behname. akse bedune refrence nadarim asan. montaha man benazaram kheili ehtiaji nis behesh asan 
-% Sahand: hazf konim ya pishnehadi baray e behboodesh darid?
-% Kiana: Man be nazaram vaghean chon kheili az idehaye basic ham baraye gheire streaming hamine va osulan idash yekam badihitowre hazf beshe.
-felan commentesh kardam age nazaretun chize digei bud avazesh konin.
-
-The space complexity of Algorithm~\ref{alg:1center} is $\cO(z^2 + zd)$, the update time is $\cO (z \log z + zd)$ and the query time is $\cO (z)$.
-If a non-outlier point $p$ is known then the space, update time and query time complexities of Algorithm~\ref{alg:1center} can be reduced by a factor of $z$.
+%The space complexity of Algorithm~\ref{alg:1center} is $\cO(z^2 + zd)$, the update time is $\cO (z \log z + zd)$ and the query time is $\cO (z)$.
+%If a non-outlier point $p$ is known then the space, update time and query time complexities of Algorithm~\ref{alg:1center} can be reduced by a factor of $z$.
 
@@
 \section{The $2$-Center Problem with $z$ Outliers}
+\label{sec:2-center}
 
-In all the algorithms given in this section it is assumed that $p_1$ is a non-outlier point.
-It is not hard to see that, this limitation can be overcome by considering $\cO(z)$ parallel instances of the algorithm, similar to Algorithm~\ref{alg:1center}.
+In this section, we provide a $(1.8 + \eps)$-approximation algorithm
+for the 2-center with outliers.
+In all algorithms presented in this section,
+we assume that the first point of the stream, $p_1$, is a non-outlier. 
+This assumption can be easily removed by considering $z + 1$ parallel instances of the algorithm, 
+similar to what we did in \Cref{sec:1-center}.
 % Behnam: Move this to upper section, this assumption can be used for previous algorithm
@@
 
-In Section \ref{subsec:smaller}, we give a description of our algorithm for a given $r' > 0$ for the case where $\delta^* < C r^*$ and $1.2r^* \le r' < (1.2 + 2\eps/3)r^*$, which returns a $(1.8 + \eps)$-approximate solution.
-We explain how to find such an $r'$ and present a full description of our algorithm for the case where $\delta^* < C r^*$ in Subsection~\ref{subsec:findr}.
-Then we inspect the case where $\delta^* \ge C r^*$ in Subsection~\ref{subsec:bigger}.
+In Section \ref{subsec:smaller}, we give a description of our algorithm for a given $r' > 0$ for the case where $\delta^* < \alpha r^*$ and $1.2r^* \le r' < (1.2 + 2\eps/3)r^*$, which returns a $(1.8 + \eps)$-approximate solution.
+We explain how to find such an $r'$ and present a full description of our algorithm for the case where $\delta^* < \alpha r^*$ in Subsection~\ref{subsec:findr}.
+Then we inspect the case where $\delta^* \ge \alpha r^*$ in Subsection~\ref{subsec:bigger}.
 
-\subsection{The Case $\delta^* < C r*$}
+\subsection{The Case $\delta^* < \alpha r*$}
 \label{subsec:smaller}
@@
 To sum up, the modified algorithm is defined as follows:
-{
-\algrenewcommand\algorithmicindent{0.8em}%
+
 \begin{algorithm}
+\caption{\sc Known$r'(P, z, r')$} 
+\algsetup{indent=1em}
 \label{alg:smallc}
-\leavevmode
-\begin{algorithmic}
-\Function{Known$r'$}{$\mathcal{P}, z, r'$}
-	\For{$(n_1, \dots, n_4) \gets \set{(n_1, \dots, n_4) \provided \sum n_i=z}$}
-		\State $CS \gets B(p_1,r')$
-		\State $p_{o_2} \gets $ \Call{NthOutlier}{$n_1 + 1$, $p_1$}
-		\If{$p_{o_2}$ arrives}
-			\State $CS\gets [ \text{the sub-case of $p_{o_2} \in B_{2, 1}^*$} ] \cup [ \text{the sub-case of $p_{o_2} \in B_{2,2}^*$} ]$
-			\For{each case $S$}
-				\State $p_{o_3} \gets$ \Call{NthOutlier}{$n_2 + 1$, $p_{o_2}$}
-				\If{$p_{o_3}$ arrives} 
-					\State $CS\gets CS\setminus S \cup [ \text{the sub-case of $p_{o_3} \in B_{2, 1}^*$} ] \cup [ \text{the sub-case of $p_{o_3} \in B_{2,2}^*$}]$
-					\For {each sub-case $S'$} 
-						\State $p_{o_4} \gets$ \Call{NthOutlier}{$n_3 + 1$, $p_{o_3}$}
-						\If {$p_{o_4}$ arrives} 
-							\State Replace $S'$ with a new candidate solution.
-							\State $p_{o_5} \gets$ \Call{NthOutlier}{$n_4 + 1$, $p_{o_4}$}
-							\If{$p_{o_5}$ arrives}
-								\State Abandon the solution.
-							\EndIf
-						\EndIf
-					\EndFor
-				\EndIf
-			\EndFor
+%\leavevmode
+\begin{algorithmic}[1]
+%\Function{Known$r'$}{$P, z, r'$}
+	\FOR{$(n_1, \dots, n_4) \gets \set{(n_1, \dots, n_4) \provided \sum n_i=z}$}
+		\STATE $CS \gets B(p_1,r')$
+		\STATE $p_{o_2} \gets $ \Call{NthOutlier}{$n_1 + 1$, $p_1$}
+		\IF{$p_{o_2}$ arrives}
+			\STATE $CS\gets [ \text{the sub-case of $p_{o_2} \in B_{2, 1}^*$} ] \cup [ \text{the sub-case of $p_{o_2} \in B_{2,2}^*$} ]$
+			\FOR{each case $S$}
+				\STATE $p_{o_3} \gets$ \Call{NthOutlier}{$n_2 + 1$, $p_{o_2}$}
+				\IF{$p_{o_3}$ arrives} 
+					\STATE $CS\gets CS\setminus S \cup [ \text{the sub-case of $p_{o_3} \in B_{2, 1}^*$} ] \cup [ \text{the sub-case of $p_{o_3} \in B_{2,2}^*$}]$
+					\FOR {each sub-case $S'$} 
+						\STATE $p_{o_4} \gets$ \Call{NthOutlier}{$n_3 + 1$, $p_{o_3}$}
+						\IF {$p_{o_4}$ arrives} 
+							\STATE Replace $S'$ with a new candidate solution.
+							\STATE $p_{o_5} \gets$ \Call{NthOutlier}{$n_4 + 1$, $p_{o_4}$}
+							\IF{$p_{o_5}$ arrives}
+								\STATE Abandon the solution.
+							\ENDIF
+						\ENDIF
+					\ENDFOR
+				\ENDIF
+			\ENDFOR
 
-		\EndIf
-		\State $\mathop{Sol}_{n_1,n_2,n_3,n_4} \gets$ the solution with the smallest larger radius, among all the sub-cases.
-	\EndFor
-	\State \Return the solution $\mathop{Sol}_{n_1,n_2,n_3,n_4}$ with the smallest radius, for all valid values of $(n_1,n_2,n_3,n_4)$.
-\EndFunction
+		\ENDIF
+		\STATE $\mathop{Sol}_{n_1,n_2,n_3,n_4} \gets$ the solution with the smallest larger radius, among all the sub-cases.
+	\ENDFOR
+	\RETURN the solution $\mathop{Sol}_{n_1,n_2,n_3,n_4}$ with the smallest radius, for all valid values of $(n_1,n_2,n_3,n_4)$.
+%\EndFunction
 \end{algorithmic}
 \end{algorithm}
-}
-Here, \textproc{NthOutlier}$(n,p)$ returns the $n$\nth point arriving after $p$ in $\mathcal{P}$ that does not lie in current candidate solution.
+
+Here, \textproc{NthOutlier}$(n,p)$ returns the $n$\nth point arriving after $p$ in $P$ that does not lie in current candidate solution.
 
 \begin{theorem}
-Given $\delta^* < C r^*$ and $1.2r^* \le r' < (1.2 + 2\eps/3)r^*$, Algorithm~\ref{alg:smallc} uses $\cO (dz^3)$ space and returns a $(1.8+\eps)$-approximate solution.
-Algorithm~\ref{alg:smallc} spends $\cO (dz^3)$ update time for each point in $\mathcal{P}$ and answers a query in $\cO (dz^3)$.
+Given $\delta^* < \alpha r^*$ and $1.2r^* \le r' < (1.2 + 2\eps/3)r^*$, Algorithm~\ref{alg:smallc} uses $\cO (dz^3)$ space and returns a $(1.8+\eps)$-approximate solution.
+Algorithm~\ref{alg:smallc} spends $\cO (dz^3)$ update time for each point in $P$ and answers a query in $\cO (dz^3)$.
 \end{theorem}
@@
 Whenever the next point is inserted, the algorithm updates the solution for each sub-case in $\cO (d)$ time.
-Therefore, the algorithm spends $\cO (dz^3)$ update time for each point of $\mathcal{P}$.
+Therefore, the algorithm spends $\cO (dz^3)$ update time for each point of $P$.
 Answering a query consists of choosing the minimum radius among all the candidate solutions, which amounts to $\cO (dz^3)$ time.
@@
 \label{lem:2lt1}
-Let $r_1^*, r_2^*$ be the radius of $1$-center and $2$-center optimal solutions with $z$ outliers, respectively. Then $r_1^* < \left(\frac{C}{2} + 2\right) r_2^*$.
+Let $r_1^*, r_2^*$ be the radius of $1$-center and $2$-center optimal solutions with $z$ outliers, respectively. Then $r_1^* < \left(\frac{\alpha}{2} + 2\right) r_2^*$.
 \end{lemma}
@@
 
-Algorithm~\ref{alg:1center} finds a $2$-approximation for $r_1^*$. By Lemma \ref{lem:1lt2} and \ref{lem:2lt1}, it gives a $2\left(\frac{C}{2} + 2\right)$-approximation for $r_2^*$.
+Algorithm~\ref{alg:1center} finds a $2$-approximation for $r_1^*$. By Lemma \ref{lem:1lt2} and \ref{lem:2lt1}, it gives a $2\left(\frac{\alpha}{2} + 2\right)$-approximation for $r_2^*$.
 
@@
 
-Our algorithm maintains $m=\ceil{\frac{1.2(3C+12)}{\eps}}$ candidate lengths.
+Our algorithm maintains $m=\ceil{{1.2 \cdot (3 \alpha+12)}/{\eps}}$ candidate lengths.
 For each candidate length $t$, assume that $r' = t$ and use it to run Algorithm~\ref{alg:smallc}.
@@
 Let $l_1=k_1$ and $l_i=2^j l_1$, where $l_i$ is the smallest number satisfying $l_i \ge k_i$.
-By Observation~\ref{obs:2apr}, $l_i$ is a $(2C + 8)$-approximation for $r_2^*$.
+By Observation~\ref{obs:2apr}, $l_i$ is a $(2\alpha + 8)$-approximation for $r_2^*$.
 If the interval $(0, 1.2 l_i]$ divides into $m$ equal segments (Figure~\ref{fig:findr}), then length of each segment is at most $2/3 \eps r_2^*$ and the endpoints as candidates are $\mathcal{L}_i = \set{j \times t_i \provided j = 1, \dots, m}$ where $t_i = \frac{1.2 l_i}{m}$.
@@
 
-\subsection{The Case $\delta^* \ge C r^*$}
+\subsection{The Case $\delta^* \ge \alpha r^*$}
 \label{subsec:bigger}
@@
 \label{obs:c+4}
-Let $d$ be the distance between arbitrary pair of points from two $C$-separated balls. Then $1 \le \frac{d}{\delta} \le \frac{C+4}{C}$.
+Let $d$ be the distance between arbitrary pair of points from two $\alpha$-separated balls. Then $1 \le \frac{d}{\delta} \le \frac{\alpha+4}{\alpha}$.
 \end{obs}
@@
 \label{lem:c-sep}
-Let $\mathcal{P}$ be a set of points and assume that $B_{2,1}^*$ and $B_{2,2}^*$ are $C$-separated ($C \ge 4$) and let $p_1$ be an arbitrary point in $B_{2,1}^*$.
-Define $S$ as the $z+1$ furthest points of $\mathcal{P}$ from $p_1$.
+Let $P$ be a set of points and assume that $B_{2,1}^*$ and $B_{2,2}^*$ are $\alpha$-separated ($\alpha \ge 4$) and let $p_1$ be an arbitrary point in $B_{2,1}^*$.
+Define $S$ as the $z+1$ furthest points of $P$ from $p_1$.
 Then $S \cap B_{2,2}^*$ is nonempty.
@@
 Let $q$ be the furthest point of $S \cap B_{2,1}^*$ from $p_1$.
-Consider $B(p_1, \card{p_1q})$.
-It is clear that $B$ covers $\mathcal{P} \setminus S$.
-Since $p_1, q \in B_{2,1}^*$, then $\card{p_1q}$ is at most $2r_2^*$.
+Consider $B(p_1, \len{p_1q})$.
+It is clear that $B$ covers $P \setminus S$.
+Since $p_1, q \in B_{2,1}^*$, then $\len{p_1q}$ is at most $2r_2^*$.
 Thus by Observation~\ref{obs:intersection}, $B_{2,2}^* \cap B = \emptyset$.
-Therefore $B_{2,2}^* \cap \mathcal{P} = \emptyset$ and hence $B_{2,2}^*$ is empty, which contradicts the optimality of this solution.
+Therefore $B_{2,2}^* \cap P = \emptyset$ and hence $B_{2,2}^*$ is empty, which contradicts the optimality of this solution.
 \end{proof}
@@
 \begin{itemize}
-\item $B_1$, a subset of $\mathcal{P}$ where $B_1 \cap B_{2,2}^* = \emptyset$, that is a set of points that provably lie outside $B_{2, 2}^*$.
-\item $B_2$, a subset of $\mathcal{P}$ along with a \emph{candidate point} $c_p$, such that if $B_{2, 2}^*$ covered the candidate point, then $B_2 \cap B_{2, 1}^* = \emptyset$.
+\item $B_1$, a subset of $P$ where $B_1 \cap B_{2,2}^* = \emptyset$, that is a set of points that provably lie outside $B_{2, 2}^*$.
+\item $B_2$, a subset of $P$ along with a \emph{candidate point} $c_p$, such that if $B_{2, 2}^*$ covered the candidate point, then $B_2 \cap B_{2, 1}^* = \emptyset$.
 \item Buffer, with size at most $z$ that if $c_p \in B_{2, 2}^*$ then all of them are outliers.
@@
 \label{lem:(z+1)-furthest}
-Let $p_1$ be an arbitrary points in $B_{2,1}^{*}$ and $q$ be the $(z+1)$\st furthest point from $p_1$. Then $\frac{C}{C+4}\card{qp_1}$ is a lower bound for $\delta^*$.
+Let $p_1$ be an arbitrary points in $B_{2,1}^{*}$ and $q$ be the $(z+1)$\st furthest point from $p_1$. Then $\frac{\alpha}{\alpha+4}\len{qp_1}$ is a lower bound for $\delta^*$.
 \end{lemma}
 \begin{proof}
-Due to Lemma~\ref{lem:c-sep}, there exists $p_2 \in B_{2,2}^*$ such that $\card{p_1p_2} \ge \card{qp_1}$.
-Thus, by Observation~\ref{obs:c+4}, $\frac{C}{C+4} \card{p_1p_2} \le \delta^*$.
+Due to Lemma~\ref{lem:c-sep}, there exists $p_2 \in B_{2,2}^*$ such that $\len{p_1p_2} \ge \len{qp_1}$.
+Thus, by Observation~\ref{obs:c+4}, $\frac{\alpha}{\alpha+4} \len{p_1p_2} \le \delta^*$.
 The claim follows immediately.
@@
 Function \textproc{AddTo$B_1$} is used to add a point $p$ to $B_1$.
-The point will be added only if the point is within $\delta$\nobreakdash-radius of the center $c_1$, where $\delta$, calculated by Algorithm~\ref{alg:case2}, is $\frac{C}{C+4}\card{qc_1}$ and $q$ is the $(z+1)$\nth furthest point from $c_1$.
+The point will be added only if the point is within $\delta$\nobreakdash-radius of the center $c_1$, where $\delta$, calculated by Algorithm~\ref{alg:case2}, is $\frac{\alpha}{\alpha+4}\len{qc_1}$ and $q$ is the $(z+1)$\nth furthest point from $c_1$.
 By Lemma~\ref{lem:(z+1)-furthest}, $\delta$ is a lower bound for $\delta^*$.
@@
 Thus Function \textsc{AddTo$B_1$} does not violate the property $B_1 \cap B_{2,2}^* = \emptyset$.
+
 \begin{algorithmic}
-\Function{AddTo$B_1$}{$p$}
-	\If{$p \in B(p_1, \delta)$}
-		\State $B_1 = B_1 \cup \set{p}, B_u = B_u \cup \set{p}$
-		\State \Return{true}
-	\EndIf
-	\State \Return{false}
-\EndFunction
+%\Function{AddTo$B_1$}{$p$}
+	\IF{$p \in B(p_1, \delta)$}
+		\STATE $B_1 = B_1 \cup \set{p}, B_u = B_u \cup \set{p}$
+		\RETURN{true}
+	\ENDIF
+	\RETURN{false}
+%\EndFunction
 \end{algorithmic}
@@
 Initially, $B_2$ is empty and $c_2$ and $r_c$ are not initialized.
-When an appropriate candidate is found, Algorithm~\ref{alg:case2} sets $c_2$ to that candidate and $r_c$ to $\frac{2\card{c_1c_2}}{C}$ and after that, points are added to $B_2$ only if they lie within $r_c$-radius of $c_2$.
+When an appropriate candidate is found, Algorithm~\ref{alg:case2} sets $c_2$ to that candidate and $r_c$ to $\frac{2\len{c_1c_2}}{\alpha}$ and after that, points are added to $B_2$ only if they lie within $r_c$-radius of $c_2$.
 At this point $c_2$ is considered as the candidate point $c_p$.
 Clearly the subdivision property for $B_2$ holds initially when $B_2$ consists of the single point $c_2$.
-All the subsequent points added to $B_2$ are within $r_c$-radius of $c_2$ and given $C\ge 7$, by Observation~\ref{obs:intersection} subdivision property is invariant under this operation.
+All the subsequent points added to $B_2$ are within $r_c$-radius of $c_2$ and given $\alpha\ge 7$, by Observation~\ref{obs:intersection} subdivision property is invariant under this operation.
 
-When $\card{B_2}$ reaches $(d+1)(z+1)$, the candidate point changes to center point of $B_2$ and $r_c$ is increased by a factor of $(2 + \frac{2}{C})$ to completely cover the new candidate point and it's surrounding ball.
-It is easy to see that $(2 + \frac{2}{C})r_c < \frac{\delta}{2}$ provided $C \ge 14$ and thus by Observation~\ref{obs:intersection} the property is not violated.
+When $|B_2|$ reaches $(d+1)(z+1)$, the candidate point changes to center point of $B_2$ and $r_c$ is increased by a factor of $(2 + \frac{2}{\alpha})$ to completely cover the new candidate point and it's surrounding ball.
+It is easy to see that $(2 + \frac{2}{\alpha})r_c < \frac{\delta}{2}$ provided $\alpha \ge 14$ and thus by Observation~\ref{obs:intersection} the property is not violated.
 
 \begin{algorithmic}
-\Function{AddTo$B_2$}{p}
-	\If{$c_2$ is set and $p \in B(c_2, r_c)$}
-		\State $B_2 \gets B_2 \cup \set{p}, B_u \gets B_u \cup \set{p}$
-		\If{$\card{B_2} = (d+1)(z+1)$}
-			\State $r_c \gets  (2 + \frac{2}{C}) \times r_c$
-			\For{$p$ in Buffer}
-				\If{$p$ in $B(c_2, r_c)$}
-					\State $B_2 \gets B_2 \cup \set{p}, B_u \gets B_u \cup \set{p}$
-				\EndIf
-			\EndFor
-		\EndIf
-		\State \Return{true}
-	\EndIf
-	\State \Return{false}
-\EndFunction
+%\FUNCTION{AddTo$B_2$}{p}
+	\IF{$c_2$ is set and $p \in B(c_2, r_c)$}
+		\STATE $B_2 \gets B_2 \cup \set{p}, B_u \gets B_u \cup \set{p}$
+		\IF{$|B_2| = (d+1)(z+1)$}
+			\STATE $r_c \gets  (2 + \frac{2}{\alpha}) \times r_c$
+			\FOR{$p$ in Buffer}
+				\IF{$p$ in $B(c_2, r_c)$}
+					\STATE $B_2 \gets B_2 \cup \set{p}, B_u \gets B_u \cup \set{p}$
+				\ENDIF
+			\ENDFOR
+		\ENDIF
+		\RETURN{true}
+	\ENDIF
+	\RETURN{false}
+%\ENDFUNCTION
 \end{algorithmic}
@@
 \label{cor:omitting-centerpoint}
-Given a set $\mathcal{P}$ of $k(d+1)$ points in $d$\nobreakdash-dimensional Euclidean space, there is a point $c_p$, not necessarily in $\mathcal{P}$, that any convex object that does not cover $c_p$, leaves at least $k$ points of $\mathcal{P}$ uncovered.
+Given a set $P$ of $k(d+1)$ points in $d$\nobreakdash-dimensional Euclidean space, there is a point $c_p$, not necessarily in $P$, that any convex object that does not cover $c_p$, leaves at least $k$ points of $P$ uncovered.
 \end{cor}
@@
 Let the new candidate point be the centerpoint of points in $B_2$, when $(z+1)(d+1)$ points have been added to $B_2$.
-We claim that with $B_2 = B(c_2, (2 + \frac{2}{C})r_c)$, ball $B(c_p, \frac{2\card{c_1c_p}}{C})$ completely covered.
-If $c_p \in B_{2,2}^*$ then by Observation~\ref{obs:c+4}, $r^* \le \frac{\card{c_1c_p}}{C}$. Thus $B_{2,2}^* \subseteq B(c_p, \frac{2\card{c_1c_p}}{C})$.
+We claim that with $B_2 = B(c_2, (2 + \frac{2}{\alpha})r_c)$, ball $B(c_p, \frac{2\len{c_1c_p}}{\alpha})$ completely covered.
+If $c_p \in B_{2,2}^*$ then by Observation~\ref{obs:c+4}, $r^* \le \frac{\len{c_1c_p}}{\alpha}$. Thus $B_{2,2}^* \subseteq B(c_p, \frac{2\len{c_1c_p}}{\alpha})$.
 Since:
 \[
-\frac{2\card{c_1c_p}}{C} \leq \frac{2}{C}(\card{c_1c_2} + r_c) \leq (1 + \frac{2}{C})r_c
+\frac{2\len{c_1c_p}}{\alpha} \leq \frac{2}{\alpha}(\len{c_1c_2} + r_c) \leq (1 + \frac{2}{\alpha})r_c
 \]
- then $B_{2,2}^* \subseteq B(c_p, (1 + \frac{2}{C})r_c) \subseteq B(c_2, (2 + \frac{2}{C})r_c)$.
-Thus supposing $C \ge 14$ and by Observation~\ref{obs:intersection}, $B_2 \cap B_{2,1}^* = \emptyset$.
+ then $B_{2,2}^* \subseteq B(c_p, (1 + \frac{2}{\alpha})r_c) \subseteq B(c_2, (2 + \frac{2}{\alpha})r_c)$.
+Thus supposing $\alpha \ge 14$ and by Observation~\ref{obs:intersection}, $B_2 \cap B_{2,1}^* = \emptyset$.
 Thus the claim follows.
@@
 \begin{itemize}
-\item If $\card{B_2} < (d+1)(z+1)$ then $c_2$ can be added to $B_1$, by definition of $B_1$.
+\item If $|B_2| < (d+1)(z+1)$ then $c_2$ can be added to $B_1$, by definition of $B_1$.
 The algorithm then tries all points in $B_2 \cup \mbox{Buffer} \setminus \set{c_2}$, until it finds a suitable candidate point for $c_2$ that does not leave too many points uncovered.
@@
 \item If $\card{B_2} \ge (d+1)(z+1)$, let $q$ be the $(z+1)$\st furthest point from $p_1$ and $p'$ be the nearest point of ball $B_2(c_2, r_c)$ to $p_1$.
-Then $\card{qp_1} > \card{p'p_1}$, since $B_2$ contains more than $z+1$ points.
+Then $\len{qp_1} > \len{p'p_1}$, since $B_2$ contains more than $z+1$ points.
 So by Lemma~\ref{lem:(z+1)-furthest}:
 \[
-\delta \ge \frac{C \card{qp_1}}{C+4} \ge \frac{C}{C+4} (\card{c_1c_2} - r_c) = \frac{C^2 - 2C}{2C + 8} r_c
+\delta \ge \frac{\alpha \len{qp_1}}{\alpha+4} \ge \frac{\alpha}{\alpha+4} (\len{c_1c_2} - r_c) = \frac{\alpha^2 - 2C}{2C + 8} r_c
 \]
-As a result, if $C \geq 14$ then $(2 + \frac{2}{C}) r_c < \frac{\delta}{2}$.
-As shown in Observation~\ref{obs:intersection}, the ball $B_2(c_2, (2 + \frac{2}{C}) r_c)$ has nonempty intersection with exactly one of $B_{2, 1}^*$ and $B_{2, 2}^*$ (not all of its points can be outliers).
+As a result, if $\alpha \geq 14$ then $(2 + \frac{2}{\alpha}) r_c < \frac{\delta}{2}$.
+As shown in Observation~\ref{obs:intersection}, the ball $B_2(c_2, (2 + \frac{2}{\alpha}) r_c)$ has nonempty intersection with exactly one of $B_{2, 1}^*$ and $B_{2, 2}^*$ (not all of its points can be outliers).
 Since the buffer overflowed, the assumption about the candidate point, $c_p$, being in $B_{2,2}^*$ must have been invalid.
@@
 
-{
-\algrenewcommand\algorithmicindent{0.6em}%
-\begin{algorithm}
+\begin{algorithm}[t]
+\caption{\sc NoName$(P)$} 
+\algsetup{indent=1em}
 \label{alg:case2}
-\leavevmode
+%\leavevmode
 \begin{algorithmic}
-\State $\delta \gets 0, r_c \gets 0$
-\State $c_1 \gets p_1$
-\For{$p \in P$}
-	\If{at least $z+1$ points have been processed}
-		\State $q \gets$  $(z+1)$-furthest point from $c_1$
-	\Else
-		\State $q \gets c_1$
-	\EndIf
-	\State $\delta \gets \frac{C}{C+4} \card{c_1q}$
-	\If{\Call{AddTo$B_1$}{$p$} = False and  \Call{AddTo$B_2$}{$p$} = False}
+\STATE $\delta \gets 0, r_c \gets 0$
+\STATE $c_1 \gets p_1$
+\FOR{$p \in P$}
+	\IF{at least $z+1$ points have been processed}
+		\STATE $q \gets$  $(z+1)$-furthest point from $c_1$
+	\ELSE
+		\STATE $q \gets c_1$
+	\ENDIF
+	\STATE $\delta \gets \frac{\alpha}{\alpha+4} \len{c_1q}$
+	\IF{\Call{AddTo$B_1$}{$p$} = False and  \Call{AddTo$B_2$}{$p$} = False}
 % Sahand: is ! a familiar notation for CS people? should we use \neg? or not?
 % Kiana: Agree, What about this one?
-		\State add $p$ to Buffer
-		\While{$\card{\mbox{Buffer}} > z$}
-			\If{$\card{B_2} \ge (d+1)(z+1)$}
-				\State $B_1 \gets B_u$, $B_2 \gets \emptyset$
-			\ElsIf{$c_2$ is set}
-				\State $B_1 \gets B_1 \cup \set{c_2}$, $B_u \gets B_u \cup \set{c_2}$
-			\EndIf
-			\State $T \gets \mbox{Buffer} \cup B_2 - \set{c_2}$
-			\State $\mbox{Buffer} \gets \emptyset, B_2 \gets \emptyset$
-			\If{first iteration of while}
-				\For{$p \in T$}
-					\If{\Call{AddTo$B_1$}{$p$}}
-						\State Remove $p$ from $T$.
-					\EndIf
-				\EndFor
-			\EndIf
-			\State $c_2 \gets$ arbitrary point in $T$
-			\State $r_c \gets \frac{2}{C}\card{c_1 c_2}$
-			\For{$p \in T$}
-				\State \Call{AddTo$B_2$}{$p$}
-			\EndFor				
-			\State $\mbox{Buffer} \gets T \setminus B_2$
-		\EndWhile
-	\EndIf
-\EndFor
+		\STATE add $p$ to Buffer
+		\WHILE{$\card{\mbox{Buffer}} > z$}
+			\IF{$\card{B_2} \ge (d+1)(z+1)$}
+				\STATE $B_1 \gets B_u$, $B_2 \gets \emptyset$
+			\ELSIF{$c_2$ is set}
+				\STATE $B_1 \gets B_1 \cup \set{c_2}$, $B_u \gets B_u \cup \set{c_2}$
+			\ENDIF
+			\STATE $T \gets \mbox{Buffer} \cup B_2 - \set{c_2}$
+			\STATE $\mbox{Buffer} \gets \emptyset, B_2 \gets \emptyset$
+			\IF{first iteration of while}
+				\FOR{$p \in T$}
+					\IF{\Call{AddTo$B_1$}{$p$}}
+						\STATE Remove $p$ from $T$.
+					\ENDIF
+				\ENDFOR
+			\ENDIF
+			\STATE $c_2 \gets$ arbitrary point in $T$
+			\STATE $r_c \gets \frac{2}{\alpha}\len{c_1 c_2}$
+			\FOR{$p \in T$}
+				\STATE \Call{AddTo$B_2$}{$p$}
+			\ENDFOR				
+			\STATE $\mbox{Buffer} \gets T \setminus B_2$
+		\ENDWHILE
+	\ENDIF
+\ENDFOR
 \end{algorithmic}
 \end{algorithm}
-}
 
@@
 Thus it suffices to consider points of Buffer as candidates and compare them to the solution $(B_u, \emptyset)$.
-{
-\algrenewcommand\algorithmicindent{0.8em}%
+
 \begin{algorithm}
+\caption{\sc Query$(q)$} 
+\algsetup{indent=1em}
 \label{alg:query}
-\leavevmode
 \begin{algorithmic}
-\Function{Query}{}
-	\State solutions = [\Call{QuerySubdivision}{$B_1$ $B_2$ Buffer}]
+%\Function{Query}{}
+	\STATE solutions = [\Call{QuerySubdivision}{$B_1$ $B_2$ Buffer}]
 
-	\If {$\card{B_2} \geq (d+1)(z+1)$}
-		\State candidates $\gets$ Buffer
-	\Else
-		\State candidates $\gets$ Buffer $\cup B_2 - \set{c_2}$
-	\EndIf
+	\IF {$\card{B_2} \geq (d+1)(z+1)$}
+		\STATE candidates $\gets$ Buffer
+	\ELSE
+		\STATE candidates $\gets$ Buffer $\cup B_2 - \set{c_2}$
+	\ENDIF
 
-	\For{$c_2 \in$ candidates}
-		\State $r_c \gets \frac{2}{C} \card{c_1 c_2}$
-		\State $B_2 \gets \emptyset$, Buffer $\gets \emptyset$ 
-		\For{$p \in$ candidates}
-			\If{not \Call{AddTo$B_2$}{$p$}}
-				\State Add $p$ to Buffer.
-			\EndIf
-		\EndFor
-		\State Add \Call{QuerySubdivision}{$B_1$, $B_2$, Buffer} to solutions.
-	\EndFor
-	\State \Return \Call{$\min$}{solutions}
-\EndFunction
-\Statex
-\Function{QuerySubdivision}{$B_1$, $B_2$, Buffer}
-	\State solutions $\gets$ empty list
-	\For{$k \gets 0, \dots,(z - \card{\mbox{Buffer}})$}
-		\State $r \gets \max(1-\mbox{center}(B_1, k), 1-\mbox{center}(B_2, z - \card{\mbox{Buffer}} - k))$
-		\State Add $r$ to solutions.
-	\EndFor
-	\State \Return \Call{$\min$}{solutions}
-\EndFunction
+	\FOR{$c_2 \in$ candidates}
+		\STATE $r_c \gets \frac{2}{\alpha} \len{c_1 c_2}$
+		\STATE $B_2 \gets \emptyset$, Buffer $\gets \emptyset$ 
+		\FOR{$p \in$ candidates}
+			\IF{not \Call{AddTo$B_2$}{$p$}}
+				\STATE Add $p$ to Buffer.
+			\ENDIF
+		\ENDFOR
+		\STATE Add \Call{QuerySubdivision}{$B_1$, $B_2$, Buffer} to solutions.
+	\ENDFOR
+	\RETURN \Call{$\min$}{solutions}
+%\EndFunction
 \end{algorithmic}
 \end{algorithm}
-}
+
+\begin{algorithm}
+\caption{\sc QuerySubdivision($B_1$, $B_2$, Buffer)} 
+\algsetup{indent=1em}
+\label{alg:query}
+\begin{algorithmic}
+%\Function{QuerySubdivision}{$B_1$, $B_2$, Buffer}
+	\STATE solutions $\gets$ empty list
+	\FOR{$k \gets 0, \dots,(z - \card{\mbox{Buffer}})$}
+		\STATE $r \gets \max(1-\mbox{center}(B_1, k), 1-\mbox{center}(B_2, z - \card{\mbox{Buffer}} - k))$
+		\STATE Add $r$ to solutions.
+	\ENDFOR
+	\RETURN \Call{$\min$}{solutions}
+%\EndFunction
+\end{algorithmic}
+\end{algorithm}
 

### 2015-04-26 paper.tex
reverting back to general for 1-center
paper reorganized
Passed to Behnam for completing the proofs, etc.

--- 2015-04-17 paper.tex
@@
 
-\usepackage{graphicx}
 \usepackage{caption,subcaption}
+\usepackage{booktabs,multirow}
 
-\usepackage[noend]{algpseudocode}
+\usepackage{algorithm}
+\usepackage[noend]{algorithmic}
+
+\usepackage{cleveref}
+
+%------------------------ Paper Notations -----------------------------
+
+\newcommand{\rc}{r}
+\newcommand{\cp}{c_p}
+\newcommand{\dz}{(d + 1)(z + 1)}
+\newcommand{\Buffer}{\ensuremath{\text{Buffer}}}
+
+\renewcommand{\O}{\ensuremath{{O}}} 
+\DeclareMathOperator*{\argmin}{arg\,min}
+\newcommand{\nd}{\nobreakdash-}
+
+%----------------------- Page Style -----------------------------------------
+
+\renewcommand{\arraystretch}{1.3}
 
 %----------------------- Environments --------------------------
-\newtheorem{corollary}{Corollary} 
+
 \newtheorem{problem}{Problem}
-\newtheorem{algorithm}{Algorithm}
 \newtheorem{definition}{Definition}
 
-%------------------------ Paper Notations -----------------------------
-\DeclareMathOperator*{\argmin}{arg\,min}
+%------------------------ Algorithm -----------------------------
+
+\newcommand{\textproc}{\textsc}
+\newcommand{\Call}[2]{\textsc{#1}(#2)}
+\renewcommand{\algorithmicforall}{{\bf for each}}
 
 %-------------------------- Notations ------------------------------------
-\newcommand{\cO}{\ensuremath{{\rm O}}}
-\newcommand{\st}{\textsuperscript{\textit{st}} }
-\newcommand{\nd}{\textsuperscript{\textit{nd}} }
-\newcommand{\nth}{\textsuperscript{\textit{th}} }
 
@@
 \newcommand{\card}[1]{\left|{#1}\right|}
+\newcommand{\len}[1]{\|{#1}\|}
 \newcommand{\setcomp}[1]{\overline{#1}}
-\newcommand{\provided}{\,:\,}
+\newcommand{\provided}{\,|\,}
 
@@
 \newcommand{\qed}{}
-\newcommand {\backspace}{\vspace{-3em}\\}
+\newcommand{\backspace}{\vspace{-3em}\\}
 
@@
 %----------------------- Title -----------------------------------------
-\title{Streaming $2$-Center with Outliers in High Dimension}
-\author{Hamid~Zarrabi-Zadeh\thanks{Department of Computer Engineering, 
+
+\title{A Streaming Algorithm for 2-Center with Outliers in High Dimensions}
+%\title{Computing 2-Center with Outliers on High-Dimensional Data Streams}
+\author{Behnam~Hatami\thanks{Department of Computer Engineering, 
+	Sharif University of Technology.
+	{\tt hatami@ce.sharif.edu}}
+	\and 
+	Hamid~Zarrabi-Zadeh\thanks{Department of Computer Engineering, 
 	Sharif University of Technology.
 	{\tt zarrabi@sharif.edu}}
-	\and 
 }
@@
 \begin{abstract}
-In this paper, we study the $2$-center streaming problem with $z$ outliers in a general space, which means finding two congruent balls covering all the points except $z$ outliers in a streaming work-space.
-Before considering this problem, we provide a  $2$-approximation algorithm for $1$-center with $z$ outliers in a general space.
-Our algorithm for the $2$-center problem uses an update time and working space polynomial in $d$ and sub-linear in $n$ to calculate a $(1.8+\eps)$-approximation solution.
+We study the Euclidean 2-center problem with outliers in the data stream model. 
+Given a stream of points in arbitrary $d$ dimensions, the goal is to find two congruent balls 
+of minimum radius covering all but $z$ points. 
+We provide a $(1.8+\eps)$-approximation streaming algorithm for the problem, 
+improving upon the previous $(4 + \eps)$-approximation algorithm available for the problem.
+The space complexity and update time of our algorithm is $\poly(d, z, {1 \over \eps})$,
+independent of the size of the stream.
 \end{abstract}
@@
 \section{Introduction}
-Metric $k$-center problem -- covering a set of point with $k$ congruent balls of minimum radius -- is a fundamental problem in computer science and has various applications in data mining and image processing.
-One of $k$\nobreakdash-center problem variants is $k$-center with $z$-outlier which finds $k$ congruent balls with minimum radius covering all but $z$ points of a point set.
-In real world applications, due to commonness of noisy data, it is important to consider outlier points.
-Because even a small number of outliers ($\cO(k)$) can increase the radius of $k$\nobreakdash-center problem unboundedly.
-In this paper we focus on streaming data model.
-In the streaming data model, input data arrives as a sequence and there is not enough space to keep the whole data set.
-Algorithms in this model have limitations in space (typically sub-linear in input size) and processing time per item.
-This model is specially suitable for massive data sets, due to its sub-linear space complexity \cite{aggarwal2007data}.
+The $k$-center problem---covering a set of points 
+using $k$ congruent balls of minimum radius---is a fundamental problem,
+arising in many applications 
+such as data mining, unsupervised learning, statistics, and image processing.
+In real-world applications, where input data is often noisy, 
+it is very important to consider outliers, 
+as even a small number of outliers can greatly affect the quality of the solution.
+The $k$-center problem is particularly very sensitive to outliers,
+and even a constant number of outliers can increase the radius of the $k$-center unboundedly.
+Therefore, it is natural to consider the following generalization of
+the the $k$-center problem: % which we call \emph{$k$-center with $z$ outliers}:
+given a set $P$ of $n$ points in arbitrary $d$ dimensions, 
+find $k$ congruent balls of minimum radius 
+to cover at least $n - z$ points of $P$.
+%One of $k$-center problem variants is $k$-center with $z$-outlier which finds $k$ congruent balls with minimum radius covering all but $z$ points of a point set.
 
-The $k$-center problem without outliers (i.e., $z=0$) in general (Euclidean) space can not be approximated with a smaller factor than $2$ ($1.822$), unless $\mathbf{P}=\mathbf{NP}$ \cite{bern1996approximation}.
-Gonzalez~\cite{gonzalez1985clustering} showed a $2$-approximation algorithm for general case of the problem.
-For small $k$ and $d$, there are more efficient algorithms.
-For Euclidean $1$-center in fixed dimensions, Chazelle~\etal~\cite{chazelle1996linear} gave a linear algorithm.
-For $2$\nobreakdash-center in the plane the best known algorithm, given by Chan \cite{chan1999more}, runs in $\cO(n \log^2 n \log^2 \log n)$ and linear space.
+In this paper, we focus on the \emph{data stream model}
+where only a single pass over the input data is allowed,
+and we have only a limited amount of working space available.
+%which is typically sublinear in the input size.
+This model is specially useful for processing large data sets,
+as it does not need the entire data set to be stored in memory.
 
-In streaming data model, Guha \cite{guha2009tight}, in parallel with McCutchen~\etal~\cite{mccutchen2008streaming} gave $(2+\eps)$-approximation for $k$-center without outliers with $\cO((\frac{dk}{\eps}) \log(\frac{1}{\eps}))$ space.
-For small $k$, better algorithms are known. For fixed $d$, there exists an $\eps$\nobreakdash-coreset for $1$-center with $\cO(\frac{1}{\eps^{\frac{d-1}{2}}})$ space.
-For higher dimensions, Agarwal~\etal~\cite{agarwal2010streaming} gave a $(\frac{1+\sqrt{3}}{2})$-approximation for $1$\nobreakdash-center problem with $\cO((\frac{d}{\eps^3})\log(\frac{1}{\eps}))$ space and and update time, and Chan~\etal~\cite{chan2014streaming} reduced its approximation factor to $1.22$, by an improved analysis.
-For $k=2$, Ahn~\etal~\cite{ahn2014computing} gave a $(2+\eps)$-approximation algorithm using $\cO(\frac{d}{\eps})$ space and update time, which was improved for Euclidean spaces by Kim~\etal~\cite{kim2014improved} to a $(1.8+\eps)$-approximation algorithm, using the same space and update time complexity.
+%In this model, input data arrives as a sequence over time, 
+%%only one pass over the input data is allowed, 
+%and we have only a limited amount of working space available, 
+%which is typically sublinear in the input size.
+%and thus, we cannot keep the entire data set in memory.
+%This makes designing streaming algorithms very challenging,
+%%as we can have only one pass over the input data, 
+%%and must decide on the fly which data to keep in our limited working space,
+%as we cannot keep the entire data set in memory,
+%and must be still able to produce a solution comparable to 
+%that of an offline algorithm that has unlimited access to the whole data set.
 
-For the problem of $k$-center with outliers, Charikar~\etal~\cite{charikar2001algorithms} gives the first offline algorithm with approximation factor $3$ ($4$), where the candidate center points of the centers can be enumerated (otherwise).
-For small $k$, there are better results known.
-$1$-center with $z$ outliers can be solved in $\cO(n \log n + z^{3} n^{\eps})$, for any $\eps > 0$, using Matou{\v{s}}ek's framework \cite{matouvsek1995geometric}.
-Agarwal \cite{agarwal2008efficient} gives a randomized $\cO(n z^{7} \log^3 z)$-time algorithm for $2$-center problem in $\IR^2$.
+The Euclidean $k$-center problem has been extensively studied in the literature.
+%There is a considerable amount of work on the geometric $k$-center problem.
+If $k$ is part of the input,
+the problem in known to be NP-hard in two or more dimensions~\cite{fowler1981optimal},
+and is even hard to approximate to within a factor close to 2, 
+unless P$\,=\,$NP~\cite{feder1988optimal}.
+Factor-2 approximation algorithms are available for the problem 
+in any dimension~\cite{gonzalez1985clustering,feder1988optimal}.
+%The $k$-center problem without outliers (i.e., $z=0$) in general (Euclidean) space can not be approximated with a smaller factor than $2$ ($1.822$), unless $\mathbf{P}=\mathbf{NP}$~\cite{bern1996approximation}.
+%Gonzalez~\cite{gonzalez1985clustering} showed a $2$-approximation algorithm for general case of the problem.
+For small $k$ and $d$, %there are more efficient algorithms.
+better solutions are available.
+The 1-center problem in fixed dimensions is known to be LP-type 
+and can be solved in $O(n)$ time~\cite{chazelle1996linear}.
+For 2-center in the plane, the current best algorithm
+runs in $\O(n \log^2 n \log^2 \log n)$ time~\cite{chan1999more}.
 
-For the problem of $k$-center with $z$ outliers in streaming data model, McCutchen~\etal~\cite{mccutchen2008streaming} (using the idea in Charikar~\etal \cite{charikar2001algorithms} as subroutine) give a $(3+\eps)$-approximation ($(4+\eps)$-approximation, depending on the used subroutine) algorithm using $\cO(\frac{zk}{\eps})$ space.
-In special case of $k=1$ in fixed dimensions, there is a streaming $\cO(\frac{z}{\eps^{\cO(d)}})$-space algorithm \cite{agarwal2007space, zarrabi2011almost}.
-For Euclidean spaces, Zarrabi-Zadeh \cite{zarrabi2009streaming} gave $(1.22 \times \sqrt{2})$\nobreakdash-approximation for $1$-center with $z$ outliers running in $\cO(dz^3 + (\frac{d}{\eps^3})\log(\frac{1}{\eps}))$ space and poly$(d)$ update time .
+For $k$-center with outliers, Charikar~\etal~\cite{charikar2001algorithms} 
+gave the first algorithm with an approximation factor of $3$, 
+that works in any dimension.
+%which is improvable to 3, if all candidate center points can be enumerated.
+%depending on whether the candidate center points can be enumerated or not, respectively.
+Better results are known for small $k$ in the plane.
+The 1-center problem with $z$ outliers in the plane can be solved 
+in $\O(n \log n + z^{3} n^{\eps})$ time, for any $\eps > 0$, 
+using Matou{\v{s}}ek's framework~\cite{matouvsek1995geometric}.
+Agarwal~\cite{agarwal2008efficient} gave a randomized 
+$\O(n z^{7} \log^3 z)$-time algorithm for 2-center with $z$ outliers in the plane.
 
-In this paper our concern is about $2$-center problem in high dimensional Euclidean space.
-The formal definition of problem is as follows.
-Given sequence $\mathcal{S}$ of points in $d$ dimensional Euclidean space (for arbitrarily large $d$), find two congruent balls of minimum radius, covering all but at most $z$ points.
-In Section~\ref{sec:2apr}, we give a simple $2$-approximation algorithm for $1$-center problem with space complexity $\cO(z^2 + zd)$.
-In the next section, we show a $(1.8 + \eps)$-approximation streaming algorithm for $2$-center with $z$ outliers in Euclidean space, and its space complexity is polynomial in $z$ and $d$ and sub-linear in $n$.
-In Section~\ref{subsec:smaller} we run $z + 1$ parallel instances of the algorithm in order to find the first non-outlier point.
-%Kiana: man ino neveshtam vali manzuretun in bud raje be parallel budan az in bishtar begim yani? yekam ziadi tekrar nemishe?
+In the streaming model, McCutchen~\etal~\cite{mccutchen2008streaming} 
+and Guha~\cite{guha2009tight} presented algorithms to maintain $(2+\eps)$-approximation 
+to the $k$-center problem in %in any metric space using 
+$\O(\frac{kd}{\eps} \log \frac{1}{\eps})$ space.
+For $k=1$, %better algorithms are known. % in high dimensions.
+%a $1.5$-approximation in high dimensions was presented by Zarrabi-Zadeh and Chan~\cite{zarrabi2006simple}.
+a factor-$((1+\sqrt{3})/{2})$ approximation 
+was presented by Agarwal and Sharathkumar~\cite{agarwal2010streaming} 
+in high dimensions, using $O(d)$ space. 
+The approximation factor was later improved 
+%to $(1+\sqrt{3})/{2}$ by Agarwal and Sharathkumar~\cite{agarwal2010streaming} 
+to $1.22$ by Chan and Pathak~\cite{chan2014streaming}.
+%If the dimension is fixed, a $(1 + \eps)$-approximation
+%can be maintained in $\O({k}/{\eps^{((d-1)/2)}})$ space 
+%using the notion of core-sets~\cite{zarrabi2008core}., 
+%Ahn~\etal~\cite{ahn2014computing} gave a $(2+\eps)$-approximation algorithm using $\O(\frac{d}{\eps})$ space and update time, which was improved for Euclidean spaces by 
+For $k=2$, Kim~\etal~\cite{kim2014improved} 
+have recently obtained a $(1.8+\eps)$-approximation  
+using $\O(\frac{d}{\eps})$ space and update time.
 
-% Kiana: I think first we should mention what others have done and then start declaring our problem. That's why I changed the location of the previous paragraph.
+For $k$-center with $z$ outliers in the streaming model, 
+McCutchen~\etal~\cite{mccutchen2008streaming} 
+%(using the idea in Charikar~\etal~\cite{charikar2001algorithms} as subroutine) 
+gave a $(4+\eps)$-approximation 
+%(or $(3+\eps)$-approximation, if all center points can be enumerated) 
+algorithm using $\O(\frac{zk}{\eps})$ space.
+When dimension is fixed, a $(1 + \eps)$-approximation to 1-center with outliers
+can be maintained in $\O({z}/{\eps^{((d-1)/2)}})$ space 
+using the notion of robust $\eps$-kernels~\cite{agarwal2007space, zarrabi2011almost}.
+For 1-center with outliers in high dimensions, 
+Zarrabi-Zadeh and Mukhopadhyay~\cite{zarrabi2009streaming} 
+gave a $(\sqrt{2}\alpha)$-approximation, 
+where $\alpha$ is the approximation factor of the underlying algorithm for maintaining 1-center. 
+Combined with the $1.22$-approximation algorithm of Chan and Pathak~\cite{chan2014streaming},
+it yields an approximation factor of $(\sqrt{2} \times 1.22) < 1.73$ 
+using $O(d^3z)$ space and $\poly(d,z)$ update time.
+%In fixed dimensions, there is a streaming $\O(\frac{z}{\eps^{\O(d)}})$-space algorithm~\cite{agarwal2007space, zarrabi2011almost}.
+
+\begin{table}[t]
+\centering
+\begin{tabular}{|c|c|c|}
+\hline
+\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}} \ \  Problem \ \ \end{tabular}} & \multicolumn{2}{c|}{Approximation Factor} \\ \cline{2-3} 
+ & Without Outliers & With Outliers \\ \hline
+1-Center & 1.22~\cite{chan2014streaming} & 1.73~\cite{zarrabi2009streaming} \\ \hline
+2-Center & $1.8 + \eps$~\cite{kim2014improved} & \textbf{$1.8 + \eps$} [Here]  \\ \hline
+$k$-Center & $2 + \eps$~\cite{guha2009tight,mccutchen2008streaming} & $4 + \eps$~\cite{mccutchen2008streaming}  \\ \hline
+\end{tabular}
+\caption {Summary of the streaming algorithms 
+for $k$-center with and without outliers in high dimensions.}
+\label{table:summary}
+\end{table}
+
+\paragraph{Our result}
+In this paper, we study the 2-center problem with outliers in high dimensions.
+We present a streaming algorithm for the problem that achieves
+an approximation factor of $1.8 + \eps$, for any $\eps > 1$,
+%using $O(d^3z/\eps)$ space.
+using $\poly(d, z, {1 \over \eps})$ space and update time.
+This improves the current streaming algorithm available for the problem
+which has an approximation factor of $4+\eps$.
+%Our work not only improves the best previous algorithm available for the case of 2-center,
+%but is also counterintuitive in the sense that its 
+The approximation factor of our algorithm matches
+that of the best streaming algorithm for the 2-center problem without outliers.
+This is somewhat surprising, considering that 
+the best current approximation factors for streaming $k$-center with and without outliers 
+differ by a factor of $\sqrt{2}$ for $k=1$,
+and differ by a factor of 2  for general~$k$. %the 1-center problem.
+See \Cref{table:summary} for a comparison.
+
+To obtain our result, we have used a combination of several ideas
+including parallelization construction, far/close ball separation,
+and keeping a lower bound on the radius and distance of the optimal balls.
+Our algorithm also utilizes the ideas used in~\cite{kim2014improved} 
+for the 2-center problem with no outliers.
+Nevertheless, our algorithm is much detailed and uses many new ingredients.
+Indeed, handling outliers makes the $k$-center problem much harder,
+as we not only need to find clusters with minimum radius, 
+but we also need to decide which subset of points to cluster.
+This is in particular more challenging in the streaming model,
+where we only have a single pass over the input, and we must decide on the fly
+which point can be an outlier, and which one can be safely dropped as a non-outlier point.
+
+\REM{
+The rest of this paper is organized as follows.
+In Section~\ref{sec:1-center}, we give a simple $2$-approximation algorithm for 
+the 1-center problem with outliers that uses $\O(z^2 + zd)$ space.
+In the next section, we show a $(1.8 + \eps)$-approximation streaming algorithm for 2-center with $z$ outliers in high dimensions. 
+%In Section~\ref{subsec:smaller} we run $z + 1$ parallel instances of the algorithm in order to find the first non-outlier point.
+}
 
@@
 \label{sec:pre}
-Let $B(c,r)$ denote a ball with center $c$ and radius $r$. We denote by $pq$ the straight line segment between these two points and by $\card{pq}$ the length of this segment. 
-Define $\delta$ of two balls $B(c,r)$ and $B'(c',r')$, the minimum distance between $B$ and $B'$ which is equal to $\max (0, \card{cc'}-r-r')$.
+Let $B(c,r)$ denote a ball of radius $r$ centered at $c$. 
+Given two points $p$ and $q$, we denote by $pq$ the straight line segment between $p$ and $q$,
+and denote by $\len{pq}$ the length of this segment. 
+Given two balls $B(c,r)$ and $B'(c',r')$, 
+we define 
+$\delta(B, B') = \max \set{0, \len{cc'}-r-r'}$
+to be the \emph{distance} between $B$ and $B'$.
+Two congruent balls $B_1$ and $B_2$ with radius $r$ are said to be \emph{$\alpha$-separated}, 
+if $\delta(B_1, B_2) \geq \alpha r$.
 
-Let $B_{2,1}^*(c_1^*, r_2^*)$ and $B_{2,2}^*(c_2^*, r_2^*)$ denote the optimal solution to $2$-center problem with $z$ outliers.
-By $\delta^*$, denote the distance between $B_{2,1}^*$ and $B_{2,2}^*$, that is, $\delta^* = \max (0, \card{c_1^*c_2^*} - 2r^*)$.
+Given an $n$-point set $P$ in $d$-dimensions,
+a point $c \in \IR^d$ is called a \emph{centerpoint} of $P$,
+if any halfspace containing $c$ contains at least $\ceil{{n}/({d + 1})}$ points of $P$. 
+%In other words, any halfspace (or convex set) that avoids a centerpoint can contain at most $\floor{\frac{dn}{d + 1}}$ points of $P$. 
+It is well-known that any finite set of points in $d$-dimensional space 
+has a centerpoint~\cite{danzer1963helly}. 
+The following observation is a corollary of this fact.
+%~\cite{edelsbrunner1987algorithms}.
 
-Two congruent balls $B_1$ and $B_2$ with radius $r$ are said to be \emph{$C$-separated}, whenever the distance $\delta$ of two balls is at least $Cr$.
+\begin{obs}
+\label{obs:omitting-centerpoint}
+	Given a set $P$ of $k(d+1)$ points in $d$-dimensional space, 
+	there is a point $c$, not necessarily in $P$, 
+	such that any convex object that does not cover $c$, 
+	leaves at least $k$ points of $P$ uncovered.
+\end{obs}
 
-%Let $\mathcal{P}$ be a configuration of $n$ point in $d$-dimensional Euclidean space.
-A point $c_p$, not necessarily in $\mathcal{P}$, is a \emph{centerpoint} of $\mathcal{P}$, if no open half-space that omits $c_p$ contains more than $\frac{dn}{d+1}$ points of $\mathcal{P}$.
+Given a point set $P$ and a point $p \in P$,
+the \emph{$k$-furthest point from $p$}
+is the $k$-th point of $P$ when points are sorted
+in their decreasing distance from~$p$.
 
-Given an $n$-point set $\mathcal{P}$ in $d$-dimensional Euclidean space, a point $c \in \IR^d$ is called a \emph{centerpoint} of $\mathcal{P}$ if any halfspace containing $c$, contains at least $\ceil{\frac{n}{d + 1}}$ points of $\mathcal{P}$.
-In other words, any halfspace (or convex set) that avoids a centerpoint can contain at most $\floor{\frac{dn}{d + 1}}$ points of $\mathcal{P}$.
+We assume the standard word-RAM model of computation. 
+Each coordinate value takes a unit of space.
+Thus, a point in $d$ dimensions takes $\O(d)$ space,
+and basic operations on the points take $\O(d)$ time.
 
@@
 
-\section{A Simple $2$-Approximation Algorithm for $1$-Center with Outliers}
-\label{sec:2apr}
+\section{A 2-Approximation for 1-Center with Outliers}
+\label{sec:1-center}
+
+To warm up, we present a simple $2$-approximation streaming algorithm
+for the 1-center problem with outliers.
+It utilized a parallelization technique that 
+will be used extensively in the rest of the paper.
+The pseudocode is provided in \Cref{alg:1-center}.
+The algorithm receives as input a stream of points, $P$,
+the number of outliers, $z$, 
+and a special point $c \in P$ which is guaranteed to be 
+a non-outlier in the optimal solution.
+It returns a ball $B$ covering all but at most $z$ points of $P$.
+%We will show later how to remove this assumption.
+
+%\begin{algorithm}
+%\caption{\sc 1-Center$(P, z)$} 
+%\algsetup{indent=1.5em}
+%\label{alg:1-center}
+%\begin{algorithmic}[1]
+%
+%	%\STATE Let $p_i$ denote the elements of $P$, for $i \in \set{1, \dots, n}$.
+%	\STATE let $p_1, \ldots, p_n$ be the points of $P$
+%	\FOR{$i = 1, \dots, z+1$}
+%		%\STATE move $p_i$ to the front of $P$ %is a non-outlier point in optimal solution.
+%		\STATE $B_i \gets$ \Call{1-Center-Special}{$P, z,p_i$}
+%	\ENDFOR
+%	%\STATE $i^* \gets \argmin_{i=1}^{z+1} r_i$
+%	\RETURN smallest ball among $\set{B_1, \ldots, B_{z+1}}$
+%
+%\end{algorithmic}
+%\end{algorithm}
 
 \begin{algorithm}
-\label{alg:1center}
-\leavevmode
-\begin{algorithmic}
-\Function{$1$-centerWithOutliers}{$\mathcal{P}, z$}
-	\State Let $p_i$ denote the elements of $\mathcal{P}$, for $i \in \set{1, \dots, n}$.
-	\ForAll{$i \gets 1, \dots, z+1$}
-		\State Assume $p_i$ is a non-outlier point in optimal solution.
-		\State $B(c_i, r_i) \gets$ \Call{KnownPoint}{$\mathcal{P}, z, p_i$}
-	\EndFor
-	\State $i^* \gets \argmin_{i=1}^{z+1} r_i$
-	\State \Return $B(c_{i^*}, r_{i^*})$
-\EndFunction
-\Statex
-\Function{KnownPoint}{$\mathcal{P}, z, p$}
-	\State $B \gets B(p, 0)$
-	\State $Q \gets \emptyset$
-	\For{$p'$ in $\mathcal{P}$}
-		\If{$p' \notin B$}
-			\State Insert $p'$ into $Q$.
-			\If{$\card{Q} = z + 1$}
-				\State $q$ $\gets$ closest point to $p$ in $Q$
-				\State Remove $q$ from $Q$.
-				\State $B \gets B(p, \card{pq})$
-			\EndIf
-		\EndIf
-	\EndFor
-	\State \Return{B}
-\EndFunction
+\caption{\sc 1-Center$(P, z, c)$} 
+\algsetup{indent=1.5em}
+\label{alg:1-center}
+\begin{algorithmic}[1]
+	%\STATE {$\triangleright$ $c$ is a non-outlier point in the optimal solution}
+	\STATE $B \gets B(c, 0)$
+	\STATE $Q \gets \emptyset$
+	\FORALL {$p$ in $P$}
+		\IF {$p \notin B$}
+			\STATE insert $p$ into $Q$
+			\IF {$|Q| = z + 1$}
+				\STATE $q$ $\gets$ closest point to $c$ in $Q$
+				\STATE remove $q$ from $Q$
+				\STATE $B \gets B(c, \len{cq})$
+			\ENDIF
+		\ENDIF
+	\ENDFOR
+	\RETURN {B}
 \end{algorithmic}
 \end{algorithm}
-Function \textproc{KnownPoint} in Algorithm~\ref{alg:1center}, takes a point $p$ as an argument which is guaranteed to be a non-outlier point in the optimal solution.
-To overcome the lack of knowledge about such a point, function \textproc{$1$\nobreakdash-centerWithOutliers} tries each of the first $z+1$ points of the stream as a candidate for a non-outlier point and generates a ball for each, using function \textproc{KnownPoint}.
-It returns the ball with the minimum radius.
-Note that, due to space limitations inherent to streaming data model, the body of for-all loop in function \textproc{$1$-centerWithOutliers} runs in parallel.
 
-\begin{theorem}
-Algorithm~\ref{alg:1center} is a $2$-approximation algorithm for $1$-center problem with $z$ outliers, in any dimension.
+%The function \textproc{1-Center-Special} in \Cref{alg:1-center-special}, 
+%takes as input a point $c$ which is guaranteed to be a non-outlier point in the optimal solution. 
+%To overcome the lack of knowledge about such a point, 
+%function \textproc{1-Center} in \Cref{alg:1-center}
+%tries each of the first $z+1$ points of the stream as a candidate for a non-outlier point and 
+%generates a ball for each, using function \textproc{1-Center-Special}. 
+%It returns the ball with the minimum radius. 
+%Note that, in the streaming model, %due to space limitations inherent to streaming data model, 
+%the body of the for loop in function \textproc{1-Center} runs in parallel.
+%To run function \textproc{1-Center} in the data stream model,
+%we run the body of the for loop in $z+1$ parallel streaming instances.
+
+\begin{theorem} \label{thm:1-center}
+	Algorithm~\ref{alg:1-center} computes a $2$-approximation to
+	the 1-center problem with $z$ outliers,
+	provided that a non-outlier point in the optimal solution in given.
 \end{theorem}
@@
 \begin{proof}
-Let $B^*(c^*, r^*)$ be the optimal solution.
-Clearly, there exists a point $p$ among the first $z+1$ points of $\mathcal{P}$, which is not an outlier in the optimal solution (Figure~\ref{fig:1center}).
-Since $p \in B^*$, then $\card{pp'} \le 2r^*$ for any point $p'\in B^*$.
-There is at least one point $q'$ among the $(z+1)$-furthest points from $p$ that is not an outlier in the optimal solution.
-Thus $\card{pq} \le \card{pq'} \le 2r^*$ and Algorithm~\ref{alg:1center} returns a valid solution of radius at most $2r^*$.
-So the proof is complete.
+Let $B^*(c^*, r^*)$ be the optimal solution,
+and $c$ be a non-outlier in the optimal solution.
+Since $c$ is covered by $B^*$,
+for all points $p \in B^*$, we have
+$\len{cp} \le \len{cc^*} + \len{c^*p} \le 2r^*$.
+Among the $z+1$ points furthest from $c$,
+there is at least one point $q$ which is not outlier in the optimal solution,
+and therefore, is contained in $B^*$
+(see \Cref{fig:1center}). 
+Thus, $\len{cq} \le 2r^*$,
+and therefore, the ball $B(c, \len{cq})$ returned by Algorithm~\ref{alg:1-center} 
+is a 2-approximation. 
 \end{proof}
 
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=12em]{figs/one-center}
+	\caption{Proof of \Cref{thm:1-center}}
+	\label{fig:1center}
+\end{figure}
+
+\noindent
+Algorithm~\ref{alg:1-center} 
+assumes that a point $c$ is known in advance
+which is guaranteed to be a non-outlier in the optimal solution. 
+To overcome the lack of knowledge about such a point, 
+we run $z+1$ instances of \Cref{alg:1-center} in parallel,
+each of which is given as $c$ one of the first $z + 1$ points in the stream.
+Clearly, there exists a point among the first $z+1$ points of $P$
+which is not an outlier in the optimal solution.
+Therefore, the smallest ball among the $z+1$ balls computed in parallel
+is always within factor~2 of the optimal solution. % by \Cref{thm:1-center-special}.
+Since the space complexity of Algorithm~\ref{alg:1-center} for one instance is $\O(zd)$, 
+and its update time is $\O (zd \log z)$, % and the query time is $\O (z)$.
+we get the following result.
+
+\begin{theorem} \label{thm:1-center-stream}
+	Given a stream of points in $d$ dimensions,
+	we can maintain a 2-approximation to the 1-center with $z$ outliers
+	in $\O(z^2d)$ space and $\O (z^2d\log z)$ update time.
+\end{theorem}
+
+%function \textproc{1-Center} in \Cref{alg:1-center}
+%tries each of the first $z+1$ points of the stream as a candidate for a non-outlier point and 
+%generates a ball for each, using function \textproc{1-Center-Special}. 
+%It returns the ball with the minimum radius. 
+%Note that, in the streaming model, %due to space limitations inherent to streaming data model, 
+%the body of the for loop in function \textproc{1-Center} runs in parallel.
+%To run function \textproc{1-Center} in the data stream model,
+%we run the body of the for loop in $z+1$ parallel streaming instances.
 %
-%\begin{figure}[h]
-%	\centering
-%	\includegraphics[width=17em]{figs/one-center}
-%	\caption{Output of Algorithm~\ref{alg:1center}}
-%	\label{fig:1center}
-%\end{figure}
-
-% Behnam: Aks be nazaram gooya nist ziad. va inke jaii behesh refrence dade nashode!
-% Kiana: hagh ba behname. akse bedune refrence nadarim asan. montaha man benazaram kheili ehtiaji nis behesh asan 
-% Sahand: hazf konim ya pishnehadi baray e behboodesh darid?
-% Kiana: Man be nazaram vaghean chon kheili az idehaye basic ham baraye gheire streaming hamine va osulan idash yekam badihitowre hazf beshe.
-felan commentesh kardam age nazaretun chize digei bud avazesh konin.
-
-The space complexity of Algorithm~\ref{alg:1center} is $\cO(z^2 + zd)$, the update time is $\cO (z \log z + zd)$ and the query time is $\cO (z)$.
-If a non-outlier point $p$ is known then the space, update time and query time complexities of Algorithm~\ref{alg:1center} can be reduced by a factor of $z$.
+%The space complexity of Algorithm~\ref{alg:1center} is $\O(z^2 + zd)$, the update time is $\O (z \log z + zd)$ and the query time is $\O (z)$.
+%If a non-outlier point $p$ is known then the space, update time and query time complexities of Algorithm~\ref{alg:1center} can be reduced by a factor of $z$.
 
@@
 
-\section{The $2$-Center Problem with $z$ Outliers}
+\section{The 2-Center Problem with Outliers}
+\label{sec:2-center}
 
-In all the algorithms given in this section it is assumed that $p_1$ is a non-outlier point.
-It is not hard to see that, this limitation can be overcome by considering $\cO(z)$ parallel instances of the algorithm, similar to Algorithm~\ref{alg:1center}.
-% Behnam: Move this to upper section, this assumption can be used for previous algorithm
-%kiana: Here is better. Since we do not have p_1 in section 4.2
+In this section, we provide a $(1.8 + \eps)$-approximation algorithm
+for the 2-center problem with outliers.
+In all algorithms presented in this section,
+we assume that the first point of the stream, $p_1$, is non-outlier. 
+This assumption can be easily removed by considering $z + 1$ parallel instances of the algorithm, 
+similar to what we did in \Cref{sec:1-center}.
+
+Let $B_1^*$ and $B_2^*$ be the optimal balls
+in an optimal solution to the 2-center problem with $z$ outliers on a point set $P$.
+We denote by $r^*$ the optimal radius,
+and by $\delta^*$ the distance between $B_1^*$ and $B_2^*$.
+To prove our main result, we distinguish between two cases.
+In \Cref{subsec:bigger}, we address the case where $\delta^* > \alpha r^*$, 
+for some constant $\alpha$ to be fixed later.
+(It will be turn out that $\alpha = 14$ is a proper choice.)
+We then present in \Cref{subsec:smaller} 
+our algorithm for the case of $\delta^* \leq \alpha r^*$.
+
+%We inspect the case where $\delta^* \ge \alpha r^*$ in Subsection~\ref{subsec:bigger}.
+%give a description of our algorithm for a given $r > 0$ for the case where $\delta^* < \alpha r^*$ and $1.2r^* \le r < (1.2 + 2\eps/3)r^*$, which returns a $(1.8 + \eps)$-approximate solution.
+We explain how to find such an $r$ and present a full description of our algorithm for the case where $\delta^* < \alpha r^*$ in Subsection~\ref{subsec:findr}.
+
+% -------------------------------- First Case -----------------------------------
+
+\subsection{The Case $\delta^* > \alpha r^*$}
+\label{subsec:bigger}
+
+In this section, we present a $1.8$-approximation algorithm for the case 
+where optimal balls are separated by a distance greater than $\alpha r^*$.
+%The value of $\alpha$ will be fixed later in this section.
+
+\begin{obs}
+\label{obs:c+4}
+	Let $B_1$ and $B_2$ be two congruent balls of radius $r$,
+	with distance $\delta > \alpha r$.
+	%If $p$ and $q$ are two points in $B_1$ and $B_2$, respectively,
+	For any two points $p \in B_1$ and $q \in B_2$,
+	we have $1 \le \frac{\len{pq}}{\delta} <  \frac{\alpha + 4}{\alpha}$.
+\end{obs}
+
+\begin{proof}
+The distance between $p$ and $q$ is at most $\delta + 4r$.
+%(see \Cref{fig:c+4}).
+Hence, $\frac{\len{pq}}{\delta} \leq 1 + {4r \over \delta} < 1 + \frac{4}{\alpha}$.
+\end{proof}
+
+\REM{
+\begin{figure}[th]
+	\centering
+	\includegraphics[width=20em]{figs/c_plus_4}
+	\vspace{-1em}
+	\caption{Illustrating Observation~\ref{obs:c+4}}
+	\label{fig:c+4}
+\end{figure}
+}
+
+\begin{obs}
+\label{obs:intersection}
+	Let $B_1$ and $B_2$ be two disjoint balls of distance greater than $\delta$,
+	and let $B$ be an arbitrary ball of radius at most $\frac{\delta}{2}$. 
+	Then $B$ intersects at most one of $B_1$ and $B_2$.
+\end{obs}
+
+\noindent 
+%Before presenting our algorithm,
+We next prove some properties regarding 
+the optimal balls, $B_1^*$ and $B_2^*$.
+
+\begin{lemma}
+\label{lem:c-sep}
+	Let $B_1^*$ and $B_2^*$ be $\alpha$-separated, with $\alpha > 4$.
+	If $p$ is a point in $B_1^*$,
+	and $S$ is a $(z+1)$-subset of $P$ furthest from~$p$,
+	then $S \cap B_2^*$ is non-empty.
+\end{lemma}
+
+\begin{proof}
+Suppose by way of contradiction that $S \cap B_2^*$ is empty. 
+Since $\card{S} = z + 1$, there is at least one point in $S$
+which is not outlier, and hence, it is in $B_1^*$.
+Let $q$ be the point in $S \cap B_1^*$ furthest from~$p$. 
+Consider $B(p, \len{pq})$. It is clear that $B$ covers $P \setminus S$. 
+Since $p, q \in B_1^*$, then $\len{pq}$ is at most $2r^*$. 
+Thus, by Observation~\ref{obs:intersection}, $B_2^* \cap B = \emptyset$. 
+Therefore, $B_2^* \cap P = \emptyset$, and hence,
+ $B_2^*$ is empty, which contradicts the optimality of the solution.
+\end{proof}
+
+\begin{lemma}
+\label{lem:(z+1)-furthest}
+	Let $p$ be a point in $B_1^{*}$,
+	and $q$ be the $(z+1)$-furthest point from $p$. 
+	Then, $\delta^* > \frac{\alpha}{\alpha+4}\len{pq}$.
+\end{lemma}
+
+\begin{proof}
+By Lemma~\ref{lem:c-sep}, there exists a point $q' \in B_2^*$ 
+such that $\len{pq'} \ge \len{pq}$. 
+Thus, by Observation~\ref{obs:c+4}, 
+%$\frac{\alpha}{\alpha+4} \len{pp_2} \le \delta^*$. 
+${\len{pq} \over \delta^*} \le {\len{pq'} \over \delta^*} < \frac{\alpha+4}{\alpha}$.
+The claim follows immediately.
+\end{proof}
+
+\begin{lemma}
+\label{lem:}
+	If $p \in B_1^*$ and $q \in B_2^*$,
+	then at most $z$ points of $P$ lie outside $B(p, 2r^*) \cup B(q, 2r^*)$.
+\end{lemma}
+
+\begin{proof}
+	TBA.
+\end{proof}
+
+\begin{lemma}
+\label{lem:}
+	Let $S$ be a subset of $P$ of size at least $\dz$,
+	enclosed by a ball of radius $\delta^* / 2$.
+	Then the centerpoint of $S$ lies either inside $B_1^{*}$ or inside $B_2^{*}$.
+\end{lemma}
+
+\begin{proof}
+	TBA.
+\end{proof}
+
+\paragraph{The Algorithm}
+We now describe our algorithm for handling the case  $\delta^* > \alpha r^*$.
+At any time, our algorithm maintains a partition of $P$ into three disjoint subsets
+$B_1$, $B_2$, and Buffer.
+The first point $p_1$ is assumed, w.l.o.g, to be in $B_1^*$. 
+The algorithm tries to partition points in such a way that 
+at the end,
+$B_1$ contains the whole $B_1^*$, and $B_2$ contains the whole $B_2^*$,
+with possibly some outliers being contained in $B_1$ and $B_2$.
+%Buffer has always size at most $z$.
+The algorithm sets $c_1 = p_1$ as the fixed center of $B_1$,
+and picks $c_2$ among the points processed so far as a candidate center for $B_2$.
+Moreover, the algorithm maintains two values $\delta$ and $r$,
+where at any time, $\delta$ is a lower bound of $\delta^*$, 
+and $r$ is an upper bound of $2r^*$.
+
+Our algorithm is presented in \Cref{alg:case-1}.
+For each input point $p \in P$, the algorithm first tries 
+to add $p$ to either $B_1$ or $B_2$,
+using functions \textproc{AddToB$_1$} and \textproc{AddToB$_2$}, respectively.
+%presented in Algorithms~\ref{alg:addB1} and~\ref{alg:addB2}.
+If none of them fits, the point is added to Buffer.
+The function \textproc{AddToB$_1$} adds a point $p$ to $B_1$
+only if it is within distance $\delta$ of the center $c_1$.
+Similarly, \textproc{AddToB$_2$} adds a point $p$ to $B_2$
+only if it is within $\rc$-radius of $c_2$. 
+The two functions also update $\delta$ and $\rc$ whenever necessary,
+to maintain the invariants to be defined shortly in Lemma~\ref{lem:invariants}.
+
+\begin{algorithm}[t]
+\caption{\sc 2-CenterCase1$(P)$} 
+\algsetup{indent=1.5em}
+\label{alg:case-1}
+\begin{algorithmic}[1]
+\STATE $c_1 \gets p_1$, $\rc  \gets 0$, $\delta \gets 0$
+\FORALL{$p \in P$}
+	\IF {\NOT (\Call{AddToB$_1$}{$p$} \OR \Call{AddToB$_2$}{$p$})}
+		\STATE add $p$ to Buffer
+		\WHILE{$\card{\mbox{Buffer}} > z$} \label{step:buffer-overflow}
+			\IF{$\card{B_2} \ge \dz$}
+				\STATE $B_1 \gets B_1 \cup B_2$, $B_2 \gets \emptyset$
+			\ELSIF{$c_2$ is set}
+				\STATE $B_1 \gets B_1 \cup \set{c_2}$ %, $B_u \gets B_u \cup \set{c_2}$
+				%\STATE remove $c_2$ from $B_2$
+			\ENDIF
+			\STATE $T \gets \mbox{Buffer} \cup B_2 \setminus \set{c_2}$
+			\STATE $B_2 \gets \emptyset$ 
+%			\IF{first iteration of while}
+%				\FOR{$p \in T$}
+%					\IF{\Call{AddToB$_1$}{$p$}}
+%						\STATE remove $p$ from $T$
+%					\ENDIF
+%				\ENDFOR
+%			\ENDIF
+			\STATE $c_2 \gets$ an arbitrary point of $T$
+			\STATE $\rc  \gets \frac{2}{\alpha}\len{c_1 c_2}$
+			\FOR{$p \in T$}
+				\STATE \Call{AddToB$_2$}{$p$}
+			\ENDFOR				
+			\STATE $\mbox{Buffer} \gets T \setminus B_2$
+		\ENDWHILE
+	\ENDIF
+\ENDFOR
+\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}[ht]
+\caption{\sc AddToB$_1(p)$} 
+\algsetup{indent=1.5em}
+\label{alg:addB1}
+\begin{algorithmic}[1]
+
+	%\STATE $q \gets c_1$
+	\IF {at least $z + 1$ points have been arrived}
+		\STATE $q \gets$  $(z+1)$-furthest point from $c_1$
+	\ELSE
+		\STATE $q \gets c_1$
+	\ENDIF
+	\STATE $\delta \gets \frac{\alpha}{\alpha+4} \len{c_1q}$
+	\IF {$p \in B(c_1, \delta)$}
+		\STATE $B_1 = B_1 \cup \set{p}$ %, B_u = B_u \cup \set{p}$
+		\RETURN{true}
+	\ENDIF
+	\RETURN{false}
+
+\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}[ht]
+\caption{\sc AddToB$_2(p)$} 
+\algsetup{indent=1.5em}
+\label{alg:addB2}
+\begin{algorithmic}[1]
+%\FUNCTION{AddToB$_2$}{p}
+	\IF{$c_2$ is set \AND $p \in B(c_2, \rc )$}
+		\STATE $B_2 \gets B_2 \cup \set{p}$ %, B_u \gets B_u \cup \set{p}$
+		\IF{$|B_2| = \dz$}
+			%\STATE $\cp  \gets$  centerpoint of $B_2$
+			\STATE $\rc  \gets  (2 + \frac{2}{\alpha}) \times \rc$
+			\FOR{$p$ in Buffer}
+				\IF{$p \in B(c_2, \rc )$}
+					\STATE $B_2 \gets B_2 \cup \set{p}$ %, B_u \gets B_u \cup \set{p}$
+					\STATE remove $p$ from Buffer
+				\ENDIF
+			\ENDFOR
+		\ENDIF
+		\RETURN{true}
+	\ENDIF
+	\RETURN{false}
+%\ENDFUNCTION
+\end{algorithmic}
+\end{algorithm}
+
+Whenever the buffer overflows (in line~\ref{step:buffer-overflow} of \Cref{alg:case-1}),
+%the assumption about $\cp \in B_2^*$ is contradicted.
+%At some point during the execution of Algorithm~\ref{alg:case-1}, the assumption about $\cp \in B_2^*$ might be contradicted when the buffer overflows. We can then conclude that
+% $\cp \notin B_2^*$.
+the algorithm takes one of the following actions
+depending on the size of $B_2$. 
+If $|B_2| \ge \dz$, then the points of $B_2$ are moved to $B_1$, and $B_2$ is reset.
+Otherwise, the old $c_2$ (if already set) is moved to $B_1$,
+and another point from $T = B_2 \cup \Buffer \setminus \set{c_2}$ is picked as $c_2$.
+The while loop iterates $O(dz)$ times,
+because after the first iteration, we are sure 
+that $T$ has at most $\dz + z$ points, from which 
+one point (i.e., $c_2$) is removed at each subsequent iteration.
+
+\paragraph{Analysis}
+For the sake of analysis, we maintain a special point,
+denoted by $\cp$, %not necessarily in $P$,
+which we call a \emph{central point}.
+The point is defined as follows:
+if $\card{B_2} < \dz$, then $\cp = c_2$, otherwise,
+$\cp$ is the centerpoint of the first $\dz$ points currently in $B_2$.
+
+\begin{lemma}
+\label{lem:invariants}
+	The following invariants are maintained during the execution of the algorithm:
+
+\begin{enumerate}
+\item [(a)] $\delta < \delta^*$ %$\delta$ is a lower bound of $\delta^*$
+\item [(b)] $B_1 \cap B_2^* = \emptyset$
+\item [(c)]  if $\cp \in B_2^*$, then 
+	\begin{enumerate}
+		\item [1.] $2r^* \le r \le \delta /2$
+		\item [2.] $B_2 \cap B_1^* = \emptyset$
+		\item [3.] all points in $\Buffer$ are outliers
+	\end{enumerate}
+\end{enumerate}
+\end{lemma}
+
+\begin{proof}
+TBA \ 
+(All non-used parts from the previous version are copied here.
+They might be useful for composing the proof of this lemma.)
+
+The function \textproc{AddToB$_1$} presented in \Cref{alg:addB1} 
+is used to add a point $p$ to $B_1$. 
+%The point $c_1$ is the first point of the stream,
+%which is assumed to be non-outlier, and is in $B_1^*$.
+The point will be added to $B_1$ only if it is within distance $\delta$ of the center $c_1$, 
+where $\delta = \frac{\alpha}{\alpha+4}\len{qc_1}$ 
+and $q$ is the $(z+1)$-furthest point from $c_1$.
+%among the points of $P$ seen so far.
+By Lemma~\ref{lem:(z+1)-furthest}, $\delta$ is a strict lower bound of $\delta^*$. 
+Therefore, any point within $\delta$-radius of $c_1$ is guaranteed to be outside $B_2^*$. 
+Thus, property P1 is not violated by this function.
+%$B_1 \cap B_2^* = \emptyset$.
+Note that if less than $z+1$ points have been seen so far,
+then $\delta = 0$, %$q = c_1$, 
+and hence, property P1 is still maintained.
+
+The function \textproc{AddToB$_2$} presented in \Cref{alg:addB2}
+is used to add a point $p$ to $B_2$.
+Initially, $B_2$ is empty and $c_2$ is not initialized. 
+When an appropriate candidate is found, 
+$c_2$ is set to that candidate by the main algorithm (Algorithm~\ref{alg:case-1}),
+and $\rc$ is set to $\frac{2}{\alpha}\len{c_1c_2}$.
+After that, points are added to $B_2$ by function \textproc{AddToB$_2$}
+only if they are within $\rc$-radius of $c_2$. 
+Consider $c_2$ as the central point $c_p$. % is considered as the central point $\cp$. 
+Clearly, property P2 holds initially when $B_2$ consists of a single point $c_2$. 
+All subsequent points added to $B_2$ are within $\rc$-radius of $c_2$.
+Therefore, for $\alpha > 7$ (Why?), Observation~\ref{obs:intersection}
+implies that $B_2 \cap B_1^* = \emptyset$,
+and hence, property P2 is maintained. %invariant under this operation.
+
+When the size of $B_2$ reaches $\dz$, 
+we update the central point $\cp$ to the centerpoint of $B_2$.
+%We claim that $B(c_2, (2 + \frac{2}{\alpha})\rc )$ completely covers
+%the ball $B(\cp, \frac{2\len{c_1\cp}}{\alpha})$.
+If $\cp \in B_2^*$, then by Observation~\ref{obs:c+4},
+we have $\frac{\len{c_1\cp}}{\delta^*} \geq 1$,
+and hence, $r^* < \frac{\len{c_1\cp}}{\alpha}$. 
+Therefore, $B_2^* \subset B(\cp, \frac{2\len{c_1\cp}}{\alpha})$.
+Moreover,
+\[
+	2 \cdot \frac{\len{c_1\cp}}{\alpha} \leq \frac{2}{\alpha}(\len{c_1c_2} + \rc ) 
+	\leq (1 + \frac{2}{\alpha})\rc.
+\]
+Therefore, $B_2^* \subseteq B(c_p, (1 + \frac{2}{\alpha})\rc )
+\subseteq B(c_2, (2 + \frac{2}{\alpha})\rc )$. 
+It is easy to see that $(2 + \frac{2}{\alpha})\rc  \le \frac{\delta}{2}$ provided that $\alpha \ge 14$.
+Thus, if we increase $\rc$ by a factor of $(2 + \frac{2}{\alpha})$, 
+%by setting $B_2 = B(c_2, (2 + \frac{2}{\alpha})\rc )$, 
+$B_2 \cap B_1^* = \emptyset$
+by Observation~\ref{obs:intersection}, and hence,
+property P2 is still maintained.
+
+Whenever the buffer overflows 
+%the assumption about $\cp \in B_2^*$ is contradicted.
+%At some point during the execution of Algorithm~\ref{alg:case-1}, the assumption about $\cp \in B_2^*$ might be contradicted when the buffer overflows. We can then conclude that
+% $\cp \notin B_2^*$.
+the algorithm takes one of the following actions
+depending on the size of $B_2$.
+
+\begin{itemize}
+\item 
+If $|B_2| < \dz$, then $c_2$ can be added to $B_1$
+without violating P1. (Why?) 
+The algorithm then tries the points in $B_2 \cup \mbox{Buffer}$, 
+until it finds a suitable candidate for $c_2$ that does not leave
+more than $z$ points uncovered. 
+Note that at most $(z+1)(d+1) + z$ points have to be tried.
+
+\item 
+If $\card{B_2} \ge \dz$, let $q$ be the $(z+1)$-furthest point from $p_1$,
+and let $p'$ be the nearest point of the ball $B_2(c_2, \rc )$ to $p_1$. 
+Then $\len{qp_1} > \len{p'p_1}$, since $B_2$ contains more than $z+1$ points. 
+Therefore, by Lemma~\ref{lem:(z+1)-furthest} we have
+\[
+\delta \ge \frac{\alpha }{\alpha+4}\len{qp_1} \ge \frac{\alpha}{\alpha+4} (\len{c_1c_2} - \rc ) = \frac{\alpha^2 - 2\alpha}{2\alpha + 8} \rc.
+\]
+As a result, if $\alpha \geq 14$ then $(2 + \frac{2}{\alpha}) \rc  < \frac{\delta}{2}$. 
+By Observation~\ref{obs:intersection}, the ball $B_2(c_2, (2 + \frac{2}{\alpha}) \rc )$ 
+has nonempty intersection with exactly one of $B_1^*$ and $B_2^*$ 
+(i.e., not all of its points can be outliers). 
+Since the buffer overflowed, the assumption about the central point, 
+$\cp$, being in $B_2^*$ has become invalid. 
+By Observation~\ref{obs:omitting-centerpoint}, if $\cp$ is not covered, 
+then the ball $B_1^*$ leaves at least $z+1$ points of $B_2$ uncovered, 
+and there will be more than $z$ outliers. 
+Thus, $\cp$ has to be covered. 
+As a result, $\cp \in B_1^*$ and all the points of $B_2$ can be added to $B_1$. 
+This is done by replacing $B_1$ with $B_1 \cup B_2$, and resetting $B_2$ to empty set.
+\end{itemize}
+\end{proof}
+
+\begin{lemma}
+\label{lem:}
+	After termination of \Cref{alg:case-1}, 
+	if $|B_2| \ge \dz$ and $\cp \not\in B_2^*$,
+	then $B_2 \cap B_2^* = \emptyset$.
+\end{lemma}
+
+\begin{proof}
+	TBA.
+\end{proof}
+
+\paragraph{Streaming Model}
+To implement our algorithm in the streaming model,
+we maintain the sets $B_1$ and $B_2$ 
+in a data structure that supports adding points,
+and gives a $\beta$-approximation to 1-center with $k$ outliers, for $k=0,\dots,z$.
+Moreover, we maintain a set $B_u = B_1 \cup B_2$ in a similar data structure.
+Note that these data structures do not need to maintain all the points. 
+They only need to have a buffer of size $\dz$ that keeps the most recently added points.
+
+Let $B_1'$, $B_2'$, and $B_u'$ be the $\beta$-approximate balls obtained from the data structures
+[This part needs clarification].
+%1-centers obtained from $B_1$, $B_2$ and $B_u$ by the $\beta$-approximation algorithm, respectively. 
+To answer a query, we can use these balls as follows. 
+By our initial assumption about $p_1$, $B_1$ contains $B_1^*$,
+and $B_1'$ is a $\beta$-approximation for $B_1^*$. (Why?)
+But for $B_2$, it might be the case that our assumption about $c_2$ 
+was incorrect, so $B_2'$ may not be a good approximation for $B_2^*$. 
+There are two cases to be considered based oon $\card{B_2}$. 
+If $\card{B_2} < (z+1)(d+1)$, then we can try each point in 
+$B_2 \cup \mbox{Buffer}$ as a candidate for the central point. 
+If $\card{B_2} \ge \dz$, then there is no need for points in $B_2$ to be considered, 
+since for those points as central point, $B_1$ will be replaced by $B_u$ and $B_2$ will be empty. (Why?)
+Thus it suffices to consider points of Buffer as candidates 
+and compare them to the solution of $(B_u, \emptyset)$.
+
+\begin{algorithm}
+\caption{\sc Query} 
+\algsetup{indent=1.5em}
+\label{alg:query}
+\begin{algorithmic}[1]
+%\Function{Query}{}
+	\STATE solutions $\gets [\Call{ComputeMin}{B_u, \emptyset, \text{Buffer}}]$
+
+	\STATE candidates $\gets$ Buffer
+	\IF {$\card{B_2} < \dz$}
+		\STATE candidates $\gets \text{Buffer} \cup B_2$ % \setminus \set{c_2}$
+	\ENDIF
+
+	\FOR{$c_2 \in$ candidates}
+		\STATE $\rc  \gets \frac{2}{\alpha} \len{c_1 c_2}$
+		\STATE $B_2 \gets \emptyset$, Buffer $\gets \emptyset$ 
+		\FOR{$p \in$ candidates}
+			\IF{\NOT \Call{AddToB$_2$}{$p$}}
+				\STATE add $p$ to Buffer
+			\ENDIF
+		\ENDFOR
+		\STATE add \Call{ComputeMin}{$B_1$, $B_2$, Buffer} to solutions
+	\ENDFOR
+	\RETURN $\min\set{\text{solutions}}$
+%\EndFunction
+\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+\caption{\sc ComputeMin($B_1, B_2, \text{\rm Buffer}$)} 
+\algsetup{indent=1.5em}
+\label{alg:query}
+\begin{algorithmic}[1]
+%\Function{ComputeMin}{$B_1$, $B_2$, Buffer}
+	\STATE solutions $\gets [\,]$
+	\FOR{$k \gets 0, \dots,(z - \card{\mbox{Buffer}})$}
+		\STATE $r_1 \gets \Call{1-Center}{B_1, k}$
+		\STATE $r_2 \gets \Call{1-Center}{B_2, z - \card{\mbox{Buffer}} - k}$
+		\STATE add $\max \set{r_1, r_2}$ to solutions
+	\ENDFOR
+	\RETURN $\min\set{\text{solutions}}$
+%\EndFunction
+\end{algorithmic}
+\end{algorithm}
+
+\REM{
+Suppose that our data structure for maintaining $B_1$, $B_2$ and $B_u$ uses $S(n,z,d)$ space, $T(n,z,d)$ update and $Q(n,z,d)$ query time.
+Note that by $Q_{o}(zd,z,d)$ we mean the query time for the offline 1-center problem with $z$ outlier in $d$ dimensions.
+The best known algorithm for 1-center without outliers is $1.22$-approximation by~\cite{chan2014streaming, agarwal2010streaming}.
+The buffering framework introduced in~\cite{zarrabi2009streaming} with $\O(dz^3 + (\frac{d}{\eps^3})\log(\frac{1}{\eps}))$ space complexity, can be used with this algorithm as subroutine to achieve a $(1.22\sqrt{2})$-approximation ($1.22\sqrt{2} < 1.8$) for 1-center problem with outliers.
 
 \begin{theorem}
-For any fixed $d > 1$, our single-pass data stream algorithm whose working space and update time are polynomial in $d$ and sub-linear in $n$, returns two centers that guarantees a $(1.8 + \eps)$-approximation for the Euclidean $2$-center problem with outliers.
+\label{thm:2nd-cmplx}
+Space complexity of Algorithm~\ref{alg:case-1} is $\O(dz+S(n,z,d))$.
+It takes $\O^*(dzT(n,z,d))$ time for update.
+Query time in Algorithm~\ref{alg:query} is $\O(zQ(n,z,d) + dz(dz+zQ_o(zd,z,d)))$ and it returns two centers that guarantee a $(1.8 + \eps)$-approximation for 2-center problem with outliers.
 \end{theorem}
 
-In Section \ref{subsec:smaller}, we give a description of our algorithm for a given $r' > 0$ for the case where $\delta^* < C r^*$ and $1.2r^* \le r' < (1.2 + 2\eps/3)r^*$, which returns a $(1.8 + \eps)$-approximate solution.
-We explain how to find such an $r'$ and present a full description of our algorithm for the case where $\delta^* < C r^*$ in Subsection~\ref{subsec:findr}.
-Then we inspect the case where $\delta^* \ge C r^*$ in Subsection~\ref{subsec:bigger}.
+\begin{proof}
+The space complexity for this algorithm is derived from the space used by $B_1$, $B_2$, $B_u$ and the Buffer which is obviously $\O(dz+S(n,z,d))$.
+The while loop runs at most once for each point, so amortized time is $\O(zdT(n,z,d))$.
+The candidates in the Algorithm~\ref{alg:query} are at most $zd$ points  so the query time will easily follows.
+\end{proof}
+}
 
-\subsection{The Case $\delta^* < C r*$}
+\begin{theorem}
+\label{thm:far-cmplx}
+	If $\delta^* > \alpha r^*$, a $1.8$-approximation to the 2-center problem with $z$ outliers 
+	can be maintained in $O(d^3z^2)$ space and $\poly(d,z)$ update time.
+\end{theorem}
+
+\begin{proof}
+The streaming algorithm of Zarrabi-Zadeh and Mukhopadhyay~\cite{zarrabi2009streaming} 
+equipped with the streaming $1.22$-approximation for 
+1-center~\cite{agarwal2010streaming, chan2014streaming}
+yields a $(1.22 \times \sqrt{2})$-approximation algorithm
+for 1-center with $z$ outliers.
+Since $1.22 \times \sqrt{2} < 1.8$, the approximation factor of our algorithm follows.
+The algorithm of~\cite{zarrabi2009streaming}
+has $O(d^3z)$ space and $\poly(d,z)$ update time,
+which implies the same bounds for \Cref{alg:case-1}.
+Since we need to run $z + 1$ instances of \Cref{alg:case-1} in parallel, 
+the space and update time is increased by a factor of $O(z)$.
+\end{proof}
+
+% -------------------------------- Second Case -----------------------------------
+
+\subsection{The Case $\delta^* \leq \alpha r^*$}
 \label{subsec:smaller}
-Our idea in this section is derived from \cite{ahn2014computing, kim2014improved}.
+Our idea in this section is derived from~\cite{ahn2014computing, kim2014improved}.
 To avoid duplication, we just outline the important parts of their algorithm and our modifications to it.
@@
 It is sufficient to have four integers, $n_1,\dots, n_4$ representing the number of outliers in depth $1$ to $4$, such that $\sum_{i=1}^{4} n_i=z$.
-To sum up, the modified algorithm is defined as follows:
-{
-\algrenewcommand\algorithmicindent{0.8em}%
+The modified algorithm is presented in \Cref{alg:smallc}.
+In this algorithm, \textproc{NthOutlier}$(n,p)$ returns the $n$-th point 
+arriving after $p$ in $P$ that does not lie in the current candidate solution.
+
 \begin{algorithm}
+\caption{\sc 2-CenterCase2$(P, z, r)$} 
+\algsetup{indent=1em}
 \label{alg:smallc}
-\leavevmode
-\begin{algorithmic}
-\Function{Known$r'$}{$\mathcal{P}, z, r'$}
-	\For{$(n_1, \dots, n_4) \gets \set{(n_1, \dots, n_4) \provided \sum n_i=z}$}
-		\State $CS \gets B(p_1,r')$
-		\State $p_{o_2} \gets $ \Call{NthOutlier}{$n_1 + 1$, $p_1$}
-		\If{$p_{o_2}$ arrives}
-			\State $CS\gets [ \text{the sub-case of $p_{o_2} \in B_{2, 1}^*$} ] \cup [ \text{the sub-case of $p_{o_2} \in B_{2,2}^*$} ]$
-			\For{each case $S$}
-				\State $p_{o_3} \gets$ \Call{NthOutlier}{$n_2 + 1$, $p_{o_2}$}
-				\If{$p_{o_3}$ arrives} 
-					\State $CS\gets CS\setminus S \cup [ \text{the sub-case of $p_{o_3} \in B_{2, 1}^*$} ] \cup [ \text{the sub-case of $p_{o_3} \in B_{2,2}^*$}]$
-					\For {each sub-case $S'$} 
-						\State $p_{o_4} \gets$ \Call{NthOutlier}{$n_3 + 1$, $p_{o_3}$}
-						\If {$p_{o_4}$ arrives} 
-							\State Replace $S'$ with a new candidate solution.
-							\State $p_{o_5} \gets$ \Call{NthOutlier}{$n_4 + 1$, $p_{o_4}$}
-							\If{$p_{o_5}$ arrives}
-								\State Abandon the solution.
-							\EndIf
-						\EndIf
-					\EndFor
-				\EndIf
-			\EndFor
+%\leavevmode
+\begin{algorithmic}[1]
+%\Function{Known$r$}{$P, z, r$}
+ 	\STATE list $\gets [\,]$
+	\FORALL{$(n_1, \dots, n_4)$ such that $\sum n_i=z$}
+		\STATE $CS \gets B(p_1,r)$
+		\STATE $p^o_{2} \gets $ \Call{NthOutlier}{$n_1 + 1$, $p_1$}
+		\IF{$p^o_{2}$ arrives}
+			\STATE $CS\gets [ \text{subcase $p^o_{2} \in B_1^*$} ] \cup [ \text{subcase $p^o_{2} \in B_2^*$} ]$
+			\FORALL{case $S$}
+				\STATE $p^o_{3} \gets$ \Call{NthOutlier}{$n_2 + 1$, $p^o_{2}$}
+				\IF{$p^o_{3}$ arrives} 
+					\STATE $CS\gets CS\setminus S \cup [ \text{subcase $p^o_{3} \in B_1^*$} ] \cup [ \text{the subcase $p^o_{3} \in B_2^*$}]$
+					\FORALL {subcase $S'$} 
+						\STATE $p^o_{4} \gets$ \Call{NthOutlier}{$n_3 + 1$, $p^o_{3}$}
+						\IF {$p^o_{4}$ arrives} 
+							\STATE replace $S'$ by a new candidate solution
+							\STATE $p^o_{5} \gets$ \Call{NthOutlier}{$n_4 + 1$, $p^o_{4}$}
+							\IF{$p^o_{5}$ arrives}
+								\STATE abandon the solution
+							\ENDIF
+						\ENDIF
+					\ENDFOR
+				\ENDIF
+			\ENDFOR
 
-		\EndIf
-		\State $\mathop{Sol}_{n_1,n_2,n_3,n_4} \gets$ the solution with the smallest larger radius, among all the sub-cases.
-	\EndFor
-	\State \Return the solution $\mathop{Sol}_{n_1,n_2,n_3,n_4}$ with the smallest radius, for all valid values of $(n_1,n_2,n_3,n_4)$.
-\EndFunction
+		\ENDIF
+		%\STATE $\mathop{Sol}_{n_1,n_2,n_3,n_4} \gets$ the solution with the smallest larger radius, among all the subcases.
+		\STATE add to list the solution with the smallest larger radius, among all subcases
+	\ENDFOR
+	\RETURN the solution in list with the smallest radius
 \end{algorithmic}
 \end{algorithm}
-}
-Here, \textproc{NthOutlier}$(n,p)$ returns the $n$\nth point arriving after $p$ in $\mathcal{P}$ that does not lie in current candidate solution.
 
 \begin{theorem}
-Given $\delta^* < C r^*$ and $1.2r^* \le r' < (1.2 + 2\eps/3)r^*$, Algorithm~\ref{alg:smallc} uses $\cO (dz^3)$ space and returns a $(1.8+\eps)$-approximate solution.
-Algorithm~\ref{alg:smallc} spends $\cO (dz^3)$ update time for each point in $\mathcal{P}$ and answers a query in $\cO (dz^3)$.
+	For $1.2r^* \le r < (1.2 + 2\eps/3)r^*$ and $\delta^* < \alpha r^*$,
+	Algorithm~\ref{alg:smallc} returns a $(1.8+\eps)$-approximate solution,
+	using $\O (dz^3)$ space and $\O (dz^3)$ update and query time.
 \end{theorem}
@@
 Since our algorithm considers all possible input cases of streaming points, there is at least one feasible solution.
-Since every feasible solution has its larger radius at most $3r'/2$, the final solution has larger radius at most $3r'/2 \le (1.8 + \eps)r^*$.
-For space complexity, our algorithm maintains at most two balls in each case, and therefore it uses $\cO(dz^3)$ space.
-Whenever the next point is inserted, the algorithm updates the solution for each sub-case in $\cO (d)$ time.
-Therefore, the algorithm spends $\cO (dz^3)$ update time for each point of $\mathcal{P}$.
-Answering a query consists of choosing the minimum radius among all the candidate solutions, which amounts to $\cO (dz^3)$ time.
+Since every feasible solution has its larger radius at most $3r/2$, the final solution has larger radius at most $3r/2 \le (1.8 + \eps)r^*$.
+For space complexity, our algorithm maintains at most two balls in each case, and therefore it uses $\O(dz^3)$ space.
+Whenever the next point is inserted, the algorithm updates the solution for each subcase in $\O (d)$ time.
+Therefore, the algorithm spends $\O (dz^3)$ update time for each point of $P$.
+Answering a query consists of choosing the minimum radius among all the candidate solutions, which amounts to $\O (dz^3)$ time.
 \end{proof}
 
-\subsubsection{Finding $r'$}
+\subsubsection{Finding $r$}
 \label{subsec:findr}
@@
 \begin{lemma}
-\label{lem:1lt2}
-A $1$-center optimal solution with $z$ outliers for a set of points is also an upper bound for the $2$-center optimal solution with $z$ outliers.
+\label{lem:1-2}
+	An optimal solution for the 1-center problem with $z$ outliers on a point set
+	gives a $(2 + {\alpha \over 2})$-approximation for
+	the 2-center problem with $z$ outliers on that set,
+	provided that $\delta^* \le \alpha r^*$.
 \end{lemma}
+
+%\begin{lemma}
+%\label{lem:1-2}
+%	Let $r_1^*$ and $r^*$ be optimal solutions for
+%	the 1-center and 2-center problems with $z$ outliers, respectively.
+%	If the optimal 2-center balls have distance at most $\alpha r^*$, 
+%	then $r^* \le r_1^* \le \left(2 + \frac{\alpha}{2}\right) r^*$.
+%\end{lemma}
+
 \begin{proof}
-Let $B^*(c^*, r_1^*)$ be the optimal solution for the $1$-center problem.
-Let $B'$ be a ball with radius $r_1^*$ and center at $\infty$.
-Clearly, $(B^*, B')$ is a solution for $2$-center problem.
-Thus, the proof is complete.
+Let $r_1^*$ and $r^*$ be the optimal radii for
+the 1-center and 2-center problems with $z$ outliers on $P$, respectively.
+It is clear that $r^* \le r_1^*$,
+because any feasible solution $B^*$ for 1-center with $z$ outliers
+yields a feasible solution $(B^*, B^*)$ for 2-center with $z$ outliers.
+%Let $B^*$ be an optimal solution for the 1-center problem with $z$ outliers. 
+%Then, $(B^*, B^*)$ is a feasible solution for the 2-center problem with $z$ outliers. 
+%Hence, $r_2^* \le r_1^*$.
+Now, suppose that $B_1^*(c_1^*, r^*)$ and $B_2^*(c_2^*, r^*)$
+are the balls in an optimal solution for the 2-center problem with $z$ outliers.
+Let $c$ be the midpoint of the segment connecting 
+$c_1^*$ to $c_2^*$ (see Figure~\ref{fig:2lt1}).
+Clearly, $B\left(c, \frac{\delta}{2} + 2r_2^*\right)$ covers both $B_1^*$ and $B_2^*$. 
+Therefore, it is a feasible solution for the 1-center problem with $z$ outliers.
+Hence, $ r_1^* \le \left(2 + \frac{\alpha}{2}\right) 2^*$.
 \end{proof}
 
-\begin{lemma}
-\label{lem:2lt1}
-Let $r_1^*, r_2^*$ be the radius of $1$-center and $2$-center optimal solutions with $z$ outliers, respectively. Then $r_1^* < \left(\frac{C}{2} + 2\right) r_2^*$.
-\end{lemma}
-\begin{proof}
-Suppose that $(B_{2, 1}^*(c_1^*, r_2^*), B_{2,2}^*(c_2^*, r_2^*))$ is an optimal solution for $2$-center problem. Consider $m$ as the midpoint of segment 
-$c_1^*c_2^*$ (Figure~\ref{fig:2lt1}).
-Clearly, $B\left(m, \frac{\delta}{2} + 2r_2^*\right)$ covers both $B_{2, 1}^*$ and $B_{2,2}^*$. So it is a solution for $1$-center problem and the proof is complete.
-\end{proof}
-
-\begin{figure}[h]
+\begin{figure}[th]
 	\centering
 	\includegraphics[width=19em]{figs/2lt1}
-	\caption{Proof of Lemma~\ref{lem:2lt1}}
+	\caption{Proof of Lemma~\ref{lem:1-2}}
 	\label{fig:2lt1}
@@
 
-Algorithm~\ref{alg:1center} finds a $2$-approximation for $r_1^*$. By Lemma \ref{lem:1lt2} and \ref{lem:2lt1}, it gives a $2\left(\frac{C}{2} + 2\right)$-approximation for $r_2^*$.
+\noindent 
+The following is a direct corollary of Lemma~\ref{lem:1-2} and Theorem~\ref{thm:1-center}.
+
+\begin{cor}
+	If $\delta^* \le \alpha r^*$, 
+	\Cref{alg:1-center} computes a $(4 + \alpha)$-approximation to $r^*$. 
+\end{cor}
 
@@
 
-Our algorithm maintains $m=\ceil{\frac{1.2(3C+12)}{\eps}}$ candidate lengths.
-For each candidate length $t$, assume that $r' = t$ and use it to run Algorithm~\ref{alg:smallc}.
-Algorithm~\ref{alg:1center} is used to estimate $r'$.
-Let $k_i$ be the $i$\nth non-zero radius calculated by the algorithm.
+Our algorithm maintains $m=\ceil{{1.2 \times (3 \alpha+12)}/{\eps}}$ candidate lengths.
+For each candidate length $t$, assume that $r = t$ and use it to run Algorithm~\ref{alg:smallc}.
+Algorithm~\ref{alg:1-center} is used to estimate $r$.
+Let $k_i$ be the $i$-th non-zero radius calculated by the algorithm.
 Obviously, the sequence of answers given by the algorithm is increasing.
 
-Let $l_1=k_1$ and $l_i=2^j l_1$, where $l_i$ is the smallest number satisfying $l_i \ge k_i$.
-By Observation~\ref{obs:2apr}, $l_i$ is a $(2C + 8)$-approximation for $r_2^*$.
-If the interval $(0, 1.2 l_i]$ divides into $m$ equal segments (Figure~\ref{fig:findr}), then length of each segment is at most $2/3 \eps r_2^*$ and the endpoints as candidates are $\mathcal{L}_i = \set{j \times t_i \provided j = 1, \dots, m}$ where $t_i = \frac{1.2 l_i}{m}$.
+Let $l_1=k_1$ and $l_i=2^j l_1$, where $l_i$ is the smallest number satisfying $l_i \ge k_i$. By Observation~\ref{obs:2apr}, $l_i$ is a $(8 + 2\alpha)$-approximation to $r_2^*$.
+If the interval $(0, 1.2 l_i]$ divides into $m$ equal segments (Figure~\ref{fig:findr}), then length of each segment is at most $2/3 \eps r_2^*$ and the endpoints as candidates are $L_i = \set{j \times t_i \provided j = 1, \dots, m}$ where $t_i = \frac{1.2 l_i}{m}$.
 The inequality $1.2 r_2^* \le j \times l_i \le (1.2 + \frac{2\eps}{3})r_2^*$ holds for at least one of these candidates.
@@
 	\includegraphics[width=21em]{figs/findr}
-	\caption{Subdivision of $(0, 1.2 l_i]$ interval}
+	\caption{Subdivision of the interval $(0, 1.2 \ell_i]$}
 	\label{fig:findr}
@@
 When the first non-zero radius is observed, $l_1$ is set.
-Algorithm~\ref{alg:smallc} should be executed for each candidate in $\mathcal{L}_1$ for all the previous points, which have been stored in a buffer.
-It is not hard to see that the space complexity for storing these points is $\cO(z)$.
-For each new point, if $l_i=l_{i-1}$ then $\mathcal{L}_i = \mathcal{L}_{i-1}$ and it suffices to add the new point to all parallel instances corresponding to candidates in $\mathcal{L}_i$.
-Otherwise, Algorithm~\ref{alg:smallc} should be executed for all of the candidates in $\mathcal{L}_i$, with all the points.
+Algorithm~\ref{alg:smallc} should be executed for each candidate in $L_1$ for all the previous points, which have been stored in a buffer.
+It is not hard to see that the space complexity for storing these points is $\O(z)$.
+For each new point, if $l_i=l_{i-1}$ then $L_i = L_{i-1}$ and it suffices to add the new point to all parallel instances corresponding to candidates in $L_i$.
+Otherwise, Algorithm~\ref{alg:smallc} should be executed for all of the candidates in $L_i$, with all the points.
 But this is not achievable due to space limitations.
-To overcome this problem, note that if the candidate $x_j=j \times t_i \in \mathcal{L}_i$ is also in $\mathcal{L}_{i-1}$, there is no need to start Algorithm~\ref{alg:smallc} over and the current execution will be continued.
-If $x_j \notin \mathcal{L}_{i-1}$, then it is certain that $x_j \ge l_{i - 1}$ (Observe that $l_i=ul_{i-1}$, for some $u\in \mathbb{N}$).
-Since the points that do not lie in the candidate solution are saved in the buffer used in Algorithm~\ref{alg:1center} (which has size at most $z$), all the non-outlier points of this algorithm lie in the candidate balls in Algorithm~\ref{alg:smallc}.
+To overcome this problem, note that if the candidate $x_j=j \times t_i \in L_i$ is also in $L_{i-1}$, there is no need to start Algorithm~\ref{alg:smallc} over and the current execution will be continued.
+If $x_j \notin L_{i-1}$, then it is certain that $x_j \ge l_{i - 1}$ (Observe that $l_i=ul_{i-1}$, for some $u\in \mathbb{N}$).
+Since the points that do not lie in the candidate solution are saved in the buffer used in Algorithm~\ref{alg:1-center} (which has size at most $z$), all the non-outlier points of this algorithm lie in the candidate balls in Algorithm~\ref{alg:smallc}.
 These outliers have been stored in a buffer, so for the new candidate length, it suffices to execute Algorithm~\ref{alg:smallc} with only the outlier points of $B_1$.
 
+%\begin{theorem}
+%\label{thm:1st-cmplx}
+%Algorithm~\ref{alg:smallc} uses $\O(\frac{dz^3}{\eps})$ space, and takes $\O(\frac{dz^4}{\eps})$ and $\O(\frac{dz^3}{\eps})$ time for update and query, respectively.
+%\end{theorem}
+
 \begin{theorem}
-\label{thm:1st-cmplx}
-Algorithm~\ref{alg:smallc} uses $\cO(\frac{dz^3}{\eps})$ space, and takes $\cO(\frac{dz^4}{\eps})$ and $\cO(\frac{dz^3}{\eps})$ time for update and query, respectively.
+\label{thm:close-cmplx}
+	If $\delta^* \leq \alpha r^*$, a $(1.8 + \eps)$-approximation to the 2-center problem with $z$ outliers 
+	can be maintained in $\O(\frac{dz^4}{\eps})$ space 
+	and $\O(\frac{dz^3}{\eps})$ update/query time.
 \end{theorem}
 
-\subsection{The Case $\delta^* \ge C r^*$}
-\label{subsec:bigger}
-
-\begin{obs}
-\label{obs:c+4}
-Let $d$ be the distance between arbitrary pair of points from two $C$-separated balls. Then $1 \le \frac{d}{\delta} \le \frac{C+4}{C}$.
-\end{obs}
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=21em]{figs/c_plus_4}
-	\caption{Depiction of two extreme case of Observation~\ref{obs:c+4}}
-	\label{fig:c+4}
-\end{figure}
-
-\begin{obs}
-\label{obs:intersection}
-Let $B_1$ and $B_2$ be two disjoint balls with distance $\delta$ and $B$ be an arbitrary ball of radius at most $\frac{\delta}{2}$. Then $B$ can intersect at most one of $B_1$ and $B_2$.
-\end{obs}
-
-\begin{lemma}
-\label{lem:c-sep}
-Let $\mathcal{P}$ be a set of points and assume that $B_{2,1}^*$ and $B_{2,2}^*$ are $C$-separated ($C \ge 4$) and let $p_1$ be an arbitrary point in $B_{2,1}^*$.
-Define $S$ as the $z+1$ furthest points of $\mathcal{P}$ from $p_1$.
-Then $S \cap B_{2,2}^*$ is nonempty.
-\end{lemma}
-\begin{proof}
-By contradiction, assume that $S \cap B_{2,2}^*$ is empty.
-It is clear that $S$ contains at least one non-outlier point.
-Let $q$ be the furthest point of $S \cap B_{2,1}^*$ from $p_1$.
-Consider $B(p_1, \card{p_1q})$.
-It is clear that $B$ covers $\mathcal{P} \setminus S$.
-Since $p_1, q \in B_{2,1}^*$, then $\card{p_1q}$ is at most $2r_2^*$.
-Thus by Observation~\ref{obs:intersection}, $B_{2,2}^* \cap B = \emptyset$.
-Therefore $B_{2,2}^* \cap \mathcal{P} = \emptyset$ and hence $B_{2,2}^*$ is empty, which contradicts the optimality of this solution.
-\end{proof}
-
-Let $B_1, B_2$ and $B_u$, be instances of a data structure that supports adding a point and gives a $\beta$-approximation for $1$-center problem with $k$ outliers, for $k=0,\dots,z$ (This data structure, does not need to maintain all the points.
-Suppose that it has a buffer with length $(d+1)(z+1)$ that maintains the most recently added points).
-Algorithm~\ref{alg:case2} assumes point $p_1$ to be in $B_{2,1}^*$.
-This algorithm maintains $c_1$ as an arbitrary point in $B_{2,1}^*$ and $c_2$ as a candidate that may be in $B_{2,2}^*$.
-It tries to divide points into three subdivisions:
-\begin{itemize}
-\item $B_1$, a subset of $\mathcal{P}$ where $B_1 \cap B_{2,2}^* = \emptyset$, that is a set of points that provably lie outside $B_{2, 2}^*$.
-\item $B_2$, a subset of $\mathcal{P}$ along with a \emph{candidate point} $c_p$, such that if $B_{2, 2}^*$ covered the candidate point, then $B_2 \cap B_{2, 1}^* = \emptyset$.
-\item Buffer, with size at most $z$ that if $c_p \in B_{2, 2}^*$ then all of them are outliers.
-\end{itemize}
-Algorithm~\ref{alg:case2} also maintains $B_u$ as union of $B_1$ and $B_2$.
-
-\begin{lemma}
-\label{lem:(z+1)-furthest}
-Let $p_1$ be an arbitrary points in $B_{2,1}^{*}$ and $q$ be the $(z+1)$\st furthest point from $p_1$. Then $\frac{C}{C+4}\card{qp_1}$ is a lower bound for $\delta^*$.
-\end{lemma}
-\begin{proof}
-Due to Lemma~\ref{lem:c-sep}, there exists $p_2 \in B_{2,2}^*$ such that $\card{p_1p_2} \ge \card{qp_1}$.
-Thus, by Observation~\ref{obs:c+4}, $\frac{C}{C+4} \card{p_1p_2} \le \delta^*$.
-The claim follows immediately.
-\end{proof}
-
-Function \textproc{AddTo$B_1$} is used to add a point $p$ to $B_1$.
-The point will be added only if the point is within $\delta$\nobreakdash-radius of the center $c_1$, where $\delta$, calculated by Algorithm~\ref{alg:case2}, is $\frac{C}{C+4}\card{qc_1}$ and $q$ is the $(z+1)$\nth furthest point from $c_1$.
-By Lemma~\ref{lem:(z+1)-furthest}, $\delta$ is a lower bound for $\delta^*$.
-So any point within $\delta$-radius of $c_1$ is guaranteed to lie outside $B_{2,2}^*$.
-Thus Function \textsc{AddTo$B_1$} does not violate the property $B_1 \cap B_{2,2}^* = \emptyset$.
-\begin{algorithmic}
-\Function{AddTo$B_1$}{$p$}
-	\If{$p \in B(p_1, \delta)$}
-		\State $B_1 = B_1 \cup \set{p}, B_u = B_u \cup \set{p}$
-		\State \Return{true}
-	\EndIf
-	\State \Return{false}
-\EndFunction
-\end{algorithmic}
-
-Function \textproc{AddTo$B_2$} is used to add a point $p$ to $B_2$.
-Initially, $B_2$ is empty and $c_2$ and $r_c$ are not initialized.
-When an appropriate candidate is found, Algorithm~\ref{alg:case2} sets $c_2$ to that candidate and $r_c$ to $\frac{2\card{c_1c_2}}{C}$ and after that, points are added to $B_2$ only if they lie within $r_c$-radius of $c_2$.
-At this point $c_2$ is considered as the candidate point $c_p$.
-Clearly the subdivision property for $B_2$ holds initially when $B_2$ consists of the single point $c_2$.
-All the subsequent points added to $B_2$ are within $r_c$-radius of $c_2$ and given $C\ge 7$, by Observation~\ref{obs:intersection} subdivision property is invariant under this operation.
-
-When $\card{B_2}$ reaches $(d+1)(z+1)$, the candidate point changes to center point of $B_2$ and $r_c$ is increased by a factor of $(2 + \frac{2}{C})$ to completely cover the new candidate point and it's surrounding ball.
-It is easy to see that $(2 + \frac{2}{C})r_c < \frac{\delta}{2}$ provided $C \ge 14$ and thus by Observation~\ref{obs:intersection} the property is not violated.
-
-\begin{algorithmic}
-\Function{AddTo$B_2$}{p}
-	\If{$c_2$ is set and $p \in B(c_2, r_c)$}
-		\State $B_2 \gets B_2 \cup \set{p}, B_u \gets B_u \cup \set{p}$
-		\If{$\card{B_2} = (d+1)(z+1)$}
-			\State $r_c \gets  (2 + \frac{2}{C}) \times r_c$
-			\For{$p$ in Buffer}
-				\If{$p$ in $B(c_2, r_c)$}
-					\State $B_2 \gets B_2 \cup \set{p}, B_u \gets B_u \cup \set{p}$
-				\EndIf
-			\EndFor
-		\EndIf
-		\State \Return{true}
-	\EndIf
-	\State \Return{false}
-\EndFunction
-\end{algorithmic}
-
-\begin{prop}
-Every finite set of points in $d$\nobreakdash-dimensional Euclidean space admits a centerpoint.\cite{edelsbrunner1987algorithms}
-\end{prop}
-
-\begin{cor}
-\label{cor:omitting-centerpoint}
-Given a set $\mathcal{P}$ of $k(d+1)$ points in $d$\nobreakdash-dimensional Euclidean space, there is a point $c_p$, not necessarily in $\mathcal{P}$, that any convex object that does not cover $c_p$, leaves at least $k$ points of $\mathcal{P}$ uncovered.
-\end{cor}
-
-Let the new candidate point be the centerpoint of points in $B_2$, when $(z+1)(d+1)$ points have been added to $B_2$.
-We claim that with $B_2 = B(c_2, (2 + \frac{2}{C})r_c)$, ball $B(c_p, \frac{2\card{c_1c_p}}{C})$ completely covered.
-If $c_p \in B_{2,2}^*$ then by Observation~\ref{obs:c+4}, $r^* \le \frac{\card{c_1c_p}}{C}$. Thus $B_{2,2}^* \subseteq B(c_p, \frac{2\card{c_1c_p}}{C})$.
-Since:
-\[
-\frac{2\card{c_1c_p}}{C} \leq \frac{2}{C}(\card{c_1c_2} + r_c) \leq (1 + \frac{2}{C})r_c
-\]
- then $B_{2,2}^* \subseteq B(c_p, (1 + \frac{2}{C})r_c) \subseteq B(c_2, (2 + \frac{2}{C})r_c)$.
-Thus supposing $C \ge 14$ and by Observation~\ref{obs:intersection}, $B_2 \cap B_{2,1}^* = \emptyset$.
-Thus the claim follows.
-
-At some point during the execution of Algorithm \ref{alg:case2}, the assumption about $c_p \in B_{2,2}^*$ might be contradicted when the buffer overflows. We can then conclude that
-% Sahand: Verify this:
-%$c_2 \notin B_{2,2}^*$.
- $c_p \notin B_{2,2}^*$.
-At this point, behavior of Algorithm~\ref{alg:case2} depends on size of $B_2$ relative to $(d+1)(z+1)$:
-\begin{itemize}
-\item If $\card{B_2} < (d+1)(z+1)$ then $c_2$ can be added to $B_1$, by definition of $B_1$.
-The algorithm then tries all points in $B_2 \cup \mbox{Buffer} \setminus \set{c_2}$, until it finds a suitable candidate point for $c_2$ that does not leave too many points uncovered.
-Note that at most $(z+1)(d+1) + z$ points have to be tried.
-\item If $\card{B_2} \ge (d+1)(z+1)$, let $q$ be the $(z+1)$\st furthest point from $p_1$ and $p'$ be the nearest point of ball $B_2(c_2, r_c)$ to $p_1$.
-Then $\card{qp_1} > \card{p'p_1}$, since $B_2$ contains more than $z+1$ points.
-So by Lemma~\ref{lem:(z+1)-furthest}:
-\[
-\delta \ge \frac{C \card{qp_1}}{C+4} \ge \frac{C}{C+4} (\card{c_1c_2} - r_c) = \frac{C^2 - 2C}{2C + 8} r_c
-\]
-As a result, if $C \geq 14$ then $(2 + \frac{2}{C}) r_c < \frac{\delta}{2}$.
-As shown in Observation~\ref{obs:intersection}, the ball $B_2(c_2, (2 + \frac{2}{C}) r_c)$ has nonempty intersection with exactly one of $B_{2, 1}^*$ and $B_{2, 2}^*$ (not all of its points can be outliers).
-Since the buffer overflowed, the assumption about the candidate point, $c_p$, being in $B_{2,2}^*$ must have been invalid.
-By Corollary~\ref{cor:omitting-centerpoint} if $c_p$ is not covered, then circle $B_{2,1}^*$ leaves at least $z+1$ points of $B_2$ uncovered, and there will be more than $z$ outliers.
-Thus, $c_p$ has to be covered.
-As a result, $c_p \in B_{2, 1}^*$ and all the points of $B_2$ can be added to $B_1$.
-This is done by replacing $B_1$ with $B_u$ and initializing $B_2$ over again.
-\end{itemize}
-
-{
-\algrenewcommand\algorithmicindent{0.6em}%
-\begin{algorithm}
-\label{alg:case2}
-\leavevmode
-\begin{algorithmic}
-\State $\delta \gets 0, r_c \gets 0$
-\State $c_1 \gets p_1$
-\For{$p \in P$}
-	\If{at least $z+1$ points have been processed}
-		\State $q \gets$  $(z+1)$-furthest point from $c_1$
-	\Else
-		\State $q \gets c_1$
-	\EndIf
-	\State $\delta \gets \frac{C}{C+4} \card{c_1q}$
-	\If{\Call{AddTo$B_1$}{$p$} = False and  \Call{AddTo$B_2$}{$p$} = False}
-% Sahand: is ! a familiar notation for CS people? should we use \neg? or not?
-% Kiana: Agree, What about this one?
-		\State add $p$ to Buffer
-		\While{$\card{\mbox{Buffer}} > z$}
-			\If{$\card{B_2} \ge (d+1)(z+1)$}
-				\State $B_1 \gets B_u$, $B_2 \gets \emptyset$
-			\ElsIf{$c_2$ is set}
-				\State $B_1 \gets B_1 \cup \set{c_2}$, $B_u \gets B_u \cup \set{c_2}$
-			\EndIf
-			\State $T \gets \mbox{Buffer} \cup B_2 - \set{c_2}$
-			\State $\mbox{Buffer} \gets \emptyset, B_2 \gets \emptyset$
-			\If{first iteration of while}
-				\For{$p \in T$}
-					\If{\Call{AddTo$B_1$}{$p$}}
-						\State Remove $p$ from $T$.
-					\EndIf
-				\EndFor
-			\EndIf
-			\State $c_2 \gets$ arbitrary point in $T$
-			\State $r_c \gets \frac{2}{C}\card{c_1 c_2}$
-			\For{$p \in T$}
-				\State \Call{AddTo$B_2$}{$p$}
-			\EndFor				
-			\State $\mbox{Buffer} \gets T \setminus B_2$
-		\EndWhile
-	\EndIf
-\EndFor
-\end{algorithmic}
-\end{algorithm}
-}
-
-Let $B_1'$, $B_2'$ and $B_u'$ be the $1$-centers obtained from $B_1$, $B_2$ and $B_u$ by the $\beta$-approximation algorithm, respectively.
-To answer a query, we use these balls.
-By the initial assumption about $p_1$, $B_1$ contains $B_{2,1}^*$ and $B_1'$ is a $\beta$-approximation for $B_{2,1}^*$.
-But for $B_2$ it may be the case that our assumption about the candidate point was incorrect or non-optimal, so $B_2'$ is not a good approximation for $B_{2,2}^*$.
-There are two cases for $\card{B_2}$ to be considered.
-If $\card{B_2} < (z+1)(d+1)$, then we can try each point in $B_2 \cup \mbox{Buffer}$ as a candidate for the candidate point.
-If $\card{B_2} \ge (d+1)(z+1)$, then there is no need for points in $B_2$ to be considered, since for those points as candidate point, $B_1$ would be replaced by $B_u$ and $B_2$ would be empty.
-Thus it suffices to consider points of Buffer as candidates and compare them to the solution $(B_u, \emptyset)$.
-{
-\algrenewcommand\algorithmicindent{0.8em}%
-\begin{algorithm}
-\label{alg:query}
-\leavevmode
-\begin{algorithmic}
-\Function{Query}{}
-	\State solutions = [\Call{QuerySubdivision}{$B_1$ $B_2$ Buffer}]
-
-	\If {$\card{B_2} \geq (d+1)(z+1)$}
-		\State candidates $\gets$ Buffer
-	\Else
-		\State candidates $\gets$ Buffer $\cup B_2 - \set{c_2}$
-	\EndIf
-
-	\For{$c_2 \in$ candidates}
-		\State $r_c \gets \frac{2}{C} \card{c_1 c_2}$
-		\State $B_2 \gets \emptyset$, Buffer $\gets \emptyset$ 
-		\For{$p \in$ candidates}
-			\If{not \Call{AddTo$B_2$}{$p$}}
-				\State Add $p$ to Buffer.
-			\EndIf
-		\EndFor
-		\State Add \Call{QuerySubdivision}{$B_1$, $B_2$, Buffer} to solutions.
-	\EndFor
-	\State \Return \Call{$\min$}{solutions}
-\EndFunction
-\Statex
-\Function{QuerySubdivision}{$B_1$, $B_2$, Buffer}
-	\State solutions $\gets$ empty list
-	\For{$k \gets 0, \dots,(z - \card{\mbox{Buffer}})$}
-		\State $r \gets \max(1-\mbox{center}(B_1, k), 1-\mbox{center}(B_2, z - \card{\mbox{Buffer}} - k))$
-		\State Add $r$ to solutions.
-	\EndFor
-	\State \Return \Call{$\min$}{solutions}
-\EndFunction
-\end{algorithmic}
-\end{algorithm}
-}
-
-Suppose that our data structure for maintaining $B_1$, $B_2$ and $B_u$ uses $S(n,z,d)$ space, $T(n,z,d)$ update and $Q(n,z,d)$ query time.
-Note that by $Q_{o}(zd,z,d)$ we mean the query time for the offline $1$-center problem with $z$ outlier in $d$ dimensions.
-The best known algorithm for $1$-center without outliers is $1.22$-approximation by \cite{chan2014streaming, agarwal2010streaming}.
-The buffering framework introduced in \cite{zarrabi2009streaming} with $\cO(dz^3 + (\frac{d}{\eps^3})\log(\frac{1}{\eps}))$ space complexity, can be used with this algorithm as subroutine to achieve a $(1.22\sqrt{2})$-approximation ($1.22\sqrt{2} < 1.8$) for $1$-center problem with outliers.
+\subsection{Final Result}
 
 \begin{theorem}
-\label{thm:2nd-cmplx}
-Space complexity of Algorithm~\ref{alg:case2} is $\cO(dz+S(n,z,d))$.
-It takes $\cO^*(dzT(n,z,d))$ time for update.
-Query time in Algorithm~\ref{alg:query} is $\cO(zQ(n,z,d) + dz(dz+zQ_o(zd,z,d)))$ and it returns two centers that guarantee a $(1.8 + \eps)$-approximation for $2$-center problem with outliers.
-% Sahand: Our analysis requires that $\beta \le 1.8+\eps$.
-Should we mention that somewhere?
-Someone might suspect using a worse approximation algorithm for 1-center he can achieve the same result with better time complexity.
-% Kiana: I don't think so.
+	A $(1.8 + \eps)$-approximation to the 2-center problem with $z$ outliers
+	can be maintained in the streaming model using 
+	$\O(dz^2 (d^2 + z^2/\eps))$ space and 
+	$\poly(d, z, {1 \over \eps})$ update/query time.
 \end{theorem}
@@
 \begin{proof}
-The space complexity for this algorithm is derived from the space used by $B_1$, $B_2$, $B_u$ and the Buffer which is obviously $\cO(dz+S(n,z,d))$.
-The while loop runs at most once for each point, so amortized time is $\cO(zdT(n,z,d))$.
-The candidates in the Algorithm \ref{alg:query} are at most $zd$ points  so the query time will easily follows.
+This is immediate from Theorems~\ref{thm:far-cmplx} and~\ref{thm:close-cmplx}.
+%and the fact that $p_1$ was assumed to be a non-outlier.
 \end{proof}
 
-\begin{theorem}
-Our algorithm uses $\cO(zS(n, z, d) + \frac{dz^4}{\eps})$ space and has time complexity $\cO^*(dz^2T(n,z,d) + \frac{dz^5}{\eps})$ and $\cO(z^2Q(n,z,d) + dz^2(dz+zQ_o(zd,z,d)) + \frac{dz^4}{\eps})$ for update and query operations, respectively.
-It returns a $(1.8 + \eps)$-approximate solution for $2$-center problem with outliers in any dimension.
-\end{theorem}
-\begin{proof}
-Result follows immediately from Theorems~\ref{thm:1st-cmplx} and \ref{thm:2nd-cmplx} and the fact that $p_1$ was assumed to be a non-outlier.
-\end{proof}
-
-with space complexity of Zarrabi-zadeh \cite{zarrabi2009streaming} algorithm, the space complexity of our algorithm would be $\cO(\frac{dz^4}{\eps} + \frac{dz}{\eps^3})$.
+%\begin{theorem}
+%Our algorithm uses $\O(zS(n, z, d) + \frac{dz^4}{\eps})$ space and has time complexity $\O^*(dz^2T(n,z,d) + \frac{dz^5}{\eps})$ and $\O(z^2Q(n,z,d) + dz^2(dz+zQ_o(zd,z,d)) + \frac{dz^4}{\eps})$ for update and query operations, respectively.
+It returns a $(1.8 + \eps)$-approximate solution for 2-center problem with outliers in any dimension.
+%\end{theorem}
+%
+%\noindent 
+%Using the algorithm of~\cite{zarrabi2009streaming}, 
+%the space complexity of our algorithm is $\O(\frac{dz^4}{\eps} + \frac{dz}{\eps^3})$.
 
@@
 
-In this paper, we presented a $(1.8 + \eps)$-approximation streaming algorithm for $2$-center problem with outliers in Euclidean space, which improves previous $(3+\eps)$-approximation algorithm by Charikar~\etal~\cite{mccutchen2008streaming}.
-It remains open whether there can be any improvements in approximation factor.
-It is an interesting problem to find an algorithm with better approximation factor or space complexity.
-It is also interesting to see if the ideas in this paper can be applied to $k$-center problem with outliers in streaming data model, even for small $k$.
+In this paper, we presented a $(1.8 + \eps)$-approximation streaming algorithm for 2-center problem with outliers in Euclidean space.
+It improves the previous $(4+\eps)$-approximation algorithm available for the problem 
+due to Charikar~\etal~\cite{mccutchen2008streaming}. 
+Finding better approximation factor or space complexity
+is an interesting problem that remains open.
+It is also interesting to see if the ideas in this paper 
+can be extended to the $k$-center problem with outliers in the data stream model
+for any $k$, or even for small values of $k \ge 3$.
+
+\paragraph{Acknowledgement}
+The authors would like to thank Kiana Ehsani and Sahand Mozaffari 
+for their thoughtful discussions, 
+and for their contribution to improve the presentation of this paper.
 

### 2015-04-28 paper.tex
add \delta > \alpha r^* variants and definition images and dag image

@@
 \usepackage[noend]{algorithmic}
+\usepackage{tikz}
+\usetikzlibrary{arrows}
 
@@
 Given a stream of points in arbitrary $d$ dimensions, the goal is to find two congruent balls 
-of minimum radius covering all but $z$ points. 
+of minimum radius covering all but $z$ points (\Cref{fig:definition}). 
 We provide a $(1.8+\eps)$-approximation streaming algorithm for the problem, 
@@
 $\O(n z^{7} \log^3 z)$-time algorithm for 2-center with $z$ outliers in the plane.
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=12em]{figs/definition}
+	\caption{$2$-center problem with 6 outlier}
+	\label{fig:definition}
+\end{figure}
 
@@
 for some constant $\alpha$ to be fixed later.
-(It will be turn out that $\alpha = 14$ is a proper choice.)
+(It will be turn out that $\alpha = 16$ is a proper choice.)
 We then present in \Cref{subsec:smaller} 
@@
 \begin{lemma}
-\label{lem:}
-	If $p \in B_1^*$ and $q \in B_2^*$,
-	then at most $z$ points of $P$ lie outside $B(p, 2r^*) \cup B(q, 2r^*)$.
+\label{lem:2r}
+	If $p \in B_1^*(c_1, r^*)$ and $q \in B_2^*(c_2, r^*)$,
+	then $B_1^* \subset B(p, 2r^*)$ and $B_2^* \subset B(q, 2r^*)$ and as a result at most $z$ points of $P$ lie outside $B(p, 2r^*) \cup B(q, 2r^*)$.
 \end{lemma}
@@
 \begin{proof}
-	TBA.
+	For any arbitrary point $p' \in B_1^*$, $\len{pq} \leq \len{pc_1} + \len{qc_1} \leq 2r^*$ and as a result $B_1^* \subset B(p, 2r^*)$(With similar proof, $B_2^* \subset B(q, 2r^*)$).
+Considering that at most $z$ points of $P$ is outlier,  the proof is complete.
 \end{proof}
@@
 \begin{lemma}
-\label{lem:}
+\label{lem:center-point}
 	Let $S$ be a subset of $P$ of size at least $\dz$,
-	enclosed by a ball of radius $\delta^* / 2$.
-	Then the centerpoint of $S$ lies either inside $B_1^{*}$ or inside $B_2^{*}$.
+	enclosed by a ball $B$ of radius less than $\delta^* / 2$.
+	Then the centerpoint $c_p$ of $S$ lies either inside $B_1^{*}$ or inside $B_2^{*}$.
 \end{lemma}
@@
 \begin{proof}
-	TBA.
+	By Observation~\ref{obs:intersection}, ball $B$ intersects exactly one of $B_1^*$ and $B_2^*$ (all points of $S$ can not be outlier).
+Without loss of generality, Let $B$ intersect with $B_1^*$.
+If $c_p \not \in B_1^*$, then there is at least $\ceil{\frac{\dz}{d+1}} = z+1$ points in $S$ locate outside of $B_1^*$ and $B_2^*$, which contradicts existance of at most $z$ outlier.
 \end{proof}
@@
 %			\ENDIF
-			\STATE $c_2 \gets$ an arbitrary point of $T$
+			\STATE $c_2 \gets$ (z+1)-furthest point of $T$ from $c_1$
 			\STATE $\rc  \gets \frac{2}{\alpha}\len{c_1 c_2}$
@@
 \item [(a)] $\delta < \delta^*$ %$\delta$ is a lower bound of $\delta^*$
-\item [(b)] $B_1 \cap B_2^* = \emptyset$
-\item [(c)]  if $\cp \in B_2^*$, then 
+\item [(b)] if $c_2$ is set, then
 \begin{enumerate}
-		\item [1.] $2r^* \le r \le \delta /2$
-		\item [2.] $B_2 \cap B_1^* = \emptyset$
-		\item [3.] all points in $\Buffer$ are outliers
+	\item[1.] $r_0 = \frac{2 \len{c_1 c_2}}{\alpha} \leq \delta/6$
+	\item[2.] $r = (2 + \frac{2}{\alpha})r_0 \leq \delta/2$
+	\item[3.] $B(c_p, \frac{2 \len{c_1 c_p}}{\alpha}) \subset B_2(c_2, r)$
 \end{enumerate}
+\item [(c)] $B_1 \cap B_2^* = \emptyset$
+\item [(d)]  if $\cp \in B_2^*$, then 
+	\begin{enumerate}
+		\item [1.] $2r^* \le r$
+		\item [3.] $B_2 \cap B_1^* = \emptyset$
+		\item [4.] all points in $\Buffer$ are outliers
+	\end{enumerate}
+
 \end{enumerate}
@@
 
-\begin{proof}
+\begin{proof} The proof consists of three parts and each part use previous parts:
+\begin{enumerate}
+\item [(a)]{
+When a $p$ arrives in the stream, \textproc{AddToB$_1$} is called, which tries to add $p$ to ball $B_1$.
+By Lemma \ref{lem:(z+1)-furthest}, if point $q$ be the $(z+1)$-furthest point of the stream from $c_1$,
+then $\frac{\alpha}{\alpha+4} \len{c_1q}$ is an increasing stream of lowerbounds for $\delta^*$. So at any point, $\delta < \delta^*$.
+} 
+\item [(b)]
+	\begin{enumerate}
+		\item [1.]{ If $c_2$ is set, then it is $(z+1)$-furthest points of a set $T \subset P$ from $c_1$.
+Let q be the $(z+1)$-furthest point of the Stream from $c_1$ at that state, then $\len{c_1c_2} \leq \len{c_1q}$ and as a result (for $16 \leq \alpha$) $r_0 \leq \delta / 6$.}
+		\item [2.] {By previous part $(2 + \frac{2}{\alpha})r_0 \leq 3r_0 \leq \delta /2$}
+		\item[3.]{ If $|B_2| < \dz$ then $c_p = c_2$ and $r = r_0$, so $B_2 = B(c_p, \frac{2 \len{c_1 c_p}}{2})$.
+
+				if $|B_2| \ge \dz$ then $c_p$ is the centerpoint of the first $\dz$ points currently in $B_2$ and $r = (2 + \frac{2}{\alpha}) r_0$.
+because the centerpoint of a set of points is in their convex hull, then $c_p \in B(c_2, r_0)$.
+So $\len{c_2, c_p} \leq r_0$ and $\frac{2 \len{c_1 c_p}}{\alpha} \leq \frac{2 (\len{c_1 c_2} + \len{c_2 c_p})}{\alpha} \leq r_0(1 + \frac{2}{\alpha})$ and As a result, $B(c_p, \frac{2 \len{c_1 c_p}}{2}) \subset B_2(c_2, r_0 + r_0(1 + \frac{2}{\alpha}))$.}
+	\end{enumerate}
+\item [(c)] {
+A point $p$ can be added to $B_1$ in two parts of the Algorithm. 
+First case is in \Cref{alg:addB1}, when  $\len{pc_1} \leq \delta$, which due to variant (a), garanties $\len{pc_1} \le \delta^*$, so $p \not \in B_2^*$.
+Second case is in \Cref{alg:case-1}, when the buffer becomes full and $c_2$ has been set before.
+
+In this case, if $|B_2| < \dz $, then $c_2 = c_p$.
+In this case we add $c_2$ to $B_1$.
+By contradiction assume that $c_p \in B_2^*$, then due to variant (d) part 1, $2r^* \leq r$ and by Lemma \ref{lem:2r}, there should be at most $z$ points outside $B_1 \cup B_2$ which contradicts size of the buffer($|Buffer| > z+1$).
+
+If $|B_2| \geq \dz$, then $c_p$ is the centerpoint of the first $\dz$ points currently in $B_2$.
+in this case, we add all of $B_2$ points to $B_1$.
+Due to variant (b), $r \leq \delta/2 < \delta^*/2$.
+So By Lemma \ref{obs:center-point} then $$ By Lemma \ref{lem:} By contradiction assume that $B_2 \cap B_2^* \neq \emptyset$.
+If $c_p \in B_2^*$, then by variant (b), $B(c_p, \frac{2 \len{c_1 c_p}}{\alpha}) \subset B(c_2, r)$
+}
+\item [(d)] {
+	\begin{enumerate}
+		\item [1.]{
+		Due to  Observation \ref{obs:c+4}, if $c_1 \in B_1^*$ and $c_p \in B_2^*$ then $1 \leq \frac{\len{c_1 c_p}}{\delta^*} \leq \frac{\len{c_1 c_p}}{\alpha r^*}$ and as a result $2r^* \leq \frac{2 \len{c_1c_p}}{\alpha}$.
+
+	if $|B_2| < \dz$ then $c_p = c_2$ and By \Cref{alg:case-1}, $r = r_0 = \frac{2}{\alpha} \len{c_1 c_2}$, so $2r^* \leq r$.
+
+	if $|B_2| \ge \dz$ then similar to variant (b) $2r^* \leq \frac{2 \len{c_1 c_p}}{\alpha} \leq (1 + \frac{2}{\alpha})r_0 \leq (2 + \frac{2}{\alpha})r_0 = r$.
+
+}
+		\item [2.]{ Due to previous part, if $c_p \in B_2^*$ then $2r^* \leq r \leq \delta /2$ and $c_p \in B_2$.
+Due to variant (a) and Observation \ref{obs:intersection}, $B_2$ intersect only with $B_2^*$ and so $B_2 \cap B_1^* = \emptyset$.
+}
+		\item [3.]{
+}
+	\end{enumerate}
+}
+\end{enumerate}
+
 TBA \ 
@@
 To avoid duplication, we just outline the important parts of their algorithm and our modifications to it.
-Kim's algorithm has $10$ different states.
+Kim's algorithm has $10$ different states (\Cref{fig:dag}).
 In each step one or many of the states can be valid and their algorithm considers all of them in parallel.
@@
 arriving after $p$ in $P$ that does not lie in the current candidate solution.
+
+\begin{figure}
+\centering
+\begin{tikzpicture}
+  [scale=.75,auto=left,every node/.style={circle,fill=blue!15}]
+ \tikzset{edge/.style = {->,> = latex'}}
+  \node (S) at (1,2) {S};
+  \node (1) at (3,2) {1};
+  \node (2a) at (5,1)  {2a};
+  \node (3a) at (5,4)  {3a};
+  \node (2b) at (7,0)  {2b};
+  \node (3b) at (7,2)  {3b};
+  \node (3d) at (7,4)  {3d};
+  \node (2c) at (9,0)  {2c};
+  \node (3c) at (9,2)  {3c};
+  \node (3e) at (9,4)  {3e};
+  \node (E) at (11, 2) {E};
+
+  \foreach \from/\to in {S/1,1/2a,1/3a,2a/2b,2b/2c,2c/E,3a/3b,3a/3b,3a/3d,3b/3c,3d/3e,3c/E,3e/E}
+    \draw[edge] (\from) to (\to);
+
+\end{tikzpicture}
+\caption{State Transition of Kim \etal \cite{kim2014improved}} algorithm \label{fig:dag}
+\end{figure}
 
@@
 $c_1^*$ to $c_2^*$ (see Figure~\ref{fig:2lt1}).
-Clearly, $B\left(c, \frac{\delta}{2} + 2r_2^*\right)$ covers both $B_1^*$ and $B_2^*$. 
+Clearly, $B\left(c, \frac{\delta}{2} + 2r^*\right)$ covers both $B_1^*$ and $B_2^*$. 
 Therefore, it is a feasible solution for the 1-center problem with $z$ outliers.
-Hence, $ r_1^* \le \left(2 + \frac{\alpha}{2}\right) 2^*$.
+Hence, $ r_1^* \le \left(2 + \frac{\alpha}{2}\right) r^*$.
 \end{proof}

### 2015-04-28 paper.tex
Minor update

@@
 	Sharif University of Technology.
-	{\tt hatami@ce.sharif.edu}}
+	{\tt bhatami@ce.sharif.edu}}
 	\and 
@@
 Due to variant (b), $r \leq \delta/2 < \delta^*/2$.
-So By Lemma \ref{obs:center-point} then $$ By Lemma \ref{lem:} By contradiction assume that $B_2 \cap B_2^* \neq \emptyset$.
-If $c_p \in B_2^*$, then by variant (b), $B(c_p, \frac{2 \len{c_1 c_p}}{\alpha}) \subset B(c_2, r)$
+So By Lemma \ref{obs:center-point} then $c_p \in B_1^*$ or $c_p \in B_2^*$.
+By cantradiction assume that $c_p \in B_2^*$.
 }
@@
 
-\begin{lemma}
-\label{lem:}
-	After termination of \Cref{alg:case-1}, 
-	if $|B_2| \ge \dz$ and $\cp \not\in B_2^*$,
-	then $B_2 \cap B_2^* = \emptyset$.
-\end{lemma}
-
-\begin{proof}
-	TBA.
-\end{proof}
+% \begin{lemma}
+% \label{lem:}
+%	After termination of \Cref{alg:case-1}, 
+%	if $|B_2| \ge \dz$ and $\cp \not\in B_2^*$,
+%	then $B_2 \cap B_2^* = \emptyset$.
+%\end{lemma}
+
+%\begin{proof}
+%	TBA.
+%\end{proof}
 

### 2015-04-29 paper.tex
Revise query section and corresponding algorithm

--- 2015-04-26 paper.tex
@@
 \newcommand{\len}[1]{\|{#1}\|}
+\newcommand{\radius}[1]{\frac{2}{\alpha} \len{c_1 #1}}
 \newcommand{\setcomp}[1]{\overline{#1}}
@@
 \label{obs:intersection}
-	Let $B_1$ and $B_2$ be two disjoint balls of distance greater than $\delta$,
-	and let $B$ be an arbitrary ball of radius at most $\frac{\delta}{2}$. 
+	Let $B_1$ and $B_2$ be two disjoint balls of distance equal to $\delta$,
+	and let $B$ be an arbitrary ball of radius less than $\frac{\delta}{2}$. 
 	Then $B$ intersects at most one of $B_1$ and $B_2$.
@@
 \begin{proof}
-	TBA.
+	For an arbitrary point $p' \in B_1^*$, $\len{pp'} \leq \len{pc_1} + \len{p'c_1} \leq 2r^*$ and as a result $B_1^* \subset B(p, 2r^*)$(With similar proof, $B_2^* \subset B(q, 2r^*)$).
+Considering that at most $z$ points of $P$ is outlier,  the proof is complete.
 \end{proof}
@@
 \begin{proof}
-	TBA.
+	By Observation~\ref{obs:intersection}, ball $B$ intersects exactly one of $B_1^*$ and $B_2^*$ (all points of $S$ can not be outlier).
+Without loss of generality, Let $B$ intersect with $B_1^*$.
+By Observation \ref{obs:omitting-centerpoint}, $c_p$ would lie in $B_1^*$ and the proof is complete.
 \end{proof}
@@
 where at any time, $\delta$ is a lower bound of $\delta^*$, 
-and $r$ is an upper bound of $2r^*$.
+and $r$ is an upper bound of $2r^*$ (if $c_p \in B_2^*$).
 
@@
 %			\ENDIF
-			\STATE $c_2 \gets$ an arbitrary point of $T$
-			\STATE $\rc  \gets \frac{2}{\alpha}\len{c_1 c_2}$
+			\STATE $c_2 \gets$ (z+1)-furthest point of $T$ from $c_1$
+			\STATE $\rc  \gets \radius{c_2}$
 			\FOR{$p \in T$}
@@
 \item [(a)] $\delta < \delta^*$ %$\delta$ is a lower bound of $\delta^*$
-\item [(b)] $B_1 \cap B_2^* = \emptyset$
-\item [(c)]  if $\cp \in B_2^*$, then 
+\item [(b)] if $c_2$ is set, then
 \begin{enumerate}
-		\item [1.] $2r^* \le r \le \delta /2$
+	\item[1.] $r \leq \delta/2$
+	\item[2.] $B(c_p, \radius{c_p}) \subset B_2(c_2, r)$
+\end{enumerate}
+\item [(c)] $B_1 \cap B_2^* = \emptyset$
+\item [(d)]  if $\cp \in B_2^*$, then 
+	\begin{enumerate}
+		\item [1.] $2r^* \le r$
 		\item [2.] $B_2 \cap B_1^* = \emptyset$
@@
 	\end{enumerate}
+
 \end{enumerate}
@@
 
-\begin{proof}
-TBA \ 
-(All non-used parts from the previous version are copied here.
-They might be useful for composing the proof of this lemma.)
-
-The function \textproc{AddToB$_1$} presented in \Cref{alg:addB1} 
-is used to add a point $p$ to $B_1$. 
-%The point $c_1$ is the first point of the stream,
-%which is assumed to be non-outlier, and is in $B_1^*$.
-The point will be added to $B_1$ only if it is within distance $\delta$ of the center $c_1$, 
-where $\delta = \frac{\alpha}{\alpha+4}\len{qc_1}$ 
-and $q$ is the $(z+1)$-furthest point from $c_1$.
-%among the points of $P$ seen so far.
-By Lemma~\ref{lem:(z+1)-furthest}, $\delta$ is a strict lower bound of $\delta^*$. 
-Therefore, any point within $\delta$-radius of $c_1$ is guaranteed to be outside $B_2^*$. 
-Thus, property P1 is not violated by this function.
-%$B_1 \cap B_2^* = \emptyset$.
-Note that if less than $z+1$ points have been seen so far,
-then $\delta = 0$, %$q = c_1$, 
-and hence, property P1 is still maintained.
-
-The function \textproc{AddToB$_2$} presented in \Cref{alg:addB2}
-is used to add a point $p$ to $B_2$.
-Initially, $B_2$ is empty and $c_2$ is not initialized. 
-When an appropriate candidate is found, 
+\begin{proof} The proof consists of four parts and each part use previous parts:
+
+Invariant (a): 
+When a point $p$ arrives in the stream, \textproc{AddToB$_1$} is called, which tries to add $p$ to ball $B_1$.
+By Lemma \ref{lem:(z+1)-furthest}, if point $q$ be the $(z+1)$-furthest point of the stream from $c_1$,
+then $\frac{\alpha}{\alpha+4} \len{c_1q}$ is an increasing stream of lowerbounds for $\delta^*$. So at any point, $\delta < \delta^*$.
+
+Invariant (b): 
+When an appropriate candidate for $c_2$ is found, 
 $c_2$ is set to that candidate by the main algorithm (Algorithm~\ref{alg:case-1}),
@@
 only if they are within $\rc$-radius of $c_2$.
-Consider $c_2$ as the central point $c_p$. % is considered as the central point $\cp$. 
-Clearly, property P2 holds initially when $B_2$ consists of a single point $c_2$. 
-All subsequent points added to $B_2$ are within $\rc$-radius of $c_2$.
-Therefore, for $\alpha > 7$ (Why?), Observation~\ref{obs:intersection}
-implies that $B_2 \cap B_1^* = \emptyset$,
-and hence, property P2 is maintained. %invariant under this operation.
-
-When the size of $B_2$ reaches $\dz$, 
-we update the central point $\cp$ to the centerpoint of $B_2$.
-%We claim that $B(c_2, (2 + \frac{2}{\alpha})\rc )$ completely covers
-%the ball $B(\cp, \frac{2\len{c_1\cp}}{\alpha})$.
-If $\cp \in B_2^*$, then by Observation~\ref{obs:c+4},
-we have $\frac{\len{c_1\cp}}{\delta^*} \geq 1$,
-and hence, $r^* < \frac{\len{c_1\cp}}{\alpha}$. 
-Therefore, $B_2^* \subset B(\cp, \frac{2\len{c_1\cp}}{\alpha})$.
-Moreover,
-\[
-	2 \cdot \frac{\len{c_1\cp}}{\alpha} \leq \frac{2}{\alpha}(\len{c_1c_2} + \rc ) 
-	\leq (1 + \frac{2}{\alpha})\rc.
-\]
-Therefore, $B_2^* \subseteq B(c_p, (1 + \frac{2}{\alpha})\rc )
-\subseteq B(c_2, (2 + \frac{2}{\alpha})\rc )$. 
-It is easy to see that $(2 + \frac{2}{\alpha})\rc  \le \frac{\delta}{2}$ provided that $\alpha \ge 14$.
-Thus, if we increase $\rc$ by a factor of $(2 + \frac{2}{\alpha})$, 
-%by setting $B_2 = B(c_2, (2 + \frac{2}{\alpha})\rc )$, 
-$B_2 \cap B_1^* = \emptyset$
-by Observation~\ref{obs:intersection}, and hence,
-property P2 is still maintained.
-
-Whenever the buffer overflows 
-%the assumption about $\cp \in B_2^*$ is contradicted.
-%At some point during the execution of Algorithm~\ref{alg:case-1}, the assumption about $\cp \in B_2^*$ might be contradicted when the buffer overflows. We can then conclude that
-% $\cp \notin B_2^*$.
-the algorithm takes one of the following actions
-depending on the size of $B_2$.
-
-\begin{itemize}
-\item 
-If $|B_2| < \dz$, then $c_2$ can be added to $B_1$
-without violating P1. (Why?) 
-The algorithm then tries the points in $B_2 \cup \mbox{Buffer}$, 
-until it finds a suitable candidate for $c_2$ that does not leave
-more than $z$ points uncovered. 
-Note that at most $(z+1)(d+1) + z$ points have to be tried.
-
-\item 
-If $\card{B_2} \ge \dz$, let $q$ be the $(z+1)$-furthest point from $p_1$,
-and let $p'$ be the nearest point of the ball $B_2(c_2, \rc )$ to $p_1$. 
-Then $\len{qp_1} > \len{p'p_1}$, since $B_2$ contains more than $z+1$ points. 
-Therefore, by Lemma~\ref{lem:(z+1)-furthest} we have
-\[
-\delta \ge \frac{\alpha }{\alpha+4}\len{qp_1} \ge \frac{\alpha}{\alpha+4} (\len{c_1c_2} - \rc ) = \frac{\alpha^2 - 2\alpha}{2\alpha + 8} \rc.
-\]
-As a result, if $\alpha \geq 14$ then $(2 + \frac{2}{\alpha}) \rc  < \frac{\delta}{2}$. 
-By Observation~\ref{obs:intersection}, the ball $B_2(c_2, (2 + \frac{2}{\alpha}) \rc )$ 
-has nonempty intersection with exactly one of $B_1^*$ and $B_2^*$ 
-(i.e., not all of its points can be outliers). 
-Since the buffer overflowed, the assumption about the central point, 
-$\cp$, being in $B_2^*$ has become invalid. 
-By Observation~\ref{obs:omitting-centerpoint}, if $\cp$ is not covered, 
-then the ball $B_1^*$ leaves at least $z+1$ points of $B_2$ uncovered, 
-and there will be more than $z$ outliers. 
-Thus, $\cp$ has to be covered. 
-As a result, $\cp \in B_1^*$ and all the points of $B_2$ can be added to $B_1$. 
-This is done by replacing $B_1$ with $B_1 \cup B_2$, and resetting $B_2$ to empty set.
-\end{itemize}
-\end{proof}
-
-\begin{lemma}
-\label{lem:}
-	After termination of \Cref{alg:case-1}, 
-	if $|B_2| \ge \dz$ and $\cp \not\in B_2^*$,
-	then $B_2 \cap B_2^* = \emptyset$.
-\end{lemma}
-
-\begin{proof}
-	TBA.
+
+If $c_2$ is set, then it is $(z+1)$-furthest points of a set $T \subset P$ from $c_1$. 
+Let q be the $(z+1)$-furthest point of the Stream from $c_1$ at that state, then $\len{c_1c_2} \leq \len{c_1q}$ and since (for $16 \leq \alpha$) $\radius{c_2} \leq \frac{1}{6}\frac{\alpha \len{c_1 q}}{(\alpha + 4)} \leq \delta / 6$, then $$r \leq (2 + \frac{2}{\alpha})\radius{c_2} \leq 3 \radius{c_2}  \leq \delta /2$$.
+
+In part 2, if $|B_2| < \dz$ then $c_p = c_2$ and $r = \radius{c_2}$, so $B_2 = B(c_p, \radius{c_p})$. 
+When the size of $B_2$ reaches $\dz$, the central point $\cp$ moves to the centerpoint of $B_2$ and $\rc$ increases by a factor of $(2 + \frac{2}{\alpha})$. 
+Because the centerpoint of $B_2$ locate in $B_2$, then $c_p \in B(c_2, \radius{c_2})$.
+So if $|B_2| \ge \dz$ then $\len{c_2 c_p} \leq \radius{c_2}$ and as a result
+$$\radius{c_p} \leq \frac{2 (\len{c_1 c_2} + \len{c_2 c_p})}{\alpha} \leq \radius{c_2}(1 + \frac{2}{\alpha})$$ 
+So $B(c_p, \radius{c_p}) \subset B_2(c_2, \radius{c_2}(2 + \frac{2}{\alpha}))$.
+
+Invariant (c): A point $p$ can be added to $B_1$ in two parts of the \Cref{alg:case-1}. 
+First case is in function \textproc{AddToB$_1$}, the point will be added to $B_1$ only if it is within distance $\delta$ of the center $c_1$,  when $\len{pc_1} \leq \delta$, which due to invariant (a), guaranties $\len{pc_1} < \delta^*$, so $p \not \in B_2^*$.
+
+Second case is in \Cref{alg:case-1}, whenever the buffer overflows and $B_2$ is non-empty the algorithm takes one of the following actions depending on the size of $B_2$.
+If $|B_2| < \dz $, then $c_2 = c_p$. \Cref{alg:case-1} add $c_2$ to $B_1$.
+By contradiction assume that $c_p \in B_2^*$, then due to invariant (b) part 1 and invariant (d) part 1, $2r^* \leq r \leq \delta/2 < \delta^*/2$.
+So by Lemma \ref{lem:2r}, there should be at most $z$ points outside $B_1 \cup B_2$ which contradicts overflow of the buffer.
+
+If $|B_2| \geq \dz$, then $c_p$ is the centerpoint of the first $\dz$ points currently in $B_2$. 
+In this case, we add all points of $B_2$ to $B_1$. Due to invariant (b), $r \leq \delta/2 < \delta^*/2$. 
+So By Lemma \ref{lem:center-point}, $c_p \in B_1^*$ or $c_p \in B_2^*$.
+By contradiction assume that $c_p \in B_2^*$.
+In this case, due to invariant (d) part 1 and invariant (b) part 2, $B_2$ covers $B(c_p, \radius{c_p})$ and $2r^* \leq r$.
+similar to previous part, it contradicts overflow of the buffer.
+
+Invariant (d): 
+Due to  Observation \ref{obs:c+4}, if $c_1 \in B_1^*$ and $c_p \in B_2^*$ then $1 \leq \frac{\len{c_1 c_p}}{\delta^*} \leq \frac{\len{c_1 c_p}}{\alpha r^*}$ and as a result $2r^* \leq \radius{c_p}$.
+If $|B_2| < \dz$ then $c_p = c_2$ and By \Cref{alg:case-1}, $r = \radius{c_2}$, so $2r^* \leq r$.
+
+If $|B_2| \ge \dz$ then similar to invariant (b): $$2r^* \leq \radius{c_p} \leq (1 + \frac{2}{\alpha})\radius{c_2} \leq (2 + \frac{2}{\alpha})\radius{c_2} = r$$
+
+In part 2, due to previous part, if $c_p \in B_2^*$ then $2r^* \leq r \leq \delta /2$ and $c_p \in B_2$.
+Due to invariant (a) and Observation \ref{obs:intersection}, $B_2$ intersect only with $B_2^*$ and so $B_2 \cap B_1^* = \emptyset$.
+
+In part 3, due to invariant (c) and invariant (d) part 1, $2r^* \leq r \leq \delta/2 < \delta^* /2$. So by Lemma \ref{lem:2r}, all points outside $B_1 \cup B_2$ are outliers.
+
 \end{proof}
@@
 
-Let $B_1'$, $B_2'$, and $B_u'$ be the $\beta$-approximate balls obtained from the data structures
-[This part needs clarification].
-%1-centers obtained from $B_1$, $B_2$ and $B_u$ by the $\beta$-approximation algorithm, respectively. 
-To answer a query, we can use these balls as follows. 
-By our initial assumption about $p_1$, $B_1$ contains $B_1^*$,
-and $B_1'$ is a $\beta$-approximation for $B_1^*$. (Why?)
-But for $B_2$, it might be the case that our assumption about $c_2$ 
-was incorrect, so $B_2'$ may not be a good approximation for $B_2^*$. 
-There are two cases to be considered based oon $\card{B_2}$. 
-If $\card{B_2} < (z+1)(d+1)$, then we can try each point in 
-$B_2 \cup \mbox{Buffer}$ as a candidate for the central point. 
-If $\card{B_2} \ge \dz$, then there is no need for points in $B_2$ to be considered, 
-since for those points as central point, $B_1$ will be replaced by $B_u$ and $B_2$ will be empty. (Why?)
-Thus it suffices to consider points of Buffer as candidates 
-and compare them to the solution of $(B_u, \emptyset)$.
+\paragraph{Query}
+At any point of the stream, we could be able to answer to a query (give the smallest $\alpha$-separated two congruent balls that covers all points except at most $z$ points).
+Due to Invariants (c), we know that $B_1 \cap B_2^* = \emptyset$. 
+So we are sure that, there exists a point $(B_2 \cup \Buffer) \cap B_2^* \neq \emptyset$.
+In this general case, our candidates $C$ for $c_2$ is set $(B_2 \cup \Buffer) \cap B_2^*$.
+
+\begin{lemma}
+\label{lem:B2dz}
+	At any point of the stream, 
+	if $|B_2| \ge \dz$ and $\cp \not\in B_2^*$,
+	then $B_2 \cap B_2^* = \emptyset$.
+\end{lemma}
+
+\begin{proof}
+	due to invariant (b) part 1 and invariant (a) we know that $r \leq \delta/2 < \delta^*/2$. 
+	By Lemma \ref{lem:center-point}, $c_p \in B_1^* \cap B_2^*$. 
+	Since $c_p \not \in B_2^*$, then $c_p \in B_1^*$. 
+	On the other hand, By Observation \ref{obs:intersection}, $B_2$ intersect with at most one of $B_1^*$ and $B_2^*$. So as a result, $B_2 \cap B_2^* = \emptyset$.
+\end{proof}
+
+As a result of Lemma \ref{lem:B2dz}, when $|B_2| \geq \dz$, we are sure that $(\{c_2\} \cup \Buffer) \cap B_2^* \neq \emptyset$. 
+So if $|B_2| \ge \dz$, then our candidates $C$ for $c_2$ are $\{c_2\} \cup \Buffer$. Our Query algorithm, works as follows.
+
+For each candidate $c \in C$, \Cref{alg:query} constructs $B'_1(c_1, \max \{\delta, \radius{c} \})$ and $B'_2(c, \radius{c})$. 
+First, consider the candidate $c$ that equals to current $c_2$, then $B_1 = B'_1$. 
+Since $\radius{c_2} \leq r \leq \delta/2$ (invariant (b) part 1) and $B'_2 \subset B_2$ then we don't need to construct any new set. 
+In general case, when $c \neq c_2$, we know that $B_1 \subset B'_1$, so we just need to see which of $\Buffer \cap B_2$ points located in $B'_1$.
+When $|B_2| \geq \dz$ and $c \neq c_2$, then it means that assumed $c_p \not \in B_2^*$. So By Lemma \ref{lem:B2dz}, $B_2$ can be added to $B'_1$ without contradicting invariant (a). 
+So in this case, just need to see which points of $\Buffer$ should be added to $B'_1$. 
+\Cref{alg:query} use functions \textproc{AddToB$'_1$} and \textproc{AddToB$'_2$} for adding a point to $B'_1$ and $B'_2$ respectively. 
+Their definition are totally same as functions \textproc{AddToB$_1$} and \textproc{AddToB$_2$} except that, they add point to $B'_i$ instead of $B_i$($i = 1, 2$).
+
+As \Cref{alg:query}, consider all valid cases of $c$, for one of $c \in C$, $c \in B_2^*$. 
+Consider that $c$ as $c^*$ and corresponding $B'_1$ and $B'_2$ as $B''_1$ and $B''_2$. 
+Since $1 \leq \frac{\len{c_1 c^*}}{\alpha^*} < \frac{\len {c_1 c^*}}{\alpha r^*}$(By Observation \ref{obs:c+4}) then $2r^* \leq \radius{c^*}$ and as a result $B^*_1 \subset B''_1$ and $B^*_2 \subset B''_2$ (By Lemma \ref{lem:2r}).
+On the other hand, due to invariant (a) and distance of new points added to $B''_1$ compare to $B_1$ is less than $\len{c_1 p} \leq \max \{\delta, \radius{c^*} \}$, so $B''_1 \cap B_2^* = \emptyset$.
+As a result $B''_1$ and $B''_2$ totally covers $B_1^*$  and $B_2^*$ respectively, with some extra outlier points and remaining points in $\Buffer$ are certainly outliers.
+The only unknown part is that \Cref{alg:query} does not know how many outliers are in $B''_1$ and $B''_2$.
+So \Cref{alg:compute-min} tries all possible cases and choose the one with the minimum radius.
 
@@
 %\Function{Query}{}
-	\STATE solutions $\gets [\Call{ComputeMin}{B_u, \emptyset, \text{Buffer}}]$
-
-	\STATE candidates $\gets$ Buffer
+	\STATE solutions $\gets [\Call{ComputeMin}{B_1, B_2, \Buffer}]$
+
+	\STATE candidates $\gets \Buffer$
 	\IF {$\card{B_2} < \dz$}
-		\STATE candidates $\gets \text{Buffer} \cup B_2$ % \setminus \set{c_2}$
-	\ENDIF
-
+		\STATE candidates $\gets \Buffer \cup B_2 \setminus \set{c_2}$
+	\ELSE
+		\STATE $B_1 \gets B_u$
+	\ENDIF
+
+	\STATE $\delta_0 = \delta$
 	\FOR{$c_2 \in$ candidates}
 		\STATE $\rc  \gets \frac{2}{\alpha} \len{c_1 c_2}$
-		\STATE $B_2 \gets \emptyset$, Buffer $\gets \emptyset$ 
+		\STATE $B'_1 \gets B_1$, $\delta \gets \max \{ \delta_0, r \}$
+		\STATE $B'_2 \gets \emptyset$, $\Buffer' \gets \emptyset$ 
 		\FOR{$p \in$ candidates}
-			\IF{\NOT \Call{AddToB$_2$}{$p$}}
-				\STATE add $p$ to Buffer
+			\IF {\NOT (\Call{AddToB$'_1$}{$p$} \OR \Call{AddToB$'_2$}{$p$})}
+				\STATE add $p$ to $\Buffer'$
 			\ENDIF
 		\ENDFOR
-		\STATE add \Call{ComputeMin}{$B_1$, $B_2$, Buffer} to solutions
+		\STATE add \Call{ComputeMin}{$B'_1$, $B'_2$, $\Buffer'$} to solutions
 	\ENDFOR
@@
 \begin{algorithm}
-\caption{\sc ComputeMin($B_1, B_2, \text{\rm Buffer}$)} 
+\caption{\sc ComputeMin($B'_1, B'_2, \text{\rm Buffer}$)} 
 \algsetup{indent=1.5em}
-\label{alg:query}
+\label{alg:compute-min}
 \begin{algorithmic}[1]
@@
 	\FOR{$k \gets 0, \dots,(z - \card{\mbox{Buffer}})$}
-		\STATE $r_1 \gets \Call{1-Center}{B_1, k}$
-		\STATE $r_2 \gets \Call{1-Center}{B_2, z - \card{\mbox{Buffer}} - k}$
+		\STATE $r_1 \gets \Call{1-Center}{B'_1, k}$
+		\STATE $r_2 \gets \Call{1-Center}{B'_2, z - \card{\mbox{Buffer}} - k}$
 		\STATE add $\max \set{r_1, r_2}$ to solutions
@@
 arriving after $p$ in $P$ that does not lie in the current candidate solution.
+
+\begin{figure}
+\centering
+\begin{tikzpicture}
+  [scale=.75,auto=left,every node/.style={circle,fill=blue!15}]
+ \tikzset{edge/.style = {->,> = latex'}}
+  \node (1) at (1,2) {1};
+  \node (2a) at (3,1)  {2a};
+  \node (3a) at (3,4)  {3a};
+  \node (2b) at (5,0)  {2b};
+  \node (3b) at (5,2)  {3b};
+  \node (3d) at (5,4)  {3d};
+  \node (2c) at (7,0)  {2c};
+  \node (3c) at (7,2)  {3c};
+  \node (3e) at (7,4)  {3e};
+  \node (E) at (9, 2) {E};
+
+  \foreach \from/\to in {1/2a,1/3a,2a/2b,2b/2c,2c/E,3a/3b,3a/3b,3a/3d,3b/3c,3d/3e,3c/E,3e/E}
+    \draw[edge] (\from) to (\to);
+
+\end{tikzpicture}
+\caption{State Transition of Kim \etal \cite{kim2014improved}} algorithm \label{fig:dag}
+\end{figure}
 

### 2015-04-30 paper.tex
Minor revision (changing invariant a and c)

@@
 In general case, when $c \neq c_2$, we know that $B_1 \subset B'_1$, so we just need to see which of $\Buffer \cap B_2$ points located in $B'_1$.
-When $|B_2| \geq \dz$ and $c \neq c_2$, then it means that assumed $c_p \not \in B_2^*$. So By Lemma \ref{lem:B2dz}, $B_2$ can be added to $B'_1$ without contradicting invariant (a). 
+When $|B_2| \geq \dz$ and $c \neq c_2$, then it means that assumed $c_p \not \in B_2^*$. So By Lemma \ref{lem:B2dz}, $B_2$ can be added to $B'_1$ without contradicting invariant (c). 
 So in this case, just need to see which points of $\Buffer$ should be added to $B'_1$. 
@@
 Since $1 \leq \frac{\len{c_1 c^*}}{\alpha^*} < \frac{\len {c_1 c^*}}{\alpha r^*}$(By Observation \ref{obs:c+4}) then $2r^* \leq \radius{c^*}$ and as a result $B^*_1 \subset B''_1$ and $B^*_2 \subset B''_2$ (By Lemma \ref{lem:2r}).
-On the other hand, due to invariant (a) and distance of new points added to $B''_1$ compare to $B_1$ is less than $\len{c_1 p} \leq \max \{\delta, \radius{c^*} \}$, so $B''_1 \cap B_2^* = \emptyset$.
+On the other hand, due to invariant (c) and distance of new points added to $B''_1$ compare to $B_1$ is less than $\len{c_1 p} \leq \max \{\delta, \radius{c^*} \}$, so $B''_1 \cap B_2^* = \emptyset$.
 As a result $B''_1$ and $B''_2$ totally covers $B_1^*$  and $B_2^*$ respectively, with some extra outlier points and remaining points in $\Buffer$ are certainly outliers.

### 2015-05-02 paper.tex
New edits + page number shrink

@@
 
+%------------------------ Cleveref Labels -----------------------------
+
+\Crefname{table}{Table}{Tables}
+\Crefname{obs}{Observation}{Observations}
+\Crefname{cor}{Corollary}{Corollaries}
+\Crefname{algorithm}{Algorithm}{Algorithms}
+\Crefname{lemma}{Lemma}{Lemmas}
+
 %------------------------ Algorithm -----------------------------
@@
 \renewcommand{\algorithmicforall}{{\bf for each}}
+\renewcommand{\algorithmiccomment}[1]{\quad $\vartriangleright$ #1}
 
@@
 Given a stream of points in arbitrary $d$ dimensions, the goal is to find two congruent balls 
-of minimum radius covering all but $z$ points (\Cref{fig:definition}). 
+of minimum radius covering all but $z$ points. 
 We provide a $(1.8+\eps)$-approximation streaming algorithm for the problem, 
@@
 arising in many applications 
-such as data mining, unsupervised learning, statistics, and image processing.
+such as data mining, machine learning, statistics, and image processing.
 In real-world applications, where input data is often noisy, 
@@
 the the $k$-center problem: % which we call \emph{$k$-center with $z$ outliers}:
-given a set $P$ of $n$ points in arbitrary $d$ dimensions, 
+given a set $P$ of $n$ points in arbitrary $d$ dimensions
+and a bound $z$ on the number of outliers,
 find $k$ congruent balls of minimum radius 
 to cover at least $n - z$ points of $P$.
+See \Cref{fig:definition} for an example.
+%for $z$ being the number of outliers.
 %One of $k$-center problem variants is $k$-center with $z$-outlier which finds $k$ congruent balls with minimum radius covering all but $z$ points of a point set.
 
-In this paper, we focus on the \emph{data stream model}
-where only a single pass over the input data is allowed,
+In this paper, we focus on the \emph{data stream} model of computation
+in which only a single pass over input is allowed,
 and we have only a limited amount of working space available.
@@
 This model is specially useful for processing large data sets,
-as it does not need the entire data set to be stored in memory.
+as it does not require the entire data set to be stored in memory.
 
@@
 If $k$ is part of the input,
-the problem in known to be NP-hard in two or more dimensions~\cite{fowler1981optimal},
+the problem in known to be NP-hard in two and more dimensions~\cite{fowler1981optimal},
 and is even hard to approximate to within a factor close to 2, 
@@
 gave the first algorithm with an approximation factor of $3$, 
-that works in any dimension.
+which works in any dimension.
 %which is improvable to 3, if all candidate center points can be enumerated.
@@
 	\centering
-	\includegraphics[width=12em]{figs/definition}
-	\caption{$2$-center problem with 6 outlier}
+	\includegraphics[width=13em]{figs/definition}
+	\caption{An example of $2$-center with 6 outliers}
 	\label{fig:definition}
@@
 %Ahn~\etal~\cite{ahn2014computing} gave a $(2+\eps)$-approximation algorithm using $\O(\frac{d}{\eps})$ space and update time, which was improved for Euclidean spaces by 
-For $k=2$, Kim~\etal~\cite{kim2014improved} 
+For $k=2$, Kim and Ahn~\cite{kim2014improved} 
 have recently obtained a $(1.8+\eps)$-approximation  
@@
 \multirow{2}{*}{\begin{tabular}[c]{@{}c@{}} \ \  Problem \ \ \end{tabular}} & \multicolumn{2}{c|}{Approximation Factor} \\ \cline{2-3} 
- & Without Outliers & With Outliers \\ \hline
+ & Without Outliers & With Outliers \\ \hline \hline
 1-Center & 1.22~\cite{chan2014streaming} & 1.73~\cite{zarrabi2009streaming} \\ \hline
@@
 differ by a factor of $\sqrt{2}$ for $k=1$,
-and differ by a factor of 2  for general~$k$. %the 1-center problem.
+and by a factor of 2  for general~$k$. %the 1-center problem.
 See \Cref{table:summary} for a comparison.
@@
 and keeping a lower bound on the radius and distance of the optimal balls.
-Our algorithm also utilizes the ideas used in~\cite{kim2014improved} 
+We have also utilized ideas used in~\cite{kim2014improved} 
 for the 2-center problem with no outliers.
-Nevertheless, our algorithm is much detailed and uses many new ingredients.
-Indeed, handling outliers makes the $k$-center problem much harder,
-as we not only need to find clusters with minimum radius, 
+%However, our algorithm is much detailed and uses many new ingredients.
+However, our problem is much harder here, % handling outliers makes the problem much harder,
+as we not only need to find balls of minimum radius, 
 but we also need to decide which subset of points to cluster.
@@
 where we only have a single pass over the input, and we must decide on the fly
-which point can be an outlier, and which one can be safely dropped as a non-outlier point.
+which point is an outlier, 
+and which one can be safely ignored as a non-outlier point,
+%using only a limited amount of storage.
+to comply with the working space restriction enforced by the model.
 
@@
 the 1-center problem with outliers that uses $\O(z^2 + zd)$ space.
-In the next section, we show a $(1.8 + \eps)$-approximation streaming algorithm for 2-center with $z$ outliers in high dimensions. 
-%In Section~\ref{subsec:smaller} we run $z + 1$ parallel instances of the algorithm in order to find the first non-outlier point.
+In the next section, we show a $(1.8 + \eps)$-approximation
+streaming algorithm for 2-center with $z$ outliers in high dimensions. 
 }
@@
 Let $B(c,r)$ denote a ball of radius $r$ centered at $c$. 
-Given two points $p$ and $q$, we denote by $pq$ the straight line segment between $p$ and $q$,
-and denote by $\len{pq}$ the length of this segment. 
+We use $r(B)$ to denote the radius of a ball $B$. % and $c(B)$, respectively.
+For two points $p$ and $q$, %by $pq$ the straight line segment between $p$ and $q$,
+the distance between $p$ and $q$ is denoted by $\len{pq}$.
 Given two balls $B(c,r)$ and $B'(c',r')$, 
@@
 to be the \emph{distance} between $B$ and $B'$.
-Two congruent balls $B_1$ and $B_2$ with radius $r$ are said to be \emph{$\alpha$-separated}, 
-if $\delta(B_1, B_2) \geq \alpha r$.
+Two balls $B_1$ and $B_2$ %with radius $r$ 
+are said to be \emph{$\alpha$-separated}, 
+%if $\delta(B_1, B_2) \geq \alpha r$.
+if $\delta(B_1, B_2) \geq \alpha \cdot \max \set{r(B_1), r(B_2)}$.
 
@@
 	Given a set $P$ of $k(d+1)$ points in $d$-dimensional space, 
-	there is a point $c$, not necessarily in $P$, 
-	such that any convex object that does not cover $c$, 
+	the centerpoint of $P$ has the property that 
+	any convex object not covering the centerpoint, 
 	leaves at least $k$ points of $P$ uncovered.
@@
 
-Given a point set $P$ and a point $p \in P$,
-the \emph{$k$-furthest point from $p$}
-is the $k$-th point of $P$ when points are sorted
-in their decreasing distance from~$p$.
-
+Given  a point set $P$,
+the \emph{$k$-furthest point from} $p \in P$
+is a point whose distance to $p$ is the $k$-th largest among all points in $P$.
+%is the $k$-th point in $P$ when points are sorted
+%in their decreasing distance from~$p$.
 We assume the standard word-RAM model of computation. 
 Each coordinate value takes a unit of space.
-Thus, a point in $d$ dimensions takes $\O(d)$ space,
+Thus, a $d$-dimensional point takes $\O(d)$ space,
 and basic operations on the points take $\O(d)$ time.
@@
 
-\section{A 2-Approximation for 1-Center with Outliers}
+\section{A Simple Algorithm for 1-Center with Outliers}
 \label{sec:1-center}
@@
 The algorithm receives as input a stream of points, $P$,
-the number of outliers, $z$, 
-and a special point $c \in P$ which is guaranteed to be 
-a non-outlier in the optimal solution.
-It returns a ball $B$ covering all but at most $z$ points of $P$.
-%We will show later how to remove this assumption.
+and the number of outliers, $z$.
+It also assumes that the first point $p_1$ of the stream is non-outlier.
+We will show later how to remove this assumption.
+The algorithm returns a ball $B$ covering all but at most $z$ points of $P$.
+%
 
@@
 \begin{algorithm}
-\caption{\sc 1-Center$(P, z, c)$} 
+\caption{\sc 1-Center$(P, z)$} 
 \algsetup{indent=1.5em}
@@
 	%\STATE {$\triangleright$ $c$ is a non-outlier point in the optimal solution}
-	\STATE $B \gets B(c, 0)$
+	\STATE $B \gets B(p_1, 0)$
 	\STATE $Q \gets \emptyset$
@@
 	the 1-center problem with $z$ outliers,
-	provided that a non-outlier point in the optimal solution in given.
+	assuming that the first point of the stream is not outlier. 
 \end{theorem}
@@
 Let $B^*(c^*, r^*)$ be the optimal solution,
-and $c$ be a non-outlier in the optimal solution.
+and $c = p_1$ be a non-outlier point in the optimal solution.
 Since $c$ is covered by $B^*$,
@@
 Among the $z+1$ points furthest from $c$,
-there is at least one point $q$ which is not outlier in the optimal solution,
+there is at least one point $q$ which is not outlier, % in the optimal solution,
 and therefore, is contained in $B^*$
@@
 Thus, $\len{cq} \le 2r^*$,
-and therefore, the ball $B(c, \len{cq})$ returned by Algorithm~\ref{alg:1-center} 
+and hence, the ball $B(c, \len{cq})$ returned by Algorithm~\ref{alg:1-center} 
 is a 2-approximation. 
@@
 	\centering
-	\includegraphics[width=12em]{figs/one-center}
+	\includegraphics[width=10em]{figs/one-center}
 	\caption{Proof of \Cref{thm:1-center}}
@@
 Algorithm~\ref{alg:1-center} 
-assumes that a point $c$ is known in advance
-which is guaranteed to be a non-outlier in the optimal solution. 
-To overcome the lack of knowledge about such a point, 
+assumes that the first point of the stream is not outlier.
+To remove this assumption,
 we run $z+1$ instances of \Cref{alg:1-center} in parallel,
-each of which is given as $c$ one of the first $z + 1$ points in the stream.
+each of which is given as input one of the first $z + 1$ points of the stream,
+followed by the rest of the points.
 Clearly, there exists a point among the first $z+1$ points of $P$
@@
 
-Let $B_1^*$ and $B_2^*$ be the optimal balls
+Let $B_1^*$ and $B_2^*$ be the balls
 in an optimal solution to the 2-center problem with $z$ outliers on a point set $P$.
@@
 for some constant $\alpha$ to be fixed later.
-(It will be turn out that $\alpha = 16$ is a proper choice.)
+(It will turn out that $\alpha = 16$ is a proper choice.)
 We then present in \Cref{subsec:smaller} 
@@
 where optimal balls are separated by a distance greater than $\alpha r^*$.
+We start by two useful observations.
 %The value of $\alpha$ will be fixed later in this section.
@@
 \label{obs:intersection}
-	Let $B_1$ and $B_2$ be two disjoint balls of distance equal to $\delta$,
+	Let $B_1$ and $B_2$ be two disjoint balls of distance $\delta$,
 	and let $B$ be an arbitrary ball of radius less than $\frac{\delta}{2}$. 
@@
 ${\len{pq} \over \delta^*} \le {\len{pq'} \over \delta^*} < \frac{\alpha+4}{\alpha}$.
-The claim follows immediately.
 \end{proof}
@@
 	If $p \in B_1^*(c_1, r^*)$ and $q \in B_2^*(c_2, r^*)$,
-	then $B_1^* \subset B(p, 2r^*)$ and $B_2^* \subset B(q, 2r^*)$ and as a result at most $z$ points of $P$ lie outside $B(p, 2r^*) \cup B(q, 2r^*)$.
+	then $B_1^* \subset B(p, 2r^*)$ and $B_2^* \subset B(q, 2r^*)$,
+	and hence, at most $z$ points of $P$ lie outside $B(p, 2r^*) \cup B(q, 2r^*)$.
 \end{lemma}
@@
 \begin{proof}
-	For an arbitrary point $p' \in B_1^*$, $\len{pp'} \leq \len{pc_1} + \len{p'c_1} \leq 2r^*$ and as a result $B_1^* \subset B(p, 2r^*)$(With similar proof, $B_2^* \subset B(q, 2r^*)$).
-Considering that at most $z$ points of $P$ is outlier,  the proof is complete.
+	For an arbitrary point $p' \in B_1^*$, $\len{pp'} \leq \len{pc_1} + \len{p'c_1} \leq 2r^*$,
+	and as a result, $B_1^* \subset B(p, 2r^*)$.
+	Similarly, we have $B_2^* \subset B(q, 2r^*)$. 
+	Considering that at most $z$ points of $P$ are outlier, the proof is complete.
 \end{proof}
@@
 	enclosed by a ball $B$ of radius less than $\delta^* / 2$.
-	Then the centerpoint $c_p$ of $S$ lies either inside $B_1^{*}$ or inside $B_2^{*}$.
+	Then the centerpoint $c_p$ of $S$ lies inside either $B_1^{*}$ or $B_2^{*}$.
 \end{lemma}
@@
 \begin{proof}
-	By Observation~\ref{obs:intersection}, ball $B$ intersects exactly one of $B_1^*$ and $B_2^*$ (all points of $S$ can not be outlier).
-Without loss of generality, Let $B$ intersect with $B_1^*$.
-By Observation \ref{obs:omitting-centerpoint}, $c_p$ would lie in $B_1^*$ and the proof is complete.
+	Not all points in $S$ can be outlier, because $\dz > z$.
+	Thus, by Observation~\ref{obs:intersection},
+	$B$ intersects exactly one of $B_1^*$ and $B_2^*$.
+	Assume, w.l.o.g., that $B$ intersect $B_1^*$. 
+	Now, by Observation \ref{obs:omitting-centerpoint}, 
+	if $c_p$ is not in $B_1^*$, 
+	then $z+1$ points of $S$ remain uncovered by $B_1^*$,
+	contradicting the fact that there at most $z$ outliers.	
 \end{proof}
@@
 The first point $p_1$ is assumed, w.l.o.g, to be in $B_1^*$. 
+(We have already assumed that $p_1$ is not outlier.)
 The algorithm tries to partition points in such a way that 
@@
 The algorithm sets $c_1 = p_1$ as the fixed center of $B_1$,
-and picks $c_2$ among the points processed so far as a candidate center for $B_2$.
+and picks $c_2$ among the points processed so far as a candidate 
+for being the center of $B_2$.
 Moreover, the algorithm maintains two values $\delta$ and $r$,
 where at any time, $\delta$ is a lower bound of $\delta^*$, 
-and $r$ is an upper bound of $2r^*$ (if $c_p \in B_2^*$).
+and $r$ is an upper bound of $2r^*$ (under a specific condition). %(if $c_p \in B_2^*$).
 
@@
 only if it is within $\rc$-radius of $c_2$. 
-The two functions also update $\delta$ and $\rc$ whenever necessary,
-to maintain the invariants to be defined shortly in Lemma~\ref{lem:invariants}.
+The two functions also update the values of $\delta$ and $\rc$ whenever necessary,
+to maintain the invariants to be defined in Lemma~\ref{lem:invariants}.
 
@@
 %			\ENDIF
-			\STATE $c_2 \gets$ (z+1)-furthest point of $T$ from $c_1$
+			\STATE $c_2 \gets$ (z+1)-furthest point from $c_1$ in $T$ 
 			\STATE $\rc  \gets \radius{c_2}$
@@
 	%\STATE $q \gets c_1$
-	\IF {at least $z + 1$ points have been arrived}
+	\IF {at least $z + 1$ points have been processed}
 		\STATE $q \gets$  $(z+1)$-furthest point from $c_1$
@@
 and another point from $T = B_2 \cup \Buffer \setminus \set{c_2}$ is picked as $c_2$.
-The while loop iterates $O(dz)$ times,
+The while loop iterates at most $O(dz)$ times,
 because after the first iteration, we are sure 
@@
 
-\paragraph{Analysis}
-For the sake of analysis, we maintain a special point,
+%\paragraph{Analysis}
+For the sake of analysis, we maintain a ``central point'', 
 denoted by $\cp$, %not necessarily in $P$,
-which we call a \emph{central point}.
-The point is defined as follows:
+%which we call a \emph{central point}.
+which is defined as follows:
 if $\card{B_2} < \dz$, then $\cp = c_2$, otherwise,
-$\cp$ is the centerpoint of the first $\dz$ points currently in $B_2$.
+$\cp$ is the centerpoint of the first $\dz$ points currently in~$B_2$.
 
@@
 
-\begin{proof} The proof consists of four parts and each part use previous parts:
-
+\begin{proof} 
+%The proof consists of four parts and each part use previous parts:
 Invariant (a): 
-When a point $p$ arrives in the stream, \textproc{AddToB$_1$} is called, which tries to add $p$ to ball $B_1$.
-By Lemma \ref{lem:(z+1)-furthest}, if point $q$ be the $(z+1)$-furthest point of the stream from $c_1$,
-then $\frac{\alpha}{\alpha+4} \len{c_1q}$ is an increasing stream of lowerbounds for $\delta^*$. So at any point, $\delta < \delta^*$.
-
-Invariant (b): 
+At the beginning, $\delta = 0$, which clearly satisfies the invariant.
+After $z+1$ points of the stream is processed, 
+function \textproc{AddToB$_1$} starts updating $\delta$
+to $\frac{\alpha}{\alpha+4}\len{c_1q}$,
+where $q$ is the $(z+1)$-furthest point from $c_1$ in the current stream.
+Now, since $c_1 \in B_1^*$, Lemma~\ref{lem:(z+1)-furthest}
+implies that $\delta < \delta^*$.
+%Note that if less than $z+1$ points have been processed so far,
+%then $\delta = 0$, and hence, the invariant holds.
+
+Invariant (b1): 
 When an appropriate candidate for $c_2$ is found, 
@@
 
-If $c_2$ is set, then it is $(z+1)$-furthest points of a set $T \subset P$ from $c_1$. 
-Let q be the $(z+1)$-furthest point of the Stream from $c_1$ at that state, then $\len{c_1c_2} \leq \len{c_1q}$ and since (for $16 \leq \alpha$) $\radius{c_2} \leq \frac{1}{6}\frac{\alpha \len{c_1 q}}{(\alpha + 4)} \leq \delta / 6$, then $$r \leq (2 + \frac{2}{\alpha})\radius{c_2} \leq 3 \radius{c_2}  \leq \delta /2$$.
+If $c_2$ is set, then it is the $(z+1)$-furthest point from $c_1$ in a set $T \subset P$.
+Let q be the $(z+1)$-furthest point from $c_1$ in the stream at that state, then $\len{c_1c_2} \leq \len{c_1q}$ and since (for $16 \leq \alpha$) $\radius{c_2} \leq \frac{1}{6}\frac{\alpha \len{c_1 q}}{(\alpha + 4)} \leq \delta / 6$, then
+$$r \leq (2 + \frac{2}{\alpha})\radius{c_2} \leq 3 \radius{c_2}  \leq \delta /2.$$
 
@@
 
-\paragraph{Streaming Model}
+%\paragraph{Streaming Model}
 To implement our algorithm in the streaming model,
@@
 
-\paragraph{Query}
+\REM{
+Suppose that our data structure for maintaining $B_1$, $B_2$ and $B_u$ uses $S(n,z,d)$ space, $T(n,z,d)$ update and $Q(n,z,d)$ query time.
+Note that by $Q_{o}(zd,z,d)$ we mean the query time for the offline 1-center problem with $z$ outlier in $d$ dimensions.
+The best known algorithm for 1-center without outliers is $1.22$-approximation by~\cite{chan2014streaming, agarwal2010streaming}.
+The buffering framework introduced in~\cite{zarrabi2009streaming} with $\O(dz^3 + (\frac{d}{\eps^3})\log(\frac{1}{\eps}))$ space complexity, can be used with this algorithm as subroutine to achieve a $(1.22\sqrt{2})$-approximation ($1.22\sqrt{2} < 1.8$) for 1-center problem with outliers.
+
+\begin{theorem}
+\label{thm:2nd-cmplx}
+Space complexity of Algorithm~\ref{alg:case-1} is $\O(dz+S(n,z,d))$.
+It takes $\O^*(dzT(n,z,d))$ time for update.
+Query time in Algorithm~\ref{alg:query} is $\O(zQ(n,z,d) + dz(dz+zQ_o(zd,z,d)))$ and it returns two centers that guarantee a $(1.8 + \eps)$-approximation for 2-center problem with outliers.
+\end{theorem}
+
+\begin{proof}
+The space complexity for this algorithm is derived from the space used by $B_1$, $B_2$, $B_u$ and the Buffer which is obviously $\O(dz+S(n,z,d))$.
+The while loop runs at most once for each point, so amortized time is $\O(zdT(n,z,d))$.
+The candidates in the Algorithm~\ref{alg:query} are at most $zd$ points  so the query time will easily follows.
+\end{proof}
+}
+
+\begin{theorem}
+\label{thm:far-cmplx}
+	If $\delta^* > \alpha r^*$, a $1.8$-approximation to the 2-center problem with $z$ outliers 
+	can be maintained in $O(d^3z^2)$ space and $\poly(d,z)$ update time.
+\end{theorem}
+
+\begin{proof}
+Our data structures for maintaining $B_1$, $B_2$, and $B_u$
+employ the streaming algorithm of~\cite{zarrabi2009streaming,chan2014streaming}
+%To maintain an approximation to 1-center with $z$ outliers,
+%we use the streaming algorithm of~\cite{zarrabi2009streaming}
+%which combined with the %current best streaming algorithm for 1-center~\cite{chan2014streaming},
+%result of~\cite{chan2014streaming},
+which has an approximation factor of $1.22 \times \sqrt{2} <1.8$.
+The algorithm of~\cite{zarrabi2009streaming}
+uses $O(d^3z)$ space and $\poly(d,z)$ update time,
+which implies the same bounds for \Cref{alg:case-1}.
+Since we need to run $z + 1$ instances of \Cref{alg:case-1} in parallel, 
+the space and update time is multiplied by a factor of $z$.
+\end{proof}
+
+% -------------------------------- Second Case -----------------------------------
+
+\subsection{The Case $\delta^* \leq \alpha r^*$}
+\label{subsec:smaller}
+
+%Our algorithm for solving the problem in this case is based on two main ingredients.
+Our idea in this section is to carefully adopt
+the algorithm of Kim and Ahn~\cite{kim2014improved},
+originally designed for maintaining an approximate 2-center.
+To avoid duplication, we just sketch the main steps of their algorithm,
+%without entering the details, 
+and explain our modifications to it. 
+Kim and Ahn's algorithm, which we refer to as the KA algorithm,
+has 9 different states, shown in~\Cref{fig:dag}.
+Depending on the points arrived so far, the algorithm is in one of the states.
+%In each step one or many of the states can be valid and their algorithm considers all of them in parallel. 
+In each state, the algorithm keeps at most two balls, as a candidate solution. 
+A transition between the states occurs whenever a point not covered by any of the two balls arrive.
+
+The algorithm starts at node 1, and proceed through the transition graph as points arrive.
+In some states, there is more than one state to follow,
+and the algorithm has no prior information which one is the correct choice.
+However, there are only three different paths to follow in the transition graph. 
+%which is a DAG,
+%consisting of only three different transition paths.  
+%(paths from node 1 to node E) 
+Hence, we can easily run three instances of the algorithm in parallel,
+each of which follows one of the paths deterministically, 
+to make sure that at any time, at least one of the instances is in a correct state.
+
+\begin{figure}
+\centering
+\begin{tikzpicture}
+  [scale=.75,auto=left,every node/.style={circle,fill=blue!15}]
+ \tikzset{edge/.style = {->,> = latex'}}
+  \node (1) at (1,2.5) {1};
+  \node (2a) at (3,1)  {2a};
+  \node (3a) at (3,4)  {3a};
+  \node (2b) at (5,0)  {2b};
+  \node (3b) at (5,2)  {3b};
+  \node (3d) at (5,4)  {3d};
+  \node (2c) at (7,0)  {2c};
+  \node (3c) at (7,2)  {3c};
+  \node (3e) at (7,4)  {3e};
+  %\node (E) at (9, 2) {E};
+
+  \foreach \from/\to in {1/2a,1/3a,2a/2b,2b/2c,3a/3b,3a/3b,3a/3d,3b/3c,3d/3e} %,2c/E,3c/E,3e/E
+    \draw[edge] (\from) to (\to);
+
+\end{tikzpicture}
+\caption{State diagram for the KA algorithm.
+Labels are taken from \cite{kim2014improved}.}
+\label{fig:dag}
+\end{figure}
+
+\newcommand{\state}{\text{state}}
+\newcommand{\level}{{j}}
+\newcommand{\counter}{\text{counter}}
+\newcommand{\Insert}{\textsc{insert}}
+\newcommand{\CA}{\text{KA}}
+
+\begin{algorithm}[t]
+\caption{\sc 2-CenterCase2$(P, z, r)$} 
+\algsetup{indent=1.5em}
+\label{alg:smallc}
+\begin{algorithmic}[1]
+	\STATE solutions $\gets \set{}$
+	\FORALL {$(n_1, n_2, n_3, n_4)$ such that $\sum n_i=z$}
+		%\FORALL {path $\pi$ in the transition graph}
+		\FORALL {$\pi \in \set{1, 2, 3}$}
+			\STATE $\counter_i \gets 0$, for $i = 1, \ldots, 4$ % $1 \le i \le 4$
+			\STATE $B_1 \gets B(p_1, r)$, $B_2 \gets \emptyset$
+			\STATE $\level \gets 1$ \COMMENT{$\level$ represents current level}
+			\FORALL {$p \in P$}
+				\IF {$p \not\in B_1 \cup B_2$}
+					\STATE $\counter_\level \gets \counter_\level + 1$
+					\IF {$\counter_\level > n_\level$}
+						\STATE $\level \gets \level+1$
+						\STATE $(B_1, B_2) \gets \CA.\Insert(p, \pi)$
+					\ENDIF
+				\ENDIF
+			\ENDFOR
+			\IF {$\level \le 4$}
+				\STATE add $\max \set{r(B_1), r(B_2)}$ to solutions
+				%\STATE add $(B_1, B_2)$ to solutions
+			\ENDIF
+		\ENDFOR
+	\ENDFOR
+	\RETURN $\min\set{\text{solutions}}$
+\end{algorithmic}
+\end{algorithm}
+
+Our modification is on the transition part.
+Points that are covered by the current solution can be safely ignored, 
+as they do not cause any change in the current solution, and hence, they cause no transition.
+Only those points that lie outside the current solution are candidates for being outliers.
+Since the number of outliers in each state is unknown,
+we try all possible choices. 
+The observation here is that the transition graph is a DAG of depth four.
+If $n_i$ ($1 \le i \le 4$) represents the number of outliers in depth $i$, 
+then it suffices to consider all tuples $(n_1,\dots, n_4)$ such that $\sum_{i=1}^{4} n_i=z$,
+It is easy to verify that there are $O(z^3)$ such tuples.
+
+The pseudocode of our algorithm is presented in \Cref{alg:smallc}.
+For each possible choices of $n_1$ to $n_4$, 
+and each of the three paths in the transition graph, numbered from 1 to 3,
+the algorithm keeps a candidate solution $(B_1, B_2)$ to the 2-center of non-outlier points,
+a parameter $\level$ representing the current level in the transition graph,
+and four counters to keep track of number of outliers seen so far at each level.
+
+The algorithm starts with $B_1 = B(p_1, r)$ and $B_2 = \emptyset$,
+which corresponds to Case 1 of the KA algorithm.
+For each new point $p$, we first check if it is contained in the current solution.
+If so, then we are done.
+Otherwise, if the number of outliers seen in the current level has not yet reached $n_\level$, 
+we consider $p$ as an outlier and proceed.
+%If our quota for consuming outliers in this level is finished, 
+Otherwise, we go to the next level, and update the current candidate solution, 
+$(B_1, B_2)$, using the KA algorithm.
+We give the transition path $\pi$ along with the point $p$ to the KA algorithm
+to help it deterministically decide which state to choose as the next one.
+
+After all points in $P$ are processed, if we are in one of the four states in the current path,
+then the obtained solution is added to the feasible solutions.
+Otherwise, the solution is not feasible, and is abandoned as in the KA algorithm.
+Finally, we return the best solution among all computed feasible solutions. 
+Kim and Ahn~\cite{kim2014improved} proved that in all feasible solutions
+computed this way,
+the larger ball among $B_1$ and $B_2$ has radius at most $3/2r$,
+provided $\delta^* \le \alpha r^*$.
+Assuming that we have a good estimate $r$ satisfying
+$1.2r^* \le r < (1.2 + 2\eps/3)r^*$,
+we get the following result.
+
+\begin{theorem} \label{thm:close}
+	For $1.2r^* \le r < (1.2 + {2 \over 3}\eps)r^*$ and $\delta^* \le \alpha r^*$,
+	\Cref{alg:smallc} computes a $(1.8+\eps)$-approximation to 
+	the 2-center with $z$ outliers 
+	in $\O (dz^3)$ space and $\O (dz^3)$ update time.
+\end{theorem}
+
+\REM{
+\begin{proof}
+Since our algorithm considers all possible input cases of streaming points, there is at least one feasible solution.
+Since every feasible solution has its larger radius at most $3r/2$, the final solution has larger radius at most $3r/2 \le (1.8 + \eps)r^*$.
+For space complexity, our algorithm maintains at most two balls in each case, and therefore it uses $\O(dz^3)$ space.
+Whenever the next point is inserted, the algorithm updates the solution for each subcase in $\O (d)$ time.
+Therefore, the algorithm spends $\O (dz^3)$ update time for each point of $P$.
+Answering a query consists of choosing the minimum radius among all the candidate solutions, which amounts to $\O (dz^3)$ time.
+\end{proof}
+}
+
+% ---------------------------
+
+\noindent
+As shown in \Cref{sec:estimate}, a desired estimate for $r$ can be
+obtained by adding another level of 
+parallelization that runs $O(1/\eps)$ instances of \Cref{alg:smallc} in parallel.
+
+\begin{theorem}
+\label{thm:close-cmplx}
+	If $\delta^* \leq \alpha r^*$, a $(1.8 + \eps)$-approximation to the 2-center problem with $z$ outliers 
+	can be maintained in $\O(\frac{dz^4}{\eps})$ space 
+	and $\O(\frac{dz^4}{\eps})$ update/query time.
+\end{theorem}
+
+%\subsection{Final Result}
+
+\noindent
+Putting all together, we get the following result
+from Theorems~\ref{thm:far-cmplx} and~\ref{thm:close-cmplx}:
+
+\begin{theorem} \label{thm:1-center-stream}
+	Given a stream of points in $d$ dimensions,
+	we can maintain a $(1.8 + \eps)$-approximation to 
+	the 2-center problem with $z$ outliers using 
+	$\O(dz^2 (d^2 + z^2/\eps))$ space and 
+	$\poly(d, z, {1 \over \eps})$ update/query time.
+\end{theorem}
+
+%\begin{theorem}
+%Our algorithm uses $\O(zS(n, z, d) + \frac{dz^4}{\eps})$ space and has time complexity $\O^*(dz^2T(n,z,d) + \frac{dz^5}{\eps})$ and $\O(z^2Q(n,z,d) + dz^2(dz+zQ_o(zd,z,d)) + \frac{dz^4}{\eps})$ for update and query operations, respectively.
+It returns a $(1.8 + \eps)$-approximate solution for 2-center problem with outliers in any dimension.
+%\end{theorem}
+%
+%\noindent 
+%Using the algorithm of~\cite{zarrabi2009streaming}, 
+%the space complexity of our algorithm is $\O(\frac{dz^4}{\eps} + \frac{dz}{\eps^3})$.
+
+%---------------------------- Conclusions ---------------------
+
+\section{Conclusions}
+\label{sec:conc}
+
+In this paper, we presented a $(1.8 + \eps)$-approximation streaming algorithm for 2-center problem with outliers in Euclidean space.
+It improves the previous $(4+\eps)$-approximation algorithm available for the problem 
+due to Charikar~\etal~\cite{mccutchen2008streaming}. 
+Finding better approximation factor or space complexity
+is an interesting problem that remains open.
+It is also interesting to see if the ideas in this paper 
+can be extended to the $k$-center problem with outliers in the data stream model,
+%for any $k$, or 
+even for small values of $k \ge 3$.
+
+\REM{ % to be added in the camera-ready version
+\paragraph{Acknowledgement}
+The authors would like to thank Kiana Ehsani and Sahand Mozaffari 
+for their thoughtful discussions, 
+and for their help to improve the quality of this paper.
+}
+
+%--------------- BIBS --------------------
+
+{
+\small
+\baselineskip=.85\baselineskip
+\bibliographystyle{abbrv}
+\bibliography{bibs/abbrv,bibs/ref}
+}
+
+%\end{document}
+
+%---------------------------- Appendix ------------------------
+
+\appendix
+
+%\newpage
+\REM{
+\section{Answering Queries}
+
 At any point of the stream, we could be able to answer to a query (give the smallest $\alpha$-separated two congruent balls that covers all points except at most $z$ points).
@@
 %\Function{Query}{}
-	\STATE solutions $\gets [\Call{ComputeMin}{B_1, B_2, \Buffer}]$
+	\STATE solutions $\gets \set{\Call{ComputeMin}{B_1, B_2, \Buffer}}$
 
@@
 %\Function{ComputeMin}{$B_1$, $B_2$, Buffer}
-	\STATE solutions $\gets [\,]$
+	\STATE solutions $\gets \set{}$
 	\FOR{$k \gets 0, \dots,(z - \card{\mbox{Buffer}})$}
@@
 
-\REM{
-Suppose that our data structure for maintaining $B_1$, $B_2$ and $B_u$ uses $S(n,z,d)$ space, $T(n,z,d)$ update and $Q(n,z,d)$ query time.
-Note that by $Q_{o}(zd,z,d)$ we mean the query time for the offline 1-center problem with $z$ outlier in $d$ dimensions.
-The best known algorithm for 1-center without outliers is $1.22$-approximation by~\cite{chan2014streaming, agarwal2010streaming}.
-The buffering framework introduced in~\cite{zarrabi2009streaming} with $\O(dz^3 + (\frac{d}{\eps^3})\log(\frac{1}{\eps}))$ space complexity, can be used with this algorithm as subroutine to achieve a $(1.22\sqrt{2})$-approximation ($1.22\sqrt{2} < 1.8$) for 1-center problem with outliers.
-
-\begin{theorem}
-\label{thm:2nd-cmplx}
-Space complexity of Algorithm~\ref{alg:case-1} is $\O(dz+S(n,z,d))$.
-It takes $\O^*(dzT(n,z,d))$ time for update.
-Query time in Algorithm~\ref{alg:query} is $\O(zQ(n,z,d) + dz(dz+zQ_o(zd,z,d)))$ and it returns two centers that guarantee a $(1.8 + \eps)$-approximation for 2-center problem with outliers.
-\end{theorem}
-
-\begin{proof}
-The space complexity for this algorithm is derived from the space used by $B_1$, $B_2$, $B_u$ and the Buffer which is obviously $\O(dz+S(n,z,d))$.
-The while loop runs at most once for each point, so amortized time is $\O(zdT(n,z,d))$.
-The candidates in the Algorithm~\ref{alg:query} are at most $zd$ points  so the query time will easily follows.
-\end{proof}
 }
 
-\begin{theorem}
-\label{thm:far-cmplx}
-	If $\delta^* > \alpha r^*$, a $1.8$-approximation to the 2-center problem with $z$ outliers 
-	can be maintained in $O(d^3z^2)$ space and $\poly(d,z)$ update time.
-\end{theorem}
-
-\begin{proof}
-The streaming algorithm of Zarrabi-Zadeh and Mukhopadhyay~\cite{zarrabi2009streaming} 
-equipped with the streaming $1.22$-approximation for 
-1-center~\cite{agarwal2010streaming, chan2014streaming}
-yields a $(1.22 \times \sqrt{2})$-approximation algorithm
-for 1-center with $z$ outliers.
-Since $1.22 \times \sqrt{2} < 1.8$, the approximation factor of our algorithm follows.
-The algorithm of~\cite{zarrabi2009streaming}
-has $O(d^3z)$ space and $\poly(d,z)$ update time,
-which implies the same bounds for \Cref{alg:case-1}.
-Since we need to run $z + 1$ instances of \Cref{alg:case-1} in parallel, 
-the space and update time is increased by a factor of $O(z)$.
-\end{proof}
-
-% -------------------------------- Second Case -----------------------------------
-
-\subsection{The Case $\delta^* \leq \alpha r^*$}
-\label{subsec:smaller}
-Our idea in this section is derived from~\cite{ahn2014computing, kim2014improved}.
-To avoid duplication, we just outline the important parts of their algorithm and our modifications to it.
-Kim's algorithm has $10$ different states (\Cref{fig:dag}).
-In each step one or many of the states can be valid and their algorithm considers all of them in parallel.
-In each state, there exist at most two balls.
-A transition between the states occurs whenever a point not covered by any of the two balls has arrived in the stream.
-This transition graph starts with a blank node (with no balls) and has depth four (without considering the end nodes).
-It is straightforward to see that this transition graph is a DAG.
-Our modification is on the transition part.
-Points that are covered by current solution can safely be ignored, as they do not cause any transitions in the state, and only those points that lie outside the solution are candidates for being an outlier.
-In each state the number of points that should be considered as outliers is unknown.
-So all the possible choices should be considered.
-It is sufficient to have four integers, $n_1,\dots, n_4$ representing the number of outliers in depth $1$ to $4$, such that $\sum_{i=1}^{4} n_i=z$.
-The modified algorithm is presented in \Cref{alg:smallc}.
-In this algorithm, \textproc{NthOutlier}$(n,p)$ returns the $n$-th point 
-arriving after $p$ in $P$ that does not lie in the current candidate solution.
-
-\begin{figure}
-\centering
-\begin{tikzpicture}
-  [scale=.75,auto=left,every node/.style={circle,fill=blue!15}]
- \tikzset{edge/.style = {->,> = latex'}}
-  \node (1) at (1,2) {1};
-  \node (2a) at (3,1)  {2a};
-  \node (3a) at (3,4)  {3a};
-  \node (2b) at (5,0)  {2b};
-  \node (3b) at (5,2)  {3b};
-  \node (3d) at (5,4)  {3d};
-  \node (2c) at (7,0)  {2c};
-  \node (3c) at (7,2)  {3c};
-  \node (3e) at (7,4)  {3e};
-  \node (E) at (9, 2) {E};
-
-  \foreach \from/\to in {1/2a,1/3a,2a/2b,2b/2c,2c/E,3a/3b,3a/3b,3a/3d,3b/3c,3d/3e,3c/E,3e/E}
-    \draw[edge] (\from) to (\to);
-
-\end{tikzpicture}
-\caption{State Transition of Kim \etal \cite{kim2014improved}} algorithm \label{fig:dag}
-\end{figure}
-
-\begin{algorithm}
-\caption{\sc 2-CenterCase2$(P, z, r)$} 
-\algsetup{indent=1em}
-\label{alg:smallc}
-%\leavevmode
-\begin{algorithmic}[1]
-%\Function{Known$r$}{$P, z, r$}
- 	\STATE list $\gets [\,]$
-	\FORALL{$(n_1, \dots, n_4)$ such that $\sum n_i=z$}
-		\STATE $CS \gets B(p_1,r)$
-		\STATE $p^o_{2} \gets $ \Call{NthOutlier}{$n_1 + 1$, $p_1$}
-		\IF{$p^o_{2}$ arrives}
-			\STATE $CS\gets [ \text{subcase $p^o_{2} \in B_1^*$} ] \cup [ \text{subcase $p^o_{2} \in B_2^*$} ]$
-			\FORALL{case $S$}
-				\STATE $p^o_{3} \gets$ \Call{NthOutlier}{$n_2 + 1$, $p^o_{2}$}
-				\IF{$p^o_{3}$ arrives} 
-					\STATE $CS\gets CS\setminus S \cup [ \text{subcase $p^o_{3} \in B_1^*$} ] \cup [ \text{the subcase $p^o_{3} \in B_2^*$}]$
-					\FORALL {subcase $S'$} 
-						\STATE $p^o_{4} \gets$ \Call{NthOutlier}{$n_3 + 1$, $p^o_{3}$}
-						\IF {$p^o_{4}$ arrives} 
-							\STATE replace $S'$ by a new candidate solution
-							\STATE $p^o_{5} \gets$ \Call{NthOutlier}{$n_4 + 1$, $p^o_{4}$}
-							\IF{$p^o_{5}$ arrives}
-								\STATE abandon the solution
-							\ENDIF
-						\ENDIF
-					\ENDFOR
-				\ENDIF
-			\ENDFOR
-
-		\ENDIF
-		%\STATE $\mathop{Sol}_{n_1,n_2,n_3,n_4} \gets$ the solution with the smallest larger radius, among all the subcases.
-		\STATE add to list the solution with the smallest larger radius, among all subcases
-	\ENDFOR
-	\RETURN the solution in list with the smallest radius
-\end{algorithmic}
-\end{algorithm}
-
-\begin{theorem}
-	For $1.2r^* \le r < (1.2 + 2\eps/3)r^*$ and $\delta^* < \alpha r^*$,
-	Algorithm~\ref{alg:smallc} returns a $(1.8+\eps)$-approximate solution,
-	using $\O (dz^3)$ space and $\O (dz^3)$ update and query time.
-\end{theorem}
-
-\begin{proof}
-Since our algorithm considers all possible input cases of streaming points, there is at least one feasible solution.
-Since every feasible solution has its larger radius at most $3r/2$, the final solution has larger radius at most $3r/2 \le (1.8 + \eps)r^*$.
-For space complexity, our algorithm maintains at most two balls in each case, and therefore it uses $\O(dz^3)$ space.
-Whenever the next point is inserted, the algorithm updates the solution for each subcase in $\O (d)$ time.
-Therefore, the algorithm spends $\O (dz^3)$ update time for each point of $P$.
-Answering a query consists of choosing the minimum radius among all the candidate solutions, which amounts to $\O (dz^3)$ time.
-\end{proof}
-
-\subsubsection{Finding $r$}
-\label{subsec:findr}
+% --------------------------- Estimating r ----------------------
+
+\section{Estimating $r$}
+\label{sec:estimate}
+
+In this section, we describe how to obtain a value $r$,
+such that $1.2r^* \le r < (1.2 + 2\eps/3)r^*$.
+The following lemma provides the main ingredient.
 
 \begin{lemma}
-\label{lem:1-2}
-	An optimal solution for the 1-center problem with $z$ outliers on a point set
+\label{lem:2-approx}
+	Given a point set $P$ in $\IR^d$,
+	an optimal solution to the 1-center problem with $z$ outliers on $P$
 	gives a $(2 + {\alpha \over 2})$-approximation for
-	the 2-center problem with $z$ outliers on that set,
+	the 2-center with $z$ outliers on $P$,
 	provided that $\delta^* \le \alpha r^*$.
 \end{lemma}
-
-%\begin{lemma}
-%\label{lem:1-2}
-%	Let $r_1^*$ and $r^*$ be optimal solutions for
-%	the 1-center and 2-center problems with $z$ outliers, respectively.
-%	If the optimal 2-center balls have distance at most $\alpha r^*$, 
-%	then $r^* \le r_1^* \le \left(2 + \frac{\alpha}{2}\right) r^*$.
-%\end{lemma}
 
@@
 	\includegraphics[width=19em]{figs/2lt1}
-	\caption{Proof of Lemma~\ref{lem:1-2}}
+	\caption{Proof of Lemma~\ref{lem:2-approx}}
 	\label{fig:2lt1}
@@
 \noindent 
-The following is a direct corollary of Lemma~\ref{lem:1-2} and Theorem~\ref{thm:1-center}.
-
-\begin{cor}
+The following is a direct corollary of Lemma~\ref{lem:2-approx} and \Cref{thm:1-center}.
+
+\begin{cor} \label{cor:4-approx}
 	If $\delta^* \le \alpha r^*$, 
@@
 
-\begin{obs}
-\label{obs:2apr}
-Let $r_1$ and $k_0$ be two positive real numbers.
+%\begin{obs}
+%\label{obs:2apr}
+%Let $r_1$ and $k_0$ be two positive real numbers.
 Define $k=k_0 2^i$ to be the smallest real number satisfying the inequality $k \ge r_1$, where $i$ is a non-negative integer.
 Clearly, $k$ is a $2$-approximation for $r_1$.
-\end{obs}
-
-Our algorithm maintains $m=\ceil{{1.2 \times (3 \alpha+12)}/{\eps}}$ candidate lengths.
-For each candidate length $t$, assume that $r = t$ and use it to run Algorithm~\ref{alg:smallc}.
-Algorithm~\ref{alg:1-center} is used to estimate $r$.
-Let $k_i$ be the $i$-th non-zero radius calculated by the algorithm.
-Obviously, the sequence of answers given by the algorithm is increasing.
-
-Let $l_1=k_1$ and $l_i=2^j l_1$, where $l_i$ is the smallest number satisfying $l_i \ge k_i$. By Observation~\ref{obs:2apr}, $l_i$ is a $(8 + 2\alpha)$-approximation to $r_2^*$.
-If the interval $(0, 1.2 l_i]$ divides into $m$ equal segments (Figure~\ref{fig:findr}), then length of each segment is at most $2/3 \eps r_2^*$ and the endpoints as candidates are $L_i = \set{j \times t_i \provided j = 1, \dots, m}$ where $t_i = \frac{1.2 l_i}{m}$.
-The inequality $1.2 r_2^* \le j \times l_i \le (1.2 + \frac{2\eps}{3})r_2^*$ holds for at least one of these candidates.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=21em]{figs/findr}
-	\caption{Subdivision of the interval $(0, 1.2 \ell_i]$}
-	\label{fig:findr}
-\end{figure}
-
-When the first non-zero radius is observed, $l_1$ is set.
-Algorithm~\ref{alg:smallc} should be executed for each candidate in $L_1$ for all the previous points, which have been stored in a buffer.
-It is not hard to see that the space complexity for storing these points is $\O(z)$.
-For each new point, if $l_i=l_{i-1}$ then $L_i = L_{i-1}$ and it suffices to add the new point to all parallel instances corresponding to candidates in $L_i$.
-Otherwise, Algorithm~\ref{alg:smallc} should be executed for all of the candidates in $L_i$, with all the points.
-But this is not achievable due to space limitations.
-To overcome this problem, note that if the candidate $x_j=j \times t_i \in L_i$ is also in $L_{i-1}$, there is no need to start Algorithm~\ref{alg:smallc} over and the current execution will be continued.
+%\end{obs}
+
+%We maintains $m=\ceil{{1.2 (3 \alpha+12)}/{\eps}}$ candidate lengths.
+%For each candidate length $r$, we run an instance of Algorithm~\ref{alg:smallc}.
+
+We use \Cref{alg:1-center} to find an estimate for $r$. 
+Let $r_i$ be the radius calculated by \Cref{alg:1-center} after receiving
+the $i$-th point, $p_i$.
+Clearly, the sequence of $r_i$'s is increasing.
+%We use a doubling strategy, similar o what is used in~\cite{zarrabi2008core}.
+Let $k$ be an integer such that $2^{k-1} \le r_i \le 2^{k}$, and set $\ell_i = 2^{k}$.
+%Let $l_1=r_1$ and $l_i=2^j l_1$, where $l_i$ is the smallest number satisfying $l_i \ge r_i$. 
+Obviously, $\ell_i \le 2 r_i$,
+and hence, by Corollary~\ref{cor:4-approx}, 
+$\ell_i$ is a $(8 + 2\alpha)$-approximation to $r^*$.
+
+We divide the interval $(0, 1.2 \ell_i]$ 
+into $m=\ceil{{1.2 (3 \alpha+12)}/{\eps}}$ equal segments,
+% (Figure~\ref{fig:findr}), then 
+each of length $t_i = 1.2 \ell_i / m$.
+Clearly,  $t_i \le (2\eps/3) r^*$.
+Therefore, in the set
+$R_i = \set{j \times t_i \provided j = 1, \dots, m}$,
+there is at least one value $r$ for which the  
+inequality $1.2 r^* \le r \le (1.2 + \frac{2\eps}{3})r^*$ holds.
+
+%\begin{figure}[h]
+%	\centering
+%	\includegraphics[width=21em]{figs/findr}
+%	\caption{Subdivision of the interval $(0, 1.2 \ell_i]$}
+%	\label{fig:findr}
+%\end{figure}
+
+%When the first non-zero radius is observed, $l_1$ is set. 
+We run $m$ instances of Algorithm~\ref{alg:smallc} for each value $r \in R_i$ in parallel. 
+%for all the previous points, which have been stored in a buffer. It is not hard to see that the space complexity for storing these points is $\O(z)$. 
+Whenever a new point $p_i$ is added, 
+if $\ell_i=\ell_{i-1}$, then $R_i = R_{i-1}$,
+and the new point is inserted to all parallel instances. %corresponding to candidates in $L_i$. 
+%Otherwise, Algorithm~\ref{alg:smallc} should be executed for all of the candidates in $L_i$, with all the points. But this is not achievable due to space limitations. 
+If $\ell_i > \ell_{i-1}$, then the set $R_i$ has two types of values.
+Those values in $R_i$ which are less than $1.2\ell_i$ are also present in $L_{i-1}$,
+because $t_i / t_{i-1}$ is a positive power of 2.
+For these values, we continue executing the corresponding instance.
+If a value $r \in R_i$ is not present in $R_{i-1}$, 
+then we have $r \ge 1.2 \ell_{i - 1} \ge \ell_{i-1}$.
+%To overcome this problem, note that if the candidate $x_j=j \times t_i \in L_i$ is also in $L_{i-1}$, there is no need to start Algorithm~\ref{alg:smallc} over and the current execution will be continued.
 If $x_j \notin L_{i-1}$, then it is certain that $x_j \ge l_{i - 1}$ (Observe that $l_i=ul_{i-1}$, for some $u\in \mathbb{N}$).
-Since the points that do not lie in the candidate solution are saved in the buffer used in Algorithm~\ref{alg:1-center} (which has size at most $z$), all the non-outlier points of this algorithm lie in the candidate balls in Algorithm~\ref{alg:smallc}.
-These outliers have been stored in a buffer, so for the new candidate length, it suffices to execute Algorithm~\ref{alg:smallc} with only the outlier points of $B_1$.
+Since those points not lying in the candidate solution 
+are saved in the buffer of Algorithm~\ref{alg:1-center} (which has size at most $z$), 
+all non-outlier points of this algorithm lie in the candidate balls of Algorithm~\ref{alg:smallc}. 
+These outliers have been stored in a buffer. 
+Therefore, for a new value $r$, 
+it suffices to execute Algorithm~\ref{alg:smallc} with only the outlier points in $B_1$.
+%Overall, we get the following result.
 
@@
 
-\begin{theorem}
-\label{thm:close-cmplx}
-	If $\delta^* \leq \alpha r^*$, a $(1.8 + \eps)$-approximation to the 2-center problem with $z$ outliers 
-	can be maintained in $\O(\frac{dz^4}{\eps})$ space 
-	and $\O(\frac{dz^3}{\eps})$ update/query time.
-\end{theorem}
-
-\subsection{Final Result}
-
-\begin{theorem}
-	A $(1.8 + \eps)$-approximation to the 2-center problem with $z$ outliers
-	can be maintained in the streaming model using 
-	$\O(dz^2 (d^2 + z^2/\eps))$ space and 
-	$\poly(d, z, {1 \over \eps})$ update/query time.
-\end{theorem}
-
-\begin{proof}
-This is immediate from Theorems~\ref{thm:far-cmplx} and~\ref{thm:close-cmplx}.
-%and the fact that $p_1$ was assumed to be a non-outlier.
-\end{proof}
-
-%\begin{theorem}
-%Our algorithm uses $\O(zS(n, z, d) + \frac{dz^4}{\eps})$ space and has time complexity $\O^*(dz^2T(n,z,d) + \frac{dz^5}{\eps})$ and $\O(z^2Q(n,z,d) + dz^2(dz+zQ_o(zd,z,d)) + \frac{dz^4}{\eps})$ for update and query operations, respectively.
-It returns a $(1.8 + \eps)$-approximate solution for 2-center problem with outliers in any dimension.
-%\end{theorem}
-%
-%\noindent 
-%Using the algorithm of~\cite{zarrabi2009streaming}, 
-%the space complexity of our algorithm is $\O(\frac{dz^4}{\eps} + \frac{dz}{\eps^3})$.
-
-%---------------------------- Conclusions ---------------------
-
-\section{Conclusions}
-\label{sec:conc}
-
-In this paper, we presented a $(1.8 + \eps)$-approximation streaming algorithm for 2-center problem with outliers in Euclidean space.
-It improves the previous $(4+\eps)$-approximation algorithm available for the problem 
-due to Charikar~\etal~\cite{mccutchen2008streaming}. 
-Finding better approximation factor or space complexity
-is an interesting problem that remains open.
-It is also interesting to see if the ideas in this paper 
-can be extended to the $k$-center problem with outliers in the data stream model
-for any $k$, or even for small values of $k \ge 3$.
-
-\paragraph{Acknowledgement}
-The authors would like to thank Kiana Ehsani and Sahand Mozaffari 
-for their thoughtful discussions, 
-and for their contribution to improve the presentation of this paper.
-
-%--------------- BIBS --------------------
-
-\small
-\baselineskip=.85\baselineskip
-\bibliographystyle{abbrv}
-\bibliography{bibs/abbrv,bibs/ref}
-
 \end{document}

### 2015-05-02 paper.tex
Adding more descriptin in finding r last paragraph (case r > l_i)

@@
 are saved in the buffer of Algorithm~\ref{alg:1-center} (which has size at most $z$), 
-all non-outlier points of this algorithm lie in the candidate balls of Algorithm~\ref{alg:smallc}. 
+all non-outlier points of this algorithm lie in the candidate balls of Algorithm~\ref{alg:smallc} which has center $p_1$ and radius $l_{i-1}$. 
 These outliers have been stored in a buffer. 
+Since Algorithm~\ref{alg:smallc} maintains two balls with radius at least $r$, which one of them (say $B_1$) has center $p_1$, then all non-outlier points of Algorithm~\ref{alg:1-center} are in $B_1$ and so they do not make transition in Algorithm~\ref{alg:smallc} states.
 Therefore, for a new value $r$, 
-it suffices to execute Algorithm~\ref{alg:smallc} with only the outlier points in $B_1$.
+it suffices to execute Algorithm~\ref{alg:smallc} with only the outlier points in $B_1$,.
 %Overall, we get the following result.

### 2015-05-02 paper.tex
small change
Invariants and query algorithm edited

--- 2015-05-02 paper.tex
@@
 	\label{fig:definition}
+	\vspace{-.5em}
 \end{figure}
@@
 where at any time, $\delta$ is a lower bound of $\delta^*$, 
-and $r$ is an upper bound of $2r^*$ (under a specific condition). %(if $c_p \in B_2^*$).
+and $r$ is an upper bound of $2r^*$ (under a certain condition). %(if $c_p \in B_2^*$).
 
@@
 	\item[1.] $r \leq \delta/2$
-	\item[2.] $B(c_p, \radius{c_p}) \subset B_2(c_2, r)$
+	\item[2.] $B(c_p, \radius{c_p}) \subseteq B_2(c_2, r)$
 \end{enumerate}
@@
 Invariant (b1): 
-When an appropriate candidate for $c_2$ is found, 
-$c_2$ is set to that candidate by the main algorithm (Algorithm~\ref{alg:case-1}),
+%When an appropriate candidate for $c_2$ is found by Algorithm~\ref{alg:case-1}, 
+%$c_2$ is set to that candidate point,
+%and $\rc$ is set to $\frac{2}{\alpha}\len{c_1c_2}$.
+%After that, points are added to $B_2$ by function \textproc{AddToB$_2$}
+%only if they are within $\rc$-radius of $c_2$. 
+When $c_2$ is set by Algorithm~\ref{alg:case-1}, 
+it is the $(z+1)$-furthest point from $c_1$ in a set $T \subseteq P$,
 and $\rc$ is set to $\frac{2}{\alpha}\len{c_1c_2}$.
-After that, points are added to $B_2$ by function \textproc{AddToB$_2$}
-only if they are within $\rc$-radius of $c_2$.
-
-If $c_2$ is set, then it is the $(z+1)$-furthest point from $c_1$ in a set $T \subset P$.
-Let q be the $(z+1)$-furthest point from $c_1$ in the stream at that state, then $\len{c_1c_2} \leq \len{c_1q}$ and since (for $16 \leq \alpha$) $\radius{c_2} \leq \frac{1}{6}\frac{\alpha \len{c_1 q}}{(\alpha + 4)} \leq \delta / 6$, then
-$$r \leq (2 + \frac{2}{\alpha})\radius{c_2} \leq 3 \radius{c_2}  \leq \delta /2.$$
-
-In part 2, if $|B_2| < \dz$ then $c_p = c_2$ and $r = \radius{c_2}$, so $B_2 = B(c_p, \radius{c_p})$. 
-When the size of $B_2$ reaches $\dz$, the central point $\cp$ moves to the centerpoint of $B_2$ and $\rc$ increases by a factor of $(2 + \frac{2}{\alpha})$. 
-Because the centerpoint of $B_2$ locate in $B_2$, then $c_p \in B(c_2, \radius{c_2})$.
-So if $|B_2| \ge \dz$ then $\len{c_2 c_p} \leq \radius{c_2}$ and as a result
-$$\radius{c_p} \leq \frac{2 (\len{c_1 c_2} + \len{c_2 c_p})}{\alpha} \leq \radius{c_2}(1 + \frac{2}{\alpha})$$ 
-So $B(c_p, \radius{c_p}) \subset B_2(c_2, \radius{c_2}(2 + \frac{2}{\alpha}))$.
-
-Invariant (c): A point $p$ can be added to $B_1$ in two parts of the \Cref{alg:case-1}. 
-First case is in function \textproc{AddToB$_1$}, the point will be added to $B_1$ only if it is within distance $\delta$ of the center $c_1$,  when $\len{pc_1} \leq \delta$, which due to invariant (a), guaranties $\len{pc_1} < \delta^*$, so $p \not \in B_2^*$.
-
-Second case is in \Cref{alg:case-1}, whenever the buffer overflows and $B_2$ is non-empty the algorithm takes one of the following actions depending on the size of $B_2$.
+Let $q$ be the $(z+1)$-furthest point from $c_1$ in the stream at that moment.
+Then $\len{c_1c_2} \leq \len{c_1q}$.
+Assuming $\alpha \ge 16$, we have 
+$\radius{c_2} \leq \frac{1}{6}\frac{\alpha \len{c_1 q}}{(\alpha + 4)} \leq \delta / 6$, 
+and hence,  
+$$
+	r \leq (2 + \frac{2}{\alpha})\radius{c_2} \leq 3 \times \radius{c_2}  \leq \delta /2,
+$$
+which means that after increasing $r$ by \textproc{AddToB$_2$},
+the invariant still holds.
+
+Invariant (b2): If $|B_2| < \dz$, then $c_p = c_2$ and $r = \radius{c_2}$, 
+and hence, $B_2 = B(c_p, \radius{c_p})$. 
+When the size of $B_2$ reaches $\dz$, 
+the central point $\cp$ moves to the centerpoint of $B_2$,
+and $\rc$ is increased by a factor of $(2 + \frac{2}{\alpha})$. 
+Because the centerpoint of $B_2$ locates in $B_2$, then $c_p \in B(c_2, \radius{c_2})$.
+Thus, if $|B_2| \ge \dz$ then $\len{c_2 c_p} \leq \radius{c_2}$, and hence
+$$
+	\radius{c_p} \leq \frac{2 (\len{c_1 c_2} + \len{c_2 c_p})}{\alpha} \leq \radius{c_2}(1 + \frac{2}{\alpha}).
+$$ 
+Therefore, $B(c_p, \radius{c_p}) \subseteq B_2(c_2, \radius{c_2}(2 + \frac{2}{\alpha}))$.
+
+Invariant (c): A point $p$ can be added to $B_1$ in two cases. % by \Cref{alg:case-1}. 
+The first case is in function \textproc{AddToB$_1$}, 
+where the point is added to $B_1$ only if it is within distance $\delta$ of the center $c_1$,  
+%when $\len{pc_1} \leq \delta$, 
+which by invariant (a), 
+guaranties $\len{pc_1} < \delta^*$. Therefore, $p \not \in B_2^*$ in this case.
+
+The second case is in \Cref{alg:case-1}, when the buffer overflows and $B_2$ is non-empty.
+The algorithm takes one of the following actions depending on the size of $B_2$.
 If $|B_2| < \dz $, then $c_2 = c_p$. \Cref{alg:case-1} add $c_2$ to $B_1$.
-By contradiction assume that $c_p \in B_2^*$, then due to invariant (b) part 1 and invariant (d) part 1, $2r^* \leq r \leq \delta/2 < \delta^*/2$.
-So by Lemma \ref{lem:2r}, there should be at most $z$ points outside $B_1 \cup B_2$ which contradicts overflow of the buffer.
-
+By contradiction assume that $c_p \in B_2^*$, then due to invariants (b1) and (d1), 
+$2r^* \leq r \leq \delta/2 < \delta^*/2$. 
+Therefore, by Lemma \ref{lem:2r}, there must be at most $z$ points outside $B_1 \cup B_2$,
+which contradicts the overflow of the buffer. 
 If $|B_2| \geq \dz$, then $c_p$ is the centerpoint of the first $\dz$ points currently in $B_2$. 
-In this case, we add all points of $B_2$ to $B_1$. Due to invariant (b), $r \leq \delta/2 < \delta^*/2$. 
-So By Lemma \ref{lem:center-point}, $c_p \in B_1^*$ or $c_p \in B_2^*$.
-By contradiction assume that $c_p \in B_2^*$.
-In this case, due to invariant (d) part 1 and invariant (b) part 2, $B_2$ covers $B(c_p, \radius{c_p})$ and $2r^* \leq r$.
-similar to previous part, it contradicts overflow of the buffer.
-
-Invariant (d): 
-Due to  Observation \ref{obs:c+4}, if $c_1 \in B_1^*$ and $c_p \in B_2^*$ then $1 \leq \frac{\len{c_1 c_p}}{\delta^*} \leq \frac{\len{c_1 c_p}}{\alpha r^*}$ and as a result $2r^* \leq \radius{c_p}$.
-If $|B_2| < \dz$ then $c_p = c_2$ and By \Cref{alg:case-1}, $r = \radius{c_2}$, so $2r^* \leq r$.
-
-If $|B_2| \ge \dz$ then similar to invariant (b): $$2r^* \leq \radius{c_p} \leq (1 + \frac{2}{\alpha})\radius{c_2} \leq (2 + \frac{2}{\alpha})\radius{c_2} = r$$
-
-In part 2, due to previous part, if $c_p \in B_2^*$ then $2r^* \leq r \leq \delta /2$ and $c_p \in B_2$.
-Due to invariant (a) and Observation \ref{obs:intersection}, $B_2$ intersect only with $B_2^*$ and so $B_2 \cap B_1^* = \emptyset$.
-
-In part 3, due to invariant (c) and invariant (d) part 1, $2r^* \leq r \leq \delta/2 < \delta^* /2$. So by Lemma \ref{lem:2r}, all points outside $B_1 \cup B_2$ are outliers.
+In this case, we add all points of $B_2$ to $B_1$. 
+By invariant (b), $r \leq \delta/2 < \delta^*/2$. 
+Therefore, By Lemma \ref{lem:center-point}, $c_p \in B_1^*$ or $c_p \in B_2^*$. 
+By contradiction, assume that $c_p \in B_2^*$. 
+In this case, due to invariants (d1) and (b2), 
+$B_2$ covers $B(c_p, \radius{c_p})$ and $2r^* \leq r$. 
+Therefore, Similar to the previous part, it contradicts the overflow of the buffer.
+
+Invariant (d1): 
+By Observation \ref{obs:c+4}, if $c_1 \in B_1^*$ and $c_p \in B_2^*$,
+then $1 \leq \frac{\len{c_1 c_p}}{\delta^*} \leq \frac{\len{c_1 c_p}}{\alpha r^*}$,
+and as a result, $2r^* \leq \radius{c_p}$. 
+If $|B_2| < \dz$, then $c_p = c_2$, and By \Cref{alg:case-1}, $r = \radius{c_2}$, hence, $2r^* \leq r$.
+If $|B_2| \ge \dz$, then similar to invariant (b), 
+$$
+	2r^* \leq \radius{c_p} \leq (1 + \frac{2}{\alpha})\radius{c_2} \leq (2 + \frac{2}{\alpha})\radius{c_2} = r.
+$$
+
+Invariant (d2): By invariant (d1), if $c_p \in B_2^*$ then $2r^* \leq r \leq \delta /2$ and $c_p \in B_2$. 
+Now, by invariant (a) and Observation~\ref{obs:intersection}, 
+$B_2$ intersect only $B_2^*$, and hence, $B_2 \cap B_1^* = \emptyset$.
+
+Invariant (d3): By invariants (c) and (d1), $2r^* \leq r \leq \delta/2 < \delta^* /2$. 
+Therefore, by Lemma \ref{lem:2r}, all points outside $B_1 \cup B_2$ are outlier.
 
@@
 Our data structures for maintaining $B_1$, $B_2$, and $B_u$
-employ the streaming algorithm of~\cite{zarrabi2009streaming,chan2014streaming}
+employ the streaming algorithm of~\cite{zarrabi2009streaming,chan2014streaming},
 %To maintain an approximation to 1-center with $z$ outliers,
@@
 \end{tikzpicture}
-\caption{State diagram for the KA algorithm.
+\caption{State diagram of the KA algorithm.
 Labels are taken from \cite{kim2014improved}.}
@@
 As shown in \Cref{sec:estimate}, a desired estimate for $r$ can be
-obtained by adding another level of 
-parallelization that runs $O(1/\eps)$ instances of \Cref{alg:smallc} in parallel.
+obtained by running $O(1/\eps)$ instances of \Cref{alg:smallc} in parallel.
+Adding another level of parallelization to remove the assumption of $p_1$
+being a non-outlier, we get the following.
 
@@
 
-%\newpage
-\REM{
+%---------------------------- Answering Queries ------------------------
+
 \section{Answering Queries}
 
-At any point of the stream, we could be able to answer to a query (give the smallest $\alpha$-separated two congruent balls that covers all points except at most $z$ points).
-Due to Invariants (c), we know that $B_1 \cap B_2^* = \emptyset$. 
-So we are sure that, there exists a point $(B_2 \cup \Buffer) \cap B_2^* \neq \emptyset$.
-In this general case, our candidates $C$ for $c_2$ is set $(B_2 \cup \Buffer) \cap B_2^*$.
-
-\begin{lemma}
-\label{lem:B2dz}
-	At any point of the stream, 
-	if $|B_2| \ge \dz$ and $\cp \not\in B_2^*$,
-	then $B_2 \cap B_2^* = \emptyset$.
-\end{lemma}
-
-\begin{proof}
-	due to invariant (b) part 1 and invariant (a) we know that $r \leq \delta/2 < \delta^*/2$. 
-	By Lemma \ref{lem:center-point}, $c_p \in B_1^* \cap B_2^*$. 
-	Since $c_p \not \in B_2^*$, then $c_p \in B_1^*$. 
-	On the other hand, By Observation \ref{obs:intersection}, $B_2$ intersect with at most one of $B_1^*$ and $B_2^*$. So as a result, $B_2 \cap B_2^* = \emptyset$.
-\end{proof}
-
-As a result of Lemma \ref{lem:B2dz}, when $|B_2| \geq \dz$, we are sure that $(\{c_2\} \cup \Buffer) \cap B_2^* \neq \emptyset$. 
-So if $|B_2| \ge \dz$, then our candidates $C$ for $c_2$ are $\{c_2\} \cup \Buffer$. Our Query algorithm, works as follows.
-
-For each candidate $c \in C$, \Cref{alg:query} constructs $B'_1(c_1, \max \{\delta, \radius{c} \})$ and $B'_2(c, \radius{c})$. 
-First, consider the candidate $c$ that equals to current $c_2$, then $B_1 = B'_1$. 
-Since $\radius{c_2} \leq r \leq \delta/2$ (invariant (b) part 1) and $B'_2 \subset B_2$ then we don't need to construct any new set. 
-In general case, when $c \neq c_2$, we know that $B_1 \subset B'_1$, so we just need to see which of $\Buffer \cap B_2$ points located in $B'_1$.
-When $|B_2| \geq \dz$ and $c \neq c_2$, then it means that assumed $c_p \not \in B_2^*$. So By Lemma \ref{lem:B2dz}, $B_2$ can be added to $B'_1$ without contradicting invariant (c). 
-So in this case, just need to see which points of $\Buffer$ should be added to $B'_1$. 
-\Cref{alg:query} use functions \textproc{AddToB$'_1$} and \textproc{AddToB$'_2$} for adding a point to $B'_1$ and $B'_2$ respectively. 
-Their definition are totally same as functions \textproc{AddToB$_1$} and \textproc{AddToB$_2$} except that, they add point to $B'_i$ instead of $B_i$($i = 1, 2$).
-
-As \Cref{alg:query}, consider all valid cases of $c$, for one of $c \in C$, $c \in B_2^*$. 
-Consider that $c$ as $c^*$ and corresponding $B'_1$ and $B'_2$ as $B''_1$ and $B''_2$. 
-Since $1 \leq \frac{\len{c_1 c^*}}{\alpha^*} < \frac{\len {c_1 c^*}}{\alpha r^*}$(By Observation \ref{obs:c+4}) then $2r^* \leq \radius{c^*}$ and as a result $B^*_1 \subset B''_1$ and $B^*_2 \subset B''_2$ (By Lemma \ref{lem:2r}).
-On the other hand, due to invariant (c) and distance of new points added to $B''_1$ compare to $B_1$ is less than $\len{c_1 p} \leq \max \{\delta, \radius{c^*} \}$, so $B''_1 \cap B_2^* = \emptyset$.
-As a result $B''_1$ and $B''_2$ totally covers $B_1^*$  and $B_2^*$ respectively, with some extra outlier points and remaining points in $\Buffer$ are certainly outliers.
-The only unknown part is that \Cref{alg:query} does not know how many outliers are in $B''_1$ and $B''_2$.
-So \Cref{alg:compute-min} tries all possible cases and choose the one with the minimum radius.
+%Using \Cref{alg:case-1},
+In the following, we show how to answer queries of this kind:
+find two $\alpha$-separated congruent balls of minimum radius
+to cover all but at most $z$ points of the stream processed so far.
+
+Our query algorithm is presented in \Cref{alg:query}.
+The idea behind the algorithm is as follows.
+By our initial assumption about $p_1$ and by invariants (c), 
+we know that $B_1$ completely contains $B_1^*$.
+%because $B_1 \cap B_2^* = \emptyset$ . 
+But for $B_2$, it might be the case that our assumption about $c_2$ 
+was incorrect, and therefore, $B_2$ may not completely contain $B_2^*$. 
+The overcome this, we try all possible candidates for $c_2$,
+and compute, for each possible combinations of 
+$B_1$, $B_2$, and Buffer, the best solution for 2-center with $z$ outliers
+using function \textproc{ComputeMin} presented in \Cref{alg:compute-min}.
 
@@
 
-}
+Now, we show that the query algorithm correctly considers all possible candidates for $c_2$.
+Let $C$ denotes the set of candidate points for $c_2$.
+By invariants (c), we know that $B_1 \cap B_2^* = \emptyset$. 
+Therefore, $(B_2 \cup \Buffer) \cap B_2^* \neq \emptyset$,
+and hence, $C \subseteq (B_2 \cup \Buffer) \cap B_2^*$. % in general.
+We now use the following lemma.
+%In this general case, our candidates $C$ for $c_2$ is set $(B_2 \cup \Buffer) \cap B_2^*$.
+
+\begin{lemma}
+\label{lem:B2dz}
+	At any time, 
+	if $|B_2| \ge \dz$ and $\cp \not\in B_2^*$,
+	then $B_2 \cap B_2^* = \emptyset$.
+\end{lemma}
+
+\begin{proof}
+	By invariants (a) and (b1), we know that $r \leq \delta/2 < \delta^*/2$. 
+	By Lemma~\ref{lem:center-point}, $c_p \in B_1^* \cap B_2^*$. 
+	Since $c_p \not \in B_2^*$, then $c_p \in B_1^*$. 
+	On the other hand, by Observation~\ref{obs:intersection}, 
+	$B_2$ intersect at most one of $B_1^*$ and $B_2^*$. 
+	Therefore, $B_2 \cap B_2^* = \emptyset$.
+\end{proof}
+
+\noindent
+By Lemma \ref{lem:B2dz}, when $|B_2| \geq \dz$, 
+we known that $(\{c_2\} \cup \Buffer) \cap B_2^* \neq \emptyset$. 
+Therefore, if $|B_2| \ge \dz$, then our candidates for $C$ are $\{c_2\} \cup \Buffer$.
+
+Our query algorithm works as follows. 
+For each candidate point $c \in C$, \Cref{alg:query} 
+constructs $B'_1(c_1, \max \{\delta, \radius{c} \})$ and $B'_2(c, \radius{c})$. 
+If the candidate $c$ equals to current $c_2$, then, $B_1 = B'_1$. 
+Since $\radius{c_2} \leq r \leq \delta/2$ by invariant (b1) and $B'_2 \subset B_2$,
+we do not need to construct any new set. 
+For $c \neq c_2$, we know that $B_1 \subset B'_1$, and hence,
+we just need to see which points in $\Buffer \cap B_2$ are located in $B'_1$.
+When $|B_2| \geq \dz$ and $c \neq c_2$, then it means that assumed $c_p \not \in B_2^*$. 
+Therefore, by Lemma \ref{lem:B2dz}, $B_2$ can be added to $B'_1$ without contradicting invariant (c). 
+So in this case, we just need to see which points of $\Buffer$ must be added to $B'_1$. 
+\Cref{alg:query} use functions \textproc{AddToB$'_1$} and \textproc{AddToB$'_2$} for adding a point to $B'_1$ and $B'_2$ respectively. 
+The definition of these functions are the same as \textproc{AddToB$_1$} and \textproc{AddToB$_2$},
+except that, they add point to $B'_i$ instead of $B_i$ ($i = 1, 2$).
+
+Since \Cref{alg:query} considers all valid candidates for $c$, 
+at least for one $c^* \in C$, we have $c^* \in B_2^*$. 
+We call the corresponding $B'_1$ and $B'_2$ by $B''_1$ and $B''_2$. 
+Since by Observation \ref{obs:c+4},
+$1 \leq \frac{\len{c_1 c^*}}{\alpha^*} < \frac{\len {c_1 c^*}}{\alpha r^*}$, 
+we have $2r^* \leq \radius{c^*}$, and therefore,
+$B^*_1 \subset B''_1$ and $B^*_2 \subset B''_2$ by Lemma~\ref{lem:2r}.
+On the other hand, since the distance of the new points added to $B''_1$ compare to $B_1$ is less than $\len{c_1 p} \leq \max \{\delta, \radius{c^*} \}$, 
+we have by invariant (c) that  $B''_1 \cap B_2^* = \emptyset$.
+As a result $B''_1$ (resp., $B''_2$) completely covers $B_1^*$  (resp., $B_2^*$), 
+and points in $\Buffer$ are certainly outliers.
+The only unknown part is that \Cref{alg:query} does not know how many outliers are in $B''_1$ and $B''_2$.
+Therefore, \Cref{alg:compute-min} tries all possible cases and choose the one with the minimum radius.
 
@@
 
-In this section, we describe how to obtain a value $r$,
+In this section, we show how to obtain a value $r$,
 such that $1.2r^* \le r < (1.2 + 2\eps/3)r^*$.
@@
 
-\begin{figure}[th]
+\begin{figure}[t]
 	\centering
@@
 Let $k$ be an integer such that $2^{k-1} \le r_i \le 2^{k}$, and set $\ell_i = 2^{k}$.
+(If $r_i = 0$, we set $\ell_i = 0$.)
 %Let $l_1=r_1$ and $l_i=2^j l_1$, where $l_i$ is the smallest number satisfying $l_i \ge r_i$. 
@@
 are saved in the buffer of Algorithm~\ref{alg:1-center} (which has size at most $z$), 
-all non-outlier points of this algorithm lie in the candidate balls of Algorithm~\ref{alg:smallc}. 
+all non-outlier points of this algorithm lie in the candidate balls of Algorithm~\ref{alg:smallc} which has center $p_1$ and radius at most $l_{i-1}$. 
 These outliers have been stored in a buffer. 
-Therefore, for a new value $r$, 
-it suffices to execute Algorithm~\ref{alg:smallc} with only the outlier points in $B_1$.
+Since Algorithm~\ref{alg:smallc} maintains two balls with radius at least $r$, 
+one of which (say $B_1$) is centered at $p_1$, 
+then all non-outlier points of Algorithm~\ref{alg:1-center} are in $B_1$,
+and hence, they do not make any transition in the states of Algorithm~\ref{alg:smallc}.
+Therefore, for any new value $r$, 
+it suffices to execute Algorithm~\ref{alg:smallc} with only the 
+outlier points in the buffer of Algorithm~\ref{alg:1-center}.
 %Overall, we get the following result.

### 2015-05-03 paper.tex
Second submission
Query added

@@
 To obtain our result, we have used a combination of several ideas
-including parallelization construction, far/close ball separation,
+including parallelization construction, far/close ball separation, centerpoint theorem,
 and keeping a lower bound on the radius and distance of the optimal balls.
@@
 \begin{algorithmic}[1]
-%\Function{Query}{}
-	\STATE solutions $\gets \set{\Call{ComputeMin}{B_1, B_2, \Buffer}}$
-
-	\STATE candidates $\gets \Buffer$
+	%\STATE solutions $\gets \set{\Call{ComputeMin}{B_1, B_2, \Buffer}}$
+	\STATE solutions $\gets \set{}$
+
+	\STATE candidates $\gets \set{c_2} \cup \Buffer $
 	\IF {$\card{B_2} < \dz$}
-		\STATE candidates $\gets \Buffer \cup B_2 \setminus \set{c_2}$
+		\STATE add $B_2$ to candidates
 	\ELSE
@@
 	\STATE $\delta_0 = \delta$
-	\FOR{$c_2 \in$ candidates}
-		\STATE $\rc  \gets \frac{2}{\alpha} \len{c_1 c_2}$
+	\FOR{$c \in$ candidates}
+		\STATE $\rc  \gets \frac{2}{\alpha} \len{c_1 c}$
 		\STATE $B'_1 \gets B_1$, $\delta \gets \max \{ \delta_0, r \}$
@@
 
-Now, we show that the query algorithm correctly considers all possible candidates for $c_2$.
-Let $C$ denotes the set of candidate points for $c_2$.
-By invariants (c), we know that $B_1 \cap B_2^* = \emptyset$. 
-Therefore, $(B_2 \cup \Buffer) \cap B_2^* \neq \emptyset$,
-and hence, $C \subseteq (B_2 \cup \Buffer) \cap B_2^*$. % in general.
-We now use the following lemma.
-%In this general case, our candidates $C$ for $c_2$ is set $(B_2 \cup \Buffer) \cap B_2^*$.
-
 \begin{lemma}
@@
 \noindent
-By Lemma \ref{lem:B2dz}, when $|B_2| \geq \dz$, 
-we known that $(\{c_2\} \cup \Buffer) \cap B_2^* \neq \emptyset$. 
-Therefore, if $|B_2| \ge \dz$, then our candidates for $C$ are $\{c_2\} \cup \Buffer$.
+%Now, we show that the query algorithm correctly considers all possible candidates for $c_2$.
+Let $C$ denote the set of candidates for $c_2$.
+By invariant~(c), we know that $B_1 \cap B_2^* = \emptyset$. 
+Therefore, there exists a point in $(B_2 \cup \Buffer) \cap B_2^*$,
+and hence, $C$ is $(B_2 \cup \Buffer) \cap B_2^*$ in general.
+%We now use the following lemma.
+%In this general case, our candidates $C$ for $c_2$ is set $(B_2 \cup \Buffer) \cap B_2^*$.
+However, when $|B_2| \geq \dz$, 
+we know by Lemma \ref{lem:B2dz} that $(\{c_2\} \cup \Buffer) \cap B_2^* \neq \emptyset$. 
+Therefore, if $|B_2| \ge \dz$, then our candidates for $C$ are only $\{c_2\} \cup \Buffer$.
 

### 2015-05-03 paper.tex
Another submission
Referring to appendix A inside the paper

@@
 in a data structure that supports adding points,
-and gives a $\beta$-approximation to 1-center with $k$ outliers, for $k=0,\dots,z$.
+and gives a $\beta$-approximation to 1-center with $z$ outliers. %, for $k=0,\dots,z$.
 Moreover, we maintain a set $B_u = B_1 \cup B_2$ in a similar data structure.
@@
 	If $\delta^* > \alpha r^*$, a $1.8$-approximation to the 2-center problem with $z$ outliers 
-	can be maintained in $O(d^3z^2)$ space and $\poly(d,z)$ update time.
+	can be maintained in $O(d^3z^2)$ space and $\poly(d,z)$ update/query time.
 \end{theorem}
@@
 \begin{proof}
-Our data structures for maintaining $B_1$, $B_2$, and $B_u$
-employ the streaming algorithm of~\cite{zarrabi2009streaming,chan2014streaming},
+Our algorithm for answering queries is provided in ~\Cref{sec:query}.
+To maintain $B_1$, $B_2$, and $B_u$, we 
+use the streaming algorithm of~\cite{zarrabi2009streaming,chan2014streaming},
 %To maintain an approximation to 1-center with $z$ outliers,
@@
 which has an approximation factor of $1.22 \times \sqrt{2} <1.8$.
-The algorithm of~\cite{zarrabi2009streaming}
-uses $O(d^3z)$ space and $\poly(d,z)$ update time,
-which implies the same bounds for \Cref{alg:case-1}.
+%The algorithm of~\cite{zarrabi2009streaming}
+The algorithm has $O(d^3z)$ space and $\poly(d,z)$ update time.
+%which implies the same bounds for \Cref{alg:case-1}.
 Since we need to run $z + 1$ instances of \Cref{alg:case-1} in parallel, 
-the space and update time is multiplied by a factor of $z$.
+the space and update time are multiplied by a factor of~$z$.
 \end{proof}
@@
 
-\REM{ % to be added in the camera-ready version
-\paragraph{Acknowledgement}
-The authors would like to thank Kiana Ehsani and Sahand Mozaffari 
-for their thoughtful discussions, 
-and for their help to improve the quality of this paper.
-}
-
 %--------------- BIBS --------------------
@@
 \section{Answering Queries}
+\label{sec:query}
 
 %Using \Cref{alg:case-1},
-In the following, we show how to answer queries of this kind:
+In the following, we show how the information maintained 
+by \Cref{alg:case-1} can be used to answer queries of this kind:
 find two $\alpha$-separated congruent balls of minimum radius
@@
 was incorrect, and therefore, $B_2$ may not completely contain $B_2^*$. 
-The overcome this, we try all possible candidates for $c_2$,
+To overcome this issue, we try all possible candidates for $c_2$,
 and compute, for each possible combinations of 
 $B_1$, $B_2$, and Buffer, the best solution for 2-center with $z$ outliers
-using function \textproc{ComputeMin} presented in \Cref{alg:compute-min}.
+using the \textproc{MinCover} function presented in \Cref{alg:compute-min}.
 
@@
 \begin{algorithmic}[1]
-	%\STATE solutions $\gets \set{\Call{ComputeMin}{B_1, B_2, \Buffer}}$
+	%\STATE solutions $\gets \set{\Call{MinCover}{B_1, B_2, \Buffer}}$
 	\STATE solutions $\gets \set{}$
 
+	\STATE candidates $\gets \Buffer \cup B_2$
+	\IF {$\card{B_2} \ge \dz$}
 		\STATE candidates $\gets \set{c_2} \cup \Buffer $
-	\IF {$\card{B_2} < \dz$}
-		\STATE add $B_2$ to candidates
-	\ELSE
-		\STATE $B_1 \gets B_u$
+		\STATE $B_1 \gets B_1 \cup B_2$
 	\ENDIF
@@
 		\ENDFOR
-		\STATE add \Call{ComputeMin}{$B'_1$, $B'_2$, $\Buffer'$} to solutions
+		\STATE add \Call{MinCover}{$B'_1$, $B'_2$, $\Buffer'$} to solutions
 	\ENDFOR
@@
 \begin{algorithm}
-\caption{\sc ComputeMin($B'_1, B'_2, \text{\rm Buffer}$)} 
+\caption{\sc MinCover($B_1, B_2, \text{\rm Buffer}$)} 
 \algsetup{indent=1.5em}
@@
 \begin{algorithmic}[1]
-%\Function{ComputeMin}{$B_1$, $B_2$, Buffer}
+%\Function{MinCover}{$B_1$, $B_2$, Buffer}
 	\STATE solutions $\gets \set{}$
 	\FOR{$k \gets 0, \dots,(z - \card{\mbox{Buffer}})$}
-		\STATE $r_1 \gets \Call{1-Center}{B'_1, k}$
-		\STATE $r_2 \gets \Call{1-Center}{B'_2, z - \card{\mbox{Buffer}} - k}$
+		\STATE $r_1 \gets \Call{1-Center}{B_1, k}$
+		\STATE $r_2 \gets \Call{1-Center}{B_2, z - \card{\mbox{Buffer}} - k}$
 		\STATE add $\max \set{r_1, r_2}$ to solutions
@@
 \end{algorithm}
+
+%Now, we show that the query algorithm correctly considers all possible candidates for $c_2$.
+Let $C$ denote the set of candidates for $c_2$.
+By invariant~(c), we know that $B_1 \cap B_2^* = \emptyset$. 
+Therefore, there exists a point in $(B_2 \cup \Buffer) \cap B_2^*$,
+and hence, $C$ is $(B_2 \cup \Buffer) \cap B_2^*$ in general.
+%We now use the following lemma.
+%In this general case, our candidates $C$ for $c_2$ is set $(B_2 \cup \Buffer) \cap B_2^*$.
+However, when $|B_2| \geq \dz$, 
+we show in the following lemma that $(\{c_2\} \cup \Buffer) \cap B_2^* \neq \emptyset$. 
+Therefore, if $|B_2| \ge \dz$, 
+we only need to consider $\{c_2\} \cup \Buffer$ as candidates for $C$.
+%our candidates for $C$ are only $\{c_2\} \cup \Buffer$.
 
@@
 \noindent
-%Now, we show that the query algorithm correctly considers all possible candidates for $c_2$.
-Let $C$ denote the set of candidates for $c_2$.
-By invariant~(c), we know that $B_1 \cap B_2^* = \emptyset$. 
-Therefore, there exists a point in $(B_2 \cup \Buffer) \cap B_2^*$,
-and hence, $C$ is $(B_2 \cup \Buffer) \cap B_2^*$ in general.
-%We now use the following lemma.
-%In this general case, our candidates $C$ for $c_2$ is set $(B_2 \cup \Buffer) \cap B_2^*$.
-However, when $|B_2| \geq \dz$, 
-we know by Lemma \ref{lem:B2dz} that $(\{c_2\} \cup \Buffer) \cap B_2^* \neq \emptyset$. 
-Therefore, if $|B_2| \ge \dz$, then our candidates for $C$ are only $\{c_2\} \cup \Buffer$.
-
 Our query algorithm works as follows. 
@@
 constructs $B'_1(c_1, \max \{\delta, \radius{c} \})$ and $B'_2(c, \radius{c})$. 
-If the candidate $c$ equals to current $c_2$, then, $B_1 = B'_1$. 
+If the candidate $c$ equals the current $c_2$, then, $B_1 = B'_1$. 
 Since $\radius{c_2} \leq r \leq \delta/2$ by invariant (b1) and $B'_2 \subset B_2$,
@@
 On the other hand, since the distance of the new points added to $B''_1$ compare to $B_1$ is less than $\len{c_1 p} \leq \max \{\delta, \radius{c^*} \}$, 
-we have by invariant (c) that  $B''_1 \cap B_2^* = \emptyset$.
-As a result $B''_1$ (resp., $B''_2$) completely covers $B_1^*$  (resp., $B_2^*$), 
-and points in $\Buffer$ are certainly outliers.
+we have by invariant~(c) that  $B''_1 \cap B_2^* = \emptyset$.
+As a result, $B''_1$ (resp., $B''_2$) completely covers $B_1^*$  (resp., $B_2^*$), 
+and points in $\Buffer$ are certainly outlier.
 The only unknown part is that \Cref{alg:query} does not know how many outliers are in $B''_1$ and $B''_2$.
@@
 
+\REM{ }% to be added in the camera-ready version
+\paragraph{Acknowledgement}
+The authors would like to thank Kiana Ehsani and Sahand Mozaffari 
+for their thoughtful discussions, 
+and for their help to improve the quality of this paper.
+
 \end{document}

### 2015-05-03 paper.tex
Some more fixes + submission

@@
 \begin{abstract}
-We study the Euclidean 2-center problem with outliers in the data stream model. 
+We study the 2-center problem with outliers in high-dimensional data streams. 
 Given a stream of points in arbitrary $d$ dimensions, the goal is to find two congruent balls 
@@
 In this paper, we focus on the \emph{data stream} model of computation
-in which only a single pass over input is allowed,
+where only a single pass over input is allowed,
 and we have only a limited amount of working space available.
 %which is typically sublinear in the input size.
-This model is specially useful for processing large data sets,
+This model is in particular useful for processing large data sets,
 as it does not require the entire data set to be stored in memory.
@@
 the problem in known to be NP-hard in two and more dimensions~\cite{fowler1981optimal},
-and is even hard to approximate to within a factor close to 2, 
+and is even hard to approximate to within a factor better than $1.82$, 
 unless P$\,=\,$NP~\cite{feder1988optimal}.
@@
 	\includegraphics[width=13em]{figs/definition}
-	\caption{An example of $2$-center with 6 outliers}
+	\caption{An example of $2$-center with 6 outliers.}
 	\label{fig:definition}
@@
 This is somewhat surprising, considering that 
-the best current approximation factors for streaming $k$-center with and without outliers 
-differ by a factor of $\sqrt{2}$ for $k=1$,
+the current best approximation factors for streaming $k$-center with and without outliers 
+differ by a multiplicative factor of $\sqrt{2}$ for $k=1$,
 and by a factor of 2  for general~$k$. %the 1-center problem.
@@
 and the number of outliers, $z$.
-It also assumes that the first point $p_1$ of the stream is non-outlier.
+It assumes that the first point $p_1$ of the stream is non-outlier.
 We will show later how to remove this assumption.
@@
 	%\STATE {$\triangleright$ $c$ is a non-outlier point in the optimal solution}
-	\STATE $B \gets B(p_1, 0)$
+	\STATE $c \gets$ the first point in $P$
+	\STATE $B \gets B(c, 0)$
 	\STATE $Q \gets \emptyset$
@@
 Let $B^*(c^*, r^*)$ be the optimal solution,
-and $c = p_1$ be a non-outlier point in the optimal solution.
+and $c$ be a non-outlier point in the optimal solution.
 Since $c$ is covered by $B^*$,
@@
 \item [(a)] $\delta < \delta^*$ %$\delta$ is a lower bound of $\delta^*$
-\item [(b)] if $c_2$ is set, then
-\begin{enumerate}
-	\item[1.] $r \leq \delta/2$
-	\item[2.] $B(c_p, \radius{c_p}) \subseteq B_2(c_2, r)$
-\end{enumerate}
+\item [(b)] $r \leq \delta/2$
+%\begin{enumerate}
+%	\item[1.] $r \leq \delta/2$
+%	\item[2.] $B(c_p, \radius{c_p}) \subseteq B_2(c_2, r)$
+%\end{enumerate}
 \item [(c)] $B_1 \cap B_2^* = \emptyset$
@@
 		\item [2.] $B_2 \cap B_1^* = \emptyset$
-		\item [3.] all points in $\Buffer$ are outliers
+		\item [3.] all points in $\Buffer$ are outlier
 	\end{enumerate}
@@
 
-Invariant (b1): 
-%When an appropriate candidate for $c_2$ is found by Algorithm~\ref{alg:case-1}, 
-%$c_2$ is set to that candidate point,
-%and $\rc$ is set to $\frac{2}{\alpha}\len{c_1c_2}$.
-%After that, points are added to $B_2$ by function \textproc{AddToB$_2$}
-%only if they are within $\rc$-radius of $c_2$. 
+Invariant (b): 
 When $c_2$ is set by Algorithm~\ref{alg:case-1}, 
@@
 $$
-which means that after increasing $r$ by \textproc{AddToB$_2$},
-the invariant still holds.
-
-Invariant (b2): If $|B_2| < \dz$, then $c_p = c_2$ and $r = \radius{c_2}$, 
+which means that the invariant holds, 
+even after increasing $r$ by function \textproc{AddToB$_2$}.
+
+Invariant (c): 
+We first claim that if $c_2$ is set, then
+$B(c_p, \radius{c_p}) \subseteq B_2(c_2, r)$.
+If $|B_2| < \dz$, then $c_p = c_2$ and $r = \radius{c_2}$, 
 and hence, $B_2 = B(c_p, \radius{c_p})$. 
@@
 
-Invariant (c): A point $p$ can be added to $B_1$ in two cases. % by \Cref{alg:case-1}. 
+A point $p$ can be added to $B_1$ in two cases. % by \Cref{alg:case-1}. 
 The first case is in function \textproc{AddToB$_1$}, 
@@
 If $|B_2| < \dz $, then $c_2 = c_p$. \Cref{alg:case-1} add $c_2$ to $B_1$.
-By contradiction assume that $c_p \in B_2^*$, then due to invariants (b1) and (d1), 
+By contradiction assume that $c_p \in B_2^*$, 
+then by invariants (b) and (d1), 
 $2r^* \leq r \leq \delta/2 < \delta^*/2$. 
@@
 Therefore, By Lemma \ref{lem:center-point}, $c_p \in B_1^*$ or $c_p \in B_2^*$. 
-By contradiction, assume that $c_p \in B_2^*$. 
-In this case, due to invariants (d1) and (b2), 
+Suppose by way of contradiction that $c_p \in B_2^*$. 
+In this case, by invariant (d1) and the claim we proved first,
 $B_2$ covers $B(c_p, \radius{c_p})$ and $2r^* \leq r$. 
@@
 and as a result, $2r^* \leq \radius{c_p}$. 
-If $|B_2| < \dz$, then $c_p = c_2$, and By \Cref{alg:case-1}, $r = \radius{c_2}$, hence, $2r^* \leq r$.
+If $|B_2| < \dz$, then $c_p = c_2$, and by \Cref{alg:case-1}, 
+$r = \radius{c_2}$, and therefore, $2r^* \leq r$.
 If $|B_2| \ge \dz$, then similar to invariant (b), 
 $$
-	2r^* \leq \radius{c_p} \leq (1 + \frac{2}{\alpha})\radius{c_2} \leq (2 + \frac{2}{\alpha})\radius{c_2} = r.
+	2r^* \leq \radius{c_p} \leq (1 + \frac{2}{\alpha})\radius{c_2} 
+	\leq (2 + \frac{2}{\alpha})\radius{c_2} = r.
 $$
@@
 %\paragraph{Streaming Model}
-To implement our algorithm in the streaming model,
-we maintain the sets $B_1$ and $B_2$ 
-in a data structure that supports adding points,
-and gives a $\beta$-approximation to 1-center with $z$ outliers. %, for $k=0,\dots,z$.
-Moreover, we maintain a set $B_u = B_1 \cup B_2$ in a similar data structure.
-Note that these data structures do not need to maintain all the points. 
-They only need to have a buffer of size $\dz$ that keeps the most recently added points.
 
@@
 Our algorithm for answering queries is provided in ~\Cref{sec:query}.
+It uses the current partition $B_1$, $B_2$, and Buffer, to compute
+an optimal solution to 2-center with $z$ outliers.
+In the streaming model, we cannot afford keeping all the points of $B_1$ and $B_2$. 
+%To implement our algorithm in the streaming model,
+Therefore, we maintain the sets $B_1$ and $B_2$ 
+in a data structure that supports adding points,
+and gives a $\beta$-approximation to 1-center with $k$ outliers, for $k=0,\dots,z$.
+Moreover, we maintain a set $B_u = B_1 \cup B_2$ in a similar data structure.
+Note that these data structures do not need to maintain all the points. 
+They only need to have a buffer of size $\dz$ to keep the most recently added points.
+
 To maintain $B_1$, $B_2$, and $B_u$, we 
@@
 %result of~\cite{chan2014streaming},
-which has an approximation factor of $1.22 \times \sqrt{2} <1.8$.
+which provides an approximation factor of $1.22 \times \sqrt{2} <1.8$.
 %The algorithm of~\cite{zarrabi2009streaming}
-The algorithm has $O(d^3z)$ space and $\poly(d,z)$ update time.
+The algorithm uses $O(d^3z)$ space and has $\poly(d,z)$ update time.
 %which implies the same bounds for \Cref{alg:case-1}.
@@
 provided $\delta^* \le \alpha r^*$.
+(Their proof is stated for $\alpha = 2$, 
+but can be extended to any $\alpha \ge 2$.)
 Assuming that we have a good estimate $r$ satisfying
 $1.2r^* \le r < (1.2 + 2\eps/3)r^*$,
-we get the following result.
+we get the following.
 
@@
 \noindent
-Putting all together, we get the following result
-from Theorems~\ref{thm:far-cmplx} and~\ref{thm:close-cmplx}:
+Theorems~\ref{thm:far-cmplx} and~\ref{thm:close-cmplx}
+together yield the following main result of the paper.
 
@@
 \caption{\sc Query} 
-\algsetup{indent=1.5em}
+\algsetup{indent=1.2em}
 \label{alg:query}
@@
 
-	\STATE candidates $\gets \Buffer \cup B_2$
+	\STATE candidates $\gets B_2 \cup \Buffer$
 	\IF {$\card{B_2} \ge \dz$}
@@
 \begin{proof}
-	By invariants (a) and (b1), we know that $r \leq \delta/2 < \delta^*/2$. 
+	By invariants (a) and (b), we know that $r \leq \delta/2 < \delta^*/2$. 
 	By Lemma~\ref{lem:center-point}, $c_p \in B_1^* \cap B_2^*$. 
@@
 If the candidate $c$ equals the current $c_2$, then, $B_1 = B'_1$. 
-Since $\radius{c_2} \leq r \leq \delta/2$ by invariant (b1) and $B'_2 \subset B_2$,
+Since $\radius{c_2} \leq r \leq \delta/2$ by invariant (b) and $B'_2 \subset B_2$,
 we do not need to construct any new set. 

### 2015-05-03 paper.tex
Minor Correction about Query Description

@@
 The idea behind the algorithm is as follows.
-By our initial assumption about $p_1$ and by invariants (c), 
-we know that $B_1$ completely contains $B_1^*$.
+By our initial assumption about $p_1$ and  by invariants (c) and (d), if $c_p \in B_2^*$ 
+we know that $B_1$ (resp., $B_2$) completely contains $B_1^*$  (resp., $B_2^*$).
 %because $B_1 \cap B_2^* = \emptyset$ . 
-But for $B_2$, it might be the case that our assumption about $c_2$ 
-was incorrect, and therefore, $B_2$ may not completely contain $B_2^*$. 
+But it might be the case that our assumption about $c_p$ 
+was incorrect, and therefore, $B_1$ (resp., $B_2$) may not completely contain $B_1^*$ (resp., $B_2^*$). 
 To overcome this issue, we try all possible candidates for $c_2$,

### 2015-05-03 paper.tex
Last submission

--- 2015-05-03 paper.tex
@@
 The idea behind the algorithm is as follows.
-By our initial assumption about $p_1$ and by invariants (c), 
-we know that $B_1$ completely contains $B_1^*$.
+By our initial assumption about $p_1$ and  by invariants (c) and (d), 
+if $c_p \in B_2^*$, then we know that $B_1$ completely contains $B_1^*$,
+and $B_2$ completely contains $B_2^*$.
 %because $B_1 \cap B_2^* = \emptyset$ . 
-But for $B_2$, it might be the case that our assumption about $c_2$ 
-was incorrect, and therefore, $B_2$ may not completely contain $B_2^*$. 
-To overcome this issue, we try all possible candidates for $c_2$,
-and compute, for each possible combinations of 
+However, it might be the case that our assumption about $c_p$ 
+was incorrect, and therefore, $B_1$ (resp., $B_2$) 
+may not completely contain $B_1^*$ (resp., $B_2^*$). 
+To overcome this issue, we try all possible candidates for $c_2$
+(which in turn, determines $c_p$),
+and compute, for each resulting partition of $P$ into 
 $B_1$, $B_2$, and Buffer, the best solution for 2-center with $z$ outliers
@@
 However, when $|B_2| \geq \dz$, 
-we show in the following lemma that $(\{c_2\} \cup \Buffer) \cap B_2^* \neq \emptyset$. 
+we will show in the following lemma that $(\{c_2\} \cup \Buffer) \cap B_2^* \neq \emptyset$. 
 Therefore, if $|B_2| \ge \dz$, 

### 2015-07-12 outlier.tex
Camera-Ready

--- 2015-05-03 paper.tex
@@
 \newtheorem{definition}{Definition}
+\newtheorem{claim}{Claim}
 
@@
 \title{A Streaming Algorithm for 2-Center with Outliers in High Dimensions}
-%\title{Computing 2-Center with Outliers on High-Dimensional Data Streams}
+
 \author{Behnam~Hatami\thanks{Department of Computer Engineering, 
-	Sharif University of Technology.
+	Sharif University of Technology, Tehran, Iran.
 	{\tt bhatami@ce.sharif.edu}}
@@
 	Hamid~Zarrabi-Zadeh\thanks{Department of Computer Engineering, 
-	Sharif University of Technology.
+	Sharif University of Technology, Tehran, Iran.
 	{\tt zarrabi@sharif.edu}}
@@
 To obtain our result, we have used a combination of several ideas
-including parallelization construction, far/close ball separation, centerpoint theorem,
-and keeping a lower bound on the radius and distance of the optimal balls.
+including parallelization, far/close ball separation, centerpoint theorem,
+and keeping a lower/upper bound on the radius and distance of the optimal balls.
 We have also utilized ideas used in~\cite{kim2014improved} 
@@
 which is not outlier, and hence, it is in $B_1^*$.
-Let $q$ be the point in $S \cap B_1^*$ furthest from~$p$. 
-Consider $B(p, \len{pq})$. It is clear that $B$ covers $P \setminus S$. 
-Since $p, q \in B_1^*$, then $\len{pq}$ is at most $2r^*$. 
+Let $q$ be a point in $S \cap B_1^*$ furthest from~$p$. 
+Consider the ball $B(p, \len{pq})$. 
+%It is clear that $B$ covers $P \setminus S$. 
+For any point $s \in P \setminus S$, 
+we have $\len{ps} \leq \len{pq}$,
+because $s \not\in S$ and $q \in S$. 
+Therefore, $B$ covers $P \setminus S$.
+Since $p, q \in B_1^*$, $\len{pq}$ is at most $2r^*$. 
 Thus, by Observation~\ref{obs:intersection}, $B_2^* \cap B = \emptyset$. 
@@
 \begin{algorithm}[t]
-\caption{\sc 2-CenterCase1$(P)$} 
+\caption{\sc 2-Center-Separated$(P)$} 
 \algsetup{indent=1.5em}
@@
 
+Invariant (c): The proof is provided in \Cref{app:inv-c}. 
+% due to space constraints.
+
+\REM{
 Invariant (c): 
@@
 Therefore, Similar to the previous part, it contradicts the overflow of the buffer. 
+}
 
@@
 Therefore, by Lemma \ref{lem:2r}, all points outside $B_1 \cup B_2$ are outlier.
-
 \end{proof}
@@
 %In each step one or many of the states can be valid and their algorithm considers all of them in parallel. 
-In each state, the algorithm keeps at most two balls, as a candidate solution. 
+In each state, the algorithm keeps at most two balls as a candidate solution. 
 A transition between the states occurs whenever a point not covered by any of the two balls arrive.
@@
   \node (1) at (1,2.5) {1};
-  \node (2a) at (3,1)  {2a};
-  \node (3a) at (3,4)  {3a};
-  \node (2b) at (5,0)  {2b};
+  \node (2a) at (3,4)  {2a};
+  \node (2b) at (5,4)  {2b};
+  \node (2c) at (7,4)  {2c};
+  \node (3a) at (3,1)  {3a};
   \node (3b) at (5,2)  {3b};
-  \node (3d) at (5,4)  {3d};
-  \node (2c) at (7,0)  {2c};
   \node (3c) at (7,2)  {3c};
-  \node (3e) at (7,4)  {3e};
+  \node (3d) at (5,0)  {3d};
+  \node (3e) at (7,0)  {3e};
   %\node (E) at (9, 2) {E};
@@
 \begin{algorithm}[t]
-\caption{\sc 2-CenterCase2$(P, z, r)$} 
+\caption{\sc 2-Center-Close$(P, z, r)$} 
 \algsetup{indent=1.5em}
@@
 	the 2-center with $z$ outliers 
-	in $\O (dz^3)$ space and $\O (dz^3)$ update time.
+	in $\O (dz^3)$ space and $\O (dz^3)$ update time,
+	assuming that the first point of the stream is not outlier. 
 \end{theorem}
@@
 It improves the previous $(4+\eps)$-approximation algorithm available for the problem 
-due to Charikar~\etal~\cite{mccutchen2008streaming}. 
+due to McCutchen and Khuller~\cite{mccutchen2008streaming}. 
 Finding better approximation factor or space complexity
@@
 
+\paragraph{Acknowledgement}
+The authors would like to thank Kiana Ehsani and Sahand Mozaffari 
+for their thoughtful discussions, and for their very helpful comments.
+%and for their help to improve the quality of this paper.
+
 %--------------- BIBS --------------------
@@
 %---------------------------- Appendix ------------------------
+\newpage
 
@@
 	By Lemma~\ref{lem:center-point}, $c_p \in B_1^* \cap B_2^*$. 
-	Since $c_p \not \in B_2^*$, then $c_p \in B_1^*$. 
+	Since $c_p \not \in B_2^*$, we have $c_p \in B_1^*$. 
 	On the other hand, by Observation~\ref{obs:intersection}, 
@@
 constructs $B'_1(c_1, \max \{\delta, \radius{c} \})$ and $B'_2(c, \radius{c})$. 
-If the candidate $c$ equals the current $c_2$, then, $B_1 = B'_1$. 
-Since $\radius{c_2} \leq r \leq \delta/2$ by invariant (b) and $B'_2 \subset B_2$,
+If the candidate $c$ equals the current $c_2$, then we have $B_1 = B'_1$. 
+Since $\radius{c_2} \leq r \leq \delta/2$ by invariant (b), and $B'_2 \subset B_2$,
 we do not need to construct any new set. 
 For $c \neq c_2$, we know that $B_1 \subset B'_1$, and hence,
-we just need to see which points in $\Buffer \cap B_2$ are located in $B'_1$.
-When $|B_2| \geq \dz$ and $c \neq c_2$, then it means that assumed $c_p \not \in B_2^*$. 
-Therefore, by Lemma \ref{lem:B2dz}, $B_2$ can be added to $B'_1$ without contradicting invariant (c). 
+we only need to see which points in $\Buffer \cap B_2$ are inside $B'_1$.
+When $|B_2| \geq \dz$ and $c \neq c_2$, then it means that $c_p \not \in B_2^*$. 
+Therefore, by Lemma \ref{lem:B2dz}, $B_2$ can be added to $B'_1$ without violating invariant (c). 
 So in this case, we just need to see which points of $\Buffer$ must be added to $B'_1$. 
-\Cref{alg:query} use functions \textproc{AddToB$'_1$} and \textproc{AddToB$'_2$} for adding a point to $B'_1$ and $B'_2$ respectively. 
-The definition of these functions are the same as \textproc{AddToB$_1$} and \textproc{AddToB$_2$},
-except that, they add point to $B'_i$ instead of $B_i$ ($i = 1, 2$).
+\Cref{alg:query} uses functions \textproc{AddToB$'_1$} and \textproc{AddToB$'_2$} 
+for adding a point to $B'_1$ and $B'_2$ respectively. 
+These functions are the same as \textproc{AddToB$_1$} and \textproc{AddToB$_2$},
+with the only exception that they add points to $B'_i$ instead of $B_i$, for $i = 1, 2$.
 
@@
 at least for one $c^* \in C$, we have $c^* \in B_2^*$. 
-We call the corresponding $B'_1$ and $B'_2$ by $B''_1$ and $B''_2$. 
+We denote the corresponding $B'_1$ and $B'_2$ by $B''_1$ and $B''_2$. 
 Since by Observation \ref{obs:c+4},
 $1 \leq \frac{\len{c_1 c^*}}{\alpha^*} < \frac{\len {c_1 c^*}}{\alpha r^*}$, 
-we have $2r^* \leq \radius{c^*}$, and therefore,
-$B^*_1 \subset B''_1$ and $B^*_2 \subset B''_2$ by Lemma~\ref{lem:2r}.
-On the other hand, since the distance of the new points added to $B''_1$ compare to $B_1$ is less than $\len{c_1 p} \leq \max \{\delta, \radius{c^*} \}$, 
+we have $2r^* \leq \radius{c^*}$, and hence
+by Lemma~\ref{lem:2r}, $B^*_1 \subset B''_1$ and $B^*_2 \subset B''_2$.
+On the other hand, since the distance of the new points added to $B''_1$ 
+%compare to $B_1$ 
+is less than $\len{c_1 p} \leq \max \{\delta, \radius{c^*} \}$, 
 we have by invariant~(c) that  $B''_1 \cap B_2^* = \emptyset$.
 As a result, $B''_1$ (resp., $B''_2$) completely covers $B_1^*$  (resp., $B_2^*$), 
-and points in $\Buffer$ are certainly outlier.
+and the points in $\Buffer$ are all outliers.
 The only unknown part is that \Cref{alg:query} does not know how many outliers are in $B''_1$ and $B''_2$.
@@
 
-\REM{ }% to be added in the camera-ready version
-\paragraph{Acknowledgement}
-The authors would like to thank Kiana Ehsani and Sahand Mozaffari 
-for their thoughtful discussions, 
-and for their help to improve the quality of this paper.
+% --------------------------- Invariant (c) ----------------------
+
+\section{Proof of Invariant (c)}
+\label{app:inv-c}
+
+Here, we provide a proof for Invariant (c).
+%We first prove the following technical claim.
+The following technical claim will be used in our proof.
+
+\begin{claim}
+	\label{claim:c}
+	If $c_2$ is set, then
+	$B(c_p, \radius{c_p}) \subseteq B_2(c_2, r)$.
+\end{claim}
+
+\begin{proof}
+If $|B_2| < \dz$, then $c_p = c_2$ and $r = \radius{c_2}$, 
+and hence, $B_2 = B(c_p, \radius{c_p})$. 
+When the size of $B_2$ reaches $\dz$, 
+the central point $\cp$ moves to the centerpoint of $B_2$,
+and $\rc$ is increased by a factor of $(2 + \frac{2}{\alpha})$. 
+Because the centerpoint of $B_2$ lies in $B_2$, then $c_p \in B(c_2, \radius{c_2})$.
+Thus, if $|B_2| \ge \dz$ then $\len{c_2 c_p} \leq \radius{c_2}$, and therefore,
+$$
+	\radius{c_p} \leq \frac{2 (\len{c_1 c_2} + \len{c_2 c_p})}{\alpha} \leq \radius{c_2}(1 + \frac{2}{\alpha}).
+$$ 
+Hence, $B(c_p, \radius{c_p}) \subseteq B_2(c_2, \radius{c_2}(2 + \frac{2}{\alpha}))$.
+\end{proof}
+
+\noindent
+Now, we prove Invariant (c),
+which states $B_1 \cap B_2^* = \emptyset$.
+
+\begin{proof}
+A point $p$ can be added to $B_1$ in two cases. % by \Cref{alg:case-1}. 
+The first case is in function \textproc{AddToB$_1$}, 
+where the point is added to $B_1$ only if it is within distance $\delta$ of the center $c_1$,  
+%when $\len{pc_1} \leq \delta$, 
+which by invariant (a), 
+guaranties $\len{pc_1} < \delta^*$. 
+Therefore, $p \not \in B_2^*$ in this case.
+
+The second case is in \Cref{alg:case-1}, when the buffer overflows and $B_2$ is non-empty.
+The algorithm takes one of the following actions depending on the size of $B_2$.
+If $|B_2| < \dz $, then $c_2 = c_p$.
+Algorithm~\ref{alg:case-1} adds $c_2$ to $B_1$.
+Suppose by way of contradiction that $c_p \in B_2^*$.
+Then, by invariants (b) and (d1), 
+$2r^* \leq r \leq \delta/2 < \delta^*/2$. 
+Therefore, by Lemma \ref{lem:2r}, there must be at most $z$ points outside $B_1 \cup B_2$,
+which contradicts the overflow of the buffer. 
+If $|B_2| \geq \dz$, then $c_p$ is the centerpoint of the first $\dz$ points currently in $B_2$. 
+In this case, we add all points of $B_2$ to $B_1$. 
+By invariant (b), $r \leq \delta/2 < \delta^*/2$. 
+Therefore, By Lemma \ref{lem:center-point}, $c_p \in B_1^*$ or $c_p \in B_2^*$. 
+Suppose by way of contradiction that $c_p \in B_2^*$. 
+In this case, by invariant (d1) and Claim~\ref{claim:c}, % that we proved first,
+$B_2$ covers $B(c_p, \radius{c_p})$ and $2r^* \leq r$. 
+Therefore, Similar to the previous part, it contradicts the overflow of the buffer. 
+\end{proof}
 
